\section*{2(a)}

\begin{itemize}
    \item[(1-2)] isentrop \quad $s$ - constant \quad $p \downarrow$
    \item[(2-3)] isobar \quad $p$ - constant \quad $T \uparrow$
    \item[(3-4)] nicht isentrop
    \item[(4-5)] isobar \quad $p$ - constant
    \item[(5-6)] isentrop \quad $s$ - constant
\end{itemize}

\subsection*{Graph Description}

The main graph is a plot with temperature $T$ on the vertical axis and entropy $S$ on the horizontal axis. The vertical axis is labeled with $T$ and has an upward arrow. The horizontal axis is labeled with $S$ and has a rightward arrow. 

There are several lines and points marked on the graph:
- A horizontal line at the bottom labeled $-30^\circ C$.
- A horizontal line in the middle labeled "isentrop".
- A diagonal line labeled "isotherm".
- Several diagonal lines labeled $p_1$, $p_2$, $p_3$, and $p_4$.

Points are marked and connected by lines:
- Point 1 is at the bottom left.
- Point 2 is directly above point 1.
- Point 3 is to the right of point 2.
- Point 4 is above point 3.
- Point 5 is to the right of point 4.
- Point 6 is below point 5.

The points are connected in the following order: 1 to 2, 2 to 3, 3 to 4, 4 to 5, and 5 to 6.

There is a smaller inset graph to the right of the main graph. This inset graph has the same axes as the main graph but is smaller in size. It shows a simplified version of the main graph with points labeled 1, 2, 3, 4, 5, and 6 connected in the same order.

``````latex

2b1 \quad w_G = ? \quad T_c = ? \\

\[
\frac{T_c}{T_5} = \left( \frac{p_c}{p_5} \right)^{\frac{0.4}{1.4}}
\]

\[
p_5 = 0.5 \, \text{bar}
\]
\[
T_5 = 431.9 \, \text{K}
\]
\[
p_c = p_0 = 0.191 \, \text{bar}
\]

\[
4 \Delta T_c = T_5 \left( \frac{0.191}{0.5} \right)^{0.286}
\]

\[
T_c = 328 \, \text{K} \, (327.33 \, \text{K})
\]

\[
w_G = - \left( \int_{5}^{c} v \, dp + \Delta h_e \right)
\]

\text{Stationär} \quad \Rightarrow \quad \text{Energiebilanz (Schubdüse)}

\[
0 = \dot{m} \left( h_e - h_a + \frac{w_5^2 - w_6^2}{2} \right) = 0
\]

\[
\sqrt{2 (h_5 - h_6)} + \frac{w_5^2}{4 \cdot 200 \, \frac{m}{s}} = w_G
\]

\[
h_5 (431.9 \, \text{K})
\]

\[
h_5 - h_6 = C_p (T_2 - T_1) =
\]

\[
1.006
\]

``````latex