

\subsection*{a)}

\begin{center}
\textbf{Graph Description:}

The graph is a Temperature-Entropy (T-s) diagram. The x-axis is labeled as $s$ with the unit $\left[\frac{kJ}{kgK}\right]$. The y-axis is labeled as $T$ with the unit $[K]$. 

There are several curves and points labeled on the graph:
- The curve labeled "isobare" (isobaric) appears multiple times.
- The curve labeled "isentrope Verdichtung" (isentropic compression) starts from point 1 and goes to point 2.
- The curve labeled "nicht-isentrope Verdichtung" (non-isentropic compression) starts from point 1 and goes to point 2'.
- The curve labeled "isentrope Schubd端se" (isentropic nozzle) starts from point 2 and goes to point 3.
- The curve labeled "nicht-isentrope Turbine" (non-isentropic turbine) starts from point 3 and goes to point 4.
- The curve labeled "isentrope Schubd端se" (isentropic nozzle) starts from point 4 and goes to point 5.
- The curve labeled "isobare" (isobaric) starts from point 5 and goes to point 6.
- The curve labeled "isobare" (isobaric) starts from point 6 and goes to point 1.

Points are labeled as follows:
- Point 1 is at the intersection of the isobare and isentrope Verdichtung curves.
- Point 2 is at the intersection of the isobare and isentrope Schubd端se curves.
- Point 2' is at the intersection of the isobare and nicht-isentrope Verdichtung curves.
- Point 3 is at the intersection of the isobare and nicht-isentrope Turbine curves.
- Point 4 is at the intersection of the isobare and isentrope Schubd端se curves.
- Point 5 is at the intersection of the isobare and isobare curves.
- Point 6 is at the intersection of the isobare and isobare curves.

\end{center}