

\subsection*{a)}

\begin{itemize}
    \item Two graphs are drawn side by side.
    \item The left graph has the y-axis labeled as $P \, [kPa]$ and the x-axis labeled as $T \, [^\circ C]$.
    \item The left graph shows three lines intersecting at a point labeled "Tripel":
        \begin{itemize}
            \item A line labeled "gasförmig" sloping downwards from left to right.
            \item A line labeled "flüssig" sloping upwards from left to right.
            \item A line labeled "fest" sloping downwards from left to right, intersecting the "flüssig" line.
        \end{itemize}
    \item There are four points labeled with numbers:
        \begin{itemize}
            \item Point 1 is on the "fest" line.
            \item Point 2 is on the "flüssig" line.
            \item Point 3 is on the "gasförmig" line.
            \item Point 4 is at the intersection of the three lines (Tripel).
        \end{itemize}
    \item The right graph has the y-axis labeled as $P \, [kPa]$ and the x-axis labeled as $T \, [^\circ C]$.
    \item The right graph shows two curves:
        \begin{itemize}
            \item A curve labeled "flüssig" sloping upwards from left to right.
            \item A curve labeled "gasförmig" sloping upwards from left to right, intersecting the "flüssig" curve.
        \end{itemize}
    \item There are three points labeled with numbers:
        \begin{itemize}
            \item Point 1 is on the "fest" line.
            \item Point 2 is on the "flüssig" line.
            \item Point 3 is on the "gasförmig" line.
        \end{itemize}
\end{itemize}