
``````latex


\section*{Student Solution}

\subsection*{4a)}

\begin{itemize}
    \item The first graph is a phase diagram with pressure \( p \) on the y-axis and temperature \( T \) on the x-axis.
    \item The y-axis is labeled with \([ \text{bar} ]\).
    \item The x-axis is labeled with \([ \text{K} ]\).
    \item There are three regions labeled as "fest" (solid), "flüssig" (liquid), and "gas" (gas).
    \item The graph shows three lines intersecting at a point labeled \( T_{\text{ripel}} \):
        \begin{itemize}
            \item A line sloping downwards from left to right, separating the "fest" and "flüssig" regions.
            \item A line sloping upwards from left to right, separating the "flüssig" and "gas" regions.
            \item A line sloping upwards from left to right, separating the "fest" and "gas" regions.
        \end{itemize}
\end{itemize}

\subsection*{4b)}

\begin{itemize}
    \item The second graph is a phase diagram with pressure \( p \) on the y-axis and temperature \( T \) on the x-axis.
    \item The y-axis is labeled with \([ \text{bar} ]\).
    \item The x-axis is labeled with \([ \text{K} ]\).
    \item There are three regions labeled as "fest" (solid), "flüssig" (liquid), and "gas" (gas).
    \item The graph shows a line sloping upwards from left to right, separating the "fest" and "gas" regions, with a point labeled \( T_{\text{ripel}} \).
    \item An arrow labeled "Sublimation" points from the "fest" region to the "gas" region.
\end{itemize}

\[
T_i = 10^\circ \text{C}
\]
\[
p_{ii} = 2 \, \text{mbar}
\]

\subsection*{4c)}

\begin{itemize}
    \item \( \dot{W}_k = 28 \, \text{W} \)
    \item Energy balance around the compressor:
    \[
    0 = \dot{m} \left[ h_e - h_a \right] + \dot{W}_k
    \]
    \item Adiabatic reversible, \( s_{erz} = 0 \)
    \item \( p_1 - p_2 \)
    \item \( T_{\text{verd}} = T_i - 6 \, \text{K} = 4^\circ \text{C} \)
\end{itemize}

\subsection*{4d)}

\begin{itemize}
    \item Energy balance around the throttle:
    \[
    Q = 0 \quad w = 0 \quad \rightarrow \quad h_4 = h_1
    \]
\end{itemize}

\subsection*{4e)}

\begin{itemize}
    \item Die Temperatur sinkt immer weiter, da \( Q \) abgeführt wird und keine Arbeit verrichtet wird.
\end{itemize}

``````latex


4d) \(\varepsilon_K = \frac{|Q_{zu}|}{|Q_{ab}| - |Q_{zu}|} = \frac{|Q_{zu}|}{|W_{t}|}\)

```