
``````latex


\section*{A1}

\subsection*{a) $\dot{Q}_{\text{aus}}$}

\begin{equation*}
\dot{Q}_{\text{aus}}
\end{equation*}

\begin{itemize}
    \item Two diagrams are drawn:
    \begin{itemize}
        \item The first diagram is a rectangle labeled "KF1" on the left side and "KF2" on the right side. There are arrows pointing into the rectangle from the top labeled "1, w" and from the left labeled "KF1". There is an arrow pointing out of the rectangle from the bottom labeled "2, w" and from the right labeled "KF2".
        \item The second diagram is a rectangle with arrows pointing into the rectangle from the left labeled "h_{aw}" and from the right labeled "h_{zw}". There is an arrow pointing out of the rectangle from the top labeled "$\dot{Q}_{\text{aus}}$" and from the bottom labeled "KF2".
    \end{itemize}
\end{itemize}

\begin{equation*}
\frac{dE}{dt} = 0 = \dot{m} (h_{aw} - h_{zw}) + \dot{Q}_{\text{aus}}
\end{equation*}

\begin{equation*}
h_{aw} (70^\circ C, x = 1)
\end{equation*}

\begin{equation*}
h_{zw} (200^\circ C, x = 1)
\end{equation*}

\begin{equation*}
\dot{Q}_{\text{aus}} = \dot{m} (h_{zw} - h_{aw})
\end{equation*}

\subsection*{b)}

\begin{equation*}
\overline{T}_{\text{KL}} = \frac{T_{1d}}{s_{a} - s_{e}} = \frac{h_{a} - h_{e}}{s_{a} - s_{e}} = \frac{e^{\frac{(T_{a} - T_{e})}{e}}}{\ln \left( \frac{T_{a}}{T_{e}} \right)} = 293.12 \, K
\end{equation*}

\subsection*{c)}

\begin{itemize}
    \item A diagram is drawn:
    \begin{itemize}
        \item The diagram is a rectangle labeled "KF1" on the left side and "KF2" on the right side. There are arrows pointing into the rectangle from the top labeled "w" and from the left labeled "KF1". There is an arrow pointing out of the rectangle from the bottom labeled "wz" and from the right labeled "KF2". Inside the rectangle, it is labeled "293.12 K" on the left side and "100^\circ C" on the right side.
    \end{itemize}
\end{itemize}

\begin{equation*}
\dot{S}_{\text{rez}} = \frac{\dot{Q}_{\text{aus}}}{323.75 \, K} - \frac{\dot{Q}_{\text{aus}}}{293.12 \, K} = 65 \, kW
\end{equation*}

\begin{equation*}
= 0.047 \, \frac{kW}{K} = 47.72 \, \frac{kW}{K}
\end{equation*}

\subsection*{d)}

\begin{equation*}
T_{\text{KF}} = 70^\circ C \quad \Delta m_{12} \quad T_{\text{pin, 12}} = 200^\circ C
\end{equation*}

\begin{equation*}
z1 \rightarrow z2 \quad \Delta m_{12} > 0
\end{equation*}

\begin{equation*}
m_{2} u_{2} - m_{1} u_{1} - \Delta m_{12} h_{e} = Q
\end{equation*}

\begin{equation*}
(m_{1} + m_{2}) u_{2} - m_{1} u_{1} - \Delta m_{12} h_{e} = Q
\end{equation*}

\begin{equation*```latex


\section*{A1}

d) 
\begin{equation}
m_1 u_2 + m_e (u_2 - h_e) - m_1 u_1 = Q
\end{equation}

\begin{equation}
m_e = \frac{Q + m_1 (h_1 - u_2)}{u_2 - h_e}
\end{equation}

\begin{equation}
Q = -35 \, \text{MJ}
\end{equation}

\begin{equation}
m_1 = 5.755 \, \text{kg}
\end{equation}

\begin{equation}
T_1 = 100^\circ \text{C}
\end{equation}

\begin{equation}
T_2 = 70^\circ \text{C}
\end{equation}

\begin{equation}
T_e = 200^\circ \text{C}
\end{equation}

\begin{equation}
u_1 (100^\circ \text{C}, 5. \text{F})
\end{equation}

\begin{equation}
u_2 (70^\circ \text{C}, 5. \text{F})
\end{equation}

\begin{equation}
u_e (200^\circ \text{C}, 5. \text{F})
\end{equation}

\begin{equation}
h_e (200^\circ \text{C}, 5. \text{F})
\end{equation}

\begin{equation}
4.13 \cdot 10^2
\end{equation}

\begin{equation}
4.29, 38 \frac{\text{kJ}}{\text{kg}} + 4.18, 94 + 0.005 (205.045)
\end{equation}

e)
\begin{equation}
\Delta S = m_2 s_2 - m_1 s_1 - \Delta m_e s_e = \frac{Q}{T} + S_{crz}
\end{equation}

``````latex


