
``````latex


\section*{Aufgabe 4}

\subsection*{a)}

\begin{description}
    \item[Graph 1:] 
    The graph is a plot with an x-axis labeled \( T \) and a y-axis labeled \( P \). The plot shows a complex curve that starts from the origin, goes upwards, and then oscillates. Within this curve, there is a quadrilateral with vertices labeled 1, 2, 3, and 4. The quadrilateral is positioned such that:
    \begin{itemize}
        \item Vertex 1 is at the bottom left.
        \item Vertex 2 is at the top left.
        \item Vertex 3 is at the top right.
        \item Vertex 4 is at the bottom right.
    \end{itemize}
    The quadrilateral is drawn with straight lines connecting these vertices in the order 1-2-3-4-1.
    
    \item[Graph 2:]
    The second graph is a plot with an x-axis labeled \( T \) and a y-axis labeled \( P \). The plot shows a curve that starts from the origin and rises upwards in a nonlinear fashion, indicating a phase boundary. The curve separates two regions:
    \begin{itemize}
        \item The region below the curve is labeled "fest".
        \item The region above the curve is labeled "gas/förmig".
    \end{itemize}
    There is a horizontal line labeled \( i \) that starts from a point on the y-axis and extends to the right, intersecting the curve. From the intersection point, a vertical line labeled \( ii \) extends downwards to the x-axis.
\end{description}

``````latex

\section*{Fortsetzung Aufgabe 4}

\subsection*{b)}

\[
\dot{m} \cdot (h_e - h_a) + \dot{Q}_k
\]

\[
1. \, \text{Hauptsatz Verdampfer} \quad 0 = \dot{m}
\]

\[
T_i = -20^\circ C
\]

\[
\Rightarrow \text{Tiefsttemperatur} = -26^\circ C = 247.15 K
\]

\[
1. \, \text{Hauptsatz am Verdichter}
\]

\[
0 = \dot{m} (h_e - h_a) + \dot{Q}_k
\]

\[
0 = \dot{m} (h_e - h_a) + \dot{W}_k
\]

\[
\dot{m} = \frac{\dot{W}_k}{h_e - h_a} = \frac{28 W}{h_e - h_a}
\]

\subsection*{d)}

\[
E_k = \frac{|\dot{Q}_k|}{|\dot{W}_k|} = \frac{\dot{Q}_k}{\dot{W}_k} = \frac{|\dot{Q}_k|}{|\dot{W}_k|}
\]

```