
``````latex


\section*{Aufgabe 2}

\subsection*{a)}

\begin{center}
\textbf{Graph Description:}
\end{center}

The graph is a plot with the x-axis labeled as $S \left[ \frac{kJ}{kg \cdot K} \right]$ and the y-axis labeled as $T \left[ \text{°C} \right]$. The graph contains several lines and points:

- A line starting from the origin (0,0) and moving upwards to the right.
- Another line starting from the origin and moving upwards to the left.
- A curved line labeled $1$ starting from the left line and moving upwards to the right.
- A point labeled $2$ on the curved line.
- A point labeled $3$ on the curved line further up from point $2$.
- A horizontal line from point $2$ to the right, labeled $0.1 \text{bar}$.
- A point labeled $4$ on the right side of the graph.
- A point labeled $5$ on the left side of the graph.
- A point labeled $6$ on the left side of the graph below point $5$.

\[
\Rightarrow \text{Man befindet sich am linken Teil der Graphen} \Rightarrow \text{Übergang auf andere Seite}
\]

\subsection*{b)}

\[
w_e \quad \text{und} \quad \overline{T}_6
\]

\textbf{Ideales Gas:}

\[
p_0 = 0.1 \text{ bar}
\]

\textbf{Bildung in die Schublade:}

\[
\left( \dot{m} \cdot \frac{\dot{Q}}{\dot{T}} \right)
\]

\textbf{Annahme:} \quad \dot{m}_{\text{ein}} = \dot{m}_{\text{aus}}

\[
\dot{m} \quad \rho \cdot V^n = \text{konst}
\]

``````latex

c) \quad \dot{m}_{\text{gen}}

\[
\Delta e_{\text{xs}} = e_{\text{xs, in}} - e_{\text{xs, out}} = 
\]

\[
\Delta e_{\text{xs, in}} = h - h_0 - T_0 (s - s_0) + k.e + p.e
\]

\[
e_{\text{xs, in}} = \Delta h - T_0 \Delta s + k.e
\]

\[
= 36.91 \frac{\text{kJ}}{\text{kg}} - 243.15 \frac{\text{kJ}}{\text{kg}} \cdot 0.335 + 48.05 \frac{\text{kJ}}{\text{kg}} - 63.5 \frac{\text{kJ}}{\text{kg}}
\]

\[
\Delta h = c_p^{\text{ig}} (T_e - T_0) = 1.006 \frac{\text{kJ}}{\text{kg K}} (340 \text{K} - 243.15 \text{K})
\]

\[
= 36.91 \frac{\text{kJ}}{\text{kg}}
\]

\[
\Delta s = c_p^{\text{ig}} \ln \left( \frac{T_e}{T_0} \right) - R \ln \left( \frac{p_e}{p_0} \right)
\]

\[
= 1.006 \frac{\text{kJ}}{\text{kg K}} \ln \left( \frac{340 \text{K}}{243 \text{K}} \right) - 0.287 \ln (1) = 0.335
\]

\[
c_v^{\text{ig}} = \frac{c_p^{\text{ig}}}{k} = \frac{1.006}{1.4} = 0.719
\]

\[
R = 0.287
\]

\[
k.e = \frac{1}{2} (v_e^2 - v_0^2) = \frac{1}{2} (510 \frac{\text{m}}{\text{s}} - 200 \frac{\text{m}}{\text{s}})^2
\]

\[
= 48,050 \frac{\text{J}}{\text{kg}} = 48.05 \frac{\text{kJ}}{\text{kg}}
\]

d) \quad \dot{m}_{\text{gen}}

\[
\dot{e}_{\text{xs, out}}
\]

\[
\text{Für Energiebilanz für eine stationäre Strömung:}
\]

\[
G = -\Delta e_{\text{xs}} + \left( 1 - \frac{T_0}{T_e} \right) Q_B - F_{\text{ex, out}}
\]

\[
\text{Exergie} = -\Delta e_{\text{xs}} + \left( 1 - \frac{T_0}{T_e} \right) Q_B
\]

\[
= -63.5 \frac{\text{kJ}}{\text{kg}} + \left( 1 - \frac{243.15 \text{K}}{1239 \text{K}} \right) 1135 \frac{\text{kJ}}{\text{kg}}
\]

\[
= 506 \frac{\text{kJ}}{\text{kg}}
\]

``````latex


\section*{Aufgabe 2}

\begin{description}
    \item[Graph Description:] The graph is a plot with the x-axis labeled as $s \left[ \frac{kJ}{kg \cdot K} \right]$ and the y-axis labeled as $T \left[ K \right]$. There are three curves labeled as 1, 2, and 3. Curve 1 starts at the origin and rises steeply, then curves to the right. Curve 2 starts slightly above the origin, follows a similar path to curve 1 but is slightly higher. Curve 3 starts even higher and follows a similar path to curves 1 and 2 but is the highest of the three. There are two horizontal lines intersecting the curves. The first horizontal line is labeled $0.16$ and intersects all three curves at different points. The second horizontal line is labeled $0.5 \, \text{kw}$ and intersects the curves at higher points. There is also a label $0.191 \, \text{bar}$ near the top right of the graph.
\end{description}

``````latex


