
``````latex


\section*{Aufgabe 4}

\subsection*{a)}

\begin{itemize}
    \item Two graphs are drawn side by side.
    \item The left graph has the y-axis labeled as $P \, [kPa]$ and the x-axis labeled as $T \, [^\circ C]$.
    \item The left graph shows three lines intersecting at a point labeled "Tripel":
        \begin{itemize}
            \item A line labeled "gasförmig" sloping downwards from left to right.
            \item A line labeled "flüssig" sloping upwards from left to right.
            \item A line labeled "fest" sloping downwards from left to right, intersecting the "flüssig" line.
        \end{itemize}
    \item There are four points labeled with numbers:
        \begin{itemize}
            \item Point 1 is on the "fest" line.
            \item Point 2 is on the "flüssig" line.
            \item Point 3 is on the "gasförmig" line.
            \item Point 4 is at the intersection of the three lines (Tripel).
        \end{itemize}
    \item The right graph has the y-axis labeled as $P \, [kPa]$ and the x-axis labeled as $T \, [^\circ C]$.
    \item The right graph shows two curves:
        \begin{itemize}
            \item A curve labeled "flüssig" sloping upwards from left to right.
            \item A curve labeled "gasförmig" sloping upwards from left to right, intersecting the "flüssig" curve.
        \end{itemize}
    \item There are three points labeled with numbers:
        \begin{itemize}
            \item Point 1 is on the "fest" line.
            \item Point 2 is on the "flüssig" line.
            \item Point 3 is on the "gasförmig" line.
        \end{itemize}
\end{itemize}

\subsection*{b)}

\begin{align*}
    T_v &= 4 \, K \, \text{über} \, T_{sbl} \quad \Leftrightarrow \quad T_v = -18^\circ C \\
    E &= 3.1 \quad 2-3 \quad (\text{stationär, adiabatisch}) \\
    \dot{m}_{23sbl} &= \frac{\dot{W}_v}{h_2 - h_3} \approx 0.834 \, \frac{\text{kg}}{\text{s}} \\
    h_2 &= h_f \, (-16^\circ C) \approx 237.74 \, \frac{\text{kJ}}{\text{kg}} \\
    h_3 &= h_f \, (8 \, \text{bar}, \, s = s_3) \approx 237.66 - 24.75 \cdot -0.9374 - 0.9066 \\
    &= (0.9298 - 0.9066) \cdot 24.75 + 237.37 \approx 277.37 \, \frac{\text{kJ}}{\text{kg}} \\
    s_2 &= s_3 = s_f \, (-16^\circ C) \approx 0.9298 \, \frac{\text{kJ}}{\text{kg} \cdot \text{K}}
\end{align*}

\subsection*{c)}

\begin{align*}
    h_1 &= h_f \, (8 \, \text{bar}) \approx 193.42 \, \frac{\text{kJ}}{\text{kg}} \\
    x_1 &= \frac{h_1 - h_f}{h_g - h_f} \approx 0.3 \quad 76 \\
    &\text{bei} \quad T_n = -16^\circ C
\end{align*}

\subsection*{d)}

\begin{align*}
    E_k &= \frac{10 \, \text{l}}{1 \, \text{l}} \cdot \frac{1}{1 \, \text{h}} = \frac{\dot{Q}_k}{\dot{m}_{12sbl}} \\
    E &= 3