
``````latex


\section*{2) T-s Diagramm}

\subsection*{a)}
\[
T \quad [K]
\]

\[
s \quad [kJ/kg \cdot K]
\]

\subsection*{b)}
$W_6, T_6$ Austritt

Schubdüse venturi $P_6 = P_0 = 0.196 \text{bar}$

\[
\frac{d}{dt} \left( m \left[ h_6 - h_0 + \frac{w_6^2}{2} \right] \right) = 0
\]

\[
h_5 - h_6 = c_p (T_5 - T_6), \quad T_6 = T_s \left( \frac{P_6}{P_5} \right)^{\frac{\kappa - 1}{\kappa}} \quad \text{mit venturi}
\]

\[
T_6 = 97.9 \left( \frac{0.196}{4.4} \right)^{\frac{2.4 - 1}{2.4}} = 328.07 K
\]

\[
h_5 - h_6 = 109.46 \frac{kJ}{kg}
\]

\[
k_{es} - k_{e6} = \frac{1}{2} m \left( w_5^2 - w_6^2 \right) \quad w_0^2 \neq 208.92 \cdot 10^7 \quad w_5 = 233.33 \frac{m}{s}
\]

\subsection*{c)}
\[
m_{ges}, ex_{str} = ex_{inter,6} - ex_{inter,0}
\]

\[
\Rightarrow \Delta ex_{str} = h_6 - h_0 - T_0 (s_6 - s_0) + k_{e6} - k_{e0}
\]

\[
k_{e6} = \frac{1}{2} w_0^2 =
\]

\newpage

\section*{Graph Description}

The graph is a T-s diagram with the temperature $T$ on the vertical axis and the entropy $s$ on the horizontal axis. The axes are labeled as follows:
- The vertical axis is labeled $T \quad [K]$.
- The horizontal axis is labeled $s \quad [kJ/kg \cdot K]$.

The graph contains several curves and points:
- There is a black curve starting from the origin (0,0) and rising steeply, then leveling off and fluctuating before rising again.
- Points are marked along the curves with numbers 0 through 6.
- Points 0, 1, and 2 are connected by a black curve.
- Points 2, 3, and 4 are connected by a magenta curve.
- Points 4, 5, and 6 are connected by another magenta curve.
- Points 3 and 5 are connected by a vertical magenta line.
- Points 0, 6, and 4 are connected by a black curve.
- The points are labeled as follows:
  - Point 0 is at the origin.
  - Point 1 is on the initial black curve.
  - Point 2 is on the initial black curve.
  - Point 3 is on the magenta curve.
  - Point 4 is on the magenta curve.
  - Point 5 is on the magenta curve.
  - Point 6 is on the black curve.

There is a note on the right side of the graph that says "blaue Kurve nicht beachten!" which means "ignore the blue curve!"

``````latex


