
``````latex


\section*{Problem 4}

\begin{itemize}
    \item[1.] $T_1 = T_i - 6 \, \text{K}$
    \item[2.] $h_2 \rightarrow \text{komp}f$
    \item[3.] $p_3 = 8 \, \text{bar}$
    \item[4.] $p_4 = p_3 + 2 \, \text{bar}$
    \item[5.] $h_4 \rightarrow h_1$
\end{itemize}

\[
\dot{Q}_k
\]

\[
\dot{W}_k
\]

\[
h_1 - h_f \quad p_1 - p_2
\]

\[
T: \quad p_7 - p_2
\]

\[
x_4 = 0 \quad h_2 = h_1
\]

\subsection*{a)}

\textbf{Description of the first graph:}

The first graph is a $P$-$\log$ graph. The vertical axis is labeled $P$ and the horizontal axis is labeled $\log$. There are two curves in the graph. The first curve starts from the bottom left and rises linearly to the top right, labeled as "eis". The second curve starts from the bottom left and rises less steeply, labeled as "wasser". There is a shaded rectangular area in the top right corner labeled "dampf".

\textbf{Description of the second graph:}

The second graph is a $P$-$T$ graph. The vertical axis is labeled $P$ and the horizontal axis is labeled $T \, ^\circ \text{C}$. There are two curves in the graph. The first curve starts from the bottom left and rises linearly to the top right, labeled as "eis". The second curve starts from the bottom left and rises less steeply, labeled as "wasser". There is a shaded rectangular area in the top right corner labeled "dampf". Points 3 and 4 are marked on the graph, with point 3 being at the intersection of the "eis" and "wasser" curves and point 4 being at the top right corner of the shaded area.

\subsection*{b)}

\[
\dot{m}_{R134a}
\]

\[
0 = \dot{m}_{R134a} (h_2 - h_3) - \dot{W}_k
\]

\[
h_2 \frac{f}{g} - h_g =
\]

\[
\dot{W}_k = 28 \, \text{W}
\]

\subsection*{c)}

\[
x_1?
\]

\[
x_1 = \frac{\dot{m}_{R134a} h_4 - h_{4.1}}{h_{4.1} - h_{6.1}}
\]

\[
A = 70 \, ^\circ 1
\]

\[
h_{c,1} = A \cdot \frac{d}{d} - 9 \, ^\circ C
\]

\[
B = -6 \, ^\circ C
\]

\[
A = 10:
\]

\[
h_{c,1} = \frac{d}{d} - 9 \, ^\circ C
\]

\[
A = 10:
\]

\[
h_{g,1} = A - 9 \, ^\circ C
\]

\[
B = -6 \, ^\circ C
\]

\[
= 247 \cdot \frac{d}{d} - 20 \, \frac{J}{kg}
\]

\[
= 4 \, \frac{kg}{k} \quad T_2 = -22 \, ^\circ C
\]

\[
T_i = 0 \rightarrow T_5 = -6 \, ^\circ C = 267.75 \, K
\]

\[
C = 39.54 \cdot 10^3
\]

\[
D = 4A - 75 \cdot 10^3
\]

\[
h_{c,1} = C + \frac{d}{d} - 9 \, ^\circ C
\]

\[
C = 244.9
\]

\[
D = 247.54 \rightarrow 40 \, ^\circ```latex


\begin{itemize}
    \item[d)] \(\varepsilon_K = \frac{|\dot{Q}_u|}{|W_u|} = \frac{|\dot{Q}_k|}{|W_k|} = \frac{c_p (T_1 - T_2)}{T_1 = 60^\circ \quad T_2 = -220^\circ} \quad A = 19: \quad c_p = 2.934 \cdot 10^3\)
    
    \(\dot{Q}_k \Rightarrow 0 = \dot{m}_{1234a} (h_1 - h_2) + \dot{Q}_k\)
    
    \(h_x (-x/f) \Rightarrow \dot{Q}_k = -\dot{m}_{134a} (T_1 - T_2) c_p = -91 \, 776 \, W\)
    
    \(h_x (-x/f) \Rightarrow \varepsilon_k = \frac{-91 \, 776 \, W}{28 \, W} = -3277.7\)
    
    \underline{-3277.7}
    
    \item[e)] 
\end{itemize}

```