
``````latex


\section*{Aufgabe: 4}

\subsection*{a)}

\begin{itemize}
    \item There is a graph with the y-axis labeled as \( T \, [K] \) and the x-axis labeled as \( P \, [\text{bar}] \).
    \item The graph has three regions labeled as "Gas", "Flüssig", and "Fest".
    \item There is a curve separating the "Gas" and "Fest" regions, and another curve separating the "Fest" and "Flüssig" regions.
    \item A point labeled "1" is in the "Gas" region, a point labeled "2" is in the "Fest" region, and a point labeled "3" is in the "Flüssig" region.
    \item Arrows indicate transitions between these points: from "1" to "2" and from "2" to "3".
    \item Below the graph, there are annotations: "isobar", "erst gefrieren", "dann sublimiert", "isobar", and "isotherm".
\end{itemize}

\subsection*{b)}

\begin{align*}
    \dot{m}_{123} (h_{ein} - h_{aus}) + Q_{12} &= 0 \\
    Q_{12} &= \dot{m}_{123} (h_{ein} - h_{1}) \rightarrow \dot{m}_{123} = \frac{Q_{12}}{h_{2} - h_{1}}
\end{align*}

\begin{itemize}
    \item Below the equations, there are annotations: "isobare Verdampfung", "1 -> 2", "GK = Tv", "gesättigten Dampf", "2 -> 3", "adiabat", and "reversibel".
\end{itemize}

\begin{align*}
    \dot{m}_{23} (h_{2} - h_{3}) + \dot{Q} &= \dot{W}_{K} \\
    \dot{m}_{23} &= \frac{\dot{W}_{K}}{h_{2} - h_{3}}
\end{align*}

\begin{itemize}
    \item There is a note: "\(\dot{W}_{K} = -28 \, W\)".
    \item There is a crossed-out section with annotations: "h_{2}", "h_{3} (3 bar)", and "kann nicht finden".
    \item At the bottom, there is a note: "s2 = s3".
\end{itemize}

``````latex


\begin{itemize}
    \item[c)] \( p_u = p_3 = 8 \, \text{bar} \)
    
    \[
    Q = \dot{m}_{\text{iso}} (h_2 - h_1)
    \]
    
    \item[d)] 
    \[
    E_k = \frac{\dot{Q}_{\text{zu}}}{\dot{W}_i}
    \]
    
    \[
    \dot{Q}_{\text{zu}} = \dot{Q}_{\text{k}} - \dot{Q}_{\text{a}}
    \]
    
    \item[e)] es wurde konstant bleiben, nur Druck verändert sich
\end{itemize}

```