The pressure in the ice-water mixture (EW) is calculated as:  
\[
p_{\text{EW}} = p_{\text{amb}} + \frac{m_K \cdot g}{A}
\]  
Where:  
\[
A = \left( \frac{10 \, \text{cm}}{2} \right)^2 \cdot \pi = 0.007853 \, \text{m}^2
\]  
Substituting values:  
\[
p_{\text{EW}} = 1 \, \text{bar} + \frac{32 \, \text{kg} \cdot 9.81 \, \text{m/s}^2}{0.007853 \, \text{m}^2}
\]  
This results in:  
\[
p_{\text{EW}} = 1.33937 \, \text{bar}
\]  

The final ice fraction \( x_{\text{ice},2} \) is determined using the equilibrium table for solid-liquid phase changes.  

Description of Diagram:  
The diagram shows a cylinder divided into two chambers. The top chamber contains the ice-water mixture (EW), while the bottom chamber contains the gas. A piston rests on the EW, exerting pressure downward. Forces acting on the piston are labeled, including atmospheric pressure and the weight of the piston.

Energy balance for the water:  
\[
\Delta U = Q_{12} - W_{\text{water}}
\]  
Heat transferred to the water:  
\[
Q_{12} = W_{12} + \Delta U = 1.367 \, \text{kJ}
\]  
Work done by the water:  
\[
W_{\text{water}} = p_{\text{amb}} \cdot \Delta V
\]  
\[
p_{\text{amb}} = 1 \, \text{bar}
\]  
\[
W_{\text{water}} = 203.07 \, \text{J}
\]  
Internal energy change for the water:  
\[
\Delta U_{\text{water}} = m_{\text{EW}} \cdot (u_2 - u_1)
\]  
\[
u_2 - u_1 = 1488.165
\]  
\[
\Delta U_{\text{water}} = 1488.165 \cdot m_{\text{EW}}
\]  
\[
m_{\text{EW}} = 0.1 \, \text{kg}
\]  
\[
\Delta U_{\text{water}} = 148.8165 \, \text{J}
\]  
Work done by the water on the environment:  
\[
W_{\text{water}} = 489.165 \, \text{J}
\]

The internal energy \( u_2 \) is calculated using the equation:  
\[
u_2 = u(0^\circ\text{C}) = -200.0328 \, \text{kJ/kg}
\]  

The formula for \( u_2 \) is expanded as:  
\[
u_2 = x \cdot u_{\text{frost}} + (1 - x) \cdot u_{\text{liquid}}
\]  
where \( x \) is the ice mass fraction, \( u_{\text{frost}} \) is the internal energy of ice, and \( u_{\text{liquid}} \) is the internal energy of liquid water.  

Substituting values:  
\[
u_2 = x \cdot u_{\text{frost}} + (1 - x) \cdot u_{\text{liquid}} = x \cdot (-200.0328) + (1 - x) \cdot 223.127 \, \text{kJ/kg}
\]  

The equation is rearranged to solve for \( x \):  
\[
x = \frac{u_2 - u_{\text{liquid}}}{u_{\text{frost}} - u_{\text{liquid}}}
\]  

Substituting the values:  
\[
x = \frac{-200.0328 - 223.127}{-200.0328 - 223.127}
\]  

The result is approximately:  
\[
x = 0.0669
\]  

Additional notes:  
The temperature is \( T = 0^\circ\text{C} \), and the pressure is \( p = 1 \, \text{bar} \). There is a comment indicating that somewhere an error in \( x \) might have occurred, leading to a negative value.  

No diagrams or figures are present on the page.