The equation for determining \( x \) is given as:  
\[
x = \frac{y_1 - y_4}{y_4 - y_2}
\]  

The expression for \( y_1 \) is:  
\[
y_1 = \frac{1}{\bar{T}_1} - \frac{1}{\bar{T}_4}
\]  

The expression for \( y_4 \) is:  
\[
y_4 = \frac{1}{\bar{T}_4} - \frac{1}{\bar{T}_2}
\]  

The expression for \( y_2 \) is:  
\[
y_2 = \frac{1}{\bar{T}_2} - \frac{1}{\bar{T}_1}
\]

The page contains two diagrams related to thermodynamic processes.  

**Diagram 1:**  
The first diagram is a qualitative \( T \)-\( s \) (temperature-entropy) diagram. It shows a thermodynamic process with labeled points and arrows indicating the direction of the process. The curve begins at point 1 and moves upward to point 2, then transitions to point 3. The process appears to involve compression and heat addition, as indicated by the upward trajectory.  

**Diagram 2:**  
The second diagram is another \( T \)-\( s \) diagram with more detailed labeling. It includes points labeled 1, 2, 3, 4, 5, and 6. The curve starts at point 1 and moves upward to point 3, indicating an increase in temperature and entropy. From point 3, the curve descends to point 4, then transitions through points 5 and 6.  

Axes:  
- The vertical axis is labeled \( T \) (temperature) in Kelvin \([K]\).  
- The horizontal axis is labeled \( s \) (entropy) in \([kJ/kg·K]\).  

Additional notes:  
- There is a handwritten note near point 1 that reads: "Triple Temp als u." This likely refers to the triple point temperature.  
- The diagrams visually represent thermodynamic processes such as compression, heat addition, and expansion.  

No further textual explanations or equations are visible on the page.

The page contains mathematical derivations related to jet engine exergy calculations. The following equations and expressions are visible:

1. The equation for outlet velocity \( w_6 \):
\[
w_6 = \sqrt{w_5^2 + \frac{2 \dot{m}_K}{\dot{m}_M} \left( h_5 - h_6 \right)}
\]

2. The expression for the temperature difference:
\[
T_6 = T_5 - \frac{w_6^2 - w_5^2}{2 c_p}
\]

3. The mass-specific increase in flow exergy:
\[
\Delta ex_{\text{flow}} = ex_{\text{flow},6} - ex_{\text{flow},0}
\]

4. The entropy production term:
\[
\dot{S}_{\text{gen}} = \frac{\dot{Q}_R}{T_{\text{Reactor},1}} - \frac{\dot{Q}_{\text{out}}}{T_{\text{KF}}}
\]

5. The energy balance equation:
\[
\dot{E}_{\text{in}} - \dot{E}_{\text{out}} + \dot{E}_{\text{gen}} = 0
\]

No diagrams or graphs are present on this page. The content appears to be focused on thermodynamic calculations for the jet engine problem.