The page contains multiple diagrams related to thermodynamic processes, specifically temperature (\( T \)) versus entropy (\( S \)) plots. Below is a description of each diagram:

1. **Top Diagram**:  
   - The graph is labeled with \( T \, [K] \) on the vertical axis and \( S \, [kJ/kg] \) on the horizontal axis.  
   - The process begins at point \( 1 \), moves to point \( 2 \) along an upward curve, and transitions to point \( 3 \) via an isobaric process.  
   - From point \( 3 \), the process moves downward to point \( 4 \), then continues to point \( 5 \) and finally to point \( 6 \).  
   - The diagram includes arrows indicating the direction of the process flow.  

2. **Middle Left Diagram**:  
   - This appears to be an isolated arrow pointing upward, possibly indicating a flow or direction of energy transfer.  

3. **Bottom Left Diagram**:  
   - Similar to the top diagram, this graph is labeled with \( T \, [K] \) on the vertical axis and \( S \) on the horizontal axis.  
   - The process starts at point \( 1 \), moves to point \( 2 \), then transitions to point \( 3 \) along an isobaric path.  
   - The process flows downward to point \( 4 \), continues to point \( 5 \), and ends at point \( 6 \).  
   - Arrows indicate the direction of the process flow.  

4. **Bottom Right Diagram**:  
   - This graph is also labeled with \( T \, [K] \) on the vertical axis and \( S \) on the horizontal axis.  
   - The process begins at point \( 1 \), moves to point \( 2 \), and transitions to point \( 3 \) via an isobaric process.  
   - From point \( 3 \), the process moves downward to point \( 4 \), continues to point \( 5 \), and ends at point \( 6 \).  
   - The diagram explicitly labels the segments as "isobaric" processes where applicable.  

Each diagram represents thermodynamic cycles or processes, with clear labeling of states and transitions.

The equation for the rate of change of entropy is given as:  
\[
\frac{dS}{dt} = \sum \dot{m}_i(t) s_i(t) + \int \frac{\dot{Q}(t)}{T_G(t)} + \dot{S}_{\text{gen}}(t)
\]