The enthalpy values are given as:  
\[
h_2 = 237.74 \, \text{kJ/kg}, \quad h_3 = 271.3 \, \text{kJ/kg}.
\]  

The first law of thermodynamics is applied for the process from state 2 to state 3:  
\[
0 = \dot{m}(h_2 - h_3) + \dot{Q} - \dot{W}.
\]  

The work term is rearranged as:  
\[
\frac{\dot{W}}{h_2 - h_3} = \dot{m}.
\]  

The heat transfer is noted as adiabatic (\( \dot{Q} = 0 \)), and the work term is given as \( -28 \, \text{kW} \). The mass flow rate is calculated as:  
\[
\dot{m} = 0.834 \, \text{kg/s}.
\]

The diagram represents a qualitative \( T \)-\( s \) diagram for a jet engine process. The temperature \( T \) is plotted on the vertical axis (in Kelvin), and the specific entropy \( s \) is plotted on the horizontal axis (in \( \text{kJ}/\text{kg·K} \)).  

Key features of the diagram:  
- The process begins at state \( 0 \), with \( p_0 = 0.191 \, \text{bar} \) and \( T_0 = -30^\circ\text{C} \).  
- State \( 1 \) corresponds to \( p_1 \), where the air is compressed adiabatically (\( \eta_{\text{comp}} < 1 \)).  
- State \( 2 \) is an isentropic compression to \( p_2 \).  
- State \( 3 \) represents an isobaric heat addition at \( p_c \) (where \( p_c \gg p_0 \)).  
- State \( 4 \) is an irreversible expansion in the turbine.  
- State \( 5 \) corresponds to mixing, and state \( 6 \) is the nozzle exit, where \( p_6 = p_0 \).  

The diagram includes labeled isobars \( p_0 \), \( p_1 \), \( p_2 \), and \( p_c \), with arrows indicating the direction of the process.  

Additional notes:  
- \( p_4 = p_5 = p_6 \).  
- The compression and expansion processes are marked as "isentrop" (isentropic) and "irrevers" (irreversible), respectively.  

No further mathematical expressions or calculations are provided.