The page begins with a labeled T-s diagram representing the thermodynamic processes of a jet engine. The vertical axis is labeled \( T \, [\text{K}] \), and the horizontal axis is labeled \( s \, [\text{kJ/kg·K}] \). The diagram includes six states (0, 1, 2, 3, 4, 5, and 6) connected by various processes.  

Description of the diagram:  
- State 0 to 1: A steep curve indicating an adiabatic, isentropic compression.  
- State 1 to 2: A vertical line representing an adiabatic, non-reversible process.  
- State 2 to 3: A horizontal line indicating an isobaric process.  
- State 3 to 4: A downward curve showing a non-reversible process.  
- State 4 to 5: A vertical line representing isentropic expansion.  
- State 5 to 6: A horizontal line indicating an isobaric process.  

Below the diagram, the processes are described in text:  
- \( 0 \to 1 \): Adiabatic and isentropic compression (\( \eta_{\text{comp}} < 1 \)), where \( p_1 > p_0 \) and \( T_1 > T_0 \).  
- \( 1 \to 2 \): Adiabatic, non-reversible process (\( s_1 \neq s_2 \)).  
- \( 2 \to 3 \): Isobaric process.  
- \( 3 \to 4 \): Non-reversible process.  
- \( 4 \to 5 \): Isentropic expansion (\( p_5 < p_4 \)).  
- \( 5 \to 6 \): Isobaric process.

The equation written is:  
\[
(p_0 \cdot v_0) + 4k + \left( (w_6^2 - w_5^2) \cdot \frac{1}{2} \right) - 4v - 4y = 145 \cdot x_0
\]  

No additional text or diagrams are present.

The page contains mathematical derivations and calculations related to jet engine exergy analysis. Below is the transcription of the visible content:

1. The equation for the outlet velocity \( w_6 \) is derived:
\[
w_6^2 = w_5^2 + 2 \left( h_5 - h_6 \right)
\]

2. The specific enthalpy difference is expressed:
\[
h_5 - h_6 = c_p \left( T_5 - T_6 \right)
\]

3. Substituting into the velocity equation:
\[
w_6^2 = w_5^2 + 2 c_p \left( T_5 - T_6 \right)
\]

4. The mass-specific increase in flow exergy \( \Delta ex_{\text{flow}} \) is calculated:
\[
\Delta ex_{\text{flow}} = ex_{\text{flow},6} - ex_{\text{flow},0}
\]

5. The flow exergy at state 6 is expressed:
\[
ex_{\text{flow},6} = \frac{w_6^2}{2} + c_p \left( T_6 - T_0 - T_0 \ln \frac{T_6}{T_0} \right)
\]

6. The flow exergy at state 0 is given:
\[
ex_{\text{flow},0} = \frac{w_0^2}{2} + c_p \left( T_0 - T_0 \ln \frac{T_0}{T_0} \right)
\]

7. The mass-specific exergy destruction \( ex_{\text{dest}} \) in the engine is calculated:
\[
ex_{\text{dest}} = \Delta ex_{\text{flow}} - \left( \text{useful work output} \right)
\]

8. Additional calculations for \( w_6 \) and \( T_6 \) are shown:
\[
w_6 = \sqrt{w_5^2 + 2 c_p \left( T_5 - T_6 \right)}
\]

9. The entropy production term is derived:
\[
\dot{S}_{\text{gen}} = \frac{\dot{Q}}{T_{\text{mean}}}
\]

No diagrams or graphs are present on the page.