The page contains multiple diagrams illustrating the thermodynamic processes of a jet engine in a temperature-entropy (\(T\)-\(s\)) diagram.  

1. The first diagram shows several isobars labeled \(p_0 = 0.191 \, \text{bar}\), \(p = 0.5 \, \text{bar}\), and \(p = p_2 = p_3\). The process begins at state \(0\) and progresses through states \(1\), \(2\), \(5\), and \(6\). The paths between states are labeled as isentropic or isobaric, with arrows indicating the direction of the process.  

2. The second diagram zooms into the region between states \(5\) and \(6\), showing the isobar \(p = 0.5 \, \text{bar}\) and the isobar \(p_0 = 0.191 \, \text{bar}\). The entropy axis (\(s\)) is labeled in \(\text{kJ}/\text{kg·K}\), and the temperature axis (\(T\)) is labeled in Kelvin (\(K\)).  

3. The third diagram provides a three-dimensional perspective of the thermodynamic processes, with states \(5\) and \(6\) highlighted. It includes isentropic and isobaric paths and labels the pressure values.  

---

The page contains a T-s diagram (temperature vs. entropy) illustrating the thermodynamic processes of a jet engine. The axes are labeled as follows:  
- The vertical axis represents temperature \( T \) in degrees Celsius (\( ^\circ \text{C} \)).  
- The horizontal axis represents entropy \( S \) in \( \frac{\text{kJ}}{\text{kg·K}} \).  

Key points and processes are marked on the diagram:  
1. **Point 0**: Represents the ambient state with pressure \( p_0 \).  
2. **Point 1**: Compression process labeled as "isentrop adiabatic" (isentropic adiabatic). Pressure increases from \( p_0 \) to \( p_1 \).  
3. **Point 2**: Isobaric heat addition labeled as "isobar planström" (isobaric heat transfer). Pressure remains constant at \( p_1 \).  
4. **Point 3**: Combustion process, labeled as "isobar".  
5. **Point 4/5**: Expansion process labeled as "adiabat, reversibel" (adiabatic, reversible).  
6. **Point 6**: Final state after expansion, returning to ambient pressure \( p_0 \).  

The diagram includes annotations for the processes:  
- Compression (isentropic adiabatic)  
- Heat addition (isobaric)  
- Expansion (adiabatic, reversible)  

The curve transitions are consistent with the thermodynamic processes of a jet engine, showing entropy changes and temperature variations across different states.