The diagram represents a qualitative T-s diagram for the jet engine process. The axes are labeled as follows:  
- The vertical axis is temperature \( T \) in Kelvin.  
- The horizontal axis is entropy \( S \) in unspecified units.  

The diagram includes the following labeled states and processes:  
- State 0: Starting point of the process.  
- State 1: Isentropic compression.  
- State 2: Isentropic compression continues.  
- State 3: Adiabatic and irreversible process.  
- State 4: Isobaric heat addition.  
- State 5: Isobaric heat addition continues.  
- State 6: Isentropic expansion.  

Arrows indicate the direction of each process, and the transitions between states are clearly marked. The temperature at the lower boundary is labeled as \( 243.15 \, \text{K} \).  

---

The process is described as stationary.  

The energy balance equation is written as:  
\[
\dot{m}_{\text{ges}} \left( \Delta h + \frac{w_6^2 - w_5^2}{2} \right) + \sum_j \dot{Q}_j - \sum_n \dot{W}_n = 0
\]  

The change in enthalpy is expressed as:  
\[
\Delta h = \frac{w_0^2 - w_5^2}{2}
\]  

The enthalpy difference is calculated using integration:  
\[
\Delta h = \int_{T_5}^{T_6} c_p \, dT = c_p \left( \ln(T_6) - \ln(T_5) \right)
\]  
Substituting values:  
\[
\Delta h = -0.27 + 66024 \, \text{J}
\]  

The equation for velocity squared is:  
\[
0.27 \cdot 66024 \cdot 2 + w_6^2 = w_6^2 = 48400.553 \, \text{m}^2/\text{s}^2
\]  

Solving for \( w_6 \):  
\[
w_6 = \sqrt{48400.553} \, \text{m/s}
\]  

Further calculation of enthalpy difference:  
\[
\Delta h = \int_{T_5}^{T_6} c_p \, dT = c_p (T_6 - T_5) = -104.442 \, \text{kJ}
\]  

Final equation:  
\[
\Delta h \cdot 2 + w_6^2 = w_6^2 = 252294.912 \, \text{m}^2/\text{s}^2
\]  

Solving for \( w_6 \):  
\[
w_6 = 504.2454159 \, \text{m/s}
\]