The change in entropy, Delta S, is equal to the sum over i of the heat transfer rate, dot Q sub i, divided by the temperature, T sub i, plus the generated entropy rate, dot S sub erz. This implies that the generated entropy rate, dot S sub erz, is equal to negative the heat transfer rate out, dot Q sub aus, divided by the temperature at the output, T sub UF, which equals 62.182 kilowatts divided by 293.12 Kelvin, resulting in 212.139 watts per Kelvin.

The ratio of DE over QE equals the sum from i to j of m sub i of t times h sub i of t plus the sum from i to j of q sub e of t plus the sum from i to j of c sub i of t minus the sum from i to j of w sub i of t.

The change in energy, Delta E, equals m sub 2 times u sub 2 minus m sub 1 times u sub 1, which equals the sum from i to j of Q sub i, and is given as Q sub aus2 equals 35 megajoules.

m sub 2 equals m sub 1 plus Delta m, m sub 2 equals 5755 kilograms, m sub AB equals x times m sub 1, m sub NB equals m sub 1 times (1 minus x), and m sub 2 equals Delta m.

The internal energy at end of combustion, u sub 1f, is 250.65 units per kilogram.

The internal energy at 200 degrees Celsius, u sub 1pf, is 42.94 units per kilogram.

The internal energy at 200 degrees Celsius, u sub 2pf, is 292.95 units per kilogram.

The internal energy at 200 degrees Celsius, u sub 3f, is 87.95 units per kilogram.

The change in time, Delta t, equals m sub 3 times u sub 3 plus m sub 2 times u sub 2 minus m sub 1 times u sub 1, which equals 35 megajoules, equals Delta m times u sub 3 plus m sub 2 times u sub 2 plus Delta m times u sub 2 minus m sub 1 times u sub 1.

The ratio of m sub 1 times u sub 1 minus m sub 1 times u sub 2 over u sub 3 plus u sub 2 equals the sum of m sub A1 times u sub A1 plus m sub A1 times u sub A1 minus m sub 1 times u sub 2pf plus 35 megajoules over u sub 3f plus u sub 2f.

This equals the sum of 0.005 plus 5755 kilograms times 250.65 units per kilogram plus 5755 kilograms times (1 minus 0.005) times 42.94 units per kilogram minus 5755 kilograms times 292.95 units per kilogram over 87.95 units per kilogram plus 292.95 units per kilogram.

Delta m sub 2 equals 2176.02 kilograms.