The mass flow rate, denoted as m-dot subscript R, equals zero.

The temperature T subscript R2 is 70 degrees Celsius and the temperature T subscript R1 is 100 degrees Celsius.

The inlet temperature, T subscript ein, is 20 degrees Celsius.

The heat output, Q subscript aus, is 35 Mega Joules.

For the energy balance of a semi-open system:

The change in internal energy, Delta U, equals the change in mass at the inlet, Delta m subscript ein, times the enthalpy at the inlet, h subscript ein, plus the heat transfer Q subscript j.

The expression m subscript 2 times u subscript 2 minus m subscript 1 times u subscript 1 equals Delta m subscript ein times h subscript ein minus Q subscript aus.

The mass m subscript 2 equals the mass m subscript 1 plus the change in mass at the inlet, Delta m subscript ein.

The mass m subscript 1 is 5755 kilograms.

The internal energy per unit mass at state 1, u subscript 1, is calculated as 2506.5 times 0.005 plus (1 minus 0.005) times 478.94, which equals 428.38.

The internal energy per unit mass at state 2, u subscript 2, at 70 degrees Celsius is 292.95.

The enthalpy at the inlet, h subscript ein, at 20 degrees Celsius is 83.96.

The enthalpy h is not equal to h subscript f.

The internal energy U equals U subscript F.

The equation (5755 plus Delta m) times 232.95 minus 5755 times 423.38 equals Delta m times 83.96 minus 35 times 10 to the power of 3 simplifies to -750754 equals -208.95 times Delta m.

Solving for Delta m gives Delta m equals 3588.9 kilograms.

The change in entropy from state 1 to state 2, Delta S subscript 12, equals m subscript 1 times s subscript 1 minus m subscript 2 times s subscript 2.

The mass m subscript 1 is 5755 kilograms, and the mass m subscript 2 is 9355 kilograms.

The entropy per unit mass at state 1, s subscript 1, is calculated as 0.005 times 7.3549 minus 8 times 9.998 times 1.3 plus 0.985 times 1.3068, which equals 1.23714.

The entropy per unit mass at state 2, s subscript 2, is 6.9549.

The change in entropy from state 1 to state 2, Delta S subscript 12, is -1237.85 kilo Joules.