Section b):

Subsection 1. Conservation equation around the thrust nozzle:

Zero equals the total mass flow rate times the quantity of enthalpy at point 5 minus enthalpy at point 6 plus half the difference of the square of velocity at point 5 and the square of velocity at point 6, plus the heat transfer rate minus the work done by the turbine.

- It is adiabatic reversible, hence the heat transfer rate equals zero.

Subsection: Entropy balance:

Zero equals the total mass flow rate times the difference in entropy between point 5 and point 6, plus the heat transfer rate divided by temperature, plus the generated entropy.

- The generated entropy equals zero, it is adiabatic.
- Zero, conventional adiabatic condition.

Entropy at point 5 equals entropy at point 6.

- Note: Calculations were done using degrees Celsius instead of Kelvin in the table, therefore add 273.15 to all temperature values.

Subsection: Determine h_5

Enthalpy at point 5 is determined by interpolation in Table A-22.

Enthalpy at point 5 equals 441.61 minus 431.43.

The fraction (440 minus 430) divided by (431.9 minus 430) times 431.43 equals 433.36 kilojoules per kilogram.

Subsection: Interpolate s_5:

Entropy at point 6 minus entropy at point 5 equals the standard entropy at temperature 6 minus the standard entropy at temperature s minus the gas constant times the natural logarithm of the ratio of pressure at point 6 to pressure at s.

- Incorrect
- Find

Graphical Description:

The graph is a Temperature-Entropy (T-S) diagram with the x-axis labeled as entropy in kilojoules per kilogram Kelvin and the y-axis labeled as temperature in Kelvin. A dome-shaped curve represents the phase change region with several points labeled from 0 to 6. The process flows from point 0 to point 6 with arrows indicating the direction, and the isobar lines are dashed and labeled as "isobar". The mass flow rates at various points are indicated.

Standard entropy at s equals the fraction (2.0887 minus 2.0653) divided by (440 minus 430) times (431.3 minus 430) plus 2.0653 equals 2.0657.

Temperature at point 6 equals temperature at point 5 equals 431.3 Kelvin.

Entropy at point 6 minus entropy at standard point B equals zero equals the standard entropy at temperature 6 minus the standard entropy at temperature 5 minus the gas constant times the natural logarithm of the ratio of pressure at point 6 to pressure at point 5.

The specific heat at constant volume equals the specific heat at constant pressure divided by k equals 0.7186 kilojoules per kilogram Kelvin.

The gas constant equals the specific heat at constant pressure minus the specific heat at constant volume equals 0.2874 kilojoules per kilogram Kelvin.

The standard entropy at temperature 6 equals the standard entropy at temperature 5 plus the gas constant times the natural logarithm of the ratio of pressure at point 6 to pressure at point 5 equals 1.7931 kilojoules per kilogram Kelvin.

Interpolate in A-22.

Temperature at point 6 equals the fraction (340 minus 330) divided by (1.7931 minus 1.78249) times (1.7931 minus 1.78249) plus 330 equals 336.81 degrees Celsius.

The work done by the turbine equals negative n times the integral from point 5 to point 6 of density times the change in volume.

The work done by the turbine equals negative the total mass times n times the integral from point 5 to point 6 of density times the change in volume.

The ratio of pressure to pressure at point 5 raised to the power of (n minus 1) divided by n equals the ratio of volume at point 5 to volume raised to the power of n minus 1.