Section d) Energy balance around water:

Change in internal energy, Delta U, equals heat transfer Q from state 1 to 2 minus the work done by the water, W_water.

Work done on the environment equals the ambient pressure, p_amb, multiplied by the change in volume, Delta V from state 1 to 2.

This equals negative 2.031 times 1 bar, which is negative 203.07 Joules.

Work done on the water equals the absolute value of W_12 minus the work on the environment.

This equals 489.16 Joules, which is equal to W_water.

The change in internal energy of the water, Delta U_water, is 1448.16 Joules.

This equals the mass of the evaporating water, m_EW, times the difference in specific internal energy from state 1 to state 2, (u_2 minus u_1).

(u_2 minus u_1) equals 1448.16 Joules divided by the mass of the evaporating water, m_EW, which is 42322 Joules per kilogram.

u_1 is the specific internal energy at 0 degrees Celsius and 1.4 bar, which is calculated as x times the specific internal energy of the solid phase plus (1 minus x) times the specific internal energy of the liquid phase, equaling negative 200.0328 kilojoules per kilogram.

u_2 equals u_1 plus 423.22, which is 223.127 kilojoules per kilogram.

This is calculated as x times the specific internal energy of the solid phase plus (1 minus x) times the specific internal energy of the liquid phase.

This can be rearranged to x times (specific internal energy of the solid minus specific internal energy of the liquid) plus the specific internal energy of the liquid.

The fraction (u_2 minus specific internal energy of the liquid) divided by (specific internal energy of the solid minus specific internal energy of the liquid) gives x, at a pressure of 1.4 bar.

The temperature is approximately 0 degrees Celsius.

x is approximately 0.66, but there seems to be an error since the absolute value of x is increasing and is negative.