Zero equals the mass flow rate times the difference between the entropy at the inlet and the entropy at the outlet plus the heat transfer rate divided by the average temperature plus the entropy generation rate.

Negative entropy generation rate equals negative mass flow rate times the difference between the entropy at the inlet and the entropy at the outlet minus the heat transfer rate at the working condition divided by the temperature at the reference condition minus the heat transfer rate at the outlet divided by the temperature at the condenser minus the heat transfer rate at the reference divided by 373.15 Kelvin.

Temperature minus temperature at A2.

The entropy at the inlet minus the entropy at the saturation condition at 70 degrees Celsius equals 0.93479.

The entropy at the outlet minus the entropy at the saturation condition at 100 degrees Celsius equals 1.3069.

Equals 0.06 kilojoules per kilogram Kelvin.

Entropy generation rate equals zero equals the mass flow rate times the difference between the entropy at the inlet and the entropy at the outlet plus the heat transfer rate divided by the average temperature plus the entropy generation rate.

Entropy generation rate equals the mass flow rate times the difference between the entropy at the inlet and the entropy at the outlet minus the heat transfer rate at the outlet divided by the temperature at the reference condition plus the heat transfer rate at the working condition divided by the average temperature.

Equals 0.057 kilojoules per kilogram Kelvin.