Energy balance:

Zero equals the mass flow rate times the sum of the enthalpy difference between state s and state 6, the difference of the squares of velocities at state 5 and state 6 divided by 2, plus the gravitational acceleration times the height difference between state 5 and state 6, plus the heat transfer rate minus the power output.

Isentropic:

The entropy at state 5 equals the entropy at state 6.

The entropy at state 5 at 431.3 Kelvin is calculated as the difference between 2.0887 and 2.06533 divided by the difference between 440 and 430, multiplied by the difference between 431.3 and 430, plus 2.06533, which equals 2.06977 (value from A-22).

The difference between entropy at state 6 and state 5 equals the difference between the entropy at standard conditions at state 6 and state 5 minus the gas constant times the natural logarithm of the ratio of pressure at state 6 to pressure at state 5, which equals zero.

The gas constant R equals 8314 divided by 28.57, which is 287.

The pressure at state 0 equals 0.181 bar.

The pressure at state 5 equals 0.5 bar.

The entropy at standard conditions at state 6 equals the entropy at standard conditions at state 5 plus the gas constant times the natural logarithm of the ratio of pressure at state 6 to pressure at state 5.

This equals 2.06977 plus 287 times the natural logarithm of the ratio of 0.181 to 0.5 times 1000, which equals 1.7935 kilojoules per kilogram Kelvin.

The entropy at standard conditions at 325 Kelvin equals 1.78249.

The entropy at standard conditions at 330 Kelvin equals 1.7935.

The temperature at state 6 equals 330 minus the ratio of the difference between 330 and 325 to the difference between 1.7935 and 1.78249, multiplied by the difference between 1.7935 and 1.78249, plus 325, which equals 328.5 Kelvin (value from A-22).

Zero equals the mass flow rate times the sum of the enthalpy difference between state s and state 6, plus the difference of the squares of velocities at state 5 and state 6 divided by 2.

The square of the velocity at state 6 equals twice the sum of the enthalpy difference between state s and state 6 plus half the square of the velocity at state 5.

The enthalpy at state s is calculated as the difference between 441.61 and 431.4 divided by the difference between 440 and 430, multiplied by the difference between 431.9 and 430, plus 431.43, which equals 433.36 kilojoules per kilogram (value from A-22).

The enthalpy at state 6 is calculated as the difference between 330.54 and 325.31 divided by the difference between 330 and 325, multiplied by the difference between 328.5 and 325, plus 325.31, which equals 328.87 kilojoules per kilogram (value from A-22).

The velocity at state 6 equals the square root of twice the product of the difference between 433.36 and 328.87 times 1000 plus half the square of 220, which equals 507 meters per second.