Required: omega_6, T_6.

Given: isentropic nozzle, U_s, p_s, T_s are known.

The equation Q equals m dot times the quantity h_s minus h_6 plus the quantity omega_s squared minus omega_6 squared all over 2 (this equation is crossed out).

m dot equals m dot total.

Exergy balance:

Q equals m dot total times the quantity h_s minus h_6 plus the quantity delta k over e, where delta k equals the quantity omega_s squared minus omega_6 squared all over 2.

h_s is found using Table A2: h_s at 930 Kelvin plus the quantity h at 990 Kelvin minus h at 952 Kelvin all over 10 Kelvin times 1.9 Kelvin.

The equations are as follows:
- h_5 equals 953.26 kilojoules per kilogram.
- Isentropic from state 5 to 6 and:
- T_6 equals T_5 times the quantity p_6 over p_5 raised to the power of (n minus 1) over n.
- T_6 equals 328.075 Kelvin.
- h_6 equals h at 328 Kelvin plus the quantity h at 333 Kelvin minus h at 328 Kelvin all over 5 Kelvin times 3.075 Kelvin.
- h_6 equals 333.93 kilojoules per kilogram.
- 0 equals m dot total times the quantity h_5 minus h_6 plus the quantity omega_5 squared minus omega_6 squared all over 2.
- m dot total squared times the quantity h_6 minus h_5 equals m dot total times the quantity omega_5 squared minus omega_6 squared all over 2 minus omega_6 squared equals 2 times the quantity h_6 minus h_5 minus omega_5 squared.
- omega_6 squared equals 2 times the quantity h_5 minus h_6 plus omega_5 squared, omega_6 equals 998.26 meters per second.
- ex_str6 minus ex_str0 equals m dot total times the quantity h_6 minus h_0 minus T_0 times the quantity s_6 minus s_0 plus delta ke.
- h_6 equals 333.93 kilojoules per kilogram, h_0 equals h at 265.15 Kelvin.
- s_6 equals s at T_6, s_0 equals s at T_0, delta ke equals the quantity omega_6 squared minus omega_0 squared all over 2.
- s at T_6 approximately equals 1.79 kilojoules per kilogram Kelvin, s_0 approximately equals 1.86 kilojoules per kilogram Kelvin.
- h_0 approximately equals 263 kilojoules per kilogram.
- Delta ex_str equals ex_str over m dot total equals 109.19 kilojoules per kilogram over 119.09 kilojoules per kilogram.