Zero equals the mass flow rate times the difference between the enthalpy at the inlet and the enthalpy at the outlet plus the heat transfer rate Q_er2.
Q_er2 (crossed out).
The difference between the outlet enthalpy and the inlet enthalpy equals the change in enthalpy, Delta h_m2.
Semi-open system.
The product of mass 2 and internal energy 2 minus the product of mass 1 and internal energy 1 equals the change in mass m2 times the supplied enthalpy plus the heat transfer rate Q_er2 minus the work input W_ein.
The internal energy at 20 degrees Celsius from table TAB-A2 is 292.55 kilojoules per kilogram.
The internal energy at 100 degrees Celsius from table TAB-A2 is 418.94 kilojoules per kilogram.
The supplied enthalpy at 20 degrees Celsius from table TAB-A2 is 83.95 kilojoules per kilogram.
Mass 2 equals mass 1 plus the change in mass 2.
Mass 1 is 5735 kilograms.
The change in mass 2 times the difference between internal energy 2 and the supplied enthalpy equals mass 1 times internal energy 1 minus mass 2 times internal energy 2 plus the heat transfer rate Q_er2.
The change in mass 2 equals the numerator (mass 1 times internal energy 1 minus mass 2 times internal energy 2 plus the heat transfer rate Q_er2) divided by the denominator (internal energy 2 minus the supplied enthalpy).
The change in mass 2 equals 5735 kilograms times 418.94 kilojoules per kilogram minus 292.55 kilojoules per kilogram plus 100 kilojoules divided by the difference 292.55 minus 83.95.
The change in mass 2 equals 3469.725 kilograms minus the change in mass 2.