The rate of change of energy with respect to time is zero, which equals the mass flow rate times the difference in enthalpy between state zero and state six plus half the difference of the squares of velocity at state zero and state six, plus the heat transfer rate divided by the mass flow rate of component K, plus the power.

Zero equals the mass flow rate times the specific heat capacity at constant pressure times the temperature difference between state zero and state six plus half the difference of the squares of velocity at state zero and state six, which equals the negative of the heat transfer rate divided by the mass flow rate of component K.

5.273 times the mass flow rate of component K equals the mass flow rate, which is the difference between the mass flow rate and the mass flow rate of component K.

The mass flow rate of component K equals the mass flow rate divided by 6.273.

The rate of change of energy with respect to time is zero, which equals the mass flow rate times the sum of the difference in enthalpy between state zero and state six and half the difference of the squares of velocity at state zero and state six, plus the heat transfer rate minus the power.

Zero equals the difference in enthalpy between state zero and state six plus half the difference of the squares of velocity at state zero and state six plus the heat transfer rate.

The velocity at state six equals the square root of two times the sum of the difference in enthalpy between state zero and state six and the heat transfer rate plus the square of the velocity at state zero.

This equals the square root of two times the sum of the specific heat capacity at constant pressure times the temperature difference between state zero and state six and the heat transfer rate plus the square of the velocity at state zero.

The heat transfer rate equals 1195 kilojoules per kilogram.

The temperature at state zero is 243.15 Kelvin.

The temperature at state six is not specified.

The velocity at state zero is 200 meters per second.