Section d) Semi-open System:

The change in energy, Delta E, is equal to the mass flow rate from state 1 to 2 times the specific enthalpy at state 12, plus the heat transfer rate from state 1 to 2, plus the work transfer rate from state 1 to 2, and this approaches zero:
Delta E equals m dot subscript 12 times h subscript 12 plus Q dot subscript 12 plus W dot subscript 12 approaches zero.

The change in internal energy mass from state 1 to state 2 is equal to the change in mass from state 1 to state 2 times the specific enthalpy at state 12:
m subscript u2 minus m subscript u1 equals Delta m subscript 12 times h subscript 12.

This implies that the change in mass from state 1 to state 2, Delta m subscript 12, is equal to the difference in internal energy mass from state 2 to state 1 divided by the specific enthalpy at state 12:
Delta m subscript 12 equals (m subscript u2 minus m subscript u1) divided by h subscript 12.

The specific internal energy at state 1, u subscript 1, is equal to the specific internal energy at 1000 degrees plus x subscript 0 times the difference between the specific internal energy in the gas phase and the fluid phase, which equals 429.37 kilojoules per kilogram.

The specific internal energy at state 2, u subscript 2, is equal to the specific internal energy at 20 degrees Celsius plus x subscript 0 times the difference between the specific internal energy in the gas phase and the fluid phase, which equals 303.368 kilojoules per kilogram.

The internal energy mass at state 2, m subscript u2, is equal to the internal energy mass at state 1 plus the change in mass from state 1 to state 2:
m subscript u2 equals m subscript u1 plus Delta m subscript 12.

The specific enthalpy at state 12, h subscript 12, is equal to the specific enthalpy in the gas phase at state 12, which equals 126.06 kilojoules per kilogram.

This implies that the change in mass from state 1 to state 2, Delta m subscript 12, is equal to the difference in internal energy mass from state 2 to state 1 divided by the specific enthalpy at state 12:
Delta m subscript 12 equals (m subscript u2 minus m subscript u1) divided by h subscript 12.

The sum of the change in mass from state 1 to state 2 and the internal energy mass at state 2 equals the difference in internal energy mass from state 2 to state 1, which is derived from the change in mass times (1 plus 1 divided by the specific enthalpy at state 12) equals the difference in internal energy mass divided by the specific enthalpy at state 12.

Finally, the change in mass from state 1 to state 2, Delta m subscript 12, is equal to the difference in internal energy mass from state 2 to state 1 divided by the specific enthalpy at state 12 times (1 plus 1 divided by the specific enthalpy at state 12), which equals 5680 micrograms.