The equations and descriptions provided are as follows:

1. The speed \( w_s \) is 220 meters per second.
2. The pressure \( p_5 \) is 0.8 bar.
3. The temperature \( T_5 \) is 431.8 Kelvin.
4. The pressure \( p_6 \) is 0.191 bar.
5. The heat transfer \( Q \) is calculated as the product of the total mass flow rate \( \dot{m}_{ges} \) and the sum of the enthalpy difference between states 5 and 6, the kinetic energy difference between states 5 and 6, subtracting the reversible work \( \dot{W}_{rev} \).

Additional details include:
- A graph is drawn with the x-axis labeled as entropy per unit mass \( S \left[ \frac{u}{kg} \right] \) and the y-axis labeled as temperature \( T \left[ K \right] \).
- Several curves represent different pressures on the graph.
- Points are labeled from 1 to 6.
- Point 1 is at the intersection of the lowest pressure curve and the y-axis.
- Point 2 is on a higher pressure curve connected to point 1 by a line labeled "reversible".
- Point 3 is on the same pressure curve as point 2, connected by an isobaric line.
- Point 4 is on a higher pressure curve connected to point 3 by a line labeled "reversible".
- Point 5 is on the same pressure curve as point 4, connected by an isobaric line.
- Point 6 is on the lowest pressure curve connected to point 5 by a line labeled "reversible".

Further equations:
- The entropy at points 5 and 6 are equal because the process is isentropic.
- The temperature ratio \( \frac{T_6}{T_5} \) is calculated using the pressure ratio \( \frac{p_6}{p_5} \) raised to the power of \( \frac{n-1}{n} \).
- The temperature \( T_6 \) is calculated to be approximately 328.675 Kelvin using the given formula and values.

Additional calculations:
- The heat transfer \( Q \) is also expressed as the product of the total mass flow rate \( m_{ges} \), specific heat at constant pressure \( Cp \), and the temperature difference \( T_5 - T_6 \), plus the kinetic energy difference.
- The overall speed \( \omega_{ges} \) is calculated using the square root of twice the product of \( Cp \), the temperature difference, divided by \( n \), subtracting 74.66.
- The heat transfer \( Q \) is also expressed in terms of specific heat \( Cp \), speed \( w \), and a constant ratio.
- The energy \( E_v \) is the ratio of specific heat \( Cp \) to \( n \).
- The speed \( \omega_6 \) is calculated using the square root of twice the sum of the product of \( Cp \) and the temperature difference plus half the square of \( \omega_5 \), resulting in approximately 507.2434 meters per second.