Given:
- The rate of heat transfer Q dot equals the mass flow rate m dot times the difference in enthalpy h5 minus h6 plus half the difference in the squares of velocities w5 squared minus w6 squared, plus Q dot minus the power W dot.
- Q dot equals the total mass flow rate m dot subscript ges times the difference in enthalpy h5 minus h6 plus half the difference in the squares of velocities w5 squared minus w6 squared.
- The difference in enthalpy h5 minus h6 equals the difference in temperatures T5 minus T6 times the specific heat capacity cp.
- The total mass flow rate m dot subscript ges equals the sum of the mass flow rates m dot subscript k plus m dot subscript H.
- The mass flow rate m dot subscript M equals 51.253 kilograms per second.
- The temperature T6 equals 328.07 Kelvin.
- The temperature T6 equals the temperature T5 times the ratio of pressure p0 over p5 raised to the power of (n-1) over n.
- The temperature T1 equals the temperature T0 times the ratio of pressure p1 over p0 raised to the power of (n-1) over n, which equals 320.059 Kelvin.

Assumption:
- The total mass flow rate m dot subscript ges times h5 minus the total mass flow rate m dot subscript ges times h6 plus half the square of velocity w5 squared minus half the square of velocity w6 squared equals the power W dot.
- The square of velocity w6 squared equals twice the difference in enthalpy h5 minus h6 plus the square of velocity w5 squared.
- The internal energy U6 equals the square root of twice the difference in enthalpy h5 minus h6 plus the square of velocity w5 squared.
- The velocity w6 equals the square root of twice the specific heat capacity cp times the difference in temperatures T5 minus T6 plus the square of velocity w5 squared, which equals 220.474 meters per second.