Requested: Heat output rate, denoted as Q-dot-out (approximately 165 kW).

Energy Balance:

The rate of change of energy with respect to time is equal to the sum of the mass flow rate times the sum of enthalpy at time t and half the sum of kinetic energy at time t plus pressure at time t, plus the sum of heat flow rates at time t, minus the sum of work rates at time t.

The mass flow rate in is zero, the mass flow rate out is zero, and the rate of change of energy with respect to time is zero.

Zero equals the mass flow rate times the difference in enthalpy from inlet to outlet plus 100 kW minus the heat output rate.

Thus, the heat output rate Q-dot-out equals 0.3 times the difference in enthalpy from inlet to outlet plus 100,000.

For pure water at an inlet temperature of 70 degrees Celsius with a quality of 0.005, and an outlet temperature of 100 degrees Celsius:

At saturation temperature 42 degrees Celsius, the enthalpy of liquid is 252.58 and the enthalpy of vapor is 2676.8 at 70 degrees Celsius.

The enthalpy at the inlet is calculated as 252.58 plus 0.005 times (2676.8 minus 252.58) equals 304.65.

At saturation temperature 42 degrees Celsius, the enthalpy of liquid is 419.80 and the enthalpy of vapor is 2676.1.

The enthalpy at the outlet is calculated as 419.80 plus 0.005 times (2676.1 minus 419.80) equals 431.76.

Therefore, the heat output rate Q-dot-out equals 0.3 times (304.65 minus 431.76) plus 100,000 equals 55968.07 Joules per second, which is 99.56 kilojoules per second.