Omega five u squared minus half of V five u squared equals the negative integral from p three to p six of v dp plus delta kinetic energy equals negative of the quantity R over one minus kappa times the quantity T six over T five minus one plus half of the quantity w five squared minus w six squared.

R equals c p minus c v.

Kappa equals c p over c v.

c v equals c p over kappa.

Zero equals h five minus h six minus half of the quantity w five squared minus w six squared minus omega five u squared.

1041.45 minus half of w five squared minus half of w six squared plus R over one minus kappa times the quantity T six minus T five equals zero.

1041.45 minus half of w six squared plus R over one minus 0.4 times the quantity 328.07 minus 431.9 equals zero.

1041.45 minus half of w six squared plus R over 0.6 times negative 103.83 equals zero.

1041.45 minus half of w six squared plus R over 0.6 times negative 103.83 equals zero.

Ex erg zero equals h zero minus h zero at T zero minus T zero times the quantity s zero minus s zero plus half of w zero squared.

Ex erg zero equals h zero minus h zero at T zero minus T zero times the quantity s zero minus s zero plus half of w zero squared.

Ex erg zero minus ex erg zero equals h zero minus h zero minus h zero at T zero plus h zero at T zero minus T zero times the quantity s zero minus s zero plus T zero times the quantity s zero minus s zero plus half of the quantity w zero squared minus w zero squared equals c p times the quantity T zero minus T zero minus T zero times the quantity exponential of m over T zero minus R ln of the quantity p zero over p zero plus half of the quantity w zero squared minus w zero squared.

Delta ex ist equals 110106 kilojoules per kilogram.

T zero equals 340 Kelvin.

T zero equals 243.15 Kelvin.

w c equals 310 meters per second.

w zero equals 200 meters per second.