c) The change in specific exergy due to the stream, denoted as Delta e_{x,str}, is equal to e_{x,str,6} minus e_{x,str,0}.

This is calculated as:
h_6 minus h_0 minus T_0 times (s_6 minus s_0) plus ke_6 minus (h_0 minus h_0 minus T_0 times (s_6 minus s_0) plus ke_0).

The specific enthalpy at condition c, denoted as h_c, equals h_0, which is the integral from T_0 to T_c of c_{p,luft} of T with respect to T, and this equals c_{p,luft} times (T_c minus T_0).

This results in:
1.006 kilojoules per kilogram Kelvin times (325.0 Kelvin minus 243.15 Kelvin) equals 85.43 kilojoules per kilogram.

From Table A-22:

The specific entropy at T_c, denoted as s^0 (T_c), is calculated as:
(1.79813 plus 1.798249) kilojoules per kilogram Kelvin times ((325.0 Kelvin plus 325 Kelvin) divided by (330 minus 325)) equals 1.798249 kilojoules per kilogram Kelvin.

s^0 (T_c) equals 1.79819 kilojoules per kilogram Kelvin.

The specific entropy at T_0, denoted as s^0 (T_0), is calculated as:
(1.49819 plus 1.49824) kilojoules per kilogram Kelvin times ((243.15 Kelvin minus 240 Kelvin) divided by (250 minus 240)) equals 1.49824 kilojoules per kilogram Kelvin.

s^0 (T_0) equals 1.49811 kilojoules per kilogram Kelvin.

Thus, the change in specific exergy due to the stream, Delta e_{x,str}, is equal to h_c minus h_0 minus T_0 times (s_6 minus s_0) plus ke_6 plus ke_0.

The kinetic energy at state 6, ke_6, equals v_6 squared divided by 2, and the kinetic energy at state 0, ke_0, equals half of v_{luft} squared, which is 20000 square meters per second squared.

This results in 128654.23 square meters per second squared.

Therefore, the change in specific exergy due to the stream, Delta e_{x,str}, equals 85.43 kilojoules per kilogram minus 243.15 Kelvin times (1.79819 kilojoules per kilogram Kelvin minus 1.49811 kilojoules per kilogram Kelvin) plus (128654.23 minus 20000) square meters per second squared.

Delta e_{x,str} equals 1280.94 kilojoules per kilogram.