For the stationary flow process at the evaporator:
The equation is zero equals the mass flow rate times the difference in enthalpy between state 2 and state 3, plus the heat transfer rate minus the work transfer rate. The work transfer rate equals the mass flow rate times the difference in enthalpy between state 2 and state 3, which leads to the mass flow rate for the states 1, 3, and 4 being equal to the work transfer rate divided by the absolute value of the difference in enthalpy between state 2 and state 3, calculated as 28 times 10 to the power of negative 3 divided by the absolute value of 237.79 minus 273.314. This results in a mass flow rate of 8.39 times 10 to the power of negative 4 kilograms per second, which is equivalent to 0.8349 grams per second.

From state 1 to state 2, there is isothermal evaporation:
The evaporation temperature equals the initial temperature minus 6, resulting in negative 16 degrees Celsius, which is also the temperature at state 2. From Table A-11, the enthalpy at state 2, with quality x_2 equals 1 and temperature at negative 16 degrees Celsius, is 237.79 kilojoules per kilogram.

For the adiabatic reversible process from state 3 to state 4:
The entropy at state 3 equals the entropy at state 4, which is the entropy of saturated vapor at negative 16 degrees Celsius, 0.9298, from Table A-11. The pressure at state 3 is 8 bar.

From Table A-12 at 8 bar:
The enthalpy at state 3 is calculated using the enthalpy of saturated liquid and the difference in entropy divided by the difference in entropy between saturated vapor and saturated liquid, multiplied by the difference in enthalpy between saturated vapor and saturated liquid, resulting in 277.379 kilojoules per kilogram.

For state 4:
The quality x_4 is zero, and the pressure at state 3 equals the pressure at state 4, which is 8 bar. From Table A-11, the entropy at state 4 equals the entropy at state 1, which is the entropy of saturated liquid at 8 bar, 0.3459.

The pressure at state 2 is read from Table A-10 at a temperature of negative 16 degrees Celsius as 7.5748 bar, and since the process is isochoric, the pressure remains 7.5748 bar.

Interpolation from Table A-11:
The table includes values for beta, entropy of saturated liquid, entropy of saturated vapor, enthalpy of saturated liquid, and enthalpy of saturated vapor for different pressures. The quality at state 4 is calculated as the difference in entropy divided by the difference in entropy between saturated vapor and saturated liquid, resulting in 0.2795.