In the center of the document, there is a picture described using coordinates and lines. The picture consists of a square and two triangles inside it, with one triangle pointing upwards and the other downwards. The square is divided into four smaller rectangles. The point at the center of the square is labeled with "m_GW". The rectangle on the left is labeled with "2" and the one on the right is labeled with "0.14".

Below the picture, there is an equation stating that m_GW equals 0.14.

Following this, there is an expression Q divided by zero.

The text "Energy balance:" introduces the next equation, which describes the rate of change of energy, dE/dt, as the sum of heat flow rates minus the sum of omega dot.

Next, the specific heat at constant volume, C_v, is given as 0.1633 kilojoules per kilogram per Kelvin.

It is stated that ice melts at 0 degrees Celsius and the condition X_Ice greater than zero implies that the temperature T_EW2 equals 0 degrees Celsius and the temperature T_g2 also equals 0 degrees Celsius.

The "Ideal Gas Equation:" is introduced, followed by an equation relating the temperatures T_2 and T_1 to the pressures p_2 and p_1 raised to the power of (n-1)/n. This leads to the expression for (T_2/T_1) raised to the power of (n-1)/n equals p_2/p_1.

The specific heat at constant pressure, C_p, is calculated by adding R and C_v, resulting in 0.79512 kilojoules per kilogram per Kelvin.

The ratio of specific heats, k, is calculated as C_p divided by C_v, which equals 4.87.

The final equation calculates the pressure p_2 as p_1 times (T_2/T_1) raised to the power of n/(n-1), resulting in 0.9 bar when p_1 is 1.5 bar and the temperatures are given as 277.15 Kelvin and 777.15 Kelvin respectively. This results in a final value of 0.9 times 405 bar.