The table consists of three columns labeled from left to right: an unnamed column for states, 'P' for pressure, and 'T' for temperature. The rows represent different states from 0 to 6. The values in the table are as follows:
- State 0 has a pressure of 0.1 bar and a temperature of 30 degrees Celsius.
- State 1 has no values provided for pressure and temperature.
- State 2 and 3 both have a pressure denoted by 'P squared' but no temperature values are provided.
- State 4 has a pressure of 0.5 bar with no temperature value.
- State 5 has a pressure of 0.5 bar and a temperature of 437.13 Kelvin.
- State 6 has a pressure of 0.1 bar with no temperature value provided.

The graph description details a plot with temperature in Kelvin on the vertical axis and entropy in Joules per kilogram Kelvin on the horizontal axis. The points from 0 to 6 are plotted as follows:
- Point 0 is at the origin.
- Point 1 is positioned above and to the right of point 0.
- Point 2 is above and to the right of point 1 and is connected to point 1 by a line labeled "isobar".
- Point 3 is above and to the right of point 2 and is connected to point 2 by a line labeled "isobar".
- Point 4 is below and to the right of point 3 and is connected to point 3 by a line labeled "isobar".
- Point 5 is below and to the left of point 4 and is connected to point 4 by a line labeled "isobar".
- Point 6 is below and to the left of point 5 and is connected to point 5 by a line labeled "isobar".

All the lines connecting these points form a closed loop, and each line segment between the points is labeled as "isobar".