The mass flow rate of R134a is denoted as m dot subscript R134a. The value of x subscript 2 is equal to 1. The process from state 2 to 3 is reversible and isentropic, meaning entropy at state 2 equals entropy at state 3. The temperature at state 2 is equal to a cancelled term T subscript i minus 6 Kelvin. The initial density is 1 bar, which equals 10 raised to the power of negative 3.25, and the ambient density is 100 Pascals, which equals 0.1 kiloPascals. The temperature at 0.0355 kiloPascals remains the same at 0.0355 kiloPascals. The temperature difference T subscript i,a is calculated as negative 22 minus negative 20.385, which simplifies to 0.1 minus 0.035, and further to negative 20 minus negative 20.385 degrees Celsius. The temperature at state 2 after adjusting by 6 Kelvin is negative 26.385 degrees Celsius. The enthalpy at state 2 is h subscript g at negative 26.385 degrees Celsius. The heat transfer rate Q dot equals the product of the mass flow rate of R134a and the difference in enthalpy between state 2 and state 3, plus Q dot superscript 0 minus 28 Watts divided by the mass flow rate of R134a, which equals the work rate W dot subscript k. The mass flow rate of R134a is calculated as 28 Watts divided by the difference in enthalpy between state 2 and state 3. The entropy at state 2 equals the entropy at state 3, which is s at negative 26.385 degrees Celsius. The quality at state 3, x subscript 3, is calculated using the formula involving entropies at 1 bar. The entropy of the fluid phase at 1 bar is 0.3495 kiloJoules per kilogram Kelvin, and the entropy of the gas phase at 1 bar is 0.8066 kiloJoules per kilogram Kelvin, both from Table A-11. The enthalpy at state 3 is calculated as the enthalpy of the fluid phase at 1 bar plus x subscript 3 times the difference between the enthalpy of the gas phase and the fluid phase at 1 bar. The enthalpy of the fluid phase at 1 bar is 93.42 kiloJoules per kilogram, and the enthalpy of the gas phase at 1 bar is 264.45 kiloJoules per kilogram, also from Table A-11.

The table description states that the table has 4 columns and 4 rows with columns labeled as T, rho, and x. The rows are labeled as 1, 2, 3, and 4. The entries in the table are as follows:
- Row 1: T is empty, rho is empty, x is empty.
- Row 2: T is 2, rho is empty, x is empty.
- Row 3: T is 3, rho is 7, x is empty.
- Row 4: T is 4, rho is 8, x is empty.