a) Required: Heat transfer from the reaction wall to the coolant.

- There are two diagrams. The first diagram shows a vertical rectangular container, divided into two halves by a vertical line in the middle. On the left side, it is labeled "T_{F,aus}" and on the right side "T_{F,ein}". An arrow points from left to right through the center of the container and is labeled "Q_{aus}".
- The second diagram shows a similar container, but without the vertical line in the middle. On the left side, it is labeled "T_{F,ein}" and on the right side "T_{F,aus}". An arrow points from left to right through the center of the container and is labeled "W".

- Steady-state flow process with one mass flow:
  - Mass flow rate times (enthalpy at inlet minus enthalpy at outlet) plus heat transfer out plus heat transfer due to radiation.
  - Heat transfer out equals mass flow rate times (enthalpy at outlet minus enthalpy at inlet).
  - Heat transfer out equals mass flow rate times (enthalpy at inlet minus enthalpy at outlet) plus mass flow rate of another substance times its specific energy.

- Enthalpy at inlet equals A2 over enthalpy at inlet times enthalpy at 70 degrees Celsius.
- Enthalpy at inlet equals A2 over enthalpy at inlet times enthalpy at 100 degrees Celsius.
- Enthalpy at inlet equals A2 over enthalpy at inlet times enthalpy at 70 degrees Celsius equals 292.88 kilojoules per kilogram.
- Enthalpy at outlet equals enthalpy at 100 degrees Celsius equals 419.04 kilojoules per kilogram.
- Heat transfer out equals 0.3 times (292.88 kilojoules per kilogram minus 419.04 kilojoules per kilogram) equals negative 100 kilowatts.
- Heat transfer out equals 62.182 kilowatts.