The equation for the rate of change of energy with respect to time is given by the sum of the product of mass flow rate entering and specific enthalpy entering minus the sum of the product of mass flow rate exiting and specific enthalpy exiting plus the sum of heat transfer rates minus the sum of work rates.

In a steady state condition, the equation simplifies to zero equals the sum of the product of mass flow rate entering and specific enthalpy entering plus the sum of heat transfer rates.

Further, zero equals the product of mass flow rate entering and specific enthalpy entering minus the product of mass flow rate exiting and specific enthalpy exiting plus the heat transfer rate exiting plus another heat transfer rate.

The product of mass flow rate entering and the difference between specific enthalpy exiting and entering equals the sum of the heat transfer rate exiting and another heat transfer rate, assuming no water is involved.

0.3 times the product of mass flow rate entering and the integral from temperature T2 to T1 of the specific heat capacity with respect to temperature plus the product of mass flow rate entering and the difference in pressure equals the heat transfer rate exiting.

For boiling liquid (water), the entering temperature is 70 degrees Celsius, referring to table A-2, the mass flow rate is 0.3119 kilograms per second. The specific enthalpy at the liquid phase is 292.98 kilojoules per kilogram, and at the gas phase, it is 2626.8 kilojoules per kilogram.

The exiting temperature is 100 degrees Celsius, referring to table A-2, the mass flow rate is 1.0149 kilograms per second. The specific enthalpy at the liquid phase is 419.04 kilojoules per kilogram, and at the gas phase, it is 2676.1 kilojoules per kilogram.

For the entire system, the equation for the rate of change of energy with respect to time is the sum of the product of mass flow rate entering and specific enthalpy entering plus the sum of heat transfer rates.

Zero equals the product of mass flow rate entering and the difference between specific enthalpy entering and exiting, considering only the system.

The product of mass flow rate entering and the difference between specific enthalpy exiting and entering equals the heat transfer rate, which is equal to another heat transfer rate.

The quality factor x is 0.005.

The specific enthalpy entering is calculated as the specific enthalpy at the liquid phase plus the quality factor times the difference between the specific enthalpy at the gas phase and the liquid phase, resulting in 304.645 kilojoules per kilogram.

The specific enthalpy exiting is calculated as the specific enthalpy at the liquid phase at 100 degrees Celsius plus the quality factor times the difference between the specific enthalpy at the gas phase and the liquid phase at 100 degrees Celsius, resulting in 430.325 kilojoules per kilogram.