x_eis,2 is greater than zero.
T_g1,2 equals what?
p_g equals what?

The pressure p_g2 equals p_g1 which is 1.2885 bar.
pV equals R times T_A.
In square brackets, the volume V_A equals R times T_A divided by p_g, which equals 0.16628 kilojoules per kilogram Kelvin times (500 plus 273.15 Kelvin) divided by 1.2885 times 10 squared kiloNewtons per square meter, resulting in 0.997745 cubic meters per kilogram.

p_A times V_A equals what?
pV divided by R equals mRT divided by R.
R equals pV_A divided by T at 0 degrees Celsius times m_eis.
pV_0 divided by R_0 equals p.

Section 3b:
x_eis,2 equals what?

Delta Q equals Q minus W.
E equals U plus pV divided by m equals zero.
Delta U equals Q minus W.
Delta U equals Q_12 equals 1.500 Joules.
U equals U.
U_1 equals U.
Temperature T equals 0 degrees Celsius and x equals 0.6.

Table 1.

u_fest (solid internal energy) equals negative 333.4158 kilojoules per kilogram.
u_fl端ssig (liquid internal energy) equals negative 0.045 kilojoules per kilogram.
u_1 equals u_fest plus x times (u_fl端ssig minus u_fest), which equals negative 333.4158 plus 0.6 times (negative 0.045 plus 333.4158) kilojoules per kilogram, resulting in negative 133.6532 kilojoules per kilogram equals u_1.

u_2 equals u_fest plus x_2 times (u_fl端ssig minus u_fest), which equals negative 333.442 plus x_2 times (negative 0.033 plus 333.442) kilojoules per kilogram.

The mass m equals 0.1 kilograms.

m times c times (u_1 minus u_2) equals Q_12.
c times m times (u_1 minus u_2) equals Q_12 divided by m.
u_2 equals u_1 minus Q_12 divided by m.
x_2 equals (u_1 minus Q_12 divided by m minus u_fest) divided by (u_fl端ssig minus u_fest).
x_2 equals (negative 133.6532 kilojoules per kilogram minus 1.500 kilojoules per 0.1 kilogram plus 333.442 kilojoules per kilogram) divided by (negative 0.033 plus 333.442 kilojoules per kilogram).
x_2 equals 0.5542.