Energy balance around the compressor:

Steady state implies that zero equals the mass flow rate of R134a times the sum of enthalpy difference between state 2 and state 3 plus kinetic energy plus potential energy, plus the sum of heat transfer minus the work done by the compressor.

The temperature at state 2 is the temperature at state 1 minus 6 Kelvin, which equals negative 10 degrees Celsius minus 6 degrees Celsius, resulting in negative 16 degrees Celsius.

The enthalpy at state 2 is the enthalpy of fluid at negative 16 degrees Celsius plus 0.1 times the difference between the enthalpy of vaporization and the enthalpy of fluid, equaling the enthalpy at state s, which is 29.3 minus 237.74 kilojoules per kilogram (refer to Table A10).

For an adiabatic reversible process, the entropy at state g3 equals the entropy at state 2, which equals the entropy at state g8 at negative 16 degrees Celsius, resulting in 0.9298 kilojoules per kilogram Kelvin (refer to Table A10).

State 2 is superheated vapor (refer to Table A12).

By interpolating, the temperature at state 3 equals 31.33 degrees Celsius plus the ratio of the difference between the entropies at state 2 and a reference state over the difference between the entropies at two reference states, multiplied by the difference between 40 degrees Celsius and 31.33 degrees Celsius, resulting in 37.8 degrees Celsius.

Thus, the enthalpy at state 3 equals 264.15 plus the ratio of the difference between the temperature at state 3 and a reference temperature over the difference between two reference temperatures, multiplied by the difference between the enthalpies at two reference states, resulting in 271.13 kilojoules per kilogram.

Finally, the mass flow rate of R134 is calculated as 0.78 times 28 times 10 to the power of 3, divided by the difference between 27,313 and 23,237.74, resulting in 0.831 kilograms per second.