W naught, T naught.

1. Energy equation at the turbine:
- Stationary: change in energy equals zero.
- No work: heat transfer Q equals zero.
- The equation zero equals mass flow rate times the quantity of enthalpy difference between point a and point c plus half the difference of squared exit velocity and squared initial velocity, implies twice the enthalpy difference between point a and point c plus half the squared exit velocity equals half the squared initial velocity.
- The equation negative two times mass flow rate times the enthalpy difference between point a and point c plus squared exit velocity equals squared initial velocity.
- W naught equals the square root of positive two times mass flow rate times the enthalpy difference between point a and point c plus squared exit velocity.
- Enthalpy at point a equals,
- Enthalpy at point c equals enthalpy at point zero minus enthalpy at point c equals specific heat capacity times the temperature difference between T naught and T c equals negative 85.43.
- T naught equals negative 30 degrees Celsius.
- T five:
- Energy equation at the nozzle:
- Temperature at point c equals temperature at point five times the ratio of pressure at point c to pressure at point five raised to the power of gamma minus one over gamma equals 328.075 Kelvin equals 54.925 degrees Celsius.
- Pressure at point six equals 0.95 bar.
- Pressure at point five equals 0.85 bar.
- Enthalpy difference between point five and point c equals specific heat capacity times the temperature difference between T five and T c equals 109.418.

1. Energy equation at the nozzle:
- The equation zero equals mass flow rate times the quantity of enthalpy difference between point five and point c plus half the difference of squared velocity at point five and squared velocity at point six.
- Enthalpy at point zero minus enthalpy at point five equals half the difference of squared velocity at point five and squared velocity at point six implies velocity at point six equals the square root of twice the enthalpy difference between point five and point c plus squared velocity at point five.
- Equals 160 meters per second.