w_c, T_6 with a system boundary around the entire system.

The equation zero equals the mass flow rate times the difference in enthalpies h_e minus h_q plus half the difference in the squares of velocities w_e squared minus w_q squared, plus the heat transfer rate minus the work rate.

Zero equals h_e minus h_q plus half the difference in the squares of velocities w_e squared minus w_q squared.

Zero equals h_0 minus h_6 plus half the difference in the squares of velocities w_0 squared minus w_6 squared.

The equation for w_6 squared equals two times the difference in enthalpies h_0 minus h_6 plus w_0 squared.

w_6 squared equals two times the specific heat capacity at constant pressure times the difference in temperatures T_1 minus T_6 plus w_0 squared.

The state from 5 to 6 is isentropic.

The pressure p_5 equals 0.13 bar and p_6 equals 0.15 bar.

The temperature T_5 equals 431.9 Kelvin.

The ratio of T_6 over T_5 equals the ratio of pressures p_c over p_5 raised to the power of (n-1) over n, where n equals 1.4.

T_6 equals T_5 times the ratio of pressures p_c over p_5 raised to the power of 0.4 over 1.4, which equals 431.9 Kelvin times the ratio of 0.15 bar over 0.13 bar raised to the power of 0.4 over 1.4, resulting in 328.07 Kelvin.

w_6 equals the square root of two times the specific heat capacity at constant pressure times the difference in temperatures negative 36 degrees Celsius plus 273.15 Kelvin minus 328.07 Kelvin plus 200 meters squared per second squared.

w_c equals 193.5 meters per second.