The value of \( r_{\text{eis}} \) is unknown.

The value of \( x_{\text{eis}_1} \) is 0.6.

The mass of ice \( m_{\text{eis}} \) is 0.06 kilograms.

The mass of water \( m_{\text{wasser}} \) is 0.04 kilograms.

First law of thermodynamics applied to ice:

The change in internal energy \( \Delta U \) is equal to heat \( Q \) minus the work done \( \dot{W}^0 \).

The volume \( v_1 \) is equal to the mass of ice \( m_{\text{eis}} \) times the volume \( V \).

The system is stationary and closed.

The change in internal energy \( \Delta U \) is equal to \( Q - \dot{W}^0 \) which is equal to the mass of the mixture \( m_{\text{ew}} \) times \( x_2 \) times the internal energy \( u_{\text{de}_2} \) plus \( m_{\text{ew}} \) times \( (1 - x_2) \) times the internal energy \( u_{fE_2} \) minus \( m_{\text{ew}} \) times \( x_1 \) times the internal energy \( u_{\text{d}1} \) minus \( m_{\text{ew}} \) times \( (1 - x_1) \) times the internal energy \( u_{fE_1} \).

The internal energy \( u_{df12} \) is equal to \( u_{df1} \) which is -0.0415 kilojoules per kilogram, denoted as \( u_d \).

The internal energy \( u_{dfE1} \) is equal to \( u_{df2} \) which is -333.458 kilojoules per kilogram, denoted as \( u_f \).

The heat \( Q \) is equal to the mass of the mixture \( m_{\text{ew}} \) times \( x_2 \) times \( u_d \) plus \( (1 - x_2) \) times \( u_f \) minus \( x_1 \) times \( u_d \) times \( (1 - x_1) \) times \( u_f \).

The expression \( \frac{Q}{m_{\text{ew}}} + x_1 \cdot u_d + (1 - x_1) \cdot u_f \) is equal to \( x_2 \cdot u_d + u_f - x_2 \cdot u_f \).

The expression \( \frac{Q}{m_{\text{ew}}} + x_1 \cdot u_d + (1 - x_1) \cdot u_f - u_f \) is equal to \( x_2 \).

The difference \( u_d - u_f \) is calculated.

The calculation involves -1.0735 kilojoules plus 6.6 minus 0.0415 plus 0.4 minus 333.458 minus 0.0415.

The result is -333.417 plus 0.045.

The final result is 0.14325.