a) Working Fluid

**Ideal Fluid**

The specific heat at constant pressure for an ideal fluid, \( c_p^{\text{if}} \), the specific heat at constant volume for an ideal fluid, \( c_v^{\text{if}} \), and the specific heat as a function of temperature for an ideal fluid, \( c^{\text{if}}(T) \), are all equal to \( f \).

The temperature change, \( \Delta T \), is 10 Kelvin.

The enthalpy at the inlet, \( h_{\text{ein}} \), is given by \( h_f + x_D \times (h_g - h_f) \) which equals 3041.6491 kilojoules per kilogram.

The mass flow rate, \( \dot{m} \), is 0.3 kilograms per second.

The equation \( 0 = \dot{m} \times (h_{\text{ein}} - h_{\text{aus}}) + \dot{Q}_R - \dot{Q}_{\text{aus}} \) represents the energy balance.

The heat flow rate out, \( \dot{Q}_{\text{aus}} \), is given by \( \dot{m} \times (h_{\text{ein}} - h_{\text{aus}}) + \dot{Q}_R \) which equals 62.256 microwatts.

Temperatures:
1. 100 degrees Celsius
2. 70 degrees Celsius

The inlet temperature, \( T_{\text{ein}} \), is 20 degrees Celsius.

The heat flow rate from state 1 to state 2, \( Q_{R,12} \), and the heat flow rate out from state 1 to state 2, \( Q_{\text{aus},12} \), are both 35 megajoules.

The system is half open.

The change in internal energy, \( \Delta E \), is given by \( m_2 \times u_2 - m_1 \times u_1 = \Delta m_{12} \times h_e \) with the sum of heat and work terms being canceled out.

The specific enthalpy, \( h_e \), from Table A-2 at 20 degrees Celsius and \( h_f \) is 83.16 watts per kilogram.

The mass at state 2, \( m_2 \), is the initial mass, \( m_1 \), plus the change in mass, \( \Delta m_{12} \).

The mass at state 2, \( m_2 \), is 5755 kilograms.

The specific internal energy at state 1, \( u_f \), from Table A-2 at 100 degrees Celsius is 426.94 watts per kilogram.

The specific internal energy at state 2, \( u_2 \), from Table A-2 at 100 degrees Celsius is 292.55 watts per kilogram.

The equation \( m_1 \times u_2 + \Delta m_{12} \times u_2 - m_1 \times u_1 = \Delta m_{12} \times h_e \) represents the energy balance.

The equation \( m_1 \times (u_2 - u_1) = \Delta m_{12} \times (h_e - u_2) \) represents the mass balance.

The change in mass, \( \Delta m_{12} \), is calculated as \( m_1 \times \frac{u_2 - u_1}{h_e - u_2} \) which equals 3486.41 kilograms.