1. Left-hand side (LHS) and Reaction:
   - Zero equals the mass flow rate in times the difference in enthalpy between the entry and the ambient plus the heat flow rate out.
   - The heat flow rate out equals the mass flow rate times the difference in enthalpy between the ambient and the entry.
   - This equals 0.3 kilograms per second times (1407.6 kilojoules per kilogram minus 1265.4 kilojoules per kilogram).
   - This results in 42.18 kilowatts.

2. The heat flow rate out equals the heat flow rate R minus the heat flow rate out:
   - This equals 100.6 kilowatts minus 42.78 kilowatts.
   - This results in 57.82 kilowatts.

3. The heat flow rate out equals 35000 kilojoules.
4. x equals 0.065.
5. m1 equals 5755 kilograms.
6. T1 equals 273.15 Kelvin.
7. Tabulated legal system at T1.
8. The mass flow rate equals the difference between mass flow rate 2 and mass flow rate 1.
9. Mass flow rate 2 equals mass flow rate 1 plus the mass flow rate out.
10. Boiling with T2 equals 273.15 Kelvin.
11. The rate of change of energy equals mass flow rate 2 times specific internal energy 2 minus mass flow rate 1 times specific internal energy 1 equals the mass flow rate times the enthalpy in plus the heat flow rate.
12. Negative mass flow rate times specific internal energy 2 minus mass flow rate times enthalpy in equals mass flow rate times specific internal energy 1 minus mass flow rate 2 plus the heat flow rate.
13. The mass flow rate equals (mass flow rate 1 times specific internal energy 1 minus mass flow rate 2 plus the heat flow rate) divided by (specific internal energy 2 minus specific internal energy 1).
14. This equals 2755.13 kilograms.
15. Replace everything.
16. TAD 1 & 2:
    - Specific internal energy 2 at 20 degrees Celsius equals 83.56 kilojoules per kilogram.
    - Specific internal energy 2 at 70 degrees Celsius equals 293.15 kilojoules per kilogram.
17. m1 equals 5755 kilograms.
18. Q equals 25000 kilojoules.
19. Enthalpy in at 20 degrees Celsius equals 83.56 kilojoules per kilogram.