The rate of change of energy with respect to time is given by the sum of the mass flow rate in times the sum of enthalpy, kinetic energy, and potential energy for the incoming mass minus the sum of the mass flow rate out times the sum of enthalpy, kinetic energy, and potential energy for the outgoing mass plus the rate of heat added minus the rate of work done, equals zero, since the pressure remains constant.

Zero equals the mass flow rate times the difference in enthalpy between the exit and the entrance plus the rate of heat added minus the rate of heat output.

The rate of heat output equals the mass flow rate times the difference in enthalpy between the exit and the entrance plus the rate of heat added.

The rate of heat output equals the mass flow rate times the product of specific heat capacity and the temperature difference between two points plus the rate of heat added.

This equals 0.3 times the product of specific heat capacity and the temperature difference plus 100 kilowatts.

This equals 0.3 times the product of specific heat capacity and 300 plus 100 kilowatts.

The specific heat capacity at 85 degrees Celsius is calculated as 1008.2 times 0.005 divided by 350, which equals 1.005.

The specific heat capacity at 100 degrees Celsius is calculated as 1008.2 times 0.005 divided by 400, which equals 1.005.

The specific heat capacity at 300 Kelvin is calculated as the difference in specific heat capacities at 400 Kelvin and 350 Kelvin divided by the temperature difference of 50 Kelvin, which equals the difference between 1008.2 and 1005 divided by 50, resulting in 0.064.

This results in 109.077868 kilowatts, approximately equal to 109.078 kilowatts.