The average temperature \( \overline{T}_{k\#} \) is given by the integral of temperature \( T \) with respect to \( s \) from \( s_2 \) to \( s_1 \) divided by \( s_a - s_e \), which simplifies to \( \frac{T_{\text{KF ein}} - T_{\text{KF aus}}}{s_{\text{aus}} - s_{\text{ein}}} \).

The value \( s_{\text{aus}} \) at 15 degrees Celsius is 0.2245 kilojoules per kilogram Kelvin, noted as A2.

The value \( s_{\text{ein}} \) at 25 degrees Celsius is 0.3674 kilojoules per kilogram Kelvin, noted as A2.

The temperature \( T_{k\#} \) is calculated as \( \frac{T_{\text{KF ein}} - T_{\text{KF aus}}}{s_{\text{aus}} - s_{\text{ein}}} \) and results in 70 degrees Celsius.

For the next part, the equation is given as \( 0 = \dot{m}_{\text{ein}} (s_e - s_a) + \frac{\dot{Q}_{\text{aus}}}{T_{kf}} + \dot{S}_{erz} \).

The generated entropy \( \dot{S}_{erz} \) is \( \dot{m}_{\text{ein}} (s_a - s_e) - \frac{\dot{Q}_{\text{aus}}}{T_{kf}} \).

The value \( s_a \) at 100 degrees Celsius is 1.3069 kilojoules per kilogram Kelvin.

The value \( s_e \) at 70 degrees Celsius is 0.9549 kilojoules per kilogram Kelvin.

The generated entropy \( \dot{S}_{erz} \) is calculated as -0.105 kilojoules per Kelvin.

For the mass change \( \Delta m_{12} \), the equation \( \Delta m_{12} (u_2 - u_1) = \Delta m_{12} (h_1 - h_2) - Q_{\text{aus}} \) is given.

This simplifies to \( \Delta m_{12} \left( u_2 - u_1 + h_2 - h_1 \right) = -Q_{\text{aus}} \).

The mass change \( \Delta m_{12} \) is calculated as \( \frac{-Q_{\text{aus}}}{u_2 - u_1 + h_2 - h_1} = \frac{83.7 \, \text{kg}}{0.465 \, \frac{\text{kJ}}{\text{kg}}} \).

The internal energy \( u_1 \) at 20 degrees Celsius is 83.98 kilojoules per kilogram, noted as A2.

The enthalpy \( h_2 \) at 70 degrees Celsius is 232.98 kilojoules per kilogram, noted as A2.

The internal energy \( u_1 \) at 20 degrees Celsius is 83.86 kilojoules per kilogram, noted as A2.

The internal energy \( u_2 \) at 70 degrees Celsius is 232.95 kilojoules per kilogram, noted as A2.