Entropy balance for cooling fluid:

Zero equals the mass flow rate of the cooling fluid times the difference between the entropy at the inlet and the outlet plus the heat flow rate at the outlet, since the pressure does not change, this implies a reversible process.

Energy balance of the cooling fluid from cooling fluid:

Zero equals the mass flow rate of the cooling fluid times the difference between the enthalpy at the inlet and the outlet plus the heat flow rate at the outlet.

The mass flow rate of the cooling fluid times the ratio of the heat flow rate at the outlet to the difference between the enthalpy at the outlet and the inlet, since the pressure does not change, this implies a reversible process.

The average temperature T-bar equals the integral from the entropy at the outlet of the cooling fluid to the entropy at the inlet of the cooling fluid of temperature T dS, divided by the difference S2 minus S1, equals the reversible heat q_rev divided by S2 minus S1, equals the difference in enthalpy h2 minus h1 divided by S2 minus S1.

h2 minus h1 equals c times (T2 minus T1) plus v times (p2 minus p1), where c is the heat capacity of the cooling fluid.

S2 minus S1 equals c times the natural logarithm of (T2 divided by T1).

The average temperature T-bar equals c times (T2 minus T1) divided by c times the natural logarithm of (T2 divided by T1), equals (T2 minus T1) divided by the natural logarithm of (T2 divided by T1), equals 293.72 Kelvin.

T1 equals the temperature at the inlet of the cooling fluid, T2 equals the temperature at the outlet of the cooling fluid.

Back side! Task c on a separate sheet.