b) The temperature \( T_i \) is negative 10 degrees Celsius and the temperature at the evaporator \( T_{\text{evaporator}} \) is negative 16 degrees Celsius.

The pressure \( p_v \) is 3 bar and \( x_4 \) equals 0.

The enthalpy \( h_4 \) is 53.42 kilojoules per kilogram, which equals \( h_1 \) because the throttling is isenthalpic.

The temperature \( T_2 \) is negative 22 degrees Celsius.

The enthalpy \( h_2 \) is 269.45 kilojoules per kilogram, refer to Table A-11.

The enthalpy \( h_2 \) is calculated as 832 times 237.74 kilojoules per kilogram, refer to Table A-10.

**First Law of Thermodynamics:** Zero equals the mass flow rate \( \dot{m} \) times the difference \( h_2 - h_3 \) plus the compressor work \( \dot{W}_k \).

This implies that the mass flow rate \( \dot{m} \) equals the compressor work \( \dot{W}_k \) divided by the difference \( h_3 - h_2 \), which is 0.000406 kilojoules per second.

**First Law for the Compressor:** Zero equals the mass flow rate \( \dot{m} \) times the difference \( h_2 - h_3 \) minus the compressor work \( \dot{W}_k \).

**First Law for the Evaporator:** Zero equals the mass flow rate \( \dot{m} \) times the difference \( h_1 - h_2 \) plus the heat transfer \( \dot{Q}_k \).

**First Law for the Condenser:** Zero equals the mass flow rate \( \dot{m} \) times the difference \( h_3 - h_4 \) plus the heat transfer \( \dot{Q}_{ab} \).

4.c) The mass flow rate \( \dot{m} \) is 4 kilograms per hour and the average temperature \( \bar{T}_2 \) is negative 22 degrees Celsius.

The final pressure \( p_f \), pressure \( p_2 \), and mean pressure \( p_m \) are 1.2 rising to 2 bar, refer to Table A-10.

**Throttling:** Zero equals the mass flow rate \( \dot{m} \) times the difference \( h_4 - h_n \).

This implies that \( h_n \) equals \( h_4 \) which is 93.42 kilojoules per kilogram, refer to Table A-11.

This also implies that \( h_n \) is 93.42 kilojoules per kilogram at a temperature of negative 22 degrees Celsius.

The enthalpy \( h_n \) equals \( h_f \) plus \( x_n \) times the difference \( h_g - h_f \).

The quality \( x_n \) equals \( h_n - h_f \) divided by \( h_g - h_f \), which is 0.3375.