1. Left-hand side (HS):
\[
\frac{d\dot{E}}{dt} = \sum \dot{m}_i \left( h_i + \frac{c_i^2}{2} + g z_i \right) - \sum \dot{m}_e \left( h_e + \frac{c_e^2}{2} + g z_e \right) + \sum \dot{Q} - \sum \dot{W}_{\text{in}}
\]
This equation represents the rate of change of energy, where the sum of mass flow rate times the sum of enthalpy, kinetic energy, and potential energy of the incoming streams minus the same for the outgoing streams plus the sum of heat transfer minus the sum of work input.

\[
0 = \dot{m} (\dot{h}_{\text{ein}} - \dot{h}_{\text{aus}}) + \dot{Q}_e - \dot{Q}_{\text{aus}}
\]
This equation states that zero equals the mass flow rate times the difference in enthalpy between input and output plus the input heat rate minus the output heat rate.

\[
\Rightarrow \dot{Q}_{\text{aus}} = \dot{m} (\dot{h}_{\text{ein}} - \dot{h}_{\text{aus}}) + \dot{Q}_e
\]
This implies that the output heat rate equals the mass flow rate times the difference in enthalpy between input and output plus the input heat rate.

\[
\dot{h}_{\text{ein}} \text{ from TAB A-2: } \dot{h}_{\text{ein}} = 292.98 \frac{\text{kJ}}{\text{kg}}
\]
The input enthalpy from Table A-2 is 292.98 kilojoules per kilogram.

\[
\dot{h}_{\text{aus}} \text{ from TAB A-2: } \dot{h}_{\text{aus}} = 419.04 \frac{\text{kJ}}{\text{kg}}
\]
The output enthalpy from Table A-2 is 419.04 kilojoules per kilogram.

\[
\Rightarrow \dot{Q}_{\text{aus}} = 0.3 \frac{\text{kg}}{\text{s}} \left( 292.98 - 419.04 \right) \frac{\text{kJ}}{\text{kg}} + 100 \text{kJ}
\]
This implies that the output heat rate equals 0.3 kilograms per second times the difference in enthalpy between input and output plus 100 kilojoules.

\[
= 62.182 \text{kJ}
\]
The result is 62.182 kilojoules.

Values:
\[
h_{\text{ein}} \text{ from TAB A2:} \quad h_{\text{ein}} = 83.896 \frac{\text{kJ}}{\text{kg}}
\]
The input enthalpy from Table A2 is 83.896 kilojoules per kilogram.

\[
\Rightarrow m_{\text{ges,1}} (u_2 - u_1) + c_{\text{sm,2}} u_2 = c_{\text{sm,2}} h_{\text{ein}} + Q_R
\]
This implies that the total mass times the difference in internal energy plus the specific mass flow rate times the internal energy equals the specific mass flow rate times the input enthalpy plus the heat transfer.

\[
\Rightarrow c_{\text{sm,2}} = \frac{m_{\text{ges,1}} (u_2 - u_1) - Q_R}{h_{\text{ein}} - u_2}
\]
This implies that the specific mass flow rate equals the total mass times the difference in internal energy minus the heat transfer divided by the difference between the input enthalpy and the internal energy.

\[
= \frac{3928.8}{3923.45 \text{ kg}}
\]
The result is the division of 3928.8 by 3923.45 kilograms.