The mass flow rate times the sum of the enthalpy at the exit and half the square of the exit velocity equals the mass flow rate times the sum of the enthalpy at the entrance and half the square of the entrance velocity.

Table A-22

The enthalpy at the exit equals

The mass flow rate times the difference in enthalpy between the exit and entrance plus half the difference of the squares of the exit and entrance velocities equals zero.

The difference in enthalpy between the exit and entrance equals the specific heat at constant pressure times the difference in temperature between T2 and T1, which equals 1.006 times the difference between 526.948 Kelvin and 431.9 Kelvin, resulting in 95.58 kilojoules per kilogram.

T1 equals 431.9 Kelvin.

T2

The ratio of T2 to T1 equals the ratio of pressure P2 to P1 raised to the power of (gamma minus one) divided by gamma.

T2 equals T1 times 1.22.

This results in T2 equaling 526.948 Kelvin, which is also T6.

The mass flow rate times the sum of 95.58 kilojoules per kilogram plus half the difference between 220 meters per second squared and the square of the entrance velocity equals zero.

Half the square of the entrance velocity equals 95580 Joules per kilogram plus 24200 Joules per kilogram.

The ratio of T6 to T5 equals the ratio of pressure P6 to P5 raised to the power of (n minus one) divided by n.

The ratio of T6 to T5 equals the ratio of 0.191 to 0.5 raised to the power of 0.4 divided by 1.4.

T6 equals T5 times 0.759.

This results in T6 equaling 337.81 Kelvin.

The mass flow rate times the difference in enthalpy between the exit and entrance plus half the difference between the squares of the exit and entrance velocities equals zero.

The difference in enthalpy between the exit and entrance equals 104.71.

Half the square of the entrance velocity equals 104710 Joules per kilogram plus half of 4200 Joules per kilogram.

This results in half the square of the entrance velocity equaling 128910 Joules per kilogram.

The square of the entrance velocity equals 257820 Joules per kilogram.

The entrance velocity equals 507.76 meters per second.

Half the square of the entrance velocity equals 119780 Joules per kilogram.

The square of the entrance velocity equals 239560 Joules per kilogram.

The entrance velocity equals 489.449 meters per second.