The change in energy, Delta E, equals the mass times the specific internal energy of water minus the mass times the specific internal energy of hydrogen plus the gravitational potential energy, which is canceled out, equals zero.

The energy at state 2 minus the energy at state 1 equals heat added minus work done, which equals the change in energy, where work done, W, equals zero.

The temperature at state 2, Tg2, is 0.003 degrees Celsius, which equals the temperature at equilibrium, Tewz.

The energy at state 1, E1, equals the mass times the specific internal energy of water minus the mass of ice plus the specific internal energy of hydrogen plus the specific internal energy of another component, mFH, times x, equals negative 333.458 kilojoules per kilogram times 0.6 kilograms per kilogram plus 0.003 times 0.116 kilojoules per kilogram.

The energy of water at state 1, E1wasser, equals negative 20.00028 kilojoules per kilogram.

The energy of water at state 2, E2wasser, equals the specific internal energy at the melting point of ice at 0.003 degrees Celsius times (1 minus x) plus the specific internal energy of ice at 0.003 degrees Celsius times x.

The change in energy of ice, Delta Eeis, equals the energy of gas at state 2 minus the energy of gas at state 2, equals the mass times the difference in specific internal energy of gas from state 2 to state 1, equals the specific heat at constant volume times the change in temperature, equals negative 389.637 kilojoules per kilogram.

The change in energy of gas, Delta Egas, equals the pressure from state 1 to state 2, P1,2, equals 4500 times gamma.

The energy of water at state 2, E2wasser, equals the heat added minus the change in energy of gas plus the energy of water at state 1, equals the specific internal energy at the melting point of ice raised to the power of x minus x times the specific internal energy at the melting point of ice raised to the power of x plus the specific internal energy of ice raised to the power of x.

x equals the fraction of (heat added minus the change in energy of gas plus the energy of water at state 1 minus the specific internal energy at the melting point of ice raised to the power of x) divided by (the specific internal energy of ice raised to the power of x minus the specific internal energy at the melting point of ice raised to the power of x).