Zero equals the mass flow rate times the difference between the enthalpy at the inlet and the enthalpy at the outlet plus the heat flow rate out.

This equals the mass flow rate times the difference between the enthalpy at 70 degrees Celsius and the enthalpy at 60 degrees Celsius plus the heat flow rate out.

One heat sink at the cooling jacket:

Zero equals the mass flow rate times the difference between the enthalpy at 288.15 Kelvin and the enthalpy at 298.15 Kelvin plus the heat flow rate out.

The heat flow rate out equals the mass flow rate of the cooling fluid times the difference between the enthalpy at 298.15 Kelvin and the enthalpy at 288.15 Kelvin.

This equals the mass flow rate of the cooling fluid times the specific heat capacity times the difference between 298.15 Kelvin and 288.15 Kelvin.

One heat sink at the reactor:

Zero equals the mass flow rate times the difference between the enthalpy at the inlet and the enthalpy at the outlet plus the heat flow rate at the reactor minus the heat flow rate out.

The enthalpy at the inlet equals 292.98 plus 0.005 times the difference between 2626.8 and 292.98, from table A-.

This equals 304.64 kilojoules per kilogram.

The enthalpy at the outlet equals 419.04 plus 0.005 times the difference between 2676.1 and 419.04, from table A-.

This equals 430.325 kilojoules per kilogram.

The heat flow rate out equals 0.3 kilograms per second times the difference between 304.64 and 430.325 kilojoules per kilogram plus 100 kilowatts.

This equals 62.2945 kilowatts.