Q equals the mass flow rate times the quantity of the enthalpy at the exit minus the enthalpy at the entrance plus half the difference of the square of the velocity at the exit and the square of the velocity at the entrance, minus the reversible work.

The difference in enthalpy between the exit and entrance is equal to the zero subscript specific heat at constant pressure times the difference in temperature between T5 and T6, which equals 104.448 kilojoules per kilogram.

The temperature Tc equals the ratio of the pressure at the reference state to the pressure at state 5 raised to the power of (k minus 1) divided by k, times the temperature at state 5, which equals 328.0746969 Kelvin.

k equals 1.4.

The sum of the actual work and the reversible work equals the mass flow rate times the gas constant times the temperature difference between T5 and T6 divided by (1 minus the polytropic efficiency), which equals 74.608 kilojoules per kilogram.

The gas constant R equals the specific heat at constant pressure minus the specific heat at constant volume, which equals 0.297987541.

The specific heat at constant volume equals the specific heat at constant pressure divided by k, which equals 0.714879 kilojoules per kilogram Kelvin.

Q equals the enthalpy at the exit minus the enthalpy at the entrance plus half the square of the velocity at the exit minus half the square of the velocity at the entrance minus the reversible work.

The velocity at the entrance equals the square root of two times the quantity of the enthalpy at the exit minus the enthalpy at the entrance plus half the velocity at the exit minus the reversible work, which equals 220.13359 meters per second.