a) Water in Food Products

A table with three columns and four rows, including the header row. The headers of the columns are 'p', 'T', and an unnamed column. The entries in the table are as follows:
- Row 1: p1 equals p2, greater than Ti.
- Row 2: p2 equals p3, Ti.
- Row 3: p3 is less than f(T,p), Ti.

Graphical Descriptions

First Graph:
The first graph is a pressure-temperature (p-T) diagram. The x-axis is labeled T in degrees Celsius and the y-axis is labeled p in millibar. The y-axis has a logarithmic scale with values marked at 0.1, 1, and 10.
- There is a curve starting from the bottom left, labeled "Water", which rises steeply and then levels off as it moves to the right.
- Another curve, labeled "Ice", starts from the bottom left and rises more gently, intersecting the "Water" curve at a point labeled "Triple Point".
- From the "Triple Point", a line extends horizontally to the right, labeled "Steam".
- The graph is divided into three regions: "Ice" below the "Water" curve, "Water" between the "Water" and "Steam" curves, and "Steam" above the "Steam" curve.

Second Graph:
The second graph is another pressure-temperature (p-T) diagram. The x-axis is labeled T in degrees Celsius and the y-axis is labeled p in millibar.
- The y-axis has values marked at 1 and 5.
- There is a curve starting from the bottom left, labeled "Water", which rises steeply and then levels off as it moves to the right.
- Another curve, labeled "Liquid", starts from the bottom left and rises more gently, intersecting the "Water" curve at a point labeled "Triple Point".
- From the "Triple Point", a line extends horizontally to the right, labeled "Isotherm".
- The graph is divided into three regions: "Water" below the "Liquid" curve, "Liquid" between the "Liquid" and "Steam" curves, and "Steam" above the "Steam" curve.
- Points labeled 1, 2, and 3 are marked on the graph, with point 1 in the "Steam" region, point 2 on the "Isotherm" line, and point 3 in the "Water" region.