The equations are as follows:

1. Zero equals the mass flow rate times enthalpy plus heat flow rate minus the work output.
2. Zero equals the mass flow rate times enthalpy plus heat flow rate minus work.
3. Work equals the mass flow rate times the difference between enthalpy at state two and enthalpy at state three.
4. The mass flow rate equals the work divided by the difference between enthalpy at state two and enthalpy at state three.
5. Enthalpy at state two equals the saturation enthalpy at temperature equal to Phi.
6. For an isentropic process, entropy at state three equals entropy at state two.
7. The ratio of pressure at state three to pressure at state two raised to the power of (n-1) over n equals the ratio of temperature at state three to temperature at state two, which implies that temperature z equals temperature at state three times the ratio of pressure at state two to pressure at state three raised to the power of (n-1) over n.

Additionally, the text in German translates to: "the cycle is stopped because it is no longer being compressed."

Graphical Content Description:
There is a graph on the right side of the page with a horizontal axis and a vertical axis, both labeled with variables that are not clearly visible. The graph features a curve that starts from the bottom left corner, rises steeply, and then levels off as it moves to the right. Several points on the curve are marked and connected by dashed lines to the axes, indicating specific values. Near the top of the page, there is a small diagram that appears to be a schematic representation of a physical system, including several components connected by lines, but the details are not clearly visible.