Zero equals the mass flow rate times enthalpy at state one plus one half the velocity squared at state one evaluated at isobaric conditions.

Zero equals negative mass flow rate times the difference in enthalpy between state zero and state six plus one half the square of angular velocity at state one minus one half the square of angular velocity at state six, which implies negative mass flow rate times the specific heat capacity at constant pressure for gas times the temperature difference between state zero and state six plus one half the square of angular velocity at state zero minus one half the square of angular velocity at state two.

One half the square of angular velocity at state one minus one half the square of angular velocity at state two equals negative specific heat capacity at constant pressure for gas times the temperature difference between state zero and state six.

Angular velocity at state one equals the square root of the square of angular velocity at state zero minus two times the specific heat capacity at constant pressure times the temperature difference between state zero and state six.

Angular velocity at state one equals 200.48 meters per second.

The product of mass, gas constant, and temperature equals pressure times volume.

The product of mass flow rate, gas constant, and temperature at state one equals the ratio of mass times gas constant times temperature at state two over volume at state two evaluated at isobaric conditions times pressure at state zero times the ratio of volume at state one over temperature at state zero.

The ratio of temperature at state six over temperature at state zero equals the ratio of pressure at state six over pressure at state zero raised to the power of (n-1) over n, implying temperature at state zero equals temperature at state six equals 340.

The ratio of temperature at state six over temperature at state five equals the ratio of pressure at state six over pressure at state five raised to the power of (n-1) over n, implying temperature at state six equals temperature at state five times the ratio of pressure at state six over pressure at state five raised to the power of (n-1) over n equals 328.07 Kelvin.

Zero equals the mass flow rate times enthalpy at state six plus the mass flow rate times exergy at state zero minus work.

Work at state zero equals the mass flow rate times the difference in enthalpy between state five and state six plus one half the square of angular velocity at state five minus one half the square of angular velocity at state six.

The specific heat capacity at constant pressure times the temperature difference between state five and state six equals one half the square of angular velocity at state six minus one half the square of angular velocity at state five, implying angular velocity at state six equals the square root of two times the specific heat capacity at constant pressure times the temperature difference between state five and state six plus one half the square of angular velocity at state five equals 220.47 meters per second.

Adiabatic and reversible implies isentropic, hence entropy at state six equals entropy at state five.

Zero equals the integral from temperature at state five to temperature at state six of the natural logarithm of the ratio of temperature at state six over temperature at state five times the specific heat capacity at constant pressure minus the gas constant times the natural logarithm of the ratio of pressure at state six over pressure at state five.

This implies temperature at state five equals temperature at state six.