The left graph is a Temperature versus Entropy diagram. The x-axis is labeled as Entropy (S) and the y-axis is labeled as Temperature (T). It includes several curves and lines:
- A black curve starts from the origin and curves upwards to the right.
- A blue curve starts from the origin, curves upwards, and then sharply turns downwards.
- A straight black line with a negative slope intersects the blue curve.
- There is a point labeled \(P_0\) on the straight black line.
- A vertical blue line extends from the x-axis to the intersection point of the blue curve and the straight black line.

The right graph is also a Temperature versus Entropy diagram with the x-axis labeled as Entropy (S) and the y-axis labeled as Temperature (T). It includes:
- A straight line with a positive slope.
- A blue curve starts from the origin, curves upwards, and then sharply turns downwards.
- A point labeled \(P_0\) on the straight line.
- A vertical blue line extends from the x-axis to the intersection point of the blue curve and the straight line.

For Problem 2a, the diagram is a Temperature versus Entropy graph. The x-axis represents entropy (S) and the y-axis represents temperature (T). The graph has several points labeled:
- Point 1 is at the bottom left.
- Point 2 is slightly to the right and above point 1.
- Point 3 is further to the right and above point 2.
- Point 4 is to the right of point 3.
- Point 5 is above point 4.
- Point 6 is to the left of point 5.

The curves connecting these points are:
- A curve from point 1 to point 2.
- A curve from point 2 to point 3.
- A curve from point 3 to point 4.
- A curve from point 4 to point 5.
- A curve from point 5 to point 6.

There is a vertical line labeled "C" between points 5 and 6. The region between points 1, 2, and 3 is shaded with diagonal lines. The region between points 3, 4, and 5 is shaded with horizontal lines. The region between points 5 and 6 is shaded with vertical lines.