d) Ice content state 2

Energy balance around the upper chamber

The work done, W_v12, is equal to 1.4 times 10 to the power of 5 Pascals times (1.104 minus 3.414) times 10 to the power of negative 3 cubic meters per second, which equals negative 285.12 Joules.

The heat transfer, Q_12^EW, is equal to the mass flow rate, 0.0034 kilograms per second, times the difference in internal energy per unit mass, 3.615 kilojoules per kilogram, minus the work done, W_12, plus 0.7857 times 5, which equals 1.3676 Joules.

e) The change in energy, Delta E, equals the change in internal energy, Delta U, which is equal to Q_12^EW minus W_12^EW.

The work done, W_v12, is zero.

The change in internal energy, Delta U, equals the mass times the difference in specific internal energy between state 2EW and state 1EW, which equals Q_12EW. Therefore, U_2EW equals Q_12EW divided by the mass plus U_1EW.

U_2EW equals U_PE plus (1.4 times h_1 plus x_2 times (U_2S minus U_PE)).

Rearranged for x_2 after substitution,

x_2 equals Q_12EW divided by (m times h_EW) plus (U_1EW minus U_PE) divided by (U_2S minus U_PE).

Aufgabe 3 (Task 3)

X_2 equals (0_Meq minus 200.08 times 10 to the power of negative 3 cubic meters per kilogram plus 0.033 times 10 to the power of negative 3 cubic meters per kilogram) divided by ((-333.648 plus 0.033) times 10 to the power of negative 3 cubic meters per kilogram).

X_2 equals 0.5589, equivalent to 55.89 percent.

Equals 55.8 percent.

Equals 0.1558.

EWA AB #1

U_1EW equals U_id(1EW) plus X_1 times (u_0(1EW) minus u_id(1EW)).

P_1EW equals P_amb plus (mK times g divided by A_K) equals 1.14 bar.

U_1EW equals negative 0.0645 cubic meters per kilogram plus 0.60 times (negative 333.648 cubic meters per kilogram plus 0.0645 cubic meters per kilogram).

Equals negative 200.08 cubic meters per kilogram.