In the center, there is a framed box containing an image named "house.png" with a label 'Q' below it.

The rate of change of energy with respect to time is equal to the rate of heat flow plus the sum of heat minus the sum of work.

The change in internal energy, Delta U, is equal to Q.

The change in specific internal energy, Delta u, is equal to q.

The specific heat q is calculated as Q12 divided by mass m, which equals 1500 Joules divided by 0.1 kilograms, resulting in 15000 Joules per kilogram, which is equivalent to 15 kilojoules per kilogram.

The specific internal energy at state 2 minus the specific internal energy at state 4 is 15 kilojoules per kilogram.

The specific internal energy at state 2 is equal to 15 kilojoules per kilogram plus the specific internal energy at state 4.

For state 1, the pressure p is 1.1 bar, the temperature Tf is 0 degrees Celsius, and the quality x1 is 0.6.

The specific internal energy at state 1, u1, is calculated as x1 times the specific internal energy of the solid phase plus (1 minus x1) times the specific internal energy of the liquid phase, which equals 0.6 times -333.458 plus 0.4 times -3.045, as per Table 1.

The specific internal energy at state 1 is -200.0928 kilojoules per kilogram.

The specific internal energy at state 2 is 15 kilojoules per kilogram minus 200.0928 kilojoules per kilogram, resulting in -185.0928 kilojoules per kilogram.

The fraction of ice at state 2, XEis,2, is calculated.

The fraction of ice times the specific internal energy of the solid phase plus (1 minus the fraction of ice) times the specific internal energy of the liquid phase equals -185.0928.

The fraction of ice times the difference between the specific internal energies of the solid and liquid phases minus 185 equals the specific internal energy of the liquid phase.

The fraction of ice, XEis, is calculated as (-185.0928 minus the specific internal energy of the liquid phase) divided by (the specific internal energy of the solid phase minus the specific internal energy of the liquid phase), which simplifies to (-185.0928 plus 0.045) divided by (-333.458 plus 0.045).

The fraction of ice at state 2, XEis,2, is 0.555.