- Diagram description: The diagram is a control volume with mass and energy flows. The control volume is a rectangle with four arrows entering and leaving it. On the left side, there is an arrow labeled with mass flow rate (m dot) entering, subscripted with T_i. On the right side, there is an arrow labeled with mass flow rate (m dot) leaving, subscripted with m. On the top side, there is an arrow labeled with heat flow rate (Q dot subscript k) entering. On the bottom side, there is an arrow labeled with m_R leaving, subscripted with T_1. The pressure on the left side is labeled as p_2 equals p_1, and the temperature on the right side is labeled as T_2.

- The symbols m dot and m dot are mentioned.

- The symbol Q dot subscript k is mentioned.

- The symbols m dot subscript R and T_1 are mentioned.

- The equation p_2 equals p_1 is provided.

- The symbols for kinetic energy rate (E dot subscript kin) and potential energy rate (E dot subscript pot) are mentioned.

- The equation for the rate of change of energy, dE/dt, equals the sum of the mass flow rate in (m dot subscript in) times (h plus v squared over 2 plus g times z) plus the sum of heat flow rate (Q dot) minus the sum of work rate (W dot).

- The equation zero equals m dot times the sum of m dot times h plus Q dot subscript k.

- The equation for Q dot subscript k equals m dot times (h subscript aus minus h subscript ein).

- The equation for the mass of R134a, M subscript R134a, equals Q dot subscript k divided by (h subscript aus minus h subscript ein).