The rate of change of entropy S with respect to time t is zero, which equals the mass flow rate m dot times the difference in entropy between the exit and the ambient (s_e minus s_a) plus the difference in heat flow rate out and heat flow rate R divided by the average temperature T bar, which equals the negative of the generated entropy rate S dot erz.

The generated entropy rate S dot erz equals the mass flow rate m dot times the difference in entropy between the ambient and the exit (s_a minus s_e) plus the difference in heat flow rate R and heat flow rate out divided by the average temperature T bar.

From Table A2:
The entropy at the exit at 70 degrees Celsius equals:
The enthalpy difference between the gas and liquid phase plus x times the enthalpy difference between the gas and liquid phase, which leads to x equals the difference between the equilibrium enthalpy and the liquid phase enthalpy divided by the difference in enthalpy between the gas and liquid phase, which equals 2333.8 kilojoules per kilogram minus 297.88 divided by 2626.8 minus 2329.38, resulting in x equals 0.874.

The entropy of vapor at the inlet S_vap,ein equals the entropy at the liquid phase S_f plus x times the difference in entropy between the gas and liquid phase (S_g minus S_f), which equals 0.95 kilojoules per kilogram Kelvin plus 0.824 times (7.755 minus 0.95 kilojoules per kilogram Kelvin), resulting in 6.1888 kilojoules per kilogram Kelvin.

The enthalpy of vapor at 100 degrees Celsius equals 2257.0 kilojoules per kilogram.
x equals the difference between the vapor enthalpy and the liquid phase enthalpy divided by the difference in enthalpy between the gas and liquid phase, resulting in x equals 0.8143.

The entropy of vapor at the outlet at 100 degrees Celsius equals the entropy at the liquid phase plus x times the difference in entropy between the gas and liquid phase, which equals 1.3069 plus 0.814 times (7.3549 minus 1.3069), resulting in 6.2298 kilojoules per kilogram Kelvin.

The generated entropy rate S dot erz equals 0.3 kilograms per second times the difference in entropy between the inlet and outlet vapor plus the sum of 100 kilojoules per second and 76.98 kilojoules per second divided by 357.9 Kelvin, resulting in 0.6948 kilojoules per second Kelvin.