Energy balance on the separate system:

Zero equals mass flow rate times the quantity of enthalpy at point zero minus enthalpy at point six plus one half times the difference of the square of velocity at point zero and the square of velocity at point six.

Two times the difference of enthalpy at point six and enthalpy at point zero equals the difference of the square of velocity at point zero and the square of velocity at point six.

Velocity at point six equals the square root of the difference of the square of velocity at point zero minus two times the difference of enthalpy at point six and enthalpy at point zero.

The difference of enthalpy at point six and enthalpy at point zero equals the specific heat at constant pressure times the difference of temperature at point zero and temperature at point six.

The ratio of temperature at point six to temperature at point zero equals the ratio of pressure at point six to pressure at point zero raised to the power of k minus one over k.

Temperature at point six equals 328.07 Kelvin.

The change in static energy equals mass flow rate times the quantity of velocity at point six minus enthalpy at point zero minus temperature at point zero prime times the difference of entropy at point six and entropy at point zero plus pressure at point zero prime times the difference of specific volume at point six and specific volume at point zero.

Equals the difference of temperature at point six and temperature at point zero times specific heat at constant pressure minus temperature at point zero times the quantity of specific heat at constant pressure times the natural logarithm of the ratio of temperature at point six to temperature at point zero minus the gas constant times the natural logarithm of the ratio of pressure at point six to pressure at point three plus pressure at point zero prime times the difference of specific volume at point six and specific volume at point zero.

Equals 57.4 minus 82.00.

Equals pressure at point zero prime times the difference of specific volume at point six and specific volume at point zero (from A-22).

The sum of external energy plus the sum of resistive energy minus the sum of the product of resistive work and the partial derivative of resistive velocity with respect to time minus resistive kinetic energy.

Implies that the rival equals equilibrium equals the quantity of one minus the ratio of temperature at point zero to temperature times heat minus the quantity of the sum of internal work minus pressure at point zero prime times the difference of resistive specific volume and specific volume at point zero.