Ideal Gas Equation:
p times v equals R times T.

Polytropic Temperature Ratio (reversible, adiabatic process line):
T6 over T5 equals (p6 over p5) raised to the power of (n minus 1) over n.

This implies T6 equals T5 times (pc over p5) raised to the power of (n minus 1) over n.

This equals 328.1 Kelvin.

The Energy Equation for the path between (Process 5-6):
0 equals m dot times (h5 minus h6) plus (w5 squared minus w6 squared) over 2 minus W dot 5.

With W dot s equals negative integral from 5 to 6 of v dp plus (w6 squared minus w5 squared) over 2.

This equals negative (n times R times (T6 minus T5) divided by (1 minus n)) plus (w6 squared minus w5 squared) over 2.

This equals n R times (T5 minus T6 over 1 minus n) plus (w5 squared minus w6 squared) over 2.

0 equals h5 minus h6 plus (w5 squared minus w6 squared) over 2 minus (n R times (T6 minus T5) over 1 minus n).

Change in specific internal energy for the stretch equals ex, str minus ex, str, 0 divided by int R equals cp over cp, eff minus cp, eff over R minus 0.287 L/kgK.

This equals h6 minus h0 minus T0 times (s6 minus s0) plus w6 squared over 2 minus (h5 minus h0 minus T0 times (s5 minus s0) plus w5 squared over 2).

This equals h6 minus h0 minus T0 times (s6 minus s0) plus w6 squared over 2 minus w5 squared over 2.

This equals cp, eff times (T6 minus T0) minus T0 times (cp, eff times ln (T6 over T0) minus R times ln (p6 over p0)) plus w6 squared over 2 minus w5 squared over 2.

This equals (T6 minus T0) over kg.

This equals 76.26 Joules per kg.

e2, loss equals T0 times s, erg.

The entropy balance yields:

0 equals s dot ingen (s0 minus s0) plus q dot A over TA plus s dot erg.

This implies s dot erg (s0 equals s0) minus qA over TB.

This equals cp, eff times ln (T0 over T0) minus R times ln (p0 over p0) minus qn over TA.

e2, loss equals T0 times s, erg.