Zero equals the mass flow rate times the difference between the enthalpy at exit and the enthalpy at entrance, plus the heat transfer rate out divided by the condenser temperature, plus the entropy generation rate.

The entropy generation rate equals the heat transfer rate out divided by the high temperature minus the heat transfer rate out divided by the condenser temperature.

The entropy generation rate equals the heat transfer rate out times the difference between the reciprocal of the high temperature and the reciprocal of the condenser temperature.

The entropy generation rate equals 62.16 kilojoules per second times the difference between the reciprocal of 373.15 Kelvin and the reciprocal of 293.12 Kelvin.

This results in negative 0.0455 kilojoules per second per Kelvin.

Graphical Descriptions:

1. There is a horizontal line with a point labeled "O" on the left end. To the right of "O", there is a horizontal arrow pointing to the right, labeled with the mass flow rate times the difference between the enthalpy at exit and the enthalpy at entrance. Above this arrow, there is a vertical arrow pointing upwards labeled with the heat transfer rate out. To the right of this, there is another vertical arrow pointing upwards labeled with the entropy generation rate.

2. There is a box divided into two equal parts. The left part is labeled "293.12 K" and has a smiley face inside. The right part is labeled with the heat transfer rate out and has an upward arrow inside. Below the box, the description is incomplete.