Energy balance on the reaction mixture:
The derivative with respect to time of the sum of mass flow rate times specific enthalpy for each component i plus the sum of molar flow rate times specific internal energy for each component j equals the sum of the product of mass flow rate and the derivative of specific enthalpy for each component i.

This implies that zero equals the mass flow rate in times specific enthalpy in minus mass flow rate out times specific enthalpy out plus the heat flow rate into the reactor minus the heat flow rate out.

The mass flow rate in equals the mass flow rate out.

This implies that the heat flow rate out equals the mass flow rate in times the difference between specific enthalpy in and specific enthalpy out plus the heat flow rate into the reactor.

The specific enthalpy in equals the specific enthalpy at 70 degrees Celsius minus the specific enthalpy out equals 292.88 kilojoules per kilogram, referring to table A2 at 70 degrees Celsius.

The specific enthalpy out equals the specific enthalpy at 100 degrees Celsius minus the specific enthalpy out equals 415.04 kilojoules per kilogram, referring to table A2 at 110 degrees Celsius.

This implies that the heat flow rate out equals 62.192 kilowatts.

Energy balance on the reaction mixture:

The change in energy equals the change in mass times the difference in specific internal energy equals the total mass at state 1 times specific enthalpy at state 1 plus the heat flow rate into the reactor minus the heat flow rate out.

This implies that the change in specific internal energy equals the total mass at state 1 times specific enthalpy at state 1 plus the heat flow rate into the reactor minus the heat flow rate out divided by the difference in specific internal energy, with the heat flow rate into the reactor equal to the heat flow rate out.

For specific enthalpy at state 1:
The specific enthalpy at state 1 equals the specific enthalpy of the fluid at 100 degrees Celsius plus the dryness fraction times the difference between the specific enthalpy of the gas and the fluid at 100 degrees Celsius equals 419.04 plus 0.005 times (2654.1 minus 419.04) equals 430.325 kilojoules per kilogram.

For specific internal energy at state 1:
The specific internal energy at state 1 equals the specific internal energy of the fluid at 100 degrees Celsius plus the dryness fraction times the difference between the specific internal energy of the gas and the fluid at 100 degrees Celsius equals 418.921 plus 0.005 times (2506.5 minus 418.9) equals 429.377 kilojoules per kilogram.

For specific internal energy at state 2:
The temperature at state 2 is 70 degrees Celsius.