w_6 equals what? T_G equals what?

w_s equals 200 meters per second, p_5 equals 0.5 bar, T_5 equals 433.9 Kelvin, p_6 equals p_0 equals 0.151 bar.

The equation zero equals m dot times (s_c minus s_a) plus Q dot over m dot plus s_e over 2 simplifies to zero equals zero plus zero plus zero, assuming adiabatic and reversible conditions.

s_c equals s_a.

Polytropic temperature ratio: n equals 1.1. T_2 over T_1 equals (p_2 over p_1) raised to the power of (n minus 1) over n.

T_G equals T_5 times (p_6 over p_5) raised to the power of (n minus 1) over n, which calculates to 433.9 Kelvin times (0.151 bar over 0.5 bar) raised to the power of (1.1 minus 1) over 1.1, resulting in 328.07 Kelvin.

Energy balance: zero equals m dot times (h_e minus h_a) plus w_e squared over 2 minus w_a squared over 2 simplifies to zero equals h_e minus h_a plus w_e squared over 2 minus w_a squared over 2.

w_a equals the square root of 2 times (h_e minus h_a) plus w_e squared.

h_e minus h_a equals c_p^g times (T_5 minus T_0), h_5 minus h_a equals c_p^g times (431.3 Kelvin minus 328.07 Kelvin) equals 1.006 kilojoules per kilogram Kelvin times 103.23 Kelvin equals 103.498 kilojoules per kilogram.

w_e equals 270 meters squared per second squared.

w_a equals the square root of 2 times 103.498 kilojoules per kilogram plus (270 meters per second squared) squared over 100.

w_a equals the square root of 2 times 103.498 kilojoules per kilogram times 1000 plus (270 meters per second) squared, resulting in 507.294 meters per second.

e_dot_exver equals what? e_dot_exver equals T_0 times s_dot_verz. Zero equals m dot times (s_0 minus s_6) plus Q_j over T_j plus s_dot_verz. s_dot_verz equals m dot times (s_6 minus s_0) minus Q_j over (T_j times m dot). s_dot_verz equals s_6 minus s_0 minus Q_j over T_j. s_dot_verz equals 0.303 kilojoules per kilogram Kelvin minus 1.95 kilojoules per kilogram over 1283 Kelvin equals negative 0.6257 kilojoules per kilogram Kelvin.