Energy balance for the gas:

The rate of change of energy with respect to time is equal to the heat flow rate minus the work rate input.

The change in energy is equal to the heat flow rate from state 1 to state 2 minus the work rate input.

The change in energy is equal to the internal energy at state 2 minus the internal energy at state 1, ignoring kinetic and potential energies.

The internal energy at state 2 minus the internal energy at state 1 plus the work rate input equals Q12.

Q12 equals the internal energy at state 2 minus the internal energy at state 1.

The difference in internal energy between state 2 and state 1 equals the specific heat at constant volume times the mass times the temperature difference between state 2 and state 1.

The specific heat at constant volume is 0.633 kilojoules per kilogram per Kelvin for temperatures ranging from 0 degrees Celsius to 500 degrees Celsius, which equals 316.5 kilojoules per kilogram per Kelvin.

The work rate input is the volume change work at constant pressure.

The work rate input equals the pressure times the difference in volume between state 2 and state 1.

This equals 1.401 Bar times the difference in volume between state 2 and 3.19 liters.

The initial volume, V1, is 0.00319 cubic meters.

The final volume, V2, is calculated as the mass times the specific gas constant times the temperature at state 2 divided by the pressure, which equals 0.001103 cubic meters.

The work rate input equals 140.1 kilopascals times the difference in volume between 0.001103 cubic meters and 0.00319 cubic meters.

This results in -0.285 kilojoules.

The product of the change in internal energy and mass equals the change in heat from state 1 to state 2, which is -316.5 kilojoules per kilogram times 0.00392 kilograms, equaling -1.083 kilojoules.

Q12 equals the work rate input plus the product of mass and the change in internal energy, which is -285.5 Joules minus 1083 Joules, resulting in -1367.5 Joules.