The mass flow rate of R134a is unknown.

Isobaric evaporation of R134a is considered.

The compressor work rate is 28 kilowatts.

The temperature in the evaporator is 6 Kelvin less than temperature T1, which equals 257.15 Kelvin.

Temperature T1 is unknown, but at -10 degrees Celsius, it is 263.15 Kelvin.

Energy balance over the compressor:
The equation is zero equals the mass flow rate times the difference in enthalpy (h_e minus h_a) plus the heat transfer rate, which leads to zero, indicating adiabatic conditions.

The mass flow rate is equal to the compressor work rate divided by the difference in enthalpy (h_e minus h_a), which is -0.08 kilowatts divided by (h_e minus h_a).

The enthalpy at the exit, h_e, is unknown at a temperature of -10 degrees Celsius for R134a.

h2 is equal to h_e.

From the table at -10 degrees Celsius, the enthalpy h_g is 237.94 kilojoules per kilogram, which equals h2 and h_e.

The enthalpy at the inlet, h_a, is unknown.

From Table A-11 at 8 bar pressure, the enthalpy h_f is 93.92 kilojoules per kilogram, and h_g is 269.15 kilojoules per kilogram. The process is adiabatic and reversible with no change in entropy, s1 equals s3, and s2 is unknown.

From Table A-10 at -10 degrees Celsius, the entropy s_g is 0.9238 kilojoules per kilogram Kelvin. From Table A-12 at 8 bar pressure, the entropy at saturation temperature T_sat is 0.5066, and at 40 degrees Celsius, it is 0.9379. The enthalpy at saturation is 269.15 kilojoules per kilogram, and at 40 degrees Celsius, it is 273.66 kilojoules per kilogram.

The enthalpy h3 is calculated using the formula involving differences in enthalpy and entropy at 40 degrees Celsius and saturation, multiplied by the difference in entropy between s and s at saturation, plus the enthalpy at saturation. The result is 271.33 kilojoules per kilogram.

The mass flow rate is calculated as -0.028 kilowatts divided by the difference in enthalpy (237.74 kilojoules per kilogram minus 271.33 kilojoules per kilogram), resulting in 0.8333 kilograms per second.

Energy balance over the compressor:
Zero equals the mass flow rate times the difference in enthalpy (h_e minus h_a) minus the input work rate of the compressor.

The mass flow rate is equal to the input work rate of the compressor divided by the difference in enthalpy (h_e minus h_a).

h_e equals h2, and h_a equals h3. From Table A-10 at 16 degrees Celsius, the enthalpy h_g is 237.74 kilojoules per kilogram.