T2 equals T2,1G which is 0.003 degrees Celsius, equivalent to 273.15 Kelvin.

First Law of Thermodynamics:

The change in internal energy, Delta E, equals mass times the difference in specific internal energy between state 2 and state 1, which equals the heat added Q12 minus the work done Wv,12.

The difference in specific internal energy between state 2 and state 1 equals the heat added Q12 divided by the mass m.

The specific internal energy at state 2 equals the specific internal energy at state 1 plus the heat added Q12 divided by the mass m.

The specific internal energy at state 2 equals the specific internal energy at state 1 plus Q12, leading to Q12 equals 1500 Joules.

Q12 equals negative 1.5 times u.

The specific internal energy at state 2 can be determined from Table 1.

The specific internal energy at state 2 at 0 degrees Celsius equals negative 333.05 kilojoules per kilogram.

The specific internal energy at state 2 at 0 degrees Celsius equals negative 0.045 kilojoules per kilogram.

For the equation u1, it equals (1 minus x1) times the specific internal energy of the liquid phase plus x1 times the specific internal energy of the solid phase.

u1 equals negative 200.0528 kilojoules per kilogram.

u2 equals u1 plus the heat added Q12 divided by the mass of water, leading to Q12 equals 1.5 kilojoules.

u2 equals negative 145.0528 kilojoules per kilogram.

At T2,is which is 0.003 degrees Celsius, the specific internal energy of the solid phase equals negative 333.442 kilojoules per kilogram.

The specific internal energy of the liquid phase at 0.003 degrees Celsius equals negative 0.033 kilojoules per kilogram.

u2 equals (1 minus x2) times the specific internal energy of the liquid phase plus x2 times the specific internal energy of the solid phase.

u2 minus the specific internal energy of the liquid phase equals x2 times the difference between the specific internal energy of the solid phase and the liquid phase.

x2 equals the difference between u2 and the specific internal energy of the liquid phase divided by the difference between the specific internal energy of the solid phase and the liquid phase.

x2 equals 0.555.