In the section titled "ideal fluid system," the equation presented is:
The rate of heat flow out, denoted as Q-dot-out, equals the mass flow rate, m-dot, times the specific heat capacity at constant pressure for an ideal fluid, c_if, times the difference in temperature from T1 to T2.

In the section titled "Entropy balance, stationary flow process," the equations are:
1. Zero equals the mass flow rate, m-dot, times the difference in entropy from s1 to s2, plus the heat flow rate, Q-dot, over temperature T, plus the integral of the infinitesimal heat flow, delta Q, over temperature T, where the process is isobaric.
2. The heat flow rate out, Q-out, over temperature T equals the mass flow rate, m-dot, times the difference in entropy from s2 to s1.
3. Temperature T equals the heat flow rate out, Q-out, over the mass flow rate, m-dot, times the difference in internal energy from u2 to u1.
4. The heat flow rate, Q-dot, over the temperature T_KF equals the heat flow rate out, Q-out, over the mass flow rate, m-dot, times the specific heat capacity at constant pressure for an ideal fluid, c_if, times the natural logarithm of the ratio of the product of temperature T_KF and heat flow rate out, Q-out, to temperature T1n.
5. The difference in entropy from s2 to s1 equals the integral from temperature T1n to T2 of the specific heat capacity at constant pressure for an ideal fluid, c_if, over temperature T, integrated with respect to temperature T, for an ideal fluid.
6. This integral simplifies to c_if times the natural logarithm of temperature T evaluated from T1n to T2.
7. Which further simplifies to c_if times the natural logarithm of the ratio of T2 to T1n.

The heat flow rate out, Q-dot-out, is given as 65 kilowatts.

In another section titled "Entropy balance, stationary flow process," the equations are:
1. Zero equals the mass flow rate, m-dot, times the difference in entropy from s1 to s2, plus the heat flow rate, Q-dot, over temperature T, plus temperature T times the residual entropy, S_rez, where there is no mass flow.
2. The residual entropy, S_rez, equals the heat flow rate out, Q-dot-out, over the temperature T_KF.
3. Substituting the values, the residual entropy, S_rez, equals 65 kilowatts over 255 Kelvin.
4. The residual entropy, S_rez, is calculated to be 0.22 kilowatts per Kelvin.

In the section titled "A1," under the subsection "b)," the mass flow rate, m-dot, is given by the ratio of h2, u1, h_ein from the table to h_aus.