a) Semi-open system:

The mass times the difference between internal energy at state 2 and state 1 equals the mass flow rate times the difference between enthalpy at entry and exit plus the heat flow rate at exit minus the work rate. 
The heat flow rate at exit equals the mass times the difference between internal energy at state 2 and state 1 minus the mass flow rate times the difference between enthalpy at entry and exit.
The heat flow rate at exit equals the mass times the difference between internal energy at state 2 and state 1 minus the mass flow rate times the difference between enthalpy at entry and exit (no work rate, since internal energy at entry equals internal energy at exit).

The heat flow rate at exit equals negative mass flow rate at entry times the difference between enthalpy at entry and enthalpy at exit.
The heat flow rate at exit equals 293.6 kilojoules per kilogram.
The heat flow rate at exit equals 37.818 kilowatts.

1.1.1 Semi-open system:

The change in energy equals mass at state 2 times internal energy at state 2 minus mass at state 1 times internal energy at state 1, which equals the mass flow rate times the difference between enthalpy at entry and exit plus heat minus the mass flow rate times half the square of velocity.
Negative heat plus mass flow rate times the difference between internal energy inside and outside equals mass times internal energy at state 2 equals mass flow rate times enthalpy at entry minus enthalpy at exit.
Negative heat plus mass flow rate times the difference between internal energy at state 2 and state 1 equals mass flow rate times the difference between enthalpy at entry and exit.
The mass flow rate equals negative heat plus mass flow rate times the difference between internal energy at state 2 and state 1 divided by the difference between enthalpy at entry and exit.
The mass flow rate equals negative heat plus mass flow rate times the difference between internal energy at state 2 and state 1 divided by the difference between enthalpy at entry and exit.