Section 4, R 134a includes three graphs:

Graph 1:
The first graph is a phase diagram with pressure \( P \) on the y-axis (labeled in bar) and temperature \( T \) on the x-axis (labeled in Kelvin). The graph displays three distinct regions labeled as solid, liquid, and gas. 
- The solid region is on the left side of the graph.
- The liquid region is in the middle.
- The gas region is on the right side.
There are three lines separating these regions:
- The line between solid and liquid is sloped upwards.
- The line between liquid and gas is also sloped upwards but less steeply.
- The line between solid and gas is curved and intersects the other two lines at a point labeled triple point.

Graph 2:
The second graph is another phase diagram with pressure \( P \) on the y-axis (labeled in bar) and temperature \( T \) on the x-axis (labeled in Kelvin). This graph also shows three regions labeled solid, liquid, and gaseous.
- The solid region is on the left side of the graph.
- The liquid region is in the middle.
- The gaseous region is on the right side.
There are three lines separating these regions:
- The line between solid and liquid is sloped upwards.
- The line between liquid and gaseous is also sloped upwards but less steeply.
- The line between solid and gaseous is curved and intersects the other two lines at a point labeled triple point.
Additionally, there are two points labeled \( x_1 \) and \( x_2 \) on the solid to liquid line, with a vertical arrow labeled \( i \) pointing upwards from \( x_2 \) to \( x_1 \). There is also a horizontal arrow labeled \( ii \) pointing from \( x_1 \) to a point labeled \( O \) on the liquid to gaseous line.

Graph 3:
The third graph is another phase diagram with pressure \( P \) on the y-axis (labeled in bar) and temperature \( T \) on the x-axis (labeled in Kelvin). This graph shows three regions but without labels.
- The leftmost region is separated by a line sloped upwards.
- The middle region is separated by a line sloped upwards but less steeply.
- The rightmost region is separated by a curved line.
The lines intersect at a point, forming a triple point similar to the previous graphs.