The average temperature \( \overline{T}_{kF} \) is given by the formula:
\[
\overline{T}_{kF} = \frac{\int_{a}^{e} T ds}{s_e - s_a} = \frac{\Delta h}{s_e - s_a} = \frac{h_a - h_e}{s_e - s_a}
\]
which equals 293.72 Kelvin.

Table 2 contains the following values:
- \( h_e \) at 70 degrees Celsius and \( x=0 \) is 297.28 kilojoules per kilogram.
- \( s_e \) at 70 degrees Celsius and \( x=0 \) is 1.3069 kilojoules per kilogram Kelvin.
- \( h_a \) at 90 degrees Celsius and \( x=0 \) is 419.94 kilojoules per kilogram.
- \( s_a \) at 90 degrees Celsius and \( x=0 \) is 0.941 kilojoules per kilogram Kelvin.
- \( h_{af} \) at 70 degrees Celsius is 89.34.
- \( h_e \) at 70 degrees Celsius is 48.70.
- \( s_e \) at 70 degrees Celsius is 0.185.
- \( s_a \) at 70 degrees Celsius is 0.3703.
- \( h_a \) at 25 degrees Celsius is 104.81.
- \( h_e \) at 25 degrees Celsius is 62.91.
- \( s_e \) at 25 degrees Celsius is 0.2445.
- \( s_a \) at 25 degrees Celsius is 0.3674.

In the section labeled "d)", the following information is provided:
- The Treadstor is set to 70 degrees Celsius.
- \( x = 0 \).
- It mentions a 4 mm cylinder reactor.
- The Treadstor temperature is 100 degrees Celsius.
- The inlet temperature \( T_{\text{ein}} \) is 20 degrees Celsius.
- The heat output \( Q_{\text{aus}} \) is 3.5 kilojoules per Kelvin.

For the semi-open system, the change in energy \( \Delta E \) is calculated as:
\[
\Delta E = m_1 u_2 - m_1 u_1 = \Delta m_{12} \left( h_{20°C} \right) + Q - W
\]
\[
\Delta m_{12} = \frac{m_1 u_2 - m_1 u_1 - Q}{h_{20°C}}
\]
\[
\Delta m_{12} = 574.41 \text{ kg}
\]
where:
- \( m_1 = 5757 \text{ kg} \)
- \( m_2 = m_1 + \Delta m_{12} \)
- \( Q = 35000 \text{ kJ} \)
- \( u_2 \) at 70 degrees Celsius and \( x = 0 \) is 202.945 kilojoules per kilogram.
- \( u_1 \) at 20 degrees Celsius and \( x = 0 \) is 418.94 kilojoules per kilogram.
- \( h \) at 20 degrees Celsius and \( x = 0 \) is 83.96 kilojoules per kilogram.