Energy balance around the reactor:

The rate of change of energy with respect to time is equal to the mass flow rate in times the difference in enthalpy between the inlet and the outlet plus the heat flow rate out minus the sum of work rates plus the heat flow rate due to reaction.

The heat flow rate out is equal to the mass flow rate in times the difference in enthalpy between the outlet and the inlet.

The enthalpy at the inlet, at 100 degrees Celsius and quality x equals 1, is 2626.8 kilojoules per kilogram.

The enthalpy at the outlet, at 100 degrees Celsius and input conditions, is 2257.0 kilojoules per kilogram.

The heat flow rate out is 0.3 kilograms per second times (2257.0 minus 2333.8) plus 100 kilowatts equals 76.96 kilowatts.

For the equations in the section:

The rate of change of energy with respect to time is equal to the mass flow rate from 1 to 2 times the enthalpy at the inlet plus the heat flow rate out from 1 to 2.

The difference in internal energy between state 2 and state 1 is equal to the mass flow rate from 1 to 2 times the enthalpy at the inlet minus the heat flow rate out from 1 to 2.

Negative of the sum of the total mass at state 1 plus the mass flow rate at 1 times the internal energy at state 2 minus the total mass at state 1 times the internal energy at state 1 equals the mass flow rate from 1 to 2 times the enthalpy at the inlet minus the heat flow rate out from 1 to 2.

Negative of the mass flow rate from 1 to 2 is equal to the total mass at state 1 times the internal energy at state 1 minus the total mass at state 1 times the internal energy at state 2 minus the heat flow divided by the difference between the internal energy at state 2 and the enthalpy at the inlet.

The enthalpy at the inlet, at 20 degrees Celsius and quality x equals 1, is 2538.1 kilojoules per kilogram.

The internal energy at state 1, at 105 degrees Celsius and quality x equals 1, is 2676.1 kilojoules per kilogram.

The internal energy at state 2, at 70 degrees Celsius and quality x equals 1, is 2626.8 kilojoules per kilogram.

Negative of the mass flow rate from 1 to 2 is equal to 5755 times 2676.1 minus 5755 times 2626.8 divided by 2626.8 minus 2538.1 equals 100 kilograms per second.