The mass flow rate of liquid, denoted as m-dot subscript L, equals the mass flow rate of gas, m-dot subscript gas, times the difference in enthalpy h6 minus h5, minus the power W-dot subscript s, all divided by h5.

The molar mass of liquid, M subscript L, is 28.07 grams per mole.

The mass flow rate of gas, m-dot subscript gas, equals the power W-dot subscript s divided by the product of L and H.

The entropy at state 5, s5, equals the entropy at state 6, s6.

The difference in entropy between state 5 and state 6 is zero, which equals the specific heat at constant pressure, c subscript p, times the natural logarithm of the ratio of temperature T5 to T6, minus the gas constant R divided by the molar mass of the liquid M subscript L, times the natural logarithm of the ratio of pressure P5 to P6.

This implies that the natural logarithm of the ratio of temperature T5 to T6 equals the gas constant R divided by the product of the molar mass of the liquid M subscript L and the specific heat at constant pressure c subscript p, times the natural logarithm of the ratio of pressure P5 to P6. This further implies that the ratio of temperature T5 to T6 equals the ratio of pressure P6 to P5 raised to the power of R divided by the product of M subscript L and c subscript p.

The temperature at state 6, T6, is 328.07 Kelvin.

The kinetic energy per unit mass at state 6, W6 squared divided by 2, equals the difference in enthalpy h5 minus h6 plus the kinetic energy per unit mass at state 5, W5 squared divided by 2.

The velocity at state 6, W6, is 507.24 meters per second.

The specific heat at constant pressure c subscript p times the difference in temperature T5 minus T6.