The equations provided are as follows:

1. The product of mass of e1 and the difference between half the square of velocity e2 and half the square of velocity e1 equals Q dot.

2. The ratio of internal energy e2 to mass e2 equals the sum of Q dot over mass e1 and internal energy e1, which is further simplified to internal energy e1 plus x2 times the difference between internal energy e2 and internal energy e1.

3. Internal energy e1 equals internal energy e1 plus x2 times the difference between internal energy e2 and internal energy e1.

4. Internal energy e1 equals 200 kilojoules per kilogram.

5. Negative 333.485 kilojoules per kilogram.

6. Negative 0.045 kilojoules per kilogram.

7. Pressure e2 equals the sum of initial pressure, the product of mass e1 and constant k e1 over area, and the product of mass e2 and gravitational acceleration over area.

8. Pressure e2 equals 2.9 bar.

9. The ratio of internal energy e2 to mass e2 equals the sum of the ratio of internal energy e1 to mass e1 and x2 times the difference between internal energy e2 and internal energy e1.

10. Q dot equals the sum of the product of mass e2 and the difference between internal energy e2 and internal energy e1 over mass e1, the ratio of internal energy e1 over mass e1, and the negative ratio of internal energy e2 over mass e2.

11. Q dot equals negative 0.106 kilojoules per kilogram.

12. The internal energy for Fe2 is calculated as the sum of negative 333.812 plus 333.488 divided by the difference between 4.9 and 2, which is further simplified to the product of the difference between 2.9 and 2, and 333.488 divided by the difference between 4.9 and 2, resulting in 333.533 kilojoules per kilogram.