The flow process is stationary:
Zero equals the mass flow rate times the quantity of enthalpy at exit minus enthalpy at entry plus half the difference of the square of velocity at exit and the square of velocity at entry, plus the sum of heat transfer rates minus the sum of work rates.

Negative heat transfer rate divided by the mass flow rate equals the enthalpy at temperature T5 minus the enthalpy at temperature T6 plus half the difference of the square of velocity at exit and the square of velocity at entry.

T5 equals 431.9 Kelvin.

For T6, the ratio of T6 to T5 equals the ratio of pressure at P6 to P5 raised to the power of (n minus 1) divided by n, which implies T6 equals 431.8 Kelvin times the ratio of 0.18 bar to 0.5 bar raised to the power of (1.4 minus 1) divided by 1.4.

T6 equals 328.47 Kelvin, approximately 328.08 Kelvin.

The enthalpy at T5 equals the enthalpy at 490 plus 431.9 Kelvin minus 430 Kelvin times the ratio of the enthalpy difference between 490 Kelvin and 430 Kelvin over the temperature difference 490 Kelvin minus 430 Kelvin, which equals 433.364 kilojoules per kilogram.

The enthalpy at T6 equals the enthalpy at 330 plus 328.08 Kelvin minus 325 Kelvin times the ratio of the enthalpy difference between 330 Kelvin and 325 Kelvin over the temperature difference 330 Kelvin minus 325 Kelvin, which equals 328.38 kilojoules per kilogram.

The velocity at entry equals the square of the velocity at exit minus the difference of enthalpy at T5 and enthalpy at T6 plus the heat transfer rate divided by the mass flow rate plus the square of the velocity at exit.

The mass flow rate is unknown.