The rate of change of energy with respect to time is equal to the mass flow rate times the difference in enthalpy at the inlet and outlet plus the heat flow rate at the outlet plus the heat flow rate due to radiation.

The change in energy is equal to the mass flow rate times the enthalpy at the inlet plus the heat flow rate, which equals the power flow rate.

The change in internal energy is equal to the mass flow rate times the enthalpy at the inlet plus the heat flow rate at the outlet.

The mass times the difference in specific internal energy between two states equals the heat flow rate plus the mass at state two times the sum of the enthalpy at the inlet and the heat flow rate.

The mass flow rate is equal to the negative of the heat flow rate plus the mass times the difference in specific internal energy between two states, all divided by the mass flow rate.

The result is negative thirty-five thousand plus five thousand seven hundred fifty-five kilograms.

The reduced temperature is seventy degrees Celsius.

The inlet temperature is twenty degrees Celsius.

The heat flow rate equals the heat flow rate equals the heat flow rate due to radiation.

The enthalpy at the inlet is eighty-three point thirty-six kilojoules per kilogram.

The temperature at point A is two at twenty degrees Celsius.

The reduced temperature is one hundred degrees Celsius.

The change in mass between state one and state two is negative thirty-five thousand plus five thousand seven hundred fifty-five times the difference between four hundred thirty-seven point three three five and eighty-three point five five, all divided by eighty-three point thirty-six.

The result is negative eleven thousand one hundred eighty-four point fifty-four kilograms.