The rate of change of energy with respect to time is equal to the sum of the heat flow rate minus the work flow rate into the system.

The change in internal energy is equal to the heat transferred in process 1 to 2 minus the work done on the system.

The product of specific internal energy and the difference between the final and initial specific internal energies is equal to the heat transferred in process 1 to 2 minus the work done on the system.

The product of specific internal energy at states g2 and g1 plus some other terms equals the heat transferred in process 1 to 2 minus the work done on the system.

The product of the mass of gas, specific heat at constant volume, and the temperature difference between state 2 and a reference state equals the heat transferred in process 1 to 2 minus the work done on the system.

The product of 0.00342 and 0.633 times the difference between 273.153 Kelvin and 273.15 Kelvin equals the heat transferred in process 1 to 2 minus the work done on the system.

The heat transferred in process 1 to 2 is negative 284.7 Joules.

The work done on the system is the integral of pressure with respect to volume from initial volume to final volume.

This integral simplifies to the pressure times the difference between the final and initial volumes.

This expression further simplifies to 1.401 times 10 to the power of 5 times the difference between 0.0011 cubic meters and 3.14 times 10 to the power of -3 cubic meters.

This results in negative 285.6 Joules.

The heat transferred in process 1 to 2 is equal to the heat transferred minus the work done on the system.

The final volume V2 is not specified.