Section: Energy balance for a closed system (Gas):

The change in energy, Delta E, equals Q12 minus Wu12.

The mass of the gas times the specific heat at constant volume times the temperature difference from T1g to T2g equals Q12 minus the integral from V1 to V2 of pressure times the differential volume.

Q12 equals the mass of the gas times the specific heat at constant volume times the temperature difference from Tg1 to Tg2 plus the pressure at state 2 times the gas times the volume difference from V1 to V2.

This equals negative 1.0832 kilojoules plus 1114.4 joules.

This results in 31.21 joules, with a note questioning if it should be less than zero.

The absolute value of Q12 equals 1500 joules.

Section: Energy balance for a closed system (Ice water):

The change in energy, Delta E, equals the mass of the ice water times the difference in internal energy from state 1 to state 2, which equals Q12.

The internal energy at state 1, u1, equals the internal energy of liquid water at 0 degrees Celsius plus the fraction of ice times the difference in internal energy between solid and liquid water at 0 degrees Celsius.

This equals negative 0.045 kilojoules per kilogram minus 333.458 kilojoules per kilogram.

This results in negative 200.0928.

The internal energy at state 2, u2, equals the internal energy of liquid water at 10 degrees Celsius plus the fraction of ice at state 2 times the difference in internal energy between solid and liquid.

This implies that Q12 divided by the mass of the ice water plus u1 equals the internal energy of liquid plus the fraction at state 2 times the difference in internal energy between solid and liquid.

The fraction at state 2, x2, equals 0.555.