Energy balance for the entire turbine:

The steady flow process equation is: the rate of change of energy, dE/dt, equals the sum over i of mass flow rate, m-dot_i, times the sum of enthalpy, h_i, kinetic energy, k.e._i, and potential energy, p.e._i, plus the sum of heat transfer rates, Q-dot_j, minus the sum of work rates, W-dot_n.

The equation becomes zero equals the total mass flow rate, m-dot_total, times the difference in enthalpy from state 0 to state 6 plus half the difference in the square of the velocities from state 0 to state 6.

For stages 5 and 6 under isentropic conditions:

The ratio of temperatures T_6 over T_5 equals the ratio of pressures p_6 over p_5 raised to the power of (n-1)/n. Solving for T_6 gives T_6 equals the ratio of pressures p_6 over p_5 raised to the power of (n-1)/n times T_5, which equals 328.07 Kelvin.

The square of the velocity at point b, w_b squared, equals two times the difference in enthalpy from state 0 to state b plus the square of the velocity at state 0, w_0 squared.

The velocity at state 0, w_0, equals the velocity at the inlet, w_in.

The temperature at state 0, T_0, equals 273.15 Kelvin.

Repeating the equation for w_b squared for clarity: w_b squared equals two times the difference in enthalpy from state 0 to state b plus the square of the velocity at state 0, w_0 squared.

The velocity at point b, w_b, equals the square root of two times the difference in enthalpy from state 0 to state b plus the square of the velocity at state 0, w_0 squared.

The velocity at point b, w_b, equals the square root of two times the integral from temperature at state b, T_b, to temperature at state 0, T_0, of the specific heat capacity of air, c_p,air, times dT plus the square of the velocity at state 0, w_0 squared. This simplifies to the square root of two times the specific heat capacity of air, c_p,air, times the difference in temperature from T_0 to T_b plus the square of the velocity at state 0, w_0 squared.