The change in internal energy from state 1 to state 2 is equal to the heat added from state 1 to state 2.

The mass of the substance times the change in internal energy from state 1 to state 2 equals the heat added from state 1 to state 2.

From Table-1 (Examination):
The internal energy of the substance in the liquid state at state 1 is negative 0.045 kilojoules per kilogram, and in the solid state at state 1 is negative 333.758 kilojoules per kilogram.

The internal energy at state 1 is calculated as the internal energy of the liquid state plus 0.6 times the difference between the internal energy of the solid state and the liquid state, which equals negative 200.1 kilojoules per kilogram.

The internal energy at state 2 is calculated as the heat added from state 1 to state 2 divided by the mass of the substance plus the internal energy at state 1, which equals negative 188.7 kilojoules per kilogram.

The pressure at state 2 is calculated as the mass times a constant k divided by the square of half the diameter, which equals 2.256 bar.

From the table:
The internal energy of the substance in the solid state at 2 bar is negative 333.495 kilojoules per kilogram, and at 10 bar is negative 333.812 kilojoules per kilogram.

The internal energy of the substance in the solid state at 2.256 bar is calculated using linear interpolation between the values at 2 bar and 10 bar, which equals negative 333.51 kilojoules per kilogram.

From the table:
The internal energy of the substance in the liquid state at 2 bar is negative 0.07 kilojoules per kilogram, and at 10 bar is negative 0.332 kilojoules per kilogram.

The internal energy of the substance in the liquid state at 2.256 bar is calculated using linear interpolation between the values at 2 bar and 10 bar.

For Task 3, subtask d):
The internal energy of the substance in the liquid state at 2.25 bar is negative 0.0871 kilojoules per kilogram.

The quality of the mixture, denoted as x, is calculated as the difference between the internal energy at state 2 and the internal energy of the liquid state, divided by the difference between the internal energy of the solid state and the liquid state, which equals 0.566.