d)

There is a table with two columns. The first column is labeled "T [degrees Celsius]" and the second column is empty. The rows of the table are as follows:
- The first row is empty.
- The second row has the number 1 in the first column and is empty in the second column.
- The third row has the number 2 in the first column and the number 70 in the second column.

The temperature at entry 12, denoted as \( T_{\text{ein,12}} \), is 20 degrees Celsius and there is a change in mass denoted as \( \Delta m_{12} \).

Description of the diagram: There is a rectangular box representing a system. Inside the box, there is a horizontal arrow pointing to the right labeled \( x=0 \). Below this arrow, there is a vertical arrow pointing upwards labeled \( T_1 \). To the left of the box, there is a horizontal arrow pointing to the left labeled \( Q_{\text{aus}} \). Below the box, there is a vertical arrow pointing upwards labeled \( Q_R \). To the right of the box, there is a label "cold open system" and \( T_{\text{ein,12}} = 20^\circ C \).

The change in energy is given by the equation:
\[ \Delta E = m_2 \cdot u_2 - m_1 \cdot u_1 + \Delta KE + \Delta PE \]
\[ = \Delta m_{12} \cdot u_{12} + Q_{\text{aus}} - Q_R \]
\[ m_2 \cdot u_2 - m_1 \cdot u_1 = \Delta m_{12} \cdot u_{12} \]
\[ (m_1 + \Delta m_{12}) \cdot u_2 - m_1 \cdot u_1 = \Delta m_{12} \cdot u_{12} \]

Reference to "TAB A-2".

The internal energy at \( x=0, 70 \theta \) is equal to the saturation internal energy at 70 degrees Celsius, which is 292.95 kJ/kg.

The internal energy at \( x \neq 100^\circ C \) is equal to the saturation internal energy at 100 degrees Celsius plus \( x \) times the difference in internal energy at 100 degrees Celsius, which is 423.164 kJ/kg.

The enthalpy at \( x=0, 20^\circ C \) is equal to the saturation enthalpy at 20 degrees Celsius, which is 83.36 kJ/kg.

The equations are as follows:
\[ m_1' u_2 + \Delta m_{12} u_2 - m_1 u_1 = \Delta m_{12} u_{12} \]
\[ m_1' u_2 - m_1 u_1 = \Delta m_{12} (u_{12} - u_2) \]
\[ \Delta m_{12} = 3764.28 \, \text{kg} \]