Omega six equals 510 meters per second.

Given:

Delta ex st equals ex st six minus ex st zero, which equals h six minus h zero minus T zero times (s six minus s zero) plus Delta k e.

h zero at T equals 280 Kelvin equals 240.02 kilojoules per kilogram plus (50.05 minus 240.2 kilojoules per kilogram) times ((250 minus 280 Kelvin) divided by (243.15 minus 240.2 kilojoules per kilogram)), which equals 242.906 kilojoules per kilogram.

h six at T equals 328.162 Kelvin equals 325.31 kilojoules per kilogram plus ((330.34 minus 325.31 kilojoules per kilogram) divided by (330 minus 325 Kelvin)) times (328.62 minus 325 Kelvin), which equals 328.957 kilojoules per kilogram.

Delta ex st equals m dot times (h zero minus h minus T zero times (s zero at T six minus s zero at T zero) plus one half times (w zero squared minus w squared)).

s six minus s zero equals s zero at T six minus s zero at T zero.

s zero at T six equals 2.106977 kilojoules per kilogram Kelvin.

s zero at T zero equals 1.47814 plus ((1.51917 minus 1.17824) divided by (250 minus 240)) times (243.15 minus 240), which equals 1.4911 kilojoules per kilogram Kelvin.

T A, B equals A minus 22.

Delta ex st equals 109.995 kilojoules per kilogram.

E dot ex vel equals T zero times (S dot ex divided by m dot).

S dot ex equals s six minus s zero plus (Q dot divided by (m dot times T zero)), which equals s zero six minus s zero zero equals 0.157867 kilojoules per kilogram Kelvin.

E dot ex vel equals 1 plus 0.1704 kilojoules per kilogram.