The average temperature T-bar is equal to the heat flow rate Q-dot-out divided by the difference between the entropy flow rates at the outlet and inlet of the cooling fluid, S-KF-out minus S-KF-in.

This is equal to the heat flow rate Q-dot-out divided by the product of the mass flow rate of the cooling fluid m-dot-KF, the specific heat capacity of the cooling fluid c-KF, and the natural logarithm of the ratio of the outlet temperature to the inlet temperature of the cooling fluid, T-KF-out over T-KF-in.

From the first law of thermodynamics applied to the cooling jacket, the heat flow rate Q-dot-out is equal to the product of the mass flow rate of the cooling fluid m-dot-KF, the specific heat capacity c-KF, and the difference between the outlet and inlet temperatures of the cooling fluid, T-KF-out minus T-KF-in.

This implies that the ratio of the heat flow rate Q-dot-out to the product of the mass flow rate of the cooling fluid m-dot-KF and the specific heat capacity c-KF is equal to the difference between the inlet and outlet temperatures, which is 61.5 RJ/kg K.

The heat flow rate Q-dot-out is also equal to the product of the mass flow rate of the cooling fluid m-dot-KF and the difference between the specific enthalpies at the inlet and outlet of the cooling fluid, h-KF-in minus h-KF-out, which is equal to the product of the mass flow rate of the cooling fluid m-dot-KF, the specific heat capacity c-KF, and the difference between the inlet and outlet temperatures.

This implies that the heat flow rate Q-dot-out is equal to the product of the mass flow rate of the cooling fluid m-dot-KF, the specific heat capacity c-KF, and the difference between the inlet and outlet temperatures.

Therefore, the average temperature T-bar is equal to the difference between the inlet and outlet temperatures divided by the natural logarithm of the ratio of the outlet temperature to the inlet temperature.

This is approximately 293.12 Kelvin.

Boxed text: A1, Page 2

Subsection c) The generated entropy rate S-dot-erz is equal to the heat flow rate Q-dot-out divided by the temperature on the right minus the heat flow rate Q-dot-out divided by the average temperature, from the entropy balance on the reactor wall.

Subsection d) The difference in the product of mass and internal energy between two states, m2 u2 minus m1 u1, is equal to the product of the change in mass and the specific enthalpy at zero quality and 20 degrees Celsius minus the heat flow rate Q-dot-out, 12.

This implies that the product of the initial mass m1 and the difference in internal energy u2 minus u1 plus the product of the change in mass and the internal energy at zero quality and 20 degrees Celsius is equal to the product of the change in mass and the specific enthalpy at zero quality and 20 degrees Celsius minus the heat flow rate Q-dot-out, 12.

This implies that the change in mass Delta m is equal to the sum of the product of the initial mass m1 and the difference in internal energy at zero quality and temperatures 70 degrees Celsius and 100 degrees Celsius plus the heat flow rate Q-dot-out, 12, divided by the difference between the specific enthalpy and the internal energy at zero quality and 20 degrees Celsius.

Subsection e) The change in entropy Delta S12 is equal to the difference in the product of mass and entropy between two states, m2 s2 minus m1 s1.