w_6 equals the square root of the quantity n times R times the difference T_6 minus T_5 divided by n minus 1, plus h_c minus h_s plus scribble plus w_5 squared, all multiplied by 2.

R equals the average R over M_Luft, which equals the average R per mol divided by h_g over R_mol, which equals 0.296 kilojoules per hour gram divided by ngk.

w_6 equals 310.61 meters per second.

Cp equals 1.006 kilojoules per kilogram Kelvin.

Exergy:

Delta e_str equals h minus h_0 minus T_0 times s minus s_0 plus ke plus pe.

Delta e_str equals the quantity h_6 minus h_0 minus T_0 times s_6 minus s_0 plus ke plus pe, which equals 12.22 kilojoules per kilogram.

h_6 at p_6 equals 0.191 and T_6 equals 328.07.

s_6 at p_6 equals 0.191 and T_6 equals 328.07.

h_6 minus h_0 equals Cp times average s of T times the difference T_6 minus T_6.

s_6 minus s_0 equals cp times the quantity natural log of T_6 over T_6 minus R times natural log of p_6 over p_0.

As instructed in task 1.

h_6 minus h_0 equals cp times average g of T_6 minus T_6, which equals 85.43 kilojoules per hour gram.

s_6 minus s_0 equals 0.30 kilojoules per kilogram Kelvin, which implies T_0 equals 73.22 kilojoules per kilogram.

ke equals scribble, w_6 squared minus w_Luft squared equals 110 kilojoules per kilogram.

Mass

Stationary Energy Balance:

0 equals m dot times the quantity h_e minus ellipsis, plus Q dot e_x,1Q minus W_t,n minus e_x,verl dot.

e_x,verl equals Delta e_x,stro,16 plus e_x,0,16 minus W_t,n.

Is it completely adiabatic?

e_x,verl equals Delta e_x,stro,16 minus W_t,n.

Turbine:

Task (b) implies W_t equals negative n times R times the quantity T_6 minus T_8 divided by 1 minus n.

Delta e_x,verl equals 100 kilojoules per kilogram plus 109260.9 kilojoules per kilogram.

Equals 204.26 kilojoules per kilogram.