1HS: h_s minus h_6.

The equation is zero equals the mass flow rate times the quantity h_s minus h_6 plus the difference of omega_s squared and omega_6 squared over 2 plus g times the difference of z_e and z_a, plus dot Q minus dot W_s.

The expression is the mass flow rate times omega_s squared over 2 plus the mass flow rate times omega_6 squared over 2.

The expression is the mass flow rate times omega_s squared over 2 times h_s equals the mass flow rate times omega_6 squared over 2 times h_6.

The equation omega_s squared times h_s equals omega_6 squared times h_6 implies omega_s times h_s over h_6 equals omega_6.

From Table A-22:

h_s equals the fraction 431.63 minus 421.26 over 431.9 minus 430 times 431.9 minus 430 plus 421.26 equals 49 plus 421.4356.

h_s equals 421.44 kilojoules per kilogram.

We need h_6?

We need T_6.

T_6 equals T_s times the fraction P_6 over P_s raised to the power of n minus 1 over n, where n equals k minus C_p over C_v equals 1.006 kilojoules per kilogram Kelvin over C_p minus R.

Given n equals 1.4.

T_6 equals 431.4 times the fraction 191,100 Pascals over 50,000 Pascals raised to the power of 1.4 minus 1 over 1.4.

This equals 328.67464 Kelvin.

This equals underlined 328.1 Kelvin.

Interpolation:

h_6 equals 328.4051 kilojoules per kilogram.

This equals 328.40 kilojoules per kilogram.

w_0 equals w_s.

w_0 equals the square root of h_s over k times h_6 equals the square root of 328.4031 over 421.48366 equals 220 meters per second.

This equals 194.2051 meters per second.

Underlined w_6 equals 194.2 meters per second.