x sub one comma two equals two.

The absolute value of Q sub twenty-one equals delta E, which equals E sub two minus E sub one, which equals m sub two times u sub two minus m sub one times u sub one.

u sub two equals u sub F, ext plus the quantity u sub F, ext minus u sub F, ext, which equals negative three hundred thirty-three thousand four hundred forty-two plus zero point one times the quantity negative zero point three three three minus the quantity negative three hundred thirty-three thousand four hundred forty-two, which equals negative three hundred thirty-three thousand four hundred forty-two plus one hundred thirty-three thousand three hundred ninety-seven.

Q sub twenty-one equals m sub two times u sub two minus m sub one times u sub one.

m sub two times u sub two equals Q sub twenty-one plus m sub one times u sub one.

u sub two equals the fraction with numerator Q sub twenty-one plus m sub one times u sub one and denominator m sub two.

u sub F, ext plus x sub two times the quantity u sub F, ext minus u sub F, ext equals the fraction with numerator Q sub twenty-one plus m sub one times u sub one and denominator m sub two.

x sub two equals the fraction with numerator the fraction with numerator Q sub twenty-one plus m sub one times u sub one and denominator m sub two minus u sub F, ext and denominator u sub F, ext minus u sub F, ext, which equals the fraction with numerator one hundred thirty-three thousand four hundred ten per kilogram minus the quantity negative three hundred thirty-three thousand four hundred forty-two per kilogram and denominator zero point one per kilogram times three hundred thirty-three thousand four hundred forty-two per kilogram, which equals the fraction with numerator one hundred thirty-three thousand four hundred ten plus three hundred thirty-three thousand four hundred forty-two and denominator zero point one times three hundred thirty-three thousand four hundred forty-two, which equals four point five five five.

u sub F, ext minus u sub F, ext equals negative zero point eight nine plus three hundred thirty-three thousand four hundred forty-two per kilogram, which equals three hundred thirty-three thousand four hundred forty-two per kilogram.

U sub one equals U sub fest plus X sub one times the quantity U sub gesamt minus U sub fest, which equals negative three hundred thirty-three thousand four hundred fifty-eight plus zero point six times the quantity negative thirty-two point zero four five minus the quantity negative three hundred thirty-three thousand four hundred fifty-eight kilojoules per kilogram, which equals negative three hundred thirty-three thousand six hundred ten kilojoules per kilogram.