Graph Description: The graph is a pressure-temperature diagram. The y-axis is labeled p (bar) and the x-axis is labeled T (Kelvin). There is a curve that starts at a point labeled 1, rises to a peak at point 2, and then falls to point 3. From point 3, there is a line that rises steeply to point 4. The region between points 1, 2, and 3 is shaded. There is a horizontal line extending from point 2 to the right, labeled T2.

The rate of change of kinetic energy E dot subscript K equals the ratio of the rate of heat transfer Q dot subscript zw to the rate of work w dot subscript t, which equals the ratio of the rate of heat transfer Q dot subscript K to the rate of work w dot subscript K, which equals the ratio of the rate of heat transfer Q dot subscript zw to the difference of the rate of heat transfer Q dot subscript ab minus Q dot subscript zw, which equals the ratio of the rate of heat transfer Q dot subscript K to the difference of the rate of heat transfer Q dot subscript ab minus Q dot subscript K.

The rate of heat transfer Q dot subscript K equals the product of the mass flow rate dot m, the specific gas constant dot R, the specific entropy s, the specific internal energy u, and the difference in enthalpy h2 minus h1.

The rate of heat transfer Q dot subscript K equals 205.79 kilojoules.

The rate of heat transfer Q dot subscript ab equals the product of the mass flow rate dot m, the specific gas constant dot R, the specific entropy s, the specific internal energy u, and the difference in enthalpy h4 minus h3.

The rate of heat transfer Q dot subscript ab equals 156.29.

The rate of change of kinetic energy E dot subscript K equals the ratio of the rate of heat transfer Q dot subscript K to the rate of work w dot subscript t, which equals 7349.64.

Table Delta 10.

The enthalpy h2 equals 234.08.

The enthalpy h1 equals the enthalpy at equilibrium h subscript e plus the product of the quality x1 and the difference in enthalpy h subscript g minus h subscript f, which equals 48.87.

The enthalpy h2 equals 234.08.

Table Delta M.

The enthalpy h4 equals the enthalpy at equilibrium h subscript e, which equals 93.42.