Energy balance, stationary, work equals zero:

Mass flow rate times the difference between the enthalpy at the exit and the enthalpy at the entrance plus the heat transfer rate into the system minus the heat transfer rate out of the system.

The heat transfer rate out of the system equals negative 37.703 kilojoules per second plus the heat transfer rate into the system.

The heat transfer rate into the system equals 62.237 kilowatts.

The heat transfer rate out of the system equals negative 37.703 kilojoules per second plus 62.3 kilowatts.

Heat flows out.

Energy balance for a semi-open system, no work:

Change in energy equals change in internal energy equals the change in mass between two states times the enthalpy at the entrance plus the heat transfer rate for the process between the two states.

Change in mass at 20 degrees Celsius equals the total mass times the specific internal energy at state 2 minus the total mass times the specific internal energy at state 1 equals the change in mass at 20 degrees Celsius times the enthalpy at 20 degrees Celsius plus the heat transfer rate for the process.

Solving for the change in mass:

Change in mass equals the total mass times the specific internal energy at state 1 plus the heat transfer rate for the process minus the total mass times the specific internal energy at state 2, all divided by the difference between the specific internal energy at state 2 and the enthalpy at 20 degrees Celsius.

From Table A-2:

Specific internal energy at 160 degrees Celsius, quality equals zero, is 418.94 kilojoules per kilogram.

Specific internal energy at 90 degrees Celsius, quality equals zero, is 292.35 kilojoules per kilogram.

Enthalpy at the entrance at 20 degrees Celsius, quality equals zero, is 83.96 kilojoules per kilogram.

The total mass equals 1755 kilograms.

Substituting in:

Change in mass equals the total mass times the difference between the specific internal energies at state 1 and state 2 plus the heat transfer rate for the process, all divided by the difference between the specific internal energy at state 2 and the enthalpy at the entrance.