The first graph is a pressure versus temperature diagram. The y-axis is labeled as pressure (P) and the x-axis is labeled as temperature (T). There are three regions labeled as "Ice", "Water", and "Steam". The boundary between "Ice" and "Water" is a line that starts from the origin and slopes upwards. The boundary between "Water" and "Steam" is a line that starts from the origin and slopes upwards more steeply. The boundary between "Ice" and "Steam" is a line that starts from the origin and slopes upwards even more steeply. There is a point labeled "Triple point" where the three lines intersect. There is a rectangular region labeled "1", "2", "3", and "4" with the top side labeled "lil" and the bottom side labeled "u".

The second graph is also a pressure versus temperature diagram. The y-axis is labeled as pressure (P) and the x-axis is labeled as temperature (T). There are three regions labeled as "Ice", "Water", and "Steam". The boundary between "Ice" and "Water" is a line that starts from the origin and slopes upwards. The boundary between "Water" and "Steam" is a line that starts from the origin and slopes upwards more steeply. The boundary between "Ice" and "Steam" is a line that starts from the origin and slopes upwards even more steeply. There is a point labeled "1" on the boundary between "Ice" and "Water". There is a point labeled "2" on the boundary between "Water" and "Steam". There is a point labeled "3" on the boundary between "Ice" and "Steam". There is a point labeled "4" in the "Water" region.