Energy balance:

The mass flow rate of R134a times the difference in enthalpy between state 2 and state 1 plus the heat transfer rate to the environment equals zero.

This implies that the mass flow rate of R134a equals negative the heat transfer rate to the environment divided by the difference in enthalpy between state 2 and state 1.

Energy balance:

The mass flow rate of R134a times the difference in enthalpy between state 3 and state 2 plus the work done by the compressor equals zero.

This implies that the mass flow rate of R134a equals negative the work done by the compressor divided by the difference in enthalpy between state 2 and state 3.

Given:

The enthalpy at state 2 (8 bar, quality equals 1) is 255.05 kilojoules per kilogram.

The temperature at state H2 is 15.45 degrees Celsius.

The temperature difference from state 2 to state 1 is 6 degrees Celsius, which implies that the temperature at state 1 is 9.45 degrees Celsius.

Energy balance:

The mass flow rate times the difference in enthalpy between state 3 and state 2 plus the internal work equals zero.

This implies that the mass flow rate equals the internal work divided by the difference in enthalpy between state 2 and state 3.

From state 4 to state 1, entropy is constant.

The entropy at state 4 (quality equals 0, entropy at state 3 during evaporation) is 0.2419.

The entropy at state 4 under certain conditions equals the entropy at state 3, which is the entropy at state 3 in the liquid phase plus the quality times the difference in entropy between the gas phase and the liquid phase at state 3.

The quality equals the difference in entropy at state 4 and the entropy at state 3 in the liquid phase divided by the difference in entropy between the gas phase and the liquid phase at state 3.

The enthalpy at state 3 equals the enthalpy at state 3 in the liquid phase plus the quality times the difference in enthalpy between the gas phase and the liquid phase at state 3.

This equals the enthalpy at state 3 in the liquid phase plus the ratio of the difference in entropy at state 4 and the entropy at state 3 in the liquid phase to the difference in entropy between the gas phase and the liquid phase at state 3, times the difference in enthalpy between the gas phase and the liquid phase at state 3.