The change in energy, denoted as Delta E, is equal to the change in internal energy, Delta U, which is the product of the mass flow rate, denoted as m dot, and the difference between the specific internal energies at two different states, u1 and u2.

The specific internal energy at state 1, u1, is calculated as the product of the quality of the steam, x, and the specific internal energy of the steam at 70 degrees Celsius, plus the product of one minus the quality of the steam and the specific internal energy of the liquid at 100 degrees Celsius.

The specific internal energy at state 2, u2, is the specific internal energy of the fluid at 70 degrees Celsius.

Substituting the values, u1 is calculated as 0.005 times 2506.5 plus 0.995 times 48.91 times the fraction 4 over 4.5, which equals 429.38 kilojoules per kilogram.

u2 is 292.55 kilojoules per kilogram.

Therefore, Delta E is the product of the mass flow rate, 5755, and the difference between u1 and u2, which equals 7841.83245, rounded to 785.0 megajoules.

Delta E is also equal to the change in mass, Delta m, times the specific heat capacity of water, c_wasser, times the change in temperature, Delta T.

Delta E can also be expressed as the difference in the new mass flow rate, m dot new, minus the original mass flow rate, m dot, times the specific heat capacity of water, c_w, times the change in temperature.

The new mass flow rate, m dot new, is calculated as the quotient of Delta E divided by the product of the specific heat capacity of water and the change in temperature, plus the original mass flow rate, where c_w is 4.22.

Substituting the values, m dot new is calculated as the quotient of 785000 kilojoules divided by the product of 4.22 kilojoules per kilogram per Kelvin and 30, plus 5755, which equals 11455 kilograms, rounded to 9475 kilograms.

Therefore, the change in mass, Delta m, is 9475 minus 5755, which equals 3720 kilograms.