Graph 1:

This graph is a pressure-volume (P-V) diagram. The x-axis is labeled with "V" and the y-axis is labeled with "P". The graph consists of a closed loop with four points labeled 1, 2, 3, and 4.

- Point 1 is at the bottom right of the loop.
- Point 2 is at the bottom left of the loop.
- Point 3 is at the top left of the loop.
- Point 4 is at the top right of the loop.

The loop is divided into two regions by a vertical line passing through point 1. The left region is labeled "gas" and the right region is labeled "liquid". There is a wavy line between points 1 and 4, indicating a phase change. The region between points 1 and 2 is labeled "liquid" and the region between points 2 and 3 is labeled "gas".

Graph 2:

This graph is also a pressure-volume (P-V) diagram. The x-axis is labeled with "V" and the y-axis is labeled with "P". The graph consists of a closed loop with four points labeled 1, 2, 3, and 4.

- Point 1 is at the bottom left of the loop.
- Point 2 is at the bottom right of the loop.
- Point 3 is at the top right of the loop.
- Point 4 is at the top left of the loop.

The loop is divided into two regions by a diagonal line passing through points 1 and 3. The left region is labeled "liquid" and the right region is labeled "gas". There is a wavy line between points 3 and 4, indicating a phase change.

Graph 3:

This graph is a pressure-temperature (P-T) diagram. The x-axis is labeled with "T" and the y-axis is labeled with "P". The graph consists of a closed loop with four points labeled 1, 2, 3, and 4.

- Point 1 is at the bottom left of the loop.
- Point 2 is at the bottom right of the loop.
- Point 3 is at the top right of the loop.
- Point 4 is at the top left of the loop.

The loop is divided into two regions by a diagonal line passing through points 1 and 3. The left region is labeled "liquid" and the right region is labeled "gas".

For the equations:

- \( h_{g2} \) and \( T_1 = -10^\circ C \)
- \( T_2 = T_1 \)
- Therefore, \( h_{g2} \) is interpolated from Table A-10.
- \( h_{g2} \) is calculated as \( \frac{hg(-8^\circ C) - hg(-12^\circ C)}{-8^\circ C - (-12^\circ C)} \cdot (-8^\circ C + 10^\circ C) + hg(-12^\circ C) = 2467.85 \frac{kJ}{kg} \)
- \( \frac{2444.31 \frac{kJ}{kg}}{243.3} \)
- \( h_{g} \)
- \( \frac{T_2}{T_1} = \left( \frac{p_2}{p_1} \right)^n \)
- Therefore, from Table A-12,
- \( p(268.1) \quad h_{g3} = h_{g2} = 264.15 \)