a) Energy balance (stationary):

The equation is zero equals the mass flow rate times the difference between the enthalpy at 70 degrees Celsius and the enthalpy at 100 degrees Celsius, plus the heat flow rate Q_R, plus the heat flow rate Q_aus, where the heat flow rate Q_R equals zero.

In the reactor, x equals 0.005.

The enthalpy at the inlet, h_ein, equals the enthalpy at 70 degrees Celsius with x equals 0.005, according to Table A-2.

The enthalpy at the inlet, h_ein, equals 232.88 plus 0.005 times the difference between 2628.8 and 232.88, which equals 394.691 kilojoules per kilogram.

The enthalpy at the outlet, h_aus, equals the enthalpy at 100 degrees Celsius with x equals 0.005, according to Table A-2.

The enthalpy at the outlet, h_aus, equals 211.04 plus 0.005 times the difference between 2676.1 and 419.04, which equals 436.3253 kilojoules per kilogram.

Therefore, the heat flow rate Q_aus equals the mass flow rate times the difference between the enthalpy at the outlet and the enthalpy at the inlet, minus the heat flow rate Q_R, which equals 0.3 times the difference between 436.3253 and 394.691 minus 100, resulting in -62.297 kilojoules per second. The sign convention is that the heat flow rate into the system is positive and the heat flow rate out of the system is negative.

If it is as shown in the sketch, the heat flow rate Q_aus equals 62.297 kilojoules per second.

Energy balance:
The equation m_2 u_2 minus m_1 u_1 equals m_2 minus m_1 times h_ein plus the heat flow rate Q_12 minus the work rate W equals zero.

Table A2:
The internal energy u_2 at 100 degrees Celsius with x equals 0.05 equals 418.94 plus 0.05 times the difference between 2505.5 and 418.94, which equals 129.3878 kilojoules per kilogram.

m_2 equals m_1 plus the change in mass, Delta m.

The equation (m_1 plus Delta m) times u_2 equals Delta m times h_ein plus the heat flow rate Q_12.

The equation Delta m times the difference between h_ein and u_2 equals m_1 times u_2 minus m_1 times u_1 minus the heat flow rate Q_12.

Delta m equals the fraction of m_1 times the difference between u_2 and u_1 minus the heat flow rate Q_12, divided by the difference between h_ein and u_2.