S2 equals S3.

Zero equals the mass flow rate of R134a times the difference in enthalpy between state 2 and state 3 plus the heat transfer rate from state 2 to state 3 minus the work done from state 2 to state 3.

The work done from state 2 to state 3 equals the compressor work, which is negative 28 kilowatts.

The mass flow rate of R134a equals the compressor work divided by the change in enthalpy, which is 7.111 times 10 to the power of negative 3 kilograms per second.

Zero equals the mass flow rate of R134a times the difference in enthalpy between state 2 and state 1.

The temperature at state 2 is negative 22 degrees Celsius, which equals 251.15 Kelvin.

S3 equals S2, which equals the entropy at a temperature of negative 22 degrees Celsius, calculated as 0.9089 minus 0.9102 times the fraction (26 minus 22) divided by (24 minus 20) plus 0.9089, resulting in 0.90955 kilojoules per kilogram Kelvin.

Verbal description of the table: The table is labeled "TAB A-10" and contains values for entropy S at different temperatures. The values used in the calculation are interpolated between the given data points.

The enthalpy at state 2, for a temperature of negative 22 degrees Celsius, is calculated as (260.45 A minus 258.36) divided by (24 minus 20) times (24 minus 22) plus 260.45, resulting in 259.57 kilojoules per kilogram.

The enthalpy at state 3 is calculated as negative (phi times 273.66 minus 264.15) divided by (0.9374 minus 0.9066) times (0.9374 minus 0.9055) plus 273.66, resulting in 265.06 kilojoules per kilogram.

O equals the mass flow rate of R134a times the difference in enthalpy between state 2 and state 3 plus the corrected heat transfer rate from state 2 to state 3 minus the corrected internal energy from state 2 to state 3.

The corrected internal energy from state 2 to state 3 equals the corrected internal energy work, which is negative 28 kilojoules.

The mass flow rate of R134a equals the corrected internal energy divided by the difference in enthalpy between state 2 and state 3, which is negative 0.028 divided by (259.57 minus 265.06), resulting in 5.896 times 10 to the power of negative 4.