Omega_c equals 2. T_6 equals question mark. s_5 equals s_6. Kappa equals chi equals gamma_4, and it is isentropic. The ratio of T_6 over T_5 equals the ratio of p_6 over p_5 raised to the power of (kappa minus 1) divided by kappa. T_6 equals T_5 times the ratio of p_0 over p_5 raised to the power of 0.4 over 1.4. T_6 equals 328.0796697 degrees Celsius. The rate of heat transfer Q dot equals the mass flow rate of gas m dot_g times the quantity h_5 minus h_6 plus half the difference of c_u5 squared minus c_u6 squared, plus Q dot_56, which is crossed out. The rate of heat transfer Q dot equals the mass flow rate of gas m dot_g times the quantity h_5 minus h_6 plus half the difference of c_u5 squared minus c_u6 squared. Half of c_u6 squared equals h_5 minus h_6 plus half of c_u5 squared. Half of c_u6 squared equals c_p times the difference T_5 minus T_6 plus half of c_u5 squared. c_u6 equals the square root of twice c_p times the difference T_5 minus T_6 plus c_u5 squared, which equals 507.284 meters per second.

The change in exergy e_x_str equals e_x_str_6 minus e_x_str_0. T_6 equals 790 degrees Celsius and the mass flow rate m_6 equals 350 kilograms per second. The change in exergy e_x_str equals the quantity h_6 minus h_0 minus T_0 times the difference s_6 minus s_0 plus the change in kinetic energy. h_6 minus h_0 equals c_p times the difference T_6 minus T_0. s_6 minus s_0 equals c_p times the natural logarithm of the ratio T_6 over T_0 minus R times the natural logarithm of the ratio P_6 over P_0. The change in kinetic energy equals half the difference of v_6 squared minus v_0 squared. R equals the universal gas constant R_u divided by the molar mass of fuel M_fuel. R equals 8.314 divided by 28.857 times 10 to the power of minus 3, which equals 288.936 Joules per kilogram Kelvin. The change in exergy e_x_str equals the quantity c_p times the difference T_6 minus T_0 minus T_0 times the quantity c_p times the natural logarithm of the ratio T_6 over T_0 minus R times the natural logarithm of the ratio P_6 over P_0 plus half the difference of v_6 squared minus v_0 squared, which equals 125.47773 kilojoules per kilogram.