The rate of change of energy with respect to time is represented as the rate of change of internal energy with respect to time, which equals the sum of mass flow rates plus the sum of reaction rates times the enthalpy at state i.

The expression n2 times u2 minus n2 times u2 equals the change in n2 times the enthalpy at 200 degrees Celsius plus the net heat transfer rate divided by the temperature T.

The expression for n2 is given as n1 plus the change in n2.

The internal energy at state 1, u1, is expressed as the internal energy at the saturated liquid state at 5 plus x times the difference between the internal energy at the saturated gas state at 1 and the saturated liquid state at 1, which equals 425.7778 kilojoules per kilogram.

The internal energy at the saturated liquid state at 100 degrees Celsius, uf1, is 419.0 kilojoules per kilogram.

The internal energy at the saturated gas state at 200 degrees Celsius, ug1, is 2305.5 kilojoules per kilogram.

The internal energy at state 2, u2, is the internal energy at the saturated liquid state at 70 degrees Celsius, which is 292.55 kilojoules per kilogram.

The next page is indicated.

In the equations, m2 times u2 plus the change in m12 times u2 minus m1 times u1 equals the change in m12 times the enthalpy at the inlet.

The expression m2 times u2 minus m1 times u1 equals the change in m12 times the difference between the enthalpy at the inlet and u2.

The change in m12 is calculated as m2 times the difference between u2 and u1 divided by the difference between the enthalpy at the inlet and u2, resulting in 3,756.84 kilograms.

The enthalpy at the inlet, hin, at 200 degrees Celsius is 83.96 kilojoules per kilogram.