The change in kinetic energy, Delta KE, equals zero.

Zero equals the change in mass m1 times the sum of h1 and half of w1 squared.

w equals the square root of two times the difference between h6 and h5.

Kinetic energy, KE, equals work, W, which is the integral from 5 to 6 of q times dV.

Half of w squared equals one over (n minus one) times the difference between T2 and T1.

Half of w squared equals c_p times the change in temperature, Delta T, which equals 92.95 kilojoules per kilogram.

w squared equals two times 92.95 kilojoules per kilogram, which equals 185.9 kilojoules per kilogram.

w equals the square root of 185.9 kilojoules per kilogram, which equals 430 meters per second.

The change in exergy due to the stream, Delta e_x,str, equals e_x,str,6 minus e_x,str,0.

Exergy due to the stream, e_x,str, equals h minus h0 minus T0 times (s minus s0) plus kinetic energy, ke.

Exergy due to the stream at the initial state, e_x,str,0, equals h6 minus h0 minus T0 times (s6 minus s0) plus ke6 minus ke0, which equals Cp times the change in temperature at s,0 minus T0 times Cp times the natural logarithm of (T6 over T0) minus T0 times (p6 over p0), which equals 1.006 kilojoules per kilogram over (310R minus (273.15 plus 30) Kelvin minus (273.15 plus 30) Kelvin) times (310R over (273.15 minus 30)), which equals 67.126 kilojoules per kilogram.

This equals Cp times (the change in temperature at s,0 minus T0 times the natural logarithm of (T6 over T0)) plus ke, which equals 1.006 kilojoules per kilogram times (310R minus (273.15 plus 30) Kelvin minus (273.15 plus 30) Kelvin) times (310R over (273.15 minus 30)), which equals 15.42 kilojoules per kilogram plus (10 meters squared per second squared), which equals 145.47 kilojoules per kilogram.