The efficiency epsilon_k is given by the ratio of the absolute value of the heat input rate (Q_dot zu) to the absolute value of the work rate (W_dot), which is equal to the ratio of the absolute value of the heat input rate to the absolute value of the difference between the heat output rate (Q_dot ab) and the heat input rate. This can be simplified to the ratio of the absolute value of the heat input rate to the difference between the absolute values of the heat output rate and the heat input rate.

The heat input rate Q_zu is equal to the mass flow rate of the turbine (m_dot TRB) times the difference in enthalpy between state 2 and state 1, which equals 156.28 watts.

The enthalpy at state 1, h_1, is calculated as the enthalpy at the liquid phase (h_f) at pressure p_1 plus the quality x_1 times the difference between the enthalpy at the gas phase (h_g) and the enthalpy at the liquid phase, resulting in 93.42 kilojoules per kilogram.

The conversion of mass flow rate from kilograms per hour to kilograms per 300 seconds is shown, resulting in 1 kilogram per 300 seconds.

The heat output rate Q_dot ab is equal to the mass flow rate of the reverse process (m_dot rev) times the difference in enthalpy between state 2 and state 3.

The entropy at state 2 and state 3, s_2 and s_3, are both equal to 0.9351 kilojoules per kilogram Kelvin.

The enthalpy at state 3, h_3, is calculated by subtracting the product of the difference in entropy between state 3 and a reference state times a constant from the enthalpy at a reference state, resulting in 272.85 kilojoules per kilogram.

The heat output rate Q_dot ab is calculated to be -199.47 watts.

The rate of entropy generation, S_dot x, is given as 3.6184, with the units not specified.