Zero equals the mass flow rate of R134a times the difference between h3 and h4 minus the heat transfer rate Qab, which equals the mass flow rate of R134a times the difference between h1 and h2 plus the heat transfer rate Qk.

The mass flow rate of R134a times the ratio of the heat transfer rate Qab to the difference between h3 and h4 equals the negative ratio of the heat transfer rate Qk to the difference between h1 and h2.

Zero equals the mass flow rate of R134a times the difference between h2 and h3 minus the work rate Wk.

The mass flow rate of R134a times the ratio of the work rate Wk to the difference between h2 and h3.

h2 equals the properties at pressure p2 and quality x equals 1, which equals the saturated vapor enthalpy at pressure p2, and is 259 kilojoules per kilogram.

Pressure p2 is 6 bar minus 5 millibar, which equals 5.995 bar, and is equal to pressure p1.

Pressure p3 equals pressure p4, which is 8 bar.

The mass flow rate of R134a is 4 kilograms per hour, which equals 0.0011 kilograms per second.

Temperature T2 is negative 22 degrees Celsius.

Pressure p1 equals pressure p2, which is 5.95 bar.

Enthalpy h1 equals enthalpy h4, which is the enthalpy at 8 bar and quality x equals 0, and is 53.42 kilojoules per kilogram.

Xn is the ratio of the difference between enthalpy hn and the saturated liquid enthalpy at pressure p1 to the difference between the saturated vapor enthalpy at pressure p1 and the saturated liquid enthalpy at pressure p1, which equals 0.0777.