(d) The mass of the phase change material times the difference in internal energy between state 2 and state 1 equals the heat transfer Q12 (Work is zero since the process is isochoric).

The change in total energy equals the change in internal energy, which cancels out the change in pressure of the phase change material.

The internal energy at state 1 is equal to the internal energy of the liquid phase at 0 degrees Celsius and 1.4 bar plus the fraction of ice times the difference between the internal energy of the solid phase and the liquid phase at 0 degrees Celsius and 1.4 bar.

This results in a value of negative 200.117 kilojoules per kilogram.

The internal energy at state 2 is equal to the internal energy of the liquid phase at 0 degrees Celsius and 1.4 bar plus the fraction of ice at state 2 times the difference between the internal energy of the solid phase and the liquid phase at 0 degrees Celsius and 1.4 bar.

The mass of the phase change material times the difference in internal energy between state 2 and state 1 is equal to the mass of the phase change material times the difference in the product of the fraction of ice at state 2 and the difference in internal energy between the solid and liquid phases minus the product of the fraction of ice at state 1 and the difference in internal energy between the solid and liquid phases, which equals the heat transfer Q12.

Continuation 3.d.:

The fraction of ice at state 2 is equal to the ratio of the heat transfer Q12 divided by the mass of the phase change material plus the fraction of ice at state 1 times the difference in internal energy between the ice and liquid phases at 0 degrees Celsius and 1.46 bar, all over the difference in internal energy between the ice and liquid phases at 0 degrees Celsius and 1.46 bar.

This results in a value of 0.559.