Zero equals the rate of heat flow out of the system divided by the temperature of the reactor minus the rate of heat flow out of the system divided by the temperature of the cooling water plus the irreversible entropy rate. This implies that the irreversible entropy rate equals 65 kilowatts divided by 295 Kelvin minus 65 kilowatts divided by 373.15 Kelvin, which equals 0.046 kilowatts per Kelvin.

Graphical Content Description:
There is a diagram labeled "Reactor" with an arrow pointing downwards labeled "Cooling Water". The diagram consists of a rectangular box labeled "Reactor" with an arrow pointing downwards from the box labeled "Cooling Water".

The outside temperature is 70 degrees Celsius, which is 343.15 Kelvin. The change in work from state 1 to state 2 is isothermal, and the inside temperature is 20 degrees Celsius. The expression W2 times V2 minus W1 times V1 equals the change in work from state 1 to state 2 times the inside volume plus the heat transfer for the process from state 1 to state 2. The change in work from state 1 to state 2 equals (W1 plus the change in work from state 1 to state 2) times V2 minus W1 times V1 divided by the heat transfer for the process from state 1 to state 2. The heat transfer for the process from state 1 to state 2 times the change in work from state 1 to state 2 equals (W1 plus the change in work from state 1 to state 2) times V2 minus W1 times V1. The change in work from state 1 to state 2 times (the heat transfer for the process from state 1 to state 2 minus V2) equals W2 times W1 minus W1 times W2. The change in work from state 1 to state 2 equals W1 times (V2 minus V1) divided by (the heat transfer for the process from state 1 to state 2 minus V2).

The change in entropy equals W2 times S2 minus W1 times S1.