Section d) Pouring from the reactor (no SFP)

The change in energy, Delta E, is equal to the change in mass between state 1 and 2, Delta m_12, times the difference in enthalpy between state 1 and state 2, h_1 minus h_2, minus the heat transferred out, Q_aus,12.

The change in internal energy, U_2 minus U_1, is equal to the change in mass between state 1 and state 2, Delta m_12, times the difference in enthalpy between state 1 and state 2, h_1 minus h_2, minus the heat transferred out, Q_aus,12.

This equals m_2 times specific internal energy at state 2, u_2, minus m_1 times specific internal energy at state 1, u_1.

The mass at state 2, m_2, is equal to the mass at state 1, m_1, plus the change in mass, Delta m_12.

TAB - A-2:

The specific internal energy at state 1, u_1, at 100 degrees Celsius is 419.94 kilojoules per kilogram.

The specific internal energy at state 2, u_2, at 70 degrees Celsius is 292.95 kilojoules per kilogram.

The expression (m_1 plus Delta m_12) times u_2 minus m_1 times u_1 equals Delta m_12 times the difference in enthalpy between state 1 and state 2, h_1 minus h_2, minus the heat transferred out, Q_aus,12.

The expression m_2 times u_2 plus Delta m_12 times u_2 minus Delta m_12 times the difference in enthalpy between state 1 and state 2, h_1 minus h_2, equals m_1 times u_1 minus the heat transferred out, Q_aus,12.

The expression Delta m_12 times the difference between u_2, h_1, and h_2 equals m_1 times the difference between u_1 and u_2 minus the heat transferred out, Q_aus,12.

The change in mass, Delta m_12, is equal to m_1 times the difference between u_1 and u_2 minus the heat transferred out, Q_aus,12, divided by the sum of u_2 minus h_1 plus h_2.