A diagram is drawn showing a control volume with mass flow rates entering and leaving the control volume, labeled as $\dot{m}_{\text{ein}}$ for entering and $\dot{m}_{\text{aus}}$ for leaving, respectively. The control volume is labeled with $KF$ on the left and right sides. The mass flow rate entering is labeled as $0.005$ and the mass flow rate leaving is labeled as $0.3$ kilograms per second. The control volume is also labeled with $QR$ at the bottom.

The equation for the energy flow rate $\dot{E}_{\text{stol}}$ is given by the mass flow rate entering times $h_1$ minus the mass flow rate leaving times $h_2$ plus the heat flow rate $\dot{Q}$ minus the work flow rate $\dot{W}_{\text{t}}$.

The equation $0 = \dot{m} (h_1 - h_2) + \dot{Q}_{\text{k}}$ is provided.

The heat flow rate $\dot{Q}$ is calculated as the mass flow rate times the difference in enthalpy $(h_2 - h_1)$, which equals $0.3$ kilograms per second times $(419.04 - 292.98)$ kilojoules per kilogram, resulting in $37.818$ kilowatts. Also, $\dot{Q}_{\text{k}}$ is calculated as $10000$ minus $37.818$ kilowatts.

$\dot{Q}_{\text{k}}$ is then simplified to $9962.182$ kilowatts.

Another diagram is drawn showing a control volume with mass flow rates entering and leaving the control volume, labeled as $\dot{m}_{\text{aus}}$ for leaving and $\dot{m}_{\text{ein}}$ for entering, respectively. The control volume is labeled with $Q_{\text{aus}}$ on the left and $Q_{\text{ein}}$ on the right.

The enthalpy $h_2$ at $100$ degrees Celsius and quality $x_2 = 0$ is equal to $h_{\text{fg}}$ at $100$ degrees Celsius, which is $419.04$ kilojoules per kilogram (from Table 42).

The enthalpy $h_1$ at $70$ degrees Celsius and quality $x_1 = 0$ is $292.98$ kilojoules per kilogram (from Table 42).