For T_0:
- Process 1-6: Energy equation
- The rate of change of energy with respect to time equals the mass flow rate times the difference in enthalpy from state 1 to state 6 plus half the mass flow rate times the difference in the square of velocity from state 1 to state 6.
- Potential is omitted, equals constant.
- T_0 equals T_6, kinetic energy over mass flow rate equals half of the square of velocity at state 1.
- T_0 equals 75 times the power of the ratio of pressure at state 1 to pressure at state 6 to the power of R over c_p, equals 79.7.
- 750 divided by 0.56 equals 3200 plus 0.5 times K equals T_6.
- h_1 minus h_6 equals half the difference of the square of velocities from state 1 to state 6.
- u_6 equals the square root of twice (h_1 minus h_6) plus the square of velocity at state 1 minus twice the velocity at state 6.
- u_6 equals the square root of twice c_p times (T_1 minus T_6) plus half the square of velocity at state 1.
- u_6 equals the square root of twice 1005 Joules per kilogram Kelvin times (731 minus 320 times 0.75 times 1000 Kelvin) plus twice 0.5 times 1000 Joules per kilogram.
- u_6 equals 320 times 7.829 meters per second equals u_6.

R equals the ratio of c_p times (T_1 minus T_6) to (u_1 minus u_6).
K equals c_p times v equals c_p over R.
u equals 0.2 times 7.4 times half the difference of (320 times 0.75 times 1000 minus 710).
u equals 7.1 times 0.6 times half the difference of (710 minus 320 times 0.75 times 1000).
u equals 7.1 times 0.6 times half the difference of (710 minus 320 times 0.75 times 1000).

The rate of change of mass flow rate times enthalpy of H_2 equals the mass flow rate times the rate of change of enthalpy of H_2 plus the mass flow rate times the rate of change of enthalpy of H_1 equals the mass flow rate times the rate of change of enthalpy of H_2 minus R times the ratio of mass flow rate times pressure at state 2 to density at state 2.
Equals mass flow rate times c_p times (T_2 minus T_1) times the natural logarithm of the ratio of 2.9 times 10^5 to 2.9 times 10^5 equals 7.005 times the ratio of 2.9 times 10^5 to 2.9 times 10^5 times the natural logarithm of the ratio of 2.9 times 10^5 to 2.9 times 10^5.
Equals 7.005 times the ratio of 2.9 times 10^5 to 2.9 times 10^5 times the natural logarithm of the ratio of 2.9 times 10^5 to 2.9 times 10^5 equals 0.3617 kilojoules per kilogram.
The reversible heat transfer equals T_0 times the reversible entropy change equals 7.005 times 1.5 times the natural logarithm of the ratio of 3.2 times 10^5 to 2.9 times 10^5 equals 7.276 kilojoules per kilogram.