Energy balance in the reactor, stationary with delta p, delta E, and W all equal to zero:

Zero equals the mass flow rate in times the difference in enthalpy in minus enthalpy out, plus the heat flow rate into the reactor minus the heat flow rate out.

(with the heat flow rate in defined as positive in the direction of the arrow)

The heat flow rate out equals the mass flow rate in times the difference in enthalpy at 200 degrees Celsius for r minus the enthalpy at 200 degrees Celsius for w, plus Q2.

In the entire reactor, the fluid is boiling, implying that we are in the two-phase region.

The enthalpy in equals the enthalpy at the saturation condition from Table 2, with temperature equal to 70 degrees Celsius and quality equal to 0.005.

The enthalpy at 70 degrees Celsius for the liquid phase is 293.2 kilojoules per kilogram, and for the gas phase, it is 2626.8 kilojoules per kilogram (referring to 20 degrees Celsius).

The enthalpy in equals the enthalpy at 70 degrees Celsius for the liquid phase plus the quality times the difference in enthalpy at 70 degrees Celsius for the gas phase minus the liquid phase, which equals 309.649 kilojoules per kilogram, and this is equal to the enthalpy in.

The enthalpy out equals the enthalpy at 200 degrees Celsius for the liquid phase plus the quality times the difference in enthalpy at 200 degrees Celsius for the gas phase minus the liquid phase, which equals 428.23 kilojoules per kilogram.

From Table A-2: The enthalpy at 200 degrees Celsius for the liquid phase is 849.04 kilojoules per kilogram, and for the gas phase, it is 2257.0 kilojoules per kilogram.

The heat flow rate out equals 0.5 kilograms per second times the sum of 309.649 and 428.23 kilojoules per kilogram plus 100 kilojoules per second, which equals 62.93 kilojoules per second, and this is equal to the heat flow rate out.