c) Perfect Gas

Energy Balance:

The change in energy, Delta E, equals m times the difference between U2 and U1, which leads to Q minus W.

Q equals m times the difference between U2 and U1 plus W, which equals 785.73 minus 366.53.

CV times the difference between T2 and T1 equals negative 785.73 plus 316.15 kilograms per second.

1Q_uL equals negative 1360.15 plus 33.

V2 equals m_S1 times R times T2 divided by p2, which equals 11.11 liters.

Volume work equals external work.

W equals p0 times V minus p0 times the difference between U2 and U1, which equals negative 284.23.

1) Water solid & liquid, is incompressible, hence volume EW is constant.

Energy balance EW:

The change in energy, Delta E, equals m times the difference between u2 and u1, equals Q minus W (since W equals 0, as V is constant).

T_EW equals 0 degrees Celsius, hence constant!

x_Ice equals the ratio of m_Ice to m_EW, which is 0.6.

x_liquid equals 1 minus x_Ice, which is 0.4.

u1 equals u_f of T0 plus x times the difference between u_g of T0 and u_f of T0, equals negative 200 kilojoules per kilogram.

u2 equals Q plus m_EW times u1 divided by m_EW, equals negative 185 kilojoules per kilogram.

x equals the ratio of u2 minus u_f plus T2 to u_liquid plus u_f plus T1, equals 0.4848.

x_solid equals 1 minus x_liquid, equals 0.5152.

e.) Delta S_12

Delta S_12 equals m2 times s2 minus m1 times s1.

m2 equals 1.4 kilograms,
m1 equals 1.0 kilograms,
s2 equals 5575 kilojoules per kilogram Kelvin,
s1 equals s_f of T1 equals 1350.85 kilojoules per kilogram Kelvin at T1 equals 70 degrees Celsius.

S equals the absolute value of Q divided by T2, equals 0.9549 kilojoules per Kelvin.

See all under liquid!

Fully compressed liquid at boiling temperature.