d) Semi-open system:

The change in energy is equal to the mass at state 2 times the internal energy at state 2 minus the mass at state 1 times the internal energy at state 1, which equals the mass flow rate at the exit times the specific enthalpy at the exit plus the sum of heat transfer minus the sum of work done by the system. This is further specified as 575 kilograms per second (reference TBA 4-2) with a saturation temperature of 100 degrees Celsius and a quality of 0.005. The mass flow rate at the exit equals the mass flow rate at state 2. The system is described as a horizontally oriented, just boiling liquid. The mass flow rate at the exit is given by the ratio of area TBA to area TBA 2 times the ratio of internal energy at the exit to internal energy at the exit, which equals the specific enthalpy of the fluid at the inlet plus the quality times the difference between the specific enthalpy of vaporization at the inlet and the specific enthalpy of the fluid at the inlet, all over the specific enthalpy of the fluid at the inlet. This value is crossed out and noted as 425.38. For TBA 2, the temperature at the inlet is 20 degrees Celsius and the specific enthalpy of the fluid at the inlet is 83.96 kilojoules per kilogram. The internal energy at state 2 is equal to the internal energy of the fluid at temperature 2, which is 252.55 kilojoules per kilogram. The system is described as a boiling liquid at a temperature of 70 degrees Celsius. The equation for the energy balance is given, and simplifying it results in the mass flow rate at the exit times the difference between the internal energy at state 2 and the specific enthalpy at the exit equals the heat transfer plus the mass at state 1 times the difference between the internal energy at state 1 and state 2. Solving for the mass flow rate at the exit, it is found to be 3589.4 kilograms per second.