The change in specific exergy, denoted as Delta e_{x,s}, is calculated as the difference between the specific exergy input, E_{x,s,in}, and the specific exergy output, E_{x,s,out}. This is expressed as:

Delta e_{x,s} equals the total mass flow rate, dot{m}_{ges}, times the expression (h_{0} minus h_{0} minus T_{0} times (S_{e} minus S_{0}) plus w_{0} squared over 2) minus the total mass flow rate, dot{m}_{ges}, times the expression (h_{0} minus h_{0} minus T_{0} times (S_{0} minus S_{0}) plus w_{0} squared over 2). Simplifying further, it becomes:

Delta e_{x,s} equals the total mass flow rate, dot{m}_{ges}, times the expression (h_{0} minus h_{0} minus T_{0} times (S_{e} minus S_{0}) plus w_{0} squared over 2 minus w_{0} squared over 2).

The product of the total mass flow rate, dot{m}_{ges}, the specific heat at constant pressure, c_{p}, and the temperature, T_{0}, equals 350 kilojoules per kilogram. The enthalpy, h_{0}, is calculated as h_{0} minus h_{0} equals c_{p} times (T_{0} minus T_{0}) equals 8.5 volts times 85.03 kilojoules per kilogram.

The temperature, T_{0}, is given as 293.15 Kelvin. The difference in entropy, S_{e} minus S_{0}, is calculated as c_{p} times the natural logarithm of (T_{0} over T_{0}) minus the gas constant, R, times (P_{0} over P_{0}). Simplifying, it becomes:

S_{e} minus S_{0} equals c_{p} times the natural logarithm of (T_{0} over T_{0}) equals 0.307 kilojoules per kilogram Kelvin.

Finally, the change in specific exergy, Delta e_{x,s}, is recalculated as:

Delta e_{x,s} equals the total mass flow rate, dot{m}_{ges}, times the expression (c_{p} times (T_{0} minus T_{0}) minus T_{0} times the natural logarithm of (T_{0} over T_{0}) plus w_{0} squared over 2 minus w_{0} squared over 2).

The change in specific exergy, Delta e_{x,s}, is then given as 56.25 times the total mass flow rate, dot{m}_{ges}, in kilojoules per kilogram.