The section describes a half-open closed system with the following equations:

- The change in energy, Delta E, equals the energy entering, Q_e, minus the energy leaving, Q_aus, minus the product of the mass flow rate out, m_dot_2, and the specific enthalpy at exit, h_e.
- The mass flow rate out, m_dot_2, equals the mass flow rate in, m_dot_1, plus the change in mass, Delta m_2.
- The equation m_dot_2 times u_2 minus m_dot_1 times u_1 equals the sum of m_dot_1 and m_dot_2 times u_2 minus m_dot_1 times u_1.
- The change in mass, Delta m_2, equals m_2.
- The product of the change in mass, Delta m_2, and the difference in specific enthalpy at exit and specific internal energy at exit, equals the product of mass, m, and the difference in specific internal energy between states 2 and 1.
- The change in mass, Delta m_2, is calculated as SIS times the difference in specific internal energy between 200 degrees Celsius and 100 degrees Celsius, divided by the difference in specific internal energy between 70 degrees Celsius and 200 degrees Celsius, resulting in 37.63 kilograms.

Specific enthalpy and specific internal energy values are given:
- Specific enthalpy at exit, h_e, at 200 degrees Celsius is 83.96 kilojoules per kilogram.
- Specific internal energy at state 2, u_2, at 70 degrees Celsius is 292.98 kilojoules per kilogram, from Table A-2.
- Specific internal energy at state 1, u_1, at 100 degrees Celsius is 448.04 kilojoules per kilogram.

The change in entropy, Delta S, equals the product of mass at state 2, m_2, and specific entropy at state 2, s_2, minus the product of mass at state 1, m_1, and specific entropy at state 1, s_1, equals the heat transfer, Q, times the difference in the inverse of the temperatures at exit, T_e, and at state, T_s. This results in a value of 1287.18 kilojoules per Kelvin.

Specific entropy values are:
- Specific entropy at state 2, s_2, at 70 degrees Celsius is 0.95849.
- Specific entropy at state 1, s_1, at 40 degrees Celsius is 1.306.

The rate of change of entropy, dS/dt, equals the heat transfer, Q, divided by the temperature at state 1, T_1, plus the heat transfer, Q, divided by the temperature at state 2, T_2, plus the entropy creation, S_cre.