Gas: specific heat at constant volume times (final temperature minus initial temperature) in a closed system, work done equals zero.

Change in energy equals heat transferred equals mass times gravity times (final internal energy minus initial internal energy).

The absolute value of heat transferred equals 3.6 times 10 to the power of 5 times (800 degrees Celsius minus 0.005 degrees Celsius) equals 1739.39 Joules.

Heat transferred equals negative of the absolute value of heat transferred, which is negative 1739.39 Joules.

For the second section:
The error in heat transferred equals the heat transferred equals mass times (final specific internal energy minus initial specific internal energy).
Specific internal energy at 0.000 degrees Celsius.
Initial specific internal energy equals latent specific internal energy plus (specific internal energy at water minus specific internal energy at test) equals negative 133.91 kilojoules per kilogram.
Heat transferred equals 75 kilojoules (from the test).
Final specific internal energy equals heat transferred divided by mass plus initial specific internal energy equals 75 divided by 0.1 minus 133.91 equals negative 75.91 kilojoules per kilogram.
Final specific internal energy equals specific internal energy at test plus x times (specific internal energy at water minus specific internal energy at test) implies x equals (final specific internal energy minus specific internal energy at test) divided by (specific internal energy at water minus specific internal energy at test) equals (negative 75.91 plus 335.442) divided by (negative 9.083 plus 335.442) equals 0.645.

0.0003 degrees Celsius.