d) 
- The specific heat at constant volume, \( c_v \), is 0.653.
- The specific heat at constant pressure, \( c_p \), is calculated as 8.314 Joules per mole Kelvin divided by 28.97 kilograms per kilomole, which equals \( c_p - c_v \).
- The gas constant, \( R \), is the difference between \( c_p \) and \( c_v \), which equals 0.29958.
- The ratio of specific heats, \( \kappa \), is the ratio of \( c_p \) to \( c_v \), which equals 7.2637.

3d)
- The heat removed from the ice water, \( Q_{12} \), is -7500 Joules.
- The pressure, \( p \), is 7.4 bar.
- The initial temperature, \( T_{01} \), is 0 degrees Celsius.
- The change in internal energy due to volume change is represented by \( m_1 (u_2 - u_1) = Q \).
- From the critical point, \( u_1 \) corresponds to \( x_{krit} = 0.6 \).
- From the table, \( u_2 \) is calculated as \( u_{krit} + x \cdot (u_{kritisch} - u_{gas}) \).
- \( u_2 \) is calculated as -337.58 kilojoules per kilogram plus 0.6 times (-0.895 minus 333.45).
- \( u_2 \) is -333.612 kilojoules per kilogram.
- \( u_2 \) is also calculated as -338.458 kilojoules per kilogram plus \( x \) times (-0.045 plus 333.458) kilojoules per kilogram.
- The negative of \( Q \) divided by \( m_1 \) equals \( u_2 - u_1 \).
- The negative of 7500 kilojoules divided by (0.036 kilograms plus 33.612 kilograms) equals the ratio of \( u \) in kilojoules per kilogram, which is 47 kilojoules per kilogram minus 28.25 kilojoules per kilogram.
- \( u_2 \) is -338.458 kilojoules per kilogram.
- \( x \) is calculated as 0.29 divided by (-0.045 plus 333.458 kilojoules per kilogram), which approximately equals \( x_{krit} 2 \).