Reference temperature \( T_{ref} \) is 295 Kelvin.

Entropy balance: zero equals the mass flow rate in times the difference in entropy \( s_2 - s_1 \) plus the heat transfer rate \( \dot{Q}_R \) divided by \( T_R \) plus the heat transfer rate \( \dot{Q}_{zu} \) divided by \( T_{zu} \) minus the heat transfer rate \( \dot{Q}_{ab} \) divided by \( T_{ab} \) plus the generated entropy rate \( \dot{S}_{er, z} \).

The generated entropy rate \( \dot{S}_{er, z} \) equals the mass flow rate in times the difference in entropy \( s_2 - s_1 \) plus the heat transfer rate \( \dot{Q}_R \) divided by \( T_R \) plus the heat transfer rate \( \dot{Q}_{zu} \) divided by \( T_{zu} \) minus the heat transfer rate \( \dot{Q}_{ab} \) divided by \( T_{ab} \).

Entropy \( s_2 \) at 100 degrees Celsius is 1.306 kilojoules per kilogram Kelvin, from Table A-2.

Entropy \( s_1 \) at 70 degrees Celsius is 0.9543 kilojoules per kilogram Kelvin, from Table A-2.

Thus, the generated entropy rate \( \dot{S}_{er, z} \) is 0.234 kilojoules per Kelvin.

The rate of change of energy \( \frac{dE}{dt} \) equals the mass flow rate 1 times \( u_1 \) plus \( \frac{p_1 v_1}{c^2} \) minus the mass flow rate 2 times \( u_2 \) plus \( \frac{p_2 v_2}{c^2} \) plus the heat transfer rate \( \dot{Q}_{R,12} \), which equals zero.

Change in internal energy \( dE = \Delta U \) equals the mass flow rate 2 times the difference in enthalpy \( h_1 - h_2 \) plus the heat transfer rate \( \dot{Q}_{R,12} \).

Enthalpy \( h_1 \) at 100 degrees Celsius is \( h_{u,1} \) plus \( x \) times the difference \( h_{ug} - h_{u,1} \).

The term \( \frac{T_{AB}}{\Delta t} \) equals 415.04 plus 0.005 times 2257.0, which equals 430.325 kilojoules per kilogram.

Enthalpy \( h_2 \) at 70 degrees Celsius is \( h_{u,2} \) plus \( x \) times the difference \( h_{ug} - h_{u,2} \).

The term \( \frac{T_{AB}}{\Delta t} \) equals 232.55 plus 0.005 times 2339.8, which equals 304.64 kilojoules per kilogram.

Change in internal energy \( \Delta U \) equals the mass flow rate 12 times the difference in internal energy \( h_{u,2} - h_{u,1} \) and \( u_2 - u_1 \).

Internal energy \( u_2 \) at 70 degrees Celsius is \( u_{u,2} \) plus \( x \) times the difference \( u_{ug} - u_{u,2} \).

The term \( \frac{T_{AB}}{\Delta t} \) equals 232.55 plus 0.005 times the difference 2466.8 minus 292.85, which equals 303.533 kilojoules per kilogram.

Internal energy \( u_1 \) at 100 degrees Celsius is \( u_{u,1} \) plus \( x \) times the difference \( u_{ug} - u_{u,1} \).

The term \( \frac{T_{AB}}{\Delta t} \) equals 415.04 plus 0.005 times the difference 2506.5 minus 418.34, which equals 423.837 kilojoules per kilogram.

The mass flow rate 12 times \( u_2 \) plus \( u_2 \) equals the mass flow rate 12 times the difference in enthalpy \( h_1 - h_2 \) minus the heat transfer rate \( \dot{Q}_R \).

The change in mass flow rate 12 times \( u_2 + h_2 - h_1 \) equals the mass flow rate 12 times the difference \( u_1 - u_2 \) minus the heat transfer rate \( \dot{Q}_R \).

The change in mass flow rate 12 equals the mass flow rate 12 times the fraction \( u_1 - u_2 + \frac{\dot{Q}_R}{\dot{m}_{12}} \) divided by \( u_2 + h_2 - h_1 \), which equals 3859.02 kilograms.

The heat transfer rate \( \dot{Q}_R \) is 35 times 1000 kilojoules.