e) The change in entropy, Delta S_12, is equal to the sum of the change in entropy of the reactor, Delta S_Reaktor, and the change in entropy of the inflow, Delta S_Zufluss.

The change in entropy of the reactor, Delta S_Reaktor, is calculated as 5735 kilograms times Delta R times the difference between s_2 and s_1.

For s_1: at 100 degrees Celsius with x equals 0.005, according to Table A2, s_1 is equal to (1 minus x) times s_f plus x times s_g, which calculates to 0.995 times 1.3069 kilojoules per kilogram Kelvin plus 0.005 times 7.358 kilojoules per kilogram Kelvin, resulting in 1.337 kilojoules per kilogram Kelvin.

The values for S_1 and S_3 are given as:
- S_1 at 20 and 70, saturated liquid, with a value of 0.5549 kilojoules per kilogram Kelvin.
- S_3 at 20 degrees, saturated liquid, with a value of 0.42366 kilojoules per kilogram Kelvin.

The change in entropy of the reactor, Delta S_Reaktor, is calculated as 3755 kilograms times the difference between 0.954 kilojoules per kilogram Kelvin and 1.337 kilojoules per kilogram Kelvin, minus 2158 kilojoules per Kelvin.

The change in entropy of the inflow, Delta S_Zufluss, is calculated as the mass flow rate, m, times the difference between S_2 and S_3, which is 3756.7 kilograms per second times the difference between 0.9549 kilojoules per kilogram Kelvin and 0.2566 kilojoules per kilogram Kelvin, resulting in 2473 kilojoules per Kelvin.

Finally, Delta S_12 is calculated as the sum of -2158 kilojoules per Kelvin and 2473 kilojoules per Kelvin, resulting in 2.75 kilojoules per kilogram.