In the reactor: The change in internal energy, Delta U, equals Q12, which is correct.

Q12 equals the mass m times the difference in specific internal energy from state 1 to state 2.

For state 1, at 100 degrees Celsius with a quality x0 of 0.005, according to Table A2, the specific internal energy u1 is calculated as:
(1 - x) times u_f plus x times u_g,
which equals 0.995 times 418.34 kilojoules per kilogram plus 0.005 times 2506.5 kilojoules per kilogram,
resulting in 423.38 kilojoules per kilogram.

For state 2, at 70 degrees Celsius, as a saturated liquid, according to Table A2, the specific internal energy u2 is 292.35 kilojoules per kilogram.

Q12 is then calculated as 5735 kilograms times (292.35 kilojoules per kilogram minus 429.38 kilojoules per kilogram),
resulting in -785154 kilojoules.

A horizontal line is drawn.

The inverse of the mass flow rate times negative Q12 equals the change in specific internal energy from state 2 to state 3, Delta u12.
The change in mass from state 1 to state 2, Delta m12, is calculated as negative Q12 divided by the difference in specific internal energy from state 2 to state 3.

For state 3, which is boiling at 20 degrees Celsius, according to Table A2, the specific internal energy u3 is 83.85 kilojoules per kilogram.

Delta m12 is then calculated as negative Q12 divided by (292.35 kilojoules per kilogram minus 83.85 kilojoules per kilogram), which equals 785154 kilojoules divided by 209 kilojoules per kilogram, resulting in 3756.71 kilograms.