Zero equals mass flow rate times enthalpy at entry minus mass flow rate times enthalpy at exit plus 100 kilowatts minus heat flow rate at exit minus work rate.

Heat flow rate at exit equals mass flow rate times enthalpy at entry minus mass flow rate times enthalpy at exit plus heat flow rate R.

From Table A2:
Enthalpy at entry, at 70 degrees Celsius, equals 292.88 kilojoules per kilogram.
Enthalpy at exit, at 100 degrees Celsius, equals 419.64 kilojoules per kilogram.
Mass flow rate at entry equals 0.3 kilograms per second.
Mass flow rate at exit equals 0.3 kilograms per second minus mass flow rate at entry.

Therefore, heat flow rate at exit equals mass flow rate times (enthalpy at entry minus enthalpy at exit) plus 100 kilowatts.
Heat flow rate at exit equals 62.182 kilowatts.

For a semi-open system:
M2 times U2 minus M1 times U1 equals change in mass times enthalpy at entry plus heat minus cooling work.
M1 equals total mass.
Heat equals heat flow rate at exit equals 835 megajoules.
M2 equals total mass plus mass B.
(total mass of gas plus mass B) times U2 minus mass of gas times U1 equals change in mass times enthalpy at entry plus negative heat flow rate at exit.
Mass of gas times U2 plus mass B times U2 minus mass of gas times U1 equals change in mass times h plus x.
Change in mass times (U2 minus enthalpy at entry divided by U2 minus enthalpy at entry) equals mass of gas times U1 plus x.
Change in mass equals (total mass times enthalpy at entry plus heat) divided by (U2 minus enthalpy at entry).

Enthalpy at entry equals enthalpy at 100 degrees minus enthalpy at 20 degrees.
Enthalpy at entry at 20 degrees Celsius equals 83.36 kilojoules per kilogram.

Total mass equals 5755 kilograms.

Change in mass equals (5755 kilograms times 418.94 kilojoules per kilogram minus 835 times 10^3 kilojoules) divided by (292.35 minus 83.36).

Change in mass equals 11368.9 kilograms.