The average temperature T_KF is given by the integral of T with respect to s from 1 to 2, divided by the difference s2 minus s1.

The rate of change of entropy generation rate S dot with respect to time t equals the mass flow rate m dot times the difference in entropy sA minus sE, plus the heat input rate Q dot zu divided by the average temperature T bar, plus the entropy at state f2.

The heat input rate Q dot zu equals the heat flow rate q dot zu, which is the product of the difference s2 minus s1 and the average temperature T bar. Therefore, the average temperature T bar equals the heat flow rate q dot zu divided by the difference s2 minus s1.

The heat flow rate q dot zu equals the heat output rate Q aus divided by the mass flow rate m dot.

In the student solution:

The average temperature T is given by the integral of T with respect to s from a to e, divided by the difference sa minus se.

The rate of change of heat flow rate Q dot with respect to time t equals the mass flow rate m dot times the difference in entropy se minus sa, plus the heat input rate Q dot zu divided by the temperature T, plus the generated entropy rate S dot erz.

Description of the figure: There is an arrow pointing to the right labeled "High heat exchanger".

The rate of change of heat flow rate Q dot with respect to time t equals the mass flow rate m dot times the difference in enthalpy he minus ha, plus the heat input rate Q dot zu minus the work rate W dot.

The mass flow rate m dot equals the heat input rate Q dot zu divided by the difference in enthalpy ha minus he.

The difference in enthalpy ha minus he equals the change in enthalpy Delta h, which is the specific heat at constant pressure cp(0) times the difference in temperature Ta0 minus Te.