The mass flow rate times the average temperature T_LF is 295 Kelvin, and the heat input rate Q_zu is 65 kilowatts.

The rate of change of heat flow with respect to time is equal to the mass flow rate times the difference between the entropy at exit and at entry, plus the heat input rate divided by the temperature, plus the generated entropy rate.

The generated entropy rate is equal to the mass flow rate times the difference between the entropy at state k and at exit, plus the heat input rate divided by the temperature.

The generated entropy rate is also equal to the heat input rate divided by the difference between the enthalpy at entry and at exit, times the difference between the entropy at entry and at exit minus one over the temperature.

This equals the heat input rate times the quantity of the natural logarithm of the ratio of temperature at entry to temperature at exit divided by the difference between the temperature at entry and T1 minus one over the temperature, which equals 1.4118 kilojoules per kilogram per second.

The change in entropy is equal to the specific heat at constant pressure times the natural logarithm of the ratio of temperature T2 to T1 minus the gas constant times the natural logarithm of the ratio of pressure p2 to p1.

In the figure, there is a rectangular box with two circular ends. An arrow labeled Q_ab enters the left circular end and another arrow labeled Q_A exits the right circular end. An arrow labeled Q_ab equals losses exits the side of the box.

From state 1 to state 2, the heat Q_ab equals Q_A and is 35 megajoules.

The rate of change of energy is equal to the mass flow rate times the difference in enthalpy of water plus the heat Q_ab minus the velocity squared over two.

The change in energy equals the mass flow rate times the difference in enthalpy at entry and exit plus the heat Q_ab from state 1 to state 2.

The change in energy equals the change in internal energy, which is the mass of water times internal energy at state 1 minus internal energy at state 2.

Where the enthalpy at entry is the enthalpy of water plus the heat of fusion at 70 degrees Celsius equals 4.18 kilojoules per kilogram.

Internal energy at state 2 is the enthalpy at exit plus the heat of fusion at 70 degrees Celsius equals mass times 292.85 kilojoules per kilogram.

Internal energy at state 1 is the mass of gas times internal energy at state 1, which equals the internal energy at fusion at 120 degrees Celsius plus the difference between the internal energy of gas and fusion at 120 degrees Celsius times 0.005, equals 429.3728 kilojoules per kilogram.

The change in internal energy equals negative 785.14 kilojoules.

The mass flow rate from state 1 to state 2 equals the change in internal energy minus the heat from state 1 to state 2 divided by the difference in enthalpy at 150 degrees Celsius at entry and exit.

For the coolant, the specific heat at constant pressure is constant.

The rate of change of heat flow with respect to time equals the mass flow rate times the change in enthalpy plus the heat flow rate due to volume.