O equals m dot times e dot.

O equals m dot times e dot subscript str plus one minus T subscript 0 over T subscript j times Q dot subscript j minus W dot subscript t, u minus E dot subscript verl.

e dot subscript verl equals e dot subscript str minus W dot subscript t, u.

Equals 100 times h over g.

W dot subscript t, u equals m dot times e dot.

Description of the diagram: There is a large arrow pointing from the equation W dot subscript t, u equals m dot times e dot to the text "Storage location works turbine on" and "Loss leader".

Energy balance.

W dot subscript turbine over m dot equals h subscript 3 minus h subscript 4 over c subscript v times T subscript 3 minus T subscript 4 plus Q dot.

w subscript c equals m dot times g times c subscript p times T subscript 3 minus T subscript 0 plus w subscript 5 squared over 2.

m dot times g equals dots.

m dot subscript k plus m dot subscript m equals m dot subscript k times 1 plus 5.1, 2.53.

0 equals m dot subscript k times h subscript 2 minus h subscript 3 plus m dot subscript k times q subscript b.

Negative q subscript b equals m dot subscript k times c subscript p times T subscript 2 minus T subscript 3.

Turbine:

0 equals m dot subscript k times c subscript p times T subscript 1 minus T subscript 2 plus Q subscript kW to the power of 0 times W subscript t over kW.

Delta ex subscript str equals ex str subscript 6 times ex subscript 0.

Equals h subscript 6 minus h subscript 0 over T subscript 0 minus T subscript 0 times s subscript 6 minus s subscript 0 plus p subscript 0 times V subscript 6 minus V subscript 0 over V subscript 0.

Equals c subscript p times T subscript 6 minus T subscript 0 minus T subscript 0 times c subscript p times ln of T subscript 6 over T subscript 1 minus R times ln of p subscript 6 over p subscript 0 plus p subscript 0 times V subscript 6 minus V subscript 0.

V subscript 0 equals R times T over p subscript 0, V subscript 6 equals R times T over p subscript 0.

R equals c subscript p times 1 minus 1 over r subscript c.

c subscript v equals c subscript p over r subscript c.