The table lists various states with corresponding values for pressure in bar, temperature in degrees Celsius, specific enthalpy in kilojoules per kilogram, and specific entropy in kilojoules per kilogram Kelvin. The states are numbered from 0 to 6, with specific values provided for some states:
- State 1 has a pressure of 0.191 bar.
- State 2 has a temperature of 243.15 degrees Celsius.
- State 5 has a pressure of 0.5 bar, a temperature of 431.9 degrees Celsius, a specific enthalpy of 220 kilojoules per kilogram, and specific entropy is not provided.
- Other states do not have any values provided.

The equations provided are:
- The pressure at State 1 equals the pressure at State 5.
- The entropy at State 1 equals the entropy at State 2.
- The entropy at State 2 equals the entropy at State 1.
- The entropy at State 5 equals the entropy at State 6.
- The entropy at State 6 equals the entropy at State 5.

The graphical description describes a Temperature-Entropy diagram:
- The x-axis represents specific entropy in kilojoules per kilogram Kelvin.
- The y-axis represents temperature in Kelvin.
- Two isobars are drawn on the graph, one at 0.5 bar and another at 0.191 bar.
- The isobar at 0.5 bar curves upwards from the bottom left to the right.
- The isobar at 0.191 bar is positioned to the left of the 0.5 bar isobar.
- Points 1 through 6 are marked on the graph, indicating different states.
- Arrows show transitions between these points: from 1 to 2, 2 to 3, 3 to 4, 4 to 5, and 5 to 6.