Energy balance around the whole turbine:

Zero equals mass flow rate times the difference in enthalpy between the exit and the entrance multiplied by half the difference in the squares of the outlet and base velocities.

Energy balance around the nozzle:

Zero equals mass flow rate times the sum of the difference in enthalpy between state 5 and state 6 and half the difference in the squares of the velocities at state 5 and state 6, plus the heat transfer rate times the terms (adiabatic) and (isobaric).

Zero equals mass flow rate times the difference in entropy between state 5 and state 6 plus the heat transfer rate divided by temperature times the term (adiabatically reversible).

The difference in entropy between state 5 and state 6 equals the specific heat at constant pressure times the natural logarithm of the ratio of temperatures at state 5 and state 6 minus the gas constant times the natural logarithm of the ratio of pressures at state 5 and state 6, which equals zero.

The ratio of temperatures at state 5 to state 6 equals the ratio of pressures at state 5 to state 6 raised to the power of the gas constant divided by the specific heat at constant pressure.

The temperature at state 6 equals 328.675 Kelvin.

The difference in enthalpy between state 5 and state 6 equals the specific heat at constant pressure times the difference in temperatures between state 5 and state 6, which equals 109.998 kilojoules per kilogram.

The square of the velocity at state 6 equals half the difference in the squares of the velocities at state 5 and state 6.

The velocity at state 6 equals the square root of twice the difference in enthalpy between state 5 and state 6 plus the square of the velocity at state 5, which equals 507.29 meters per second.

The specific heat at constant pressure equals the specific heat at constant volume divided by the specific heat ratio, which equals 0.7185 kilojoules per kilogram Kelvin.

The gas constant equals the specific heat at constant pressure minus the specific heat at constant volume, which equals 0.289 kilojoules per kilogram Kelvin.