c) The change in exergy due to the stream, denoted as Delta e_x,str, is calculated as follows:
- The expression inside the brackets includes the change in enthalpy (h_6 - h_6), the product of the reference temperature (T_0) and the change in entropy (s_6 - s_6), and half the difference of the squares of velocities (w_6 squared minus w_0 squared divided by 2).
- The change in enthalpy (h_6 - h_6) equals c_p times (T_0 minus T_6), which is -85.43 kilojoules per kilogram.
- The change in entropy (s_6 - s_6) equals c_p times the natural logarithm of (T_0 over T_6) minus R times (p_0 over p_6), which is -0.3013 kilojoules per kilogram Kelvin.
- Half the difference of the squares of velocities (w_6 squared minus w_0 squared divided by 2) is -108.64 kilojoules per kilogram.
- The total change in exergy due to the stream, Delta e_x,str, is underlined as -96.187 kilojoules per kilogram.

d1) The equation given (from the hint) is:
- Zero equals negative Delta e_x,str plus the product of (1 minus T_0 over T) and (Q dot over m dot_ges) minus (W dot over m dot_ges) minus e_x,vel.
- The term (1 minus T_0 over T) times (Q dot over m dot_ges) equals 159.073 kilojoules per kilogram.
- Q dot over m dot_ges equals 159.073 kilojoules per kilogram when divided by 1.
- The total mass flow rate, m dot_ges, is 6.293.
- The mass flow rate of component k, m dot_k, equals m dot_ges minus m dot_k, which is 5.293.
- m dot_k equals m dot_ges times (1 over the sum of 5.293 and 1), which simplifies to m dot_ges over 6.293.

The exergy due to velocity, e_x,vel, is calculated as:
- Negative Delta e_x,str plus the product of (1 minus T_0 over T) and (Q dot over m dot_ges), which equals 250.286 kilojoules per kilogram.
- The final value is underlined as 57.886 kilojoules per kilogram.