In a semi-open reaction mixture system, the change in energy is given by the equation:

Delta E equals m subscript 2 times U subscript 2 minus m subscript 1 times U subscript 1 plus the cancelled terms Delta KE plus Delta PE, which equals Delta m subscript ein times h subscript ein plus the cancelled terms Q subscript out minus Q subscript in.

The change in mass entering, Delta m subscript ein, is equal to m subscript 2 minus m subscript 1, which implies m subscript 2 equals m subscript 1 plus Delta m subscript ein.

The change in mass entering is also given by the equation:

Delta m subscript ein equals the fraction (Delta m plus m subscript 1 times U subscript 2 minus m subscript 1 times U subscript 1) divided by (h subscript ein minus U subscript 2).

Simplifying further, Delta m subscript ein equals the fraction (m subscript 2 times U subscript 2 minus m subscript 1 times U subscript 1) divided by (h subscript ein minus U subscript 2), which simplifies to m subscript 1 times the fraction (U subscript 2 minus U subscript 1) divided by (h subscript ein minus U subscript 2).

The change in mass, Delta m, is 3,469.69 kilograms.

Additional details provided include:
- m subscript 1 equals m subscript ges equals 5755 kilograms.
- From Table A-2:
  - h subscript ein at 20 degrees Celsius equals 83.96 kilojoules per kilogram.
  - U subscript 2 at 70 degrees Celsius equals 222.87 kilojoules per kilogram.
  - U subscript 1 at 70 degrees Celsius equals 418.94 kilojoules per kilogram.