The change in energy is given by the negative absolute value of Q12 minus the work W12 at constant volume, since the process is isochoric.

The mass of the working fluid times the change in internal energy from state 1 to state 2 of the working fluid equals the negative of Q12.

At 0 degrees Celsius, the internal energy of the working fluid, u1, is equal to the internal energy of the liquid plus the fraction xA times the difference between the internal energy of ice and the liquid.

The internal energy of the liquid at 0 degrees Celsius is -0.045 kilojoules per kilogram.

The internal energy of ice at 0 degrees Celsius is -333.45 kilojoules per kilogram.

The internal energy of the working fluid is -290.08 kilojoules per kilogram.

At 0 degrees Celsius, the internal energy of the working fluid at state 2, u2, is equal to the internal energy of the liquid plus the fraction x2 times the difference between the internal energy of ice and the liquid.

The temperature of the working fluid at state 2 equals the ambient temperature at state 2.

The internal energy of the liquid at 0.003 degrees Celsius is -0.033 kilojoules per kilogram.

The internal energy of ice at 0.003 degrees Celsius is -333.44 kilojoules per kilogram.

The negative of Q12 plus the internal energy of the working fluid equals the internal energy of the liquid plus the fraction x2 times the difference between the internal energy of ice and the liquid.

The fraction x2 is given by the ratio of Q12 to the sum of the mass of the working fluid plus the internal energy of the working fluid minus the internal energy of the liquid (ice).

The difference in internal energy between ice and liquid at 0.003 degrees Celsius.

E stands for solid and F stands for liquid.