The upward velocity omega_up is 200 meters per second.
The initial pressure p_0 is 0.9316 bar.
The initial temperature T_0 is negative 30 degrees Celsius, which is equivalent to 270.15 Kelvin.
The initial entropy S_0 is not specified.
The total mass flow rate dot_m_ges is the sum of dot_m_n and dot_m_k.

At state 1, the entropy S_1 is equal to S_0.
The temperature T_1 and pressure p_1 are not specified.
At state 5, the entropy S_5 is equal to S_0.
The temperature T_5 is 431.8 Kelvin.
The pressure p_5 is 0.5 bar.
The velocity omega_5 is 200 meters per second.

The temperature T_2 is not specified.
The pressure p_2 is equal to p_3.
The temperature T_3 is not specified.
The pressure p_3 is equal to p_2.
The temperature T_4 and pressure p_4 are not specified.

At state 6, the entropy S_6 is equal to S_5 and is isentropic.
The temperature T_6 is calculated as T_5 times the ratio of p_6 over p_5 raised to the power of (n-1)/n, resulting in 328.0747 Kelvin.

The heat transfer Q is the product of the total mass flow rate dot_m_ges and the sum of h_5 minus h_6 plus half the difference of omega_5 squared and omega_6 squared.
This is equal to the product of c_p and the difference of T_5 and T_6 plus half of omega_5 squared minus half of omega_6 squared.

The velocity omega_6 is the square root of twice the product of c_p and the difference of T_5 and T_6 plus omega_5 squared, resulting in 507.244 meters per second.

The standard entropy S_0 degrees is equal to S_n degrees, which is 270.26 kilojoules per kilogram Kelvin.