With T2 equals negative 22 degrees Celsius. The pressure P2 equals P1 equals 1.2132 bar from Table A-10. The fraction (h minus hf) divided by (hg minus hf) equals x1 equals 0.3347 underlined.

Student Solution:

Graph 1:

The first graph is a phase diagram with pressure p in bar on the vertical axis and temperature T in degrees Celsius on the horizontal axis. The graph contains three regions labeled "solid", "fluid", and "gas". 

- The "solid" region is located in the upper left part of the graph.
- The "fluid" region is located in the upper right part of the graph.
- The "gas" region is located in the lower part of the graph.

There are three lines separating these regions:

1. A line starting from the origin and curving upwards to the right, separating the "solid" and "gas" regions. This line is labeled with points 1 and 2.
2. A line starting from the origin and curving upwards to the right, separating the "solid" and "fluid" regions.
3. A line starting from the origin and curving upwards to the right, separating the "fluid" and "gas" regions. This line intersects the other two lines at a point labeled "Triple".

Graph 2:

The second graph is another phase diagram with pressure p in bar on the vertical axis and temperature T in degrees Celsius on the horizontal axis. The graph contains three regions labeled "solid", "fluid", and "gas". 

- The "solid" region is located in the lower left part of the graph.
- The "fluid" region is located in the lower part of the graph.
- The "gas" region is located in the upper right part of the graph.

There are two lines separating these regions:

1. A line starting from the origin and curving upwards to the right, separating the "solid" and "fluid" regions. This line is labeled with points 1 and 2.
2. A line starting from the origin and curving upwards to the right, separating the "fluid" and "gas" regions. This line intersects the other line at a point.