b)

A table with seven columns labeled d, p, T, x, w, q, s, and four rows including headers:
- Row 1: d equals 1, p equals p1, T equals T_iso, x equals 0, w, q, and s are empty.
- Row 2: d equals 2, p equals p2, T equals 90 degrees, x equals 1, w equals 2.8 W, q equals q23 equals 0, s is empty.
- Row 3: d equals 3, p equals p3, T, x equals 0, w, q, and s are empty.

List of items:
- T_i equals 10 K over subpoint t equals 10 degrees.
- The average T_verd equals the average T minus delta t_k equals 4 degrees.
- s_2 is less than s_3.
- First HS from 2 to 3 instead of f. process.
- 0 equals m_dot from 2 to 3 times [h_2 minus h_3] plus Q_dot minus W_k_dot, adiabatic.
- v_k_dot divided by [h_2 minus h_3] equals m_R_dot.

Equations:
- Epsilon_K equals Q_K_dot divided by W_T_dot equals Q_K_dot divided by W_K_dot.
- For Q_K_dot, 1 tis from A to Z:
  0 equals m_dot times [h_1 minus h_2] plus Q_K_dot minus W^0.
- Q_K_dot equals m_dot times [h_2 minus h_1].
- Q_K_dot equals 0.27 times 6 kJ/s equals 2.96 kW.
- Epsilon_K equals 8.79.

Further equations:
- h_2 equals h_g at T_2 equals 47 degrees equals 242.53 kJ/kg.
- s_2 equals s_g at R equals 40 equals 0.9169 kJ/(kgK).
- h_3 equals (s at s_2 equals s_3 at Mischv.).
- h_3m equals (s at s_2 equals 0.90 kJ/(kgK)) equals 249.15 kJ/kg.
- h_3c equals (s at s_2 equals 0.937 kJ/(kgK)) equals 243.66 kJ/kg.
- h_3 equals (s_2 minus s_3c) divided by (s_3m minus s_3c) times (h_3m minus h_3c) plus h_3c equals 264.33 kJ/kg.
- m_R_dot equals A_dot times s_4 divided by (s_3 minus s_5) equals 1.543 times 10^(-3) kg/s.