S5 equals S6.

Zero equals the change in entropy, which is the integral from T5 to TC of the isobaric specific heat capacity over temperature dT minus the gas constant R times the natural logarithm of the ratio of P0 to P5.

Zero equals the isobaric specific heat capacity times the quantity of the natural logarithm of the ratio of TC to T5 minus R times the natural logarithm of the ratio of P0 to P5.

Also, the ratio of TC to T5 equals the ratio of P0 to P5 raised to the power of (n-1) over n, which implies that TC equals T5 times the ratio of P0 to P5 raised to the power of (n-1) over n.

TC equals 328.07 Kelvin.

Zero equals the mass flow rate times the quantity of h5 minus h6 plus half the difference of the squares of w5 and w6, plus the relative heat flow rate plus the difference of the total heat flow rate and the sum of the mass flow rates in.

Zero equals h5 minus h6 plus half the difference of the squares of w5 and w6 minus the rate of work.

The rate of work equals the square root of two times the quantity of h5 minus h6 minus the rate of work plus half the square of w5.

The rate of work W equals the heat flow rate times the difference of T0 and T5 divided by one minus the efficiency eta.

The rate of work Wc equals 259.56 kilojoules.

The rate of work Wc equals the square root of two times the quantity of the absolute value of the rate of change of h5 minus the rate of change of hc minus half the square of w5.

w5 equals 220 meters per second, assuming an ideal gas.

The difference of h5 and hc equals the specific heat capacity at constant pressure times the difference of T0 and T5.

The rate of work Wc equals the square root of two times the quantity of the specific heat capacity at constant pressure times the difference of T0 and T5 minus the product of the heat flow rate and the difference of T0 and T5 divided by one minus the efficiency eta minus half the square of w5.

The rate of work Wc equals 551.5 kilojoules per second.

The rate of work Wc equals 510 kilojoules per second divided by T0 equals 310 Kelvin.

Zero equals the mass flow rate times the quantity of the enthalpy at the entrance minus the enthalpy at the exit minus T0 times the difference of entropy at the entrance and exit plus half the difference of the squares of w5 and w0, plus the heat flow rate in minus the ideal exergy.

The change in exergy equals the rate of work Wc minus the heat flow rate minus T0 times the difference of entropy at states 0 and 1 plus half the difference of the squares of w5 and w0.

The change in exergy equals the specific heat capacity at constant pressure times the quantity of T0 minus Ta minus T0 times the natural logarithm of the ratio of T0 to Ta plus half the difference of the squares of w5 and w0.

h0 minus h0 equals the specific heat capacity at constant pressure times the difference of T2 and T0.

s0 minus s0 equals the specific heat capacity at constant pressure times the natural logarithm of the ratio of T0 to T0.

The ideal exergy equals T0 times the rate of change of entropy due to exergy.

The rate of change of entropy due to exergy equals the mass flow rate times the difference of entropy at the exit and entrance.

The ineffectual exergy equals T0 times the difference of entropy at the exit and entrance.