T2 equals 70 degrees Celsius, the mass flow rate at e2 and the mass flow rate out both equal zero.

The change in mass at 20 degrees Celsius.

The heat flow Q_R12 equals the heat flow Q_am, which is 35 megajoules.

Energy flow around water, closed system:

E2, s2 minus the quotient of Q_R12 and m12 equals the change in mass from 1 to 2 times the difference between u1 and u2.

The change in mass from 1 to 2 equals the quotient of Q_R12 and the difference between u2 and u1.

u2 at 70 degrees Celsius is 32.95 kilojoules per kilogram, refer to Table A2.

u1 at 100 degrees Celsius is 417.84 kilojoules per kilogram, refer to Table A2.

The change in mass from 1 to 2 is negative 35.10 kilojoules per kilogram.

The difference between 292.95 and 417.84 kilojoules per kilogram equals 277.8 kilograms.

Continuation:

Caloric System:

The product of m2 and u2 minus the product of m1 and u1 equals the product of the change in mass from 1 to 2 and h_ein plus Q_aus. m2 equals m1 plus the change in mass from 1 to 2. The product of the change in mass from 1 to 2 and h_ein minus the product of m1 plus the change in mass from 1 to 2 and u2 equals the product of m1 and u1 minus Q_aus. The product of the change in mass from 1 to 2 and the difference between h_ein and u2 equals zero. The change in mass from 1 to 2 equals the quotient of the difference between the product of m1 and u1 and Q_aus plus the product of u2 and m1, and the difference between h_ein and u2.

h_ein equals 83.96 kilojoules per kilogram, refer to Table A-2 at 20 degrees Celsius. u1 at 1000 degrees Celsius is 4186.94 kilojoules per kilogram, refer to Table A2. u2 at 20 degrees Celsius is 292.55 kilojoules per kilogram, refer to Table A2. Q_aus equals negative 35 megajoules.