Given: angular velocity omega_2 equals omega_1 and temperature T_2. The ratio of temperature T over standard temperature T_s equals the ratio of pressure P over standard pressure P_s raised to the power of (gamma minus 1) divided by gamma. Temperature T_2 equals the ratio of pressure P_2 over P_1 raised to the power of (gamma minus 1) divided by gamma, multiplied by temperature T_1, which equals the ratio of 0.5 bar over 0.1 bar raised to the power of (1.4 minus 1) divided by 1.4, multiplied by 431.5 Kelvin, resulting in a temperature T_2 of 328.075 Kelvin.

The rate of change of energy dE/dt equals the sum over i of mass flow rate m dot_i times (enthalpy h_i minus h_e plus half the difference of omega_i squared minus omega_e squared), plus the sum over j of heat flow rate Q dot_j minus the sum over u of work rate W dot_u. Zero equals mass flow rate m dot_a times (enthalpy h_e minus h_a plus half the difference of omega_e squared minus omega_a squared). Two times (enthalpy h_2 minus h_e) equals omega_e squared minus omega_2 squared, implying omega_2 equals the square root of two times (enthalpy h_2 minus h_e) plus omega_2 squared.

Enthalpy h_a equals enthalpy at 431.5 Kelvin, denoted as A2Z. Enthalpy h_a equals enthalpy at 431.5 plus 1.5 times the ratio of enthalpy at 440 Kelvin minus enthalpy at 430 Kelvin over 10, resulting in 432.364 kilojoules per kilogram.

Enthalpy difference h_2 minus h at 328.075 Kelvin equals enthalpy at 320 Kelvin plus 8.075 times the ratio of enthalpy at 350 Kelvin minus enthalpy at 320 Kelvin over 10, resulting in 328.405 kilojoules per kilogram.

Angular velocity omega_1 equals omega_3 equals 220 meters per second. Angular velocity omega_2 equals the square root of two times (enthalpy h_1 minus h_2) plus omega_1 squared, resulting in 220.47 meters per second.

The rate of energy transfer dot_E_x_sir equals mass flow rate dot_m times energy per unit mass e_x_sir, which equals dot_m times (enthalpy h_0 minus h_y minus temperature T_0 times (entropy s_0 minus s_y) plus kinetic energy ke_0 plus high pressure component hpc). Zero equals initial energy e_x_sir_0 equals final energy e_x_sir_e. Energy e_x_sir equals (enthalpy h_0 minus h_y minus temperature T_0 times (entropy s_0 minus s_y) plus kinetic energy ke_0 plus high pressure component hpc) minus the same expression, resulting in zero.

Enthalpy h_0 equals enthalpy at temperature T_0 equals enthalpy at 328.075 Kelvin, interpreted in section b as 328.405 kilojoules per kilogram. Enthalpy h_ke equals enthalpy at 243 Kelvin. Enthalpy h_e equals enthalpy at 50 degrees Celsius equals enthalpy at 243 Kelvin, which equals enthalpy at 240 Kelvin plus 3.15 times the ratio of enthalpy at 250 Kelvin minus enthalpy at 240 Kelvin over 10, resulting in 243.129 kilojoules per kilogram.

Temperature T_y equals T_0 equals 243.15 Kelvin. Entropy s_0 equals entropy at 328.075 Kelvin, which equals entropy at 320 Kelvin plus 8.075 times the ratio of entropy at 330 Kelvin minus entropy at 320 Kelvin over 10, resulting in 1.752 kilojoules per kilogram Kelvin. Entropy s_e equals entropy at 243.15 Kelvin, which equals entropy at 240 Kelvin plus 3.15 times the ratio of entropy at 250 Kelvin minus entropy at 240 Kelvin over 10, resulting in 1.493 kilojoules per kilogram Kelvin.

Kinetic energy ke_0 equals half times velocity v_0 squared, which equals half times 510 meters per second squared, resulting in 130.050 meters squared per second squared. Kinetic energy h_ke equals half times velocity v_e squared, which equals half times 200 meters per second squared, resulting in 20.000 meters squared per second squared.

The change in energy Delta e_2_out equals enthalpy h_e minus h_c minus temperature T_0 times (entropy s_e minus s_c) plus kinetic energy h_ze minus h_zc, resulting in 122.150 kilojoules per kilogram.