W_s, P_s, T_s, P_6 are given.

The nozzle is adiabatically reversible (isentropic).

This implies that T_6 minus T_5 times the ratio of P_6 over P_5 raised to the power of (n-1) over n equals 431.9 Kelvin times the ratio of 0.191 bar over 0.5 bar raised to the power of 0.4 over 1.4, which equals 328.0 Kelvin.

Zero equals the mass flow rate times the difference in enthalpy h_e minus h_a plus half the difference in the squares of the velocities omega_e squared minus omega_a squared plus g times the difference in height z_e minus z_a, plus the sum of heat transfer rates minus the sum of work rates.

Zero equals the mass flow rate times the difference in enthalpy h_e minus h_a plus half the difference in the squares of the velocities omega_e squared minus omega_a squared.

The difference in enthalpy h_e minus h_a equals the specific heat at constant pressure c_p times the difference in temperatures T_5 minus T_6.

The velocity at the exit w_e equals the velocity at state 5, w_5.

Negative two times the difference in enthalpy h_e minus h_a equals omega_a squared times the ratio of d over g times omega_a squared.

Omega_a squared equals omega_5 squared plus two times the specific heat at constant pressure for air c_p,iruft times the difference in temperatures T_5 minus T_6.

Omega_a equals the square root of omega_5 squared plus two times the specific heat at constant pressure for air c_p,iruft times the difference in temperatures T_5 minus T_6.

This results in a velocity of 220.47 meters per second.