d) Exergy balance around sr. FP (entire system).
Zero equals the exergy of the stream at point zero minus the exergy of the stream at point six plus the exergy of heat at point zero minus the exergy of heat at point six minus the exergy loss.
The exergy loss equals negative change in exergy of sr plus negative change in exergy of heat.
The change in exergy of heat is not specified.

Regarding entropy balance:
Zero equals the mass flow rate at point zero times entropy at point zero minus the mass flow rate at point six times entropy at point six plus the heat transfer rate at point zero divided by temperature at point zero plus generated entropy.
The generated entropy equals entropy at point six minus entropy at point zero minus heat transfer rate at point six divided by temperature at point zero.
The heat transfer rate at point six equals the heat transfer rate at point B, and the temperature equals the change in enthalpy from point six to point zero divided by the change in entropy from point six to point zero, which equals the specific heat capacity times the change in temperature divided by the specific heat capacity times the natural logarithm of the ratio of the initial temperature to the initial temperature, resulting in 288.87 Kelvin, and the change in entropy from point six to point zero equals the specific heat capacity times the natural logarithm of the ratio of the initial temperature to the initial temperature.
The generated entropy equals 3.7 kilojoules per kilogram per Kelvin.
The exergy loss equals the initial temperature times the generated entropy, resulting in negative 923.856 kilojoules per kilogram.