C sub P equals R sub g plus C sub v, which equals 166.28 Joules per kilogram Kelvin plus 633 Joules per kilogram Kelvin, equals 799.28 Joules per kilogram Kelvin. Delta U sub g equals C sub P times M sub g times Delta T, which equals 799.28 Joules per kilogram Kelvin times 0.0034 kilograms times (273.15 Kelvin minus 173.15 Kelvin), approximately equals 1358.8 Joules. V sub g2 equals M sub g times R sub g times T sub g2 divided by p sub g1, which equals 0.0034 kilograms times 166.28 Joules per kilogram Kelvin times 273.15 Kelvin divided by 1.4 times 10 to the power of 5 Pascals, approximately equals 1.103 Liters. Delta h equals Delta U divided by A, equals Delta U divided by A.

Chi sub Ew,1 equals the fraction of m sub Eis,1 over m sub EW, equals m sub Eis,1 divided by 0.1 kilograms, should equal 0.6, which implies m sub Eis,1 equals 0.06 kilograms, thus m sub FL equals m sub EW minus m sub Eis,1 equals 0.04 kilograms. U sub EW,1 equals m sub Eis,1 times U sub Eis,1 plus m sub FL times U sub FL, equals 0.06 kilograms times negative 333.458 kilojoules per kilogram plus 0.04 kilograms times negative 0.045 kilojoules per kilogram, approximately equals negative 20 kilojoules. U sub EW,2 equals U sub EW,1 plus the absolute value of Q sub 12, equals negative 20 kilojoules plus 1440.7 Joules, equals negative 18.56 kilojoules. The equation should equal m sub Eis,2 times U sub Eis plus m sub FL,2 times U sub FL, equals m sub Eis,2 times negative 333.458 kilojoules per kilogram plus (0.1 kilograms minus m sub Eis,2) times negative 0.045 kilojoules per kilogram, equals m sub Eis,2 times (negative 333.458 kilojoules per kilogram plus 0.045 kilojoules per kilogram) minus 0.1 kilograms times 0.045 kilojoules per kilogram. This implies m sub Eis,2 equals (0.1 kilograms times 0.045 kilojoules per kilogram minus 18.56 kilojoules) divided by (negative 333.458 kilojoules per kilogram plus 0.045 kilojoules per kilogram), approximately equals 0.0557 kilograms. Thus, chi sub Eis,2 equals the fraction of m sub Eis,2 over m sub EW, equals 0.0557 kilograms divided by 0.1 kilograms, equals 0.557.