data

The expression for ex_t1,6 is given by:
ex_t1,6 equals the quantity h_6 minus h_0 minus T_0 times the quantity s minus s_0 plus c_e1 divided by t.

neglect

The expression for ex_t1,0 is given by:
ex_t1,0 equals the quantity h_0 minus h_0 minus T_0 times the quantity s_0 minus s_0 plus c_e0 divided by t.

The expression for ex_t1,0 is also given by:
ex_t1,0 equals the quantity w squared divided by 2, which equals 200,000 square meters per square second, which equals 200,000 Joules per kilogram.

The change in enthalpy from state 0 to state 6 is given by:
h_6 minus h_0 equals the integral from 10 to 16 of c_p dT, which equals 71,006 Joules per kilogram Kelvin times the quantity 328.002 Kelvin minus 243.754 Kelvin, which equals 85,429 Joules per kilogram.

The change in entropy from state 0 to state 6 is given by:
s_6 minus s_0 equals the integral from 10 to 16 of c_p over T dT minus R times the natural logarithm of the ratio p_0 over p_0, which equals 71,006 Joules per kilogram Kelvin times the natural logarithm of the ratio 328.014 to 243.754, which equals 0.3016 Joules per kilogram Kelvin.

The expression for ex_t1,6 is also given by:
ex_t1,6 equals the quantity 85,429 Joules per kilogram minus 243.15 Kelvin times 0.3016 Joules per kilogram Kelvin plus the quantity 49.19 squared divided by 2, which equals 742.144 Joules per kilogram.

The change in ex_t1,c is given by:
Delta ex_t1,c equals ex_t1,6 minus ex_t1,0, which equals 722.144 Joules per kilogram.

The rate of change of entropy S with respect to time t is given by:
dS/dt equals the quantity v_seg times the quantity S_0 minus S_0 divided by t_seg times t_seg.

The quantity S_erz is given by:
S_erz equals v_seg times the quantity S_f minus S_0, which equals 0.3076 kilograms per second.

The rate of energy transfer E_x,vol is given by:
dot E_x,vol equals dot m_0 times S_erz, which equals 243.15 Amperes per second times 0.3076 reciprocal kilograms, which equals 73.334 reciprocal seconds.