The content includes a table with two rows and two columns, where the first row contains "U2" and "Q12", and the second row contains "U1" and "W12".

The energy balance around the system boundary is given by the equation:
dE/dt equals the sum of Q dot subscript j minus the sum of W dot subscript n.

It is stated that since there is no friction, W12 is reversible, and is given by the integral from 1 to 2 of p dV.

The specific volume v2 is calculated as:
v2 equals 3.14 times 10 to the power of negative 3 cubic meters divided by 3.429 times 10 to the power of negative 3 kilograms, which equals 0.918397 cubic meters per kilogram.

For vg2, it is calculated as:
vg2 equals m12 divided by p, which equals 3.449 times 10 to the power of negative 3 kilograms times 0.76628 cubic meters per kilogram times 273.15 Kelvin divided by 1.4 times 10 to the power of 2 Joules per cubic meter, approximately equals 1.103 times 10 to the power of negative 2 cubic meters.
Then, vg2 equals 1.103 times 10 to the power of negative 2 cubic meters divided by 3.449 times 10 to the power of negative 3 kilograms, which equals 0.324364 cubic meters per kilogram.

The work W12 is calculated as the integral from 1 to 2 of p dv, equals R T bar p times (v2 minus v1), equals 1.4 times 10 to the power of 2 Joules per cubic meter times (0.324364 cubic meters per kilogram minus 0.948837 cubic meters per kilogram), equals negative 83.164 Joules per kilogram.
Then, W12 equals W12 times m12, equals negative 83.164 Joules per kilogram times 3.449 times 10 to the power of negative 3 kilograms, equals negative 0.286434 Joules.

The internal energy change u2 minus u1 is calculated as:
u2 minus u1 equals usg2 minus usg1, equals cv times (T2 minus T1) times m12, equals 0.683 Joules per kilogram Kelvin times (273.15 Kelvin minus 77.15 Kelvin) times 3.449 times 10 to the power of negative 3 kilograms, equals negative 710827 Joules.

The heat Q12 is calculated as:
Q12 equals u2 minus u1 plus W12, equals negative 1.36614 Joules.
The absolute value of Q12 is 1.36614 Joules.

Another section includes a table with one column containing epsilon_w and Q12.

The energy balance equation is repeated, and it is noted that there is zero since there is no volume work.

The internal energy change U2 minus U1 equals Q12.

U1 is calculated as Uf plus x times (ug minus uf).

The pressure in the EW at state 1 is given by a table: mass fraction, thus p equals eta1 times UEW (given).

From Table 1:
uf equals negative 0.045 kilojoules per kilogram plus 0.6 times (negative 33.3 kilojoules per kilogram plus 0.045 kilojoules per kilogram), equals negative 200.09 kilojoules per kilogram.

U1 equals u1 times mEW, equals negative 200 kilojoules per kilogram.

U2 equals Q12 plus U1, equals 1366.4 kilojoules minus 200 kilojoules, equals negative 78.6336 kilojoules.

x is calculated as:
x equals (U2 minus Uf) divided by (ug minus uf), equals (negative 78.6336 kilojoules plus 0.045 kilojoules per kilogram times 0.1 kilograms) divided by (0.1 kilograms times (negative 33.3 kilojoules per kilogram plus 0.045 kilojoules per kilogram)), equals 0.5587.

m2 E1,0 equals x1 E1,1 times mEW, equals 0.5587 times 0.1 kilograms, equals 55.87 grams.