Partial derivative of E with respect to t equals the summation of m dot of t multiplied by h of t plus kinetic energy of t plus potential energy of t plus summation of Q dot of t minus summation of W dot of t.  

Zero equals m dot multiplied by (h_e minus h_a) plus Q dot_R minus Q dot_out. Therefore, Q dot_out equals m dot multiplied by (h_e minus h_a) minus Q dot_R.  

h_e at 100 degrees Celsius equals 292.84 kilojoules per kilogram, from Table A-2.  
h_a at 70 degrees Celsius equals 419.94 kilojoules per kilogram, from Table A-2.  

Q dot_out equals 0.3 kilograms per second multiplied by [(292.84 kilojoules per kilogram minus 419.94 kilojoules per kilogram)] plus 100 kilowatts equals 62.182 kilowatts.  

---

dE over dt equals the sum of m_i(t) multiplied by h_i(t) plus q_e(t) plus the sum of m_i(t) multiplied by c_i(t) minus the sum of m_i(t) multiplied by w_i(t).  

Delta E equals m_2 multiplied by u_2 minus m_1 multiplied by u_1 plus the sum of Q_i equals Q_out,12 equals 35 MJ.  

m_2 equals m_1 plus Delta m.  
m_1 equals 5755 kg.  
m_2 equals x multiplied by m_1 divided by m_1 equals m_1 multiplied by (1 minus x).  
m_2 equals Delta m.  

u_1 [100 degrees Celsius] equals 2506.5 kilojoules per kilogram.  
u_1f [100 degrees Celsius] equals 419.94 kilojoules per kilogram.  
u_2f [70 degrees Celsius] equals 292.95 kilojoules per kilogram.  
u_3f [20 degrees Celsius] equals 87.95 kilojoules per kilogram.  

Delta E equals m_3 multiplied by u_3 plus m_2 multiplied by u_2 minus m_1 multiplied by u_1 equals 35 MJ equals Delta m multiplied by u_3 plus m_1 multiplied by u_1f plus Delta m multiplied by u_2 minus m_1 multiplied by u_1.  

Delta m equals m_1 multiplied by u_1 minus m_1 multiplied by u_1f minus m_1 multiplied by u_2 divided by u_3 plus u_2 equals m_1 multiplied by u_1g plus m_1 multiplied by u_1f minus m_1 multiplied by u_2f plus 35 MJ divided by u_3f plus u_2f equals 0.005 multiplied by 5755 kg multiplied by 2506.5 kilojoules per kilogram plus 5755 kg multiplied by (1 minus 0.005) multiplied by 419.94 kilojoules per kilogram minus 5755 kg multiplied by 292.95 kilojoules per kilogram plus 35 MJ divided by 87.95 kilojoules per kilogram plus 292.95 kilojoules per kilogram.  

Delta m_12 equals 2176.02 kilograms.