R subscript g equals 8.314 divided by M subscript g equals 50 equals 0.16628 kilojoules per kilogram Kelvin.  

p times V equals m times R times T.  

Pressure in EW:  

A equals (10 times 0.05 squared) times pi divided by 4 equals 0.007853 square meters.  

p subscript EW equals m subscript K times g divided by A plus p subscript amb equals 1.33937 bar.  

Diagram: A cylinder is shown with labels for m subscript EW equals 0.1 kilograms and m subscript K equals 32 kilograms.  

Pressure in gas:  

p subscript g equals m subscript EW times g divided by A plus p subscript amb equals p subscript EW equals 1.33937 bar.

Energy balance for the water:  
Delta U equals Q12 minus W_water.  
Q12 equals W12 plus delta U equals 1.367 kJ.  

Work on the water:  
Delta U_water equals m_EW times (u2 minus u1).  
Delta U_water equals 0.1 times (1488 minus 1065).  
Delta U_water equals 423.2 J.  

Work on the water equals W_water minus work on the environment.  
Work on the environment equals p_amb times delta V equals 1 bar times 2.031 L equals 203.07 J.  

Work on the water equals 489.16 J equals W_water.

u2 equals u1 plus 423.22 equals 223.127 kilojoules per kilogram.  

u2 equals x multiplied by u vapor plus (1 minus x) multiplied by u liquid.  

x equals u2 minus u liquid divided by u vapor minus u liquid.  

x equals 0.0669.  

ps equals 1.46 bar.  

T equals 0 degrees Celsius.  

Somewhere an error in x adds up and is negative?  

u liquid equals u at 0 degrees Celsius equals 200.0328 kilojoules per kilogram.