An equation is written:  
dE/dt = 0 = m dot (h0 - h6) + (w0 squared - w6 squared) divided by 2 + qB divided by m dot K + W.  

Another equation is crossed out:  
0 = m dot (cp(T0 - T6) + (w0 squared - w6 squared) divided by 2) = - qB divided by m dot K.  

Additional crossed-out content:  
5.273: m dot K = m dot M - m dot MK.  
m dot K = m dot divided by 6.293 =

dE/dt equals zero equals m-dot multiplied by (h zero minus h six plus (w six squared minus w zero squared divided by two) plus q B) minus W.  

Zero equals h zero minus h six plus (w six squared minus w zero squared divided by two) plus q B.  

w six equals square root of (two multiplied by (h zero minus h six plus q B) plus w zero squared).  

Equals square root of (two multiplied by (cp multiplied by (T zero minus T six) plus q B) plus w zero squared).  

q B equals 1195 kilojoules per kilogram.  
T zero equals 243.15 kelvin.  
T six equals ...  
w zero equals 200 meters per second.  

Diagram: A schematic of a nozzle labeled "b".  

Zero equals S-dot irreversibility not equal to m-dot multiplied by (s zero minus s six) plus Q-dot divided by T zero adiabatic.  

s zero minus s six equals zero equals cp multiplied by ln(T six divided by T zero) minus R multiplied by ln(p six divided by p zero).  

T six divided by T zero equals (p six divided by p zero) raised to the power of (n minus one divided by n).  

T six equals T zero multiplied by (p six divided by p zero) raised to the power of (n minus one divided by n).  

T six equals 328.1 kelvin.  

w six equals 20.