The equation for exergy is:  
d exergy over dt is greater than the sum of exergy in minus the sum of exergy out minus the sum of work minus p zero times dv over dt minus exergy loss.  

Exergy equation:  
exergy in minus exergy out equals h zero minus h six minus T zero times (s zero minus s six) plus the sum of (1 minus T zero over T j) times Q j minus delta ke minus delta pe minus the sum of exergy x over m dot minus the sum of work ex over m dot.  

Find the sum of (1 minus T zero over T j) times Q j over m dot.  

Equals the sum of (1 minus T zero over T j) times Q j.  
Equals (1 minus 243.15 K over 1289 K) times 1195 kJ per kg.  
Equals 868.581 kJ per kg.  

Let z be between 0 and 1, and eta vs is less than 1.  

Efficiency equation:  
eta vs equals v zero over v zero minus h zero minus h hs over h zero minus h one.  

Energy balance equation:  
0 equals m dot times (h zero minus h one) plus Q dot minus W dot.  

Work equation:  
W dot over m dot equals W total equals h zero minus h four equals Cp times m dot times (T zero minus T i) equals 1.006 times (243.15 K minus T i).  

Find T i:  
In states 1 to 4, 0 equals m dot times (h four minus h one), so h four equals h one.  

From state 3 to 4:  
p four equals p three equals constant. Cp is constant. T four equals T i.  

Find T four:  
T four equals T three due to p proportional to T.  
T three equals 1289 K.  

Work total equals 1.006 times (243.15 minus 1289).  
Equals minus 1272.428 kW per kg.  

Exergy equation:  
Exergy equals h zero minus h six minus T zero times (s zero minus s six) plus 868.581 plus 1272.428.  
Equals Cp times (T zero minus T six) minus T zero times (Cp times (T zero over T six) plus 2202.02).