The page contains diagrams labeled as part of "Aufgabe 2 a)" (Task 2a).  

1. **First Diagram (Top)**:  
   - The diagram is a T-s (temperature-entropy) graph.  
   - Axes:  
     - The vertical axis is labeled "T [K]" (temperature in Kelvin).  
     - The horizontal axis is labeled "s [kJ/kg]" (entropy in kilojoules per kilogram).  
   - The process is illustrated with a cycle consisting of six states: 0, 1, 2, 3, 5, and 6.  
   - Key annotations:  
     - Between states 0 and 1: "adiabatisch irrev." (adiabatic irreversible).  
     - Between states 1 and 2: "isentrop." (isentropic).  
     - Between states 2 and 3: "isobar" (isobaric).  
     - Between states 3 and 5: "isobar" (isobaric).  
     - Between states 5 and 6: "isentrop." (isentropic).  
     - Between states 6 and 0: "adiabatisch irrev." (adiabatic irreversible).  
   - Additional notes:  
     - "p2 = p3" is written near states 2 and 3.  
     - "p0 = p6" is written near states 0 and 6.  

2. **Second Diagram (Middle)**:  
   - Another T-s graph with similar axes:  
     - Vertical axis labeled "T [K]" (temperature in Kelvin).  
     - Horizontal axis labeled "s [kJ/kg]" (entropy in kilojoules per kilogram).  
   - The process is illustrated with six states: 0, 1, 2, 3, 4/5, and 6.  
   - Key annotations:  
     - Between states 0 and 1: "adiabatisch irrev." (adiabatic irreversible).  
     - Between states 1 and 2: "isentrop." (isentropic).  
     - Between states 2 and 3: "isobar" (isobaric).  
     - Between states 3 and 4/5: "isobar Mantelstrom" (isobaric mantle flow).  
     - Between states 4/5 and 6: "isentrop." (isentropic).  
     - Between states 6 and 0: "adiabatisch irrev." (adiabatic irreversible).  
   - Additional notes:  
     - "p2 = p3 = p5" is written near states 2, 3, and 5.  
     - "p0 = p6" is written near states 0 and 6.  
     - "relativ als p0 = p6" (relative to p0 = p6) is noted near states 0 and 6.  

3. **Third Diagram (Bottom)**:  
   - A simplified cycle diagram without labeled axes.  
   - States 0, 1, 2, 3, 4/5, and 6 are connected in a similar sequence as the previous diagrams.  
   - No additional annotations are present.  

The diagrams visually represent the thermodynamic processes described in Task 2a.