0 to 1: adiabatic compression, \( p = 0.191 \, \text{bar} \)  
1 to 2: adiabatic-reversible compression (isentropic)  
2 to 3: isobaric heat addition  
3 to 4: adiabatic-irreversible turbine (entropy generation)  
4 to 5: isobaric mixing chamber, \( p = 0.5 \, \text{bar} \)  
5 to 6: reversible adiabatic nozzle (isentropic), \( p = 0.191 \, \text{bar} \)  

A T-s diagram is drawn with labeled points 0, 1, 2, 3, 4, 5, and 6.  
- The vertical axis is labeled \( T \, [K] \).  
- Temperatures are marked as 1289 K, 431.9 K, and 243.15 K.  
- The horizontal axis is labeled \( s \, [\text{kJ/kg·K}] \).  
- The diagram includes isobars and isentropic lines.  
- The label "Auf anderen Seite" (on the other side) is written near the diagram.  

---

Ss minus S6 equals zero equals Cp integral from Ts to Tg of one over T dt minus R ln of (ps over p6).  

Zero equals 1.006 kilojoules per kilogram Kelvin times [crossed-out section] minus R ln of (ps over p6).  

R equals Cp minus Cp over n equals 0.2874 kilojoules per kilogram Kelvin.  

ps equals 0.5 bar, p6 equals 0.191 bar.  

0.276575 kilojoules per kilogram Kelvin equals 1.006 kilojoules per kilogram Kelvin ln of (431.9 Kelvin over Tg).  

0.274925 equals ln of (431.9 Kelvin over Tg).  

1.316433 equals 431.9 Kelvin over Tg.  

Arrow pointing to Tg equals 328.08 Kelvin.  

Arrow pointing to hs minus h6 equals Cp times (Ts minus Tg).  

Equals 1.006 kilojoules per kilogram Kelvin times (431.9 Kelvin minus 328.08 Kelvin).  

Equals 104.44 kilojoules per kilogram.  

Minus 104.44 kilojoules per kilogram equals ws squared minus wc squared over 2.  

wc squared equals 2 times (ws squared over 2 plus 104.44 kilojoules per kilogram).  

Equals 48608.88.  

Minus wc equals 220.47 meters per second.

A graph is drawn with the y-axis labeled as "T [K]" and the x-axis labeled as "S [kJ/kg·K]".  
The graph includes the following points and annotations:  
- Point 0 at the bottom left.  
- Point 1 slightly above and to the right of point 0.  
- Point 2 further to the right of point 1.  
- Point 3 at the top right, with a steep curve connecting it to point 2.  
- Point 4 at the top, connected to point 3 by a curve labeled "P = P2".  
- Point 5 below point 4, connected by a curve labeled "P = P0".  
- Point 6 below point 5.  

Temperature values are marked on the y-axis:  
- 1289 at the top.  
- 431.9 below it.  
- 322.08 below 431.9.  
- 243.15 at the bottom.