Three diagrams are drawn:

1. The first diagram is labeled "T-s" (temperature-entropy) and shows curves with points labeled "2", "3", and "4". The arrow indicates movement between these points. The axes are labeled "T" (vertical axis) and "s" (horizontal axis). There is an additional label "s_KS/s_KSK" near the horizontal axis.

2. The second diagram is labeled "N-w" and shows curves with points labeled "1", "2", "3", "4", and "5". The arrow indicates movement between these points. The label "Isobar" is written near point "3". The axes are labeled "N" (vertical axis) and "w" (horizontal axis).

3. The third diagram is labeled "T-s" and includes curves with points labeled "0", "1", "2", "3", "4", and "5". The axes are labeled "T" (vertical axis) and "s_KS/s_KSK" (horizontal axis). Additional labels include "p3/p0", "p4/p0", and "p5/p0" near the curves.

Below the diagrams, the following text and equations are written:

---

Energy balance at the nozzle:  
Düse = Drossel Keine Arbeit  
Q = m dot times (h5 minus h6 plus w6 squared minus w5 squared divided by 2) equals 0 equals 0 equals 1 divided by m dot times (h5 minus h6 plus delta RE plus Q dot KS minus W dot KS) equals 0.  
h6 minus h5 equals w5 squared minus w6 squared divided by 2.

---

Isentropic adiabatic reversible:  
n equals k equals 1.4.  
T6 divided by T5 equals (p6 divided by p5) raised to the power of (n minus 1 divided by n).  
T6 equals T5 times (p6 divided by p5) raised to the power of (0.4 divided by 1.4).  
T6 equals 431.9 times (0.5 divided by 0.94) raised to the power of (0.4 divided by 1.4).  
T6 equals 378.1 K.

---

h6 minus h5 (ideal gas):  
c_p equals 1.006.  
h6 minus h5 equals c_p times (T6 minus T5).  
h6 minus h5 equals 1.006 times (w5 squared divided by 2) times (378.1 minus 431.9).  
h6 minus h5 equals minus 104.145 times w5 squared divided by 2.