Energy balance: Full volume remains constant.  

0 equals inlet mass flow rate times [enthalpy at inlet minus enthalpy at outlet plus change in specific internal energy plus change in specific entropy] plus heat flow from reaction plus heat flow out minus work.  

Using Table A-2:  
Enthalpy at inlet (70째C) equals enthalpy at 70째C equals 2,082.88 kilojoules per kilogram.  
Steam quality at inlet (x_in) equals 0.  

Enthalpy at outlet (100째C) equals enthalpy at 100째C equals 4,181.04 kilojoules per kilogram.  
Steam quality at outlet (x_out) equals 0.  

Negative heat flow out equals heat flow from reaction plus inlet mass flow rate times [enthalpy at inlet minus enthalpy at outlet].  

Negative heat flow out equals 100 kilowatts plus 0.3 kilograms per second times [2,082.88 kilojoules per kilogram minus 4,181.04 kilojoules per kilogram].  

Negative heat flow out equals negative 62.19 kilowatts.  

---

Thermodynamic mean temperature \( T_{KF} \):  

For stationary flow processes:  
Heat flow out equals heat flow into coolant.  

Thermodynamic mean temperature \( T_{KF} \) equals entropy at outlet minus entropy at inlet.  

Entropy at outlet minus entropy at inlet equals integral from inlet temperature to outlet temperature of specific heat divided by temperature.  

Entropy at outlet minus entropy at inlet equals 4.18 kilojoules per kilogram Kelvin times logarithm of [298.15 Kelvin divided by 288.15 Kelvin].  

Entropy at outlet minus entropy at inlet equals 0.14726 kilojoules per kilogram Kelvin.  

Thermodynamic mean temperature \( T_{KF} \) equals heat flow out divided by entropy at outlet minus entropy at inlet.  

Thermodynamic mean temperature \( T_{KF} \) equals 62.19 kilowatts divided by (0.14726 kilojoules per kilogram Kelvin).  

Thermodynamic mean temperature \( T_{KF} \) equals 283.12 Kelvin.  

---

Mass flow rate of coolant \( \dot{m}_{KF} \):  

Mass flow rate of coolant equals heat flow into coolant divided by specific heat times temperature difference.  

Mass flow rate of coolant equals 62.19 kilowatts divided by (4.18 kilojoules per kilogram Kelvin times 10 Kelvin).  

Mass flow rate of coolant equals 1.488 kilograms per second.

Entropy balance for a closed system:  
Q out divided by T KF minus Q out divided by T equals 100 degrees Celsius.  

Arrow leads to:  
E minus S dot erz equals Q dot out multiplied by (1 divided by 373.15 Kelvin minus 1 divided by 283.15 Kelvin).  

1 divided by T reactor minus 1 divided by T KF equals negative 45.147 watts per Kelvin.  

S dot erz equals 45.147 watts per Kelvin.  

---

Energy balance:  
m1 multiplied by U1 plus delta m12 multiplied by U12 equals m2 multiplied by U2.  

---

Table A-10:  
U1 equals U at 100 degrees Celsius equals 761.8 kilojoules per kilogram.  
U12 equals U at 20 degrees Celsius.  
U2 equals U at 70 degrees Celsius.