[Diagram]  
A labeled system boundary ("Sys. Grenze") is shown with arrows indicating mass flow (\( \dot{m} \)) entering and exiting. The diagram includes several components inside the boundary.  

\( \dot{Q} = 0 \)  
\( \dot{W} = 0 \)  
(Note: "Work goes into compression" is written in parentheses.)  

\( \frac{d ex}{dt} = \sum \dot{E}_{ex,str} - E_{ex,verl} \)  
\( = \dot{e}_{x,0} - e_{x,6} - e_{x,verl} \)  

(Note: Some terms are crossed out.)  

\( \dot{Q} \neq 0 \)  

"Stimmt nicht" (translated: "Not correct") is written next to the equation.

O equals exergy zero minus exergy six plus  

Entropy: O equals mass flow rate times (entropy e minus entropy a) plus heat flow divided by temperature plus entropy production rate.  

O equals entropy e minus entropy a plus heat flow divided by temperature plus entropy production rate.  

Entropy production rate equals exergy loss divided by temperature zero.  

O equals entropy zero minus entropy six plus heat flow divided by temperature plus exergy loss divided by temperature zero.  

Natural logarithm of (temperature zero divided by temperature six) plus heat flow divided by temperature plus exergy loss divided by temperature zero equals zero.  

Heat flow equals 1195 kilojoules per kilogram.  

Temperature equals 1289 kelvin.  

Exergy loss equals negative natural logarithm of (temperature zero divided by temperature six) times heat flow divided by temperature times temperature zero.  

Exergy loss equals negative 152.1 kilojoules per kilogram.  

(Underlined: exergy loss equals negative 152.1 kilojoules per kilogram.)