Exergy of a flow  

Exergy flow equals mass flow rate multiplied by the sum of enthalpy minus reference enthalpy minus reference temperature multiplied by entropy minus reference entropy plus kinetic energy plus potential energy.  

Equation:  
Exergy flow equals mass flow rate multiplied by the sum of enthalpy minus reference enthalpy minus reference temperature multiplied by entropy minus reference entropy plus kinetic energy.  

State 0:  
Exergy at state 0 equals mass flow rate multiplied by the sum of reference enthalpy minus reference enthalpy minus reference temperature multiplied by reference entropy minus reference entropy plus kinetic energy.  

Exergy at state 0 equals mass flow rate multiplied by kinetic energy equals mass flow rate multiplied by velocity squared divided by two.  

Exergy at state 0 equals velocity squared divided by two equals 20,000 meters squared per second squared.  

State 6:  
Exergy at state 6 equals the sum of enthalpy at state 6 minus reference enthalpy minus reference temperature multiplied by entropy at state 6 minus reference entropy plus velocity squared divided by two.  

Enthalpy at state 6 minus reference enthalpy equals specific heat capacity multiplied by temperature at state 6 minus reference temperature equals 97.431 kilojoules per kilogram.  

Entropy at state 6 minus reference entropy equals specific heat capacity multiplied by the logarithm of temperature at state 6 divided by reference temperature minus gas constant multiplied by the logarithm of pressure at state 6 divided by reference pressure.  

Gas constant equals universal gas constant divided by molar mass equals 28.97 kilojoules per kilomole equals 0.287 kilojoules per kilogram Kelvin.  

Exergy at state 6 equals 97.431 kilojoules per kilogram minus gas constant multiplied by the logarithm of pressure at state 6 divided by reference pressure.  

Pressure at state 6 divided by reference pressure equals 1.  

Entropy at state 6 minus reference entropy equals the integral of specific heat capacity divided by temperature integrated from reference temperature to temperature at state 6.  

Entropy at state 6 minus reference entropy equals specific heat capacity multiplied by the logarithm of temperature at state 6 divided by reference temperature.  

Entropy at state 6 minus reference entropy equals 0.337 kilojoules per kilogram Kelvin.  

Exergy at state 6 equals 97.431 kilojoules per kilogram minus 243.15 Kelvin multiplied by 0.337 kilojoules per kilogram Kelvin plus 510 meters squared per second squared divided by two.  

Exergy at state 6 equals 130065.5 kilojoules per kilogram equals 130065.5 kilojoules per kilogram.

Delta ex equals ex six minus ex zero equals 110065.5 kilojoules per kilogram.