The equation is written:  
delta E equals delta u plus delta KE plus delta PE equals 0.  

The energy balance is expanded:  
0 equals negative m multiplied by (u_6 minus u_5) plus m divided by 2 multiplied by (w_6 squared minus w_5 squared).  

Substituting:  
u equals c_v multiplied by (T_6 minus T_5) plus 1 divided by 2 multiplied by (w_6 squared minus w_5 squared).  

Values are substituted:  
c_v equals c_p minus R; c_p divided by k equals c_v.  
c_v equals 0.718 kJ/kg·K.  

The equation becomes:  
0 equals negative 0.718 multiplied by (328.075 K minus 431.9 K) plus 1 divided by 2 multiplied by (w_6 squared minus 220 squared meters per second squared).  

Simplified:  
0 equals negative 74.178 kJ/kg plus 1 divided by 2 multiplied by (w_6 squared minus 220 squared meters per second squared).  

Result:  
w_6 equals 219.66 meters per second.

Delta ex_str equals ex_str,6 minus ex_str,0.  

Delta ex_str equals [h_6 minus h_0 minus T_0 multiplied by (s_6 minus s_0) plus u_e plus (w_e squared divided by 2)].  

Delta ex_str equals [c_p multiplied by (T_6 minus T_0) minus T_0 multiplied by (c_p multiplied by ln(T_6 divided by T_0) minus R multiplied by ln(p_6 divided by p_0)) plus (w_e squared divided by 2)].  

Delta ex_str equals 1.006 kilojoules per kilogram Kelvin multiplied by (340 Kelvin minus 273.15 Kelvin) minus 273.15 Kelvin multiplied by (1.006 kilojoules per kilogram Kelvin multiplied by ln(340 Kelvin divided by 273.15 Kelvin) minus (0.48312 kilojoules per kilogram Kelvin multiplied by ln(0.5 bar divided by 0.191 bar))) plus (220 meters per second squared divided by 2).  

Delta ex_str equals 37.4311 kilojoules per kilogram minus 0.48312 kilojoules per kilogram plus (51 multiplied by 220 squared divided by 2 multiplied by 1000).  

Delta ex_str equals 240 kilojoules per kilogram.