Because \( x_{g,2} > 0 \) and \( T \) remains in the entire mixture, \( T_{12} = 0^\circ \text{C} \) must be constant at \( 1.14 \, \text{bar} \).  

In the two-phase region, \( p = \text{const} = 1.14 \, \text{bar} \), the temperature remains here at \( 0^\circ \text{C} \) according to the table.  

The pressure also remains constant because \( p_{amb} \) and \( m_K \) are constant.

State 1:  
Mass of ice-water mixture equals 0.1 kilograms.  
Ice content equals mass of ice divided by mass of ice-water mixture, which equals 0.6.  
Temperature equals 0 degrees Celsius.  

Energy balance for ice-water mixture with heat transfer:  
Change in internal energy equals heat transfer minus work, which equals zero because potential energy equals zero.  

Internal energy at state 1 equals ice content times latent heat of fusion at 0 degrees Celsius plus ice content times (internal energy of liquid minus internal energy of fusion) times mass of ice-water mixture.  

Internal energy at state 1 equals 20.125 joules.  

Internal energy at state 2 equals heat transfer plus internal energy at state 1, which equals negative 18.952 joules.  

Ice content equals internal energy at state 2 minus internal energy at fusion divided by internal energy at state 1 minus internal energy at fusion.  

Internal energy at state 1 equals 0.1 kilograms times (negative 333.458 plus ice content times (negative 0.045 plus 333.458)), which equals negative 13.3 kilojoules.  

Internal energy at state 2 equals internal energy at state 1 plus heat transfer, which equals negative 12.25 kilojoules.