Equation:  
v subscript w equals epsilon subscript w minus epsilon subscript 4 divided by delta n.

Another equation:  
Q subscript K equals negative Q subscript K plus [epsilon subscript w minus epsilon subscript 4] multiplied by delta n.

Text:  
"0 - evaporation 2 start freeze."

Table:  
A table is drawn with columns labeled as follows:  
- Column 1: "x"  
- Column 2: "b"  
- Column 3: "M"  
- Column 4: "x"  
- Column 5: "I"  
- Column 6: "V"  
- Column 7: "Y"  

Values in the table:  
- Row 1: "0"  
- Row 2: "0.8 epsilon"  
- Row 3: "M 8 Z"  
- Row 4: "0"  
- Row 5: "0"  
- Row 6: "0"  
- Row 7: "0"  

Diagram:  
A graph is drawn with the following features:  
- The x-axis is labeled "p."  
- The y-axis is labeled "T."  
- A curve is drawn, starting at the "triple" point and extending upward.  
- The curve is labeled "solid" and "liquid" at different sections.  
- The point labeled "triple" is marked on the graph.  
- The region labeled "solid" is crossed out.  
- Another label "gas" is written near the curve.  

Additional text near the graph:  
- "Freeze"  
- "Sublimation"  
- "Phase 3"  

No further content is visible.

Nine hundred sixty times v zero equals v x equals (h four minus h five) divided by (h four minus h six).

(h four minus h five) times v x plus h four equals h four.

Epsilon one divided by epsilon two equals (r two divided by r one) times (s four divided by s five).  
Epsilon one divided by epsilon two equals (r two divided by r one) times (s four divided by s five).  
v zero minus v four equals log s nine divided by s eight equals (r two divided by r one) times v four.

v four divided by r one times epsilon two divided by epsilon six equals (log s eight divided by s four) equals (zero minus x one thousand one hundred forty-eight) divided by h four.

x zero minus q four plus (h four minus h five) times w equals zero.  
[some content crossed out]  
h four minus h five equals v zero minus v four.

Epsilon five divided by epsilon six equals (s four minus s three) times v.  
[some content crossed out]  
(s four minus s five) equals v times w.

Epsilon one divided by epsilon two equals v four plus (v four minus q four).  
(s six minus s five) divided by (s six minus s two) equals epsilon four.

Two times v four times integral of (epsilon one divided by epsilon two) equals (r two divided by r one) times (s six minus s zero) equals (x one thousand one hundred forty-eight divided by h four).

Integral of (epsilon one divided by epsilon two) equals (s six divided by s zero) times (log s six divided by s zero) equals (x one thousand one hundred forty-eight divided by h four).

Addition (a).