Partial derivative of E with respect to t equals the sum over i of m sub i of t multiplied by h sub i of t plus p sub e of t plus the sum over i of Q sub i of t minus the sum over n of L sub n of t.

Zero equals m multiplied by (h sub e minus h sub a) plus Q dot sub aus minus Q dot sub aus equals m multiplied by (h sub e minus h sub u) plus Q dot R.

h sub e at 15 degrees Celsius equals 292.94 u squared over kg, from table A-2.

h sub u at 200 degrees Celsius equals 419.64 u squared over kg, from table A-2.

Q dot sub aus equals 0.3 u squared over s multiplied by (292.94 u squared over kg minus 419.64 u squared over kg) plus 100 kilowatt equals 62.182 kilowatt.

dE over dTheta equals the sum from i equals one to n of m sub i of theta times h sub i of theta plus L sub i of theta plus q sub e of theta plus the sum from j equals one to s of q sub j of theta minus the sum from k equals one to r of w sub k of theta.

Delta E equals m sub 2 times u sub 2 minus m sub 1 times u sub 1 plus the sum of q sub i equals q sub aus times 2 equals 35 megajoules.

m sub 2 equals m sub 1 plus delta m. m sub 1 equals 5755 kilograms. m sub dry equals x prime times m sub f. m sub wet equals m sub f times one minus x prime. m sub 2 equals delta m.

u sub 1 from EOC equals 250.6 kilojoules per kilogram. u sub dry from 200 degrees Celsius equals 4.186 kilojoules per kilogram. u sub wet from 200 degrees Celsius equals 292.95 kilojoules per kilogram. u sub 2 from 200 degrees Celsius equals 87.95 kilojoules per kilogram.

Delta E equals m sub 3 times u sub 3 plus m sub 2 times u sub 2 minus m sub 1 times u sub 1 equals 35 megajoules equals delta m times u sub 2 plus m sub dry times u sub dry plus delta m times u sub 2 minus m sub 1 times u sub 1.

m sub dry times u sub dry minus m sub wet times u sub wet minus m sub 1 times u sub 1 equals u sub 3 plus u sub 2 equals m sub dry times u sub dry plus m sub wet times u sub wet minus m sub 1 times u sub 2 plus 35 megajoules.

equals 0.005 times 5755 kilograms times 250.6 kilojoules per kilogram plus 5755 kilograms times one minus 0.005 times 4.186 kilojoules per kilogram minus 5755 kilograms times 292.95 kilojoules per kilogram.

equals 87.95 kilojoules per kilogram plus 292.95 kilojoules per kilogram.

Delta m sub 2 equals 2176.02 kilograms.