TASK 4d
dE ex over dt equals the sum of E ex, str, i plus the sum of E ex, Gi minus the sum of Wu minus E ex, ver, l.

Zero equals the sum of E ex, str, i plus E ex, QB minus E ex, ver, l.

e dot ex, ver, l equals h zero minus h zero minus T zero times (s zero minus s zero) plus ke plus (one minus T zero over T B) times q B.

e dot ex, ver, l equals delta ex, str plus (one minus T zero over T B) times q B.

100 kilojoules per kilogram

70 degrees Celsius

1285 Kelvin

Thus

e dot ex, ver, l equals 100 kilojoules per kilogram plus (one minus 273.15 minus 30 over 1289) times 1195 equals 1069.58 kilojoules.

Delta U equals Q one two minus W one two.

U two minus h one equals Q one two minus W one two, massen konstant gleich.

u two minus u one equals q one two minus w one two.

Q one two equals U two minus U one plus W one two, nur von Gas (Volumenarbeit).

equals m ew (u two ew minus u one ew) plus m g (u two g minus u one g) plus integral from one to two p dV, Kraft.

rho integral from one to two dV equals (V two minus V one).

Isentropic equation.

T two over T one equals (V one over V two) to the power of n minus one.

n equals k equals R bar plus c v over c v equals 1.2627.

V one over V two equals (T two over T one) to the power of one over n minus one.

V two equals V one times (T two over T one) to the power of one over n minus one equals V one over m g times one over (273.15 over 500 plus 273.15) to the power of one over n minus one equals 0.1682.

V two equals m g times V one.

rho integral from one to n dV equals 0.006167.

p sub u equals p sub z equals 8 bar

adiabatic throttle arrow isotherm T sub g equals T sub 4

x sub u equals 0 arrow saturated at 8 bar

T sub u equals 31.33 degrees Celsius

TABA-11 liquid-vapor at 8 bar