zu 07 !! 

pF p2 

a) delta am (u2 minus u1) equals CQ 
am T2 equals T1 equals Q 
am Cv (T2 minus T1) equals CQ 
Qv equals minus MOD D 

b) delta U equals sum Q 
m equals (u2 minus u1) equals Qv2 
u2 mean minus u1 mean equals minus Qv2 
u2 equals minus Qv mean plus Umew divided by mcw 
u2 equals minus 181.9238 

T2 equals 0.005 C 
Cp equals 0.633 
Cv equals Cp minus R 
Cv equals 0.46672 

u1 equals minus 200.0928 (siehe letzte Seite) 
Uverlustig equals 0.045 
Ufest equals minus 333.458 
u2 equals Ufluss plus x2 (Urest minus Uverlustig) 
x2 equals (u2 minus Uverlustig) divided by (Ufest minus Uverlustig) 
x2 equals 0.05662 
x2 equals 5.662 percent

a) m dot ein equals m dot aus equals 0.3 kilograms per second, stationary flow process.

Sum of Q dot equals Q dot E minus Q dot aus. (Q dot aus is negatively defined!)

O equals m dot ein (h ein minus h aus) plus sum of Q dot.

Q dot aus equals m dot ein (h ein minus h aus) plus Q dot E.

h ein equals h g (70 degrees Celsius) equals 2668 kilojoules per kilogram.

h aus equals h g (400 degrees Celsius) equals 2761.1 kilojoules per kilogram (Table A-2).

Q dot aus equals 85.24 kilowatts.

b) T bar equals integral from s a to s e of T ds, ideal fluid.

T bar approximately equals T ein plus T aus divided by 2 approximately equals 293.15 Kelvin.

c) O equals m dot (s e minus s a) plus minus Q dot divided by T bar plus s dot erz. (between water and coolant, total entropy?)

s dot erz equals m dot ein (s aw minus s ew) plus Q dot divided by T bar.

s aw equals s g (70 degrees Celsius) equals 7.2533 kilojoules per kilogram Kelvin.

s ew equals 7.3543 kilojoules per kilogram Kelvin (Table A-3).

s dot erz equals 0.41 kilowatts per Kelvin.

d) m dot equals 0.

T m equals 70 degrees Celsius.

T c equals 70 degrees Celsius.

Delta m z equals T ein m z equals 70 degrees Celsius.

Q R m z equals approximately 35 megajoules.