Temperature in degrees Celsius: 70 to 100
Boiler: 100 degrees Celsius

d one
delta U equals delta m twelve h ein minus Q R twelve minus m two u two minus m one u one

delta m twelve equals m two u two minus m one u one plus Q R twelve over h ein

Integral from t_1 to t_2 of c_p dT equals c_p times (T_5 minus T_6) equals 1.006 kilojoules per kilogram times (431.9 Kelvin minus 380.7 Kelvin) equals 101.45 kilojoules per kilogram.

omega_0 equals square root of (2 times (h_0T minus h_02) plus omega_0 squared over xi) equals 2 times 104.45 times 10 to the power of 3 joules per kilogram times (2000 meters per second squared over joules) equals 498.80 meters per second.

c) e_KSstr.6 minus e_KSstr.0 plus h_0b minus h_0c (s_6 minus s_0) plus k_e6 minus k_e0.

h_0b minus h_0c equals c_p times (T_6 minus T_0) equals 1006 kilojoules per kilogram (382.0 Kelvin minus 243.15 Kelvin) plus 85.43 kilojoules per kilogram.

s_0c minus s_0 equals c_p times ln (T_6 over T_0) minus R times ln (p_6 over p_1) equals 1.006 kilojoules per kilogram times ln (382.0 Kelvin over 243.15 Kelvin) minus 0.30 kilojoules per kilogram Kelvin.

Delta e_KSstr. equals k_e0 equals 1 over 2 omega_0 squared over omega_str.

Delta e_KSstr. equals 85.43 kilojoules per kilogram minus 243.15 times 15 Kelvin (0.3 kilojoules per kilogram Kelvin) plus (498.80 meters per second squared minus (200 meters per second) squared) over 2 equals 116.63 kilojoules per kilogram.

d) m dot_H equals 5.279 times m dot_K.

m dot_ges equals m dot_H plus m dot_K.

0 equals (crossed out equation).

e_KW,1 equals T_0 times Delta s_0str. over m dot_ges.

Diagram: A triangle with arrows labeled as u_in, u_out, W_K, and W_K plus u_in, verdichter.

"Sturz in Brennkammer, Turbine, Mischkammer, Verdichter."