b) Sublimation: C to G implies p equals one millibar or one point two cubed bar equals two times ten to the power of three times twenty Kelvin. Negative twenty degrees Celsius equals zero point one kilobar equals state during sublimation.

Aus TAB A 6: Interpolation. Temperature at zero point two kilobar minus temperature at zero point two zero three eight kilobar minus temperature at zero point zero eight eight three kilobar equals negative twenty-two degrees Celsius approximately twenty point three eight five degrees Celsius, greater than one.

T2 equals sub-cool twenty Kelvin minus twenty point three eight five degrees Celsius from graph diagram. Twenty Kelvin above sublimation point.

Sub-cool equals twenty point three eight five degrees Celsius less than twenty degrees Celsius, when taken from diagram.

Process 1 to 2: Compressor. Compressed state equals six Kelvin equals two point six degrees Celsius.

Stationary state process: Zero in R134a equals one plus two plus y squared plus y cubed plus negative y squared plus y cubed plus zero equals zero simplified.

Q dot equals question mark. We know WKP equals Q dot R equals Q dot AB equals Q dot K equals Q dot AB.

WKP equals l equals Q dot AL equals dt equals W dot KP equals Q dot R equals Q dot AL implies W dot KP equals Q dot R equals Q dot AL.

Process 3 to 4: Zero equals m dot equals negative three hundred eighty-four zero equals h3 minus h4 equals negative Q dot AB equals m dot equals negative two three four zero equals Q dot AB divided by h3 minus h4.

Step 2 of the cooling medium

P