Delta S twelve equals m dot max times s two minus m dot times s one minus [crossed out text]

T one equals one hundred

s equals one point three three one four kilojoule per kilogram

s two equals s g equals seven point seven five three three

Delta S twelve equals four point eight three [crossed-out text] minus thirty-five megajoule divided by two hundred ninety-five Kelvin

equals minus eleven

Delta S twelve equals nine point eight one three kilojoule

p sub s equals p sub 6, p sub c equals 1

T sub 6 divided by T sub 5 equals (p sub 6 divided by p sub 5) to the power of 0.6 divided by 1.4

T sub 6 equals (p sub 6 divided by p sub 5) to the power of 0.6 divided by 1.4 times T sub 5

T sub 0 equals 328.07 Kelvin

W sub 5/6 equals R times (T sub 6 minus T sub 5) divided by negative 0.4 equals 7 times 71.498 kilojoules per kilogram

R times the square root of 2 divided by 2

M equals 28.07 kilogram divided by kilogram

R equals 28 plus log of 1

w sub e equals h sub e minus h sub a plus (w sub e squared minus w sub a squared) divided by 2 times 1.2

w sub e plus h sub 6

w sub a squared equals 2 times h sub 5 minus 2 times h sub 6 plus w sub e squared minus 2 times w sub e

w sub a prime equals 2 times c sub p times (T sub 5 minus T sub 6) plus (1000 meters per second squared) divided by 2 times w sub e

w sub s equals 3.16 meters squared per second

State 2, Q equals zero.

m6 times (u2 minus u1) equals mE (u2 minus u1).

m times mc times (cv times (T2 minus T1)) equals mcw times (u2 minus u1).

Equals 1,139.89.

Negative 11,353.03 times D12 times u2 minus u1.

u1 equals negative 146.12 divided by 19.

u1 equals negative 133.91.

Interpolation at pressure equals 0.003.

x equals negative 146 minus u1 divided by u2 minus u1.

x equals 560.568.