Mass flow rate R134a  
Compressor  
First law of thermodynamics.  
Zero equals mass flow rate times (enthalpy exit minus enthalpy entrance) plus zero minus work rate compressor.  

Entropy two equals entropy three.  
Temperature two equals temperature one minus six Kelvin.  
Temperature one equals two hundred seventy-three point fifteen Kelvin plus ten Kelvin equals two hundred eighty-three point fifteen Kelvin.  
Temperature two equals two hundred seventy-seven point fifteen Kelvin.  

Work rate compressor equals mass flow rate R134a times (enthalpy two minus enthalpy three).  

Enthalpy two (temperature equals two hundred seventy-seven point fifteen Kelvin) — gas phase saturated.  

Table A-10  
Enthalpy two saturated (four degrees Celsius) equals two hundred forty-nine point fifty-three kilojoules per kilogram.  
Entropy two saturated equals zero point nine one six nine kilojoules per kilogram Kelvin.  

Enthalpy three (eight bar, entropy two).  
Wet steam:  
Entropy three equals entropy fluid (eight bar) plus quality times (entropy gas (eight bar) minus entropy fluid (eight bar)).  
A-11  
Entropy fluid equals zero point three four five nine.  
Entropy gas equals zero point nine zero zero six.  

Quality equals zero point two nine nine nine.  

Table A-11  
Enthalpy two saturated (eight bar) equals enthalpy fluid (eight bar) plus quality times (enthalpy gas (eight bar) minus enthalpy fluid (eight bar)).  
Enthalpy fluid equals ninety-three point forty-two.  
Enthalpy gas equals two hundred sixty-four point fifteen.  

Enthalpy saturated equals one hundred forty-four point six three seven kilojoules per kilogram.  

Work rate compressor equals mass flow rate R134a times (enthalpy two minus enthalpy three).  
Work rate compressor equals twenty-eight watts equals twenty-eight joules per second.  

Crossed out:  
Twenty-eight times ten to the power of negative three kilojoules per second divided by (enthalpy two minus enthalpy three) kilojoules per kilogram equals four point nine zero six seven times ten to the power of negative four kilograms per second equals mass flow rate R134a.  

Mass flow rate R134a equals two point six six nine times ten to the power of negative four kilograms per second.