Water - cooler fluid

a) Reactor wall

| p | T | x = 1 |
|---|---|---|
| 1 | 70 degrees Celsius | x = 1 |
| 2 | 100 degrees Celsius | x = 1 |

Q out

0 = m dot [h in minus h out] plus Q R minus Q out

Q out = m dot [h in minus h out] plus Q B

h in {70 degrees Celsius, x = 1} equals 2626.8 kilojoules per kilogram

h out {100 degrees Celsius, x = 1} equals 2676.1 kilojoules per kilogram

Q out equals 85.2 kilowatts (positive according to convention)

b) 0 equals m dot k plus [s k F e minus s k F a] plus Q dot aus over T k F plus S dot ges. 0 da kein Druckverlust.

s k F z minus s k F a equals c i t ln (T k F e over T k F a).

T bar k F equals minus m k F integral over T k F.

Q aus equals minus m k F c i t ln (T k F e over T k F a) unbekannt?

c) S dot ges equals Sigma Q dot aus over T equals Q dot aus over T Reaktor plus Q dot aus over T k F.

S dot ges equals 0.06049 less than 1 over s times K.

Reaktor Q dot aus T bar equals 105 degrees C.

Wand Q aus over T k F.

d) Table with columns T, m1 equals 57.55 kg.

Row 1: 100 degrees C, x0 equals 0.005, Q dot L12 equals 35 MJ.

Row 2: 90 degrees C, x equals 1.

m2 equals m1 plus delta m12 b e i plus Q R minus Q L12.

Delta m12 h i x minus delta m12 u2 equals m1 u2 minus m1 u1 minus Q R.

Delta m12 equals m k2 minus u1 minus Q R over m ein minus u1.

Equals 170.8 t.

h ein [20 degrees C, x equals 1] equals 2538.4 kJ over kg.

u1 [100 degrees C, x equals 0.005] equals 429.38 kJ over kg.

u2 [70 degrees C, x equals 1] equals 2463.6 kJ over kg.

Delta S one two equals m two s two minus m one s one equals sixty-four point seven five five kilojoules per kilogram Kelvin.

m one equals five seven five five kilograms.  
m two equals m one plus Delta m one two equals nine three five five kilograms.

s two [seventy degrees Celsius, x equals one] equals seven point seven five five three kilojoules per kilogram Kelvin.  
s one [four hundred degrees Celsius, x equals zero point zero zero five] equals s f plus x (s g minus s f) equals one point three three seven one four kilojoules per kilogram Kelvin.

Aus TAB A-2.