T_KF equals integral of T dls over surface area minus surface area.  
Integral from surface area to surface area of T dT.  
Equals one-third times (T_aus cubed minus T_ein cubed).  
Equals S_e times integral of T dls over integral of T dT.  
Equals T_e times integral from S_e to S times e to the power of negative S over c double prime times dls over c double prime times ln of (T_max over T_min).  
Equals T_e times e to the power of S over c double prime times integral from S_e to S times e to the power of negative S over c double prime times dls.  
Equals T_e times e to the power of S over c double prime times [e to the power of negative S over c double prime minus e to the power of negative S_e over c double prime].  
Equals T_e times e to the power of S over c double prime divided by c double prime times ln of (T_min over T_max).  
S minus S_e equals c double prime times ln of (T over T_e) → T equals T_e times e to the power of S minus S_e over c double prime.  
Equals ______.

Energy balance around the aircraft propulsion system:

Stationary implies zero equals m dot gas times (h zero minus h six plus (w inlet squared minus w six squared) divided by two) plus Q_B minus V dot im.

Adiabatic reversible implies isentropic.

Polytropic relation: T_6 divided by T_5 equals (p_6 divided by p_5) to the power of k minus 1 over k.

Therefore, T_6 equals 438.931.9 times (0.191 divided by 0.5) to the power of 0.4 divided by 1.4 equals 328.75 Kelvin.

(I) implies zero equals m dot gas.

Energy balance around the combustion chamber:

Stationary implies zero equals m dot gas times (h_5 minus h_4 plus (w_5 squared minus w_4 squared) divided by two) plus Q dot combustion adiabatic minus sum of w dot combustion chamber presumably no work.

Therefore, zero equals c_p times (T_5 minus T_4) plus (w_5 squared minus w_4 squared) divided by two.

Therefore, w_6 squared equals 2 times c_p times (T_5 minus T_4) plus w_5 squared.

w_6 equals square root of 2 times 1.006 times (431.9 minus 328.0.75) times 10 to the power of 3 plus 22 squared.

Equals 457.29 meters per second.

Equals 507.24 meters per second.