Mass flow rate times kinetic work equals twenty-eight watts.

Steady-state flow process with kinetic energy equals zero and is adiabatic.

Zero equals mass flow rate times (enthalpy two minus enthalpy three plus velocity two squared minus velocity three squared divided by two plus gravitational acceleration times (height two minus height three) plus delta kinetic work.

Arrow to kinetic work equals mass flow rate times (enthalpy two minus enthalpy three).

Arrow to mass flow rate equals kinetic work divided by (enthalpy two minus enthalpy three).

Entropy two equals entropy three equals isentropic.

Crossed out content.

Mass fraction A equals zero.

Crossed out content.

Enthalpy A equals enthalpy f at eighty bar equals ninety-three point forty-two kilojoules per kilogram (Table A-71).

Temperature i equals question mark.

Temperature i equals temperature sublimation plus seventy Kelvin equals seventy Kelvin.

Crossed out content.

Temperature two equals temperature sublimation plus seventy Kelvin equals zero degrees Celsius plus seventy Kelvin equals seventy degrees Celsius.

Temperature two equals seventy degrees Celsius minus fifty degrees Celsius equals forty degrees Celsius.

Enthalpy two equals enthalpy g at forty degrees Celsius equals 194.19 kilojoules per kilogram (Table A-70).

Crossed out content.

Entropy three equals entropy two equals entropy g at forty degrees Celsius equals 0.9769 kilojoules per kilogram Kelvin.

Mass fraction x three equals entropy three minus entropy f at eighty bar divided by entropy g at eighty bar minus entropy f at eighty bar equals 0.9769 minus 0.3959 divided by 0.9066 minus 0.3459.