a) 1. HS Kontinentaler Reader:
O equals M dot times (he minus ha) plus Q dot.
Q dot equals M dot times (ha minus he) equals crossed out text.
ha of T1 equals haf of T2 equals 252.38 kilojoule per kilogram, A equals 2.
he of T2 equals hef of T2 equals 449.01 kilojoule per kilogram, A equals 2.
Q dot equals C times 3 times (252.38 minus 449.01) equals minus 37.8 kilojoule.

W squared equals two hundred twenty meters squared per second squared, W subscript s squared equals two hundred twenty meters squared per second squared.

Integral from five to six of V dp equals minus n times integral from five to six of V dV equals minus n times R times (T6 minus T5) over one minus n.

R subscript L equals R over M subscript L equals zero point two eight seven kilogram per joule.

Minus one times zero point two eight seven times ten to the power of three times (three hundred twenty-eight point zero seven minus ninety-three point fifteen) over one minus one point four equals minus one hundred four point two three seven kilojoule per kilogram.

Insert.

Delta e subscript x, str equals (h subscript c minus h subscript o minus T subscript o times (s subscript 6 minus s subscript o) plus Delta ke).

h subscript o minus h subscript o equals c subscript p times (T subscript 6 minus T subscript o) equals one point zero zero six times (three hundred twenty-eight point zero seven minus (thirty plus two hundred seventy-three point fifteen)) equals eighty-five point nine three kilojoule per kilogram.

T subscript o equals minus thirty plus two hundred seventy-three point fifteen equals two hundred forty-three point fifteen.

s subscript 6 minus s subscript o equals c subscript p times ln (T subscript c over T subscript o) minus R times ln (p subscript o over p subscript o).

Equals zero point three zero one kilojoule per kilogram.

Delta ke equals one half times (w subscript 6 squared minus w subscript o squared) equals one half times (five hundred sixty squared minus two hundred squared) equals eleven thousand fifty joule per kilogram.

Delta e subscript x, str equals eighty-five point nine three kilojoule per kilogram minus two hundred forty-three point fifteen times (zero point three zero one kilojoule per kilogram) plus eleven thousand fifty times ten to the power of minus three kilojoule per kilogram.

Equals one hundred twenty-two point two nine kilojoule per kilogram.