a) dE by dt equals sum of m times (h i plus q i) plus sum of q minus sum of m times h n, zero, because the pressure remains constant.

Zero equals m times (h e minus h a) plus q R minus q aus.

q aus equals m times (h e minus h a) plus q R.

q aus equals m times (h times c times (T2 minus T1) plus q R).

Equals zero point three times (c times (t plus 300) plus 100 kW.

Equals zero point three times (c times t plus 300) plus 100 kW.

At 85 degrees Celsius, arrow 1008 point 6 over 400 equals 7 point 005.

350 over 350 equals 1 point 005.

100 kW minus 7 point 005 kW over 400 times 350 times 1 point 005 equals 7008.62.

c times (h of 200 K) minus h of 350 K (t gas 350) over 900 minus 300 plus h of 350 K.

Equals 109.07868 kW approximately equals 109.078 kW.

b) T bar equals S zero over S a integral ds.

s a minus s e for the same state as calculated.

c) stationary, zero equals m times (s e minus s a) plus q j over T j plus S erg.

S erg equals q j over T j equals q aus over 295 K equals 6500 W over 22.0239 per K.

d) stationary, zero equals m times (h e minus h a) plus q R minus q aus minus W.

m i equals q R minus q aus equals 7000 W plus 6500 W minus 3500 W.

h e plus h a over h a plus h e.

e) s 12 equals m times t 1 over t equals s a 1 plus sum of q j over T j minus S erg.

Zero equals m times (s e minus s a) plus sum of q j over T j plus S erg.

Because with the same equation.

dS e minus S a equals sum of q j over T j, zero because the two are equal.

Zero equals m times (s e minus s a) equals sum of q j over T j plus S erg.

rho times V equals m times R times T

m zero equals rho times V divided by R times T zero equals F divided by A times V zero divided by R times T zero equals open parenthesis 32.1 divided by 50 times open parenthesis 500 plus 273.15 close parenthesis close parenthesis divided by 0.83 squared times 3.78 divided by 8.314 equals 9.9825399 approximately equals 9.983 grams

rho equals F divided by A equals F K plus F EW divided by A times rho zero equals 4087.059939 approximately equals 4087 kilograms per meter squared times 40080 newtons per meter squared