Change in energy equals mass times change in temperature minus mass plus gravitational potential energy equals zero.

E subscript 2 minus E subscript 1 equals phi minus W equals zero. W equals zero.

T subscript gas equals zero point zero zero three degrees Celsius equals T subscript water.

E subscript 1 equals m times (u subscript H2O minus m subscript Eis plus u subscript FL plus u subscript mFL) times x equals negative three hundred thirty-three point four five eight times (l over kg) times zero point six zero six times (log plus zero point zero zero zero two times log squared).

E subscript 1 Wasser equals negative twenty point zero zero zero two eight (l over kg).

E subscript 2 Wasser equals u subscript f (T equals zero point zero zero three degrees Celsius) times (y minus x) plus u subscript mH2O (T equals zero point zero zero three degrees Celsius) times x.

Delta E subscript equals E subscript 2 gas minus E subscript 1 gas equals m (u subscript 2 gas minus u subscript 1 gas) times c subscript v (T subscript 2 minus T subscript 1) equals negative three hundred ninety-nine point six three seven (l over kg).

Delta E subscript gas equals P subscript 1 2 equals four thousand five hundred seven.

E subscript 2 Wasser equals phi subscript M minus Delta E subscript gas plus E subscript 1 Wasser equals u subscript f times x minus x u subscript f plus u subscript mH2O times x.

x equals phi minus Delta E subscript gas plus E subscript 1 Wasser minus u subscript f.

u subscript E subscript H2O times x minus u subscript f. 

u subscript Eis minus u subscript f.