O equals m (se minus sa) plus the sum of Q over T plus the sum of se.
Sere equals 2 over T (integral of ds minus the sum of Q over T).
Sere equals Qaus over TKF minus Qaus over Texitor.
65 kilojoules per second over 7.3 K equals 65 kilojoules per second over 7.5115 K equals 0.00461 kilojoules per Kelvin.

U two equals negative twenty-eight point five eight kilojoules per kilogram minus negative one hundred forty point one one six eight kilojoules per kilogram divided by zero point one one five kilograms per meter.

X equals one comma two equals U two minus U one times zero point zero zero five divided by F R minus U two minus U one times zero point zero zero five degrees Celsius divided by F R times zero point zero zero five degrees Celsius minus U two minus U one times zero point zero zero five degrees Celsius.

Equals U two minus U F R times zero point zero zero zero five minus U two minus U F R times zero point zero zero zero five degrees Celsius divided by U F R times zero point zero zero zero five degrees Celsius minus U two minus U F R times zero point zero zero zero five degrees Celsius.

Equals zero point one five seven zero equals fifty-seven percent.

A diagram is drawn with axes labeled T and s. There are points labeled 1, 2, 3, 4, 5, and 6. Two curves are shown, one labeled P0 and the other labeled PS. Arrows indicate directions along the curves.

Zero equals m times (he minus ha minus To times (se minus sa) plus delta ke plus delta pe) plus the sum of (one minus To divided by Tj) times Qj ex, bhr equals the sum of Wein minus Ex, ver.

Ex, ver equals he minus ha minus To times (se minus sa) plus delta ke plus delta pe plus the sum of (one minus To divided by Tj) times Wj in.

In der Brennkammer wird Wärme zugeführt.

mK equals 6.293 m ges.

L equals qB equals qB divided by mK equals 1115 kilojoules per kilogram divided by 6.293 m ges.

qB auf m ges ist 1115 kilojoules per kilogram divided by 6.293.

T equals 1289 Kelvin.

Ex, vere equals delta ex, bhr plus the sum of (one minus 1289 Kelvin divided by 289.15 Kelvin) times 1115 kilojoules per kilogram divided by 6.293.

Equals 254.073 kilojoules per kilogram.