a) Stationary:

Zero equals m dot times the sum of h in minus h out plus Q out minus Q in minus W in minus Q R minus A R.

Q out equals m dot times h in minus h out minus W t.

Q out equals 0.13 kilograms per second.

h in arrow TAB minus A2.

h evap in equals 2333.8 kilojoules per kilogram.

h evap out equals 2257.0 kilojoules per kilogram.

Q out equals 0.13 kilograms per second times 2333.8 kilojoules per kilogram minus 2257.0 kilojoules per kilogram minus 100 kilojoules per second.

Equals 76.96 kilowatts.

b)

T UF equals T2 minus T1 divided by ln of T2 over T1.

Also, T bar equals integral from s a to s e of T ds divided by s e minus s a.

Equals 357.9 U.

c)

dS dt equals zero equals m dot times s e minus s a plus Q out minus Q R divided by T bar equals minus S dot erz.

Stationary.

S erz equals m dot times s a minus s e plus Q R minus Q out divided by T.

TAB A2:

S e (70 degrees) equals:

h fg equals h f plus x times h fg minus h f, implies x equals h eq minus h f divided by h g minus h f.

Equals 2333.8 kilojoules per kilogram minus 297.88 divided by 2626.8 minus 2322.02.

Equals 0.874.

c) TASK 2

s vapor in = s sub f plus x times (s sub g minus s sub f) = 0.95 times 4.8 plus 0.1824 times (7.755 minus 0.9549)

= 6.1888 kilojoules per kilogram kelvin

h vap (100 degrees Celsius) = 2257.0 kilojoules per kilogram

x = (h vap minus h sub f) divided by (h sub g minus h sub f) = 0.8143

(100 degrees Celsius) s vapor out = s sub f plus x times (s sub g minus s sub f) = 1.3069 plus 0.814 times (7.3549 minus 1.3069) = 6.2298 kilojoules per kilogram kelvin

s entropy = 0.3 kilojoules per second times [6.1888 kilojoules per kilogram kelvin minus 6.2298 kilojoules per kilogram kelvin] plus (100 kilograms per second times 76.98) divided by 357.94

s entropy = 0.6948 kilojoules per second

a) T sub 2 = 70 degrees Celsius

T sub 1 = 100 degrees Celsius

omega sub 12

T sub in = 20 degrees Celsius

delta E = E sub 2 minus E sub 1 = omega sub 12 times m sub 2 u sub 2 minus m sub 1 u sub 1 = omega sub 12 times (h sub 1 minus h sub 2) plus Q dot out