0-1 Isentropic, q equals 0  
1-2 Isentropic, q equals 0  
2-3 Isobaric, w equals 0  
3-4 Q equals 0, not Isentropic  
4-5 Isobaric, w equals 0  
5-6 Isentropic

b) omega sub 6 squared equals omega sub 5 squared minus W dot e sub n over m dot plus h sub 5 minus h sub 6.

W dot e sub n equals R times T sub 6 minus T sub 5 over 1 minus 1.4 equals 0.12367 joules per gram times 328.07 kelvin minus 431.13 kelvin over 0.4.

Equals negative 741.42 joules per gram.

omega sub c equals the square root of (200 meters per second) squared plus 741.42 joules per gram over m dot gas plus 104.45 meters cubed per kilogram.

c) delta e equals e dot over m dot equals h sub 0 minus h sub 6 minus T sub 0 (s sub 0 minus s sub 6) plus 1/2 (omega sub 0 squared minus omega sub 6 squared).

h sub 0 minus h sub 6 equals negative (h sub c minus h sub 0) equals exp T sub 0 minus T sub 6 equals 1.1006 meters cubed per kilogram [2 times 931.15 kelvin minus 328.07 kelvin].

Equals negative 85.3559 meters cubed per kilogram.

s sub 6 minus s sub 0 equals integral from T sub 1 to T sub 2 of c sub p (T) over T dT minus R ln (P sub 6 over P sub 0).

Equals ln (T sub 0 over T sub 0) times c sub p equals 0.3013 meters cubed per kilogram.

s sub 0 minus s sub 6 equals negative s sub 6 minus s sub 0 equals negative 0.3013 meters cubed per kilogram.

delta e equals negative 85.3559 meters cubed per kilogram times 243 m dot (negative 0.3013 meters cubed per kilogram plus 1/2 (200 meters per second squared minus (510 meters per second squared)).

Equals 2.167 times 10 to the power of 7 meters cubed per kilogram.