m dot R134a. I one equals twenty degrees Celsius, crossed out, twenty-four degrees Celsius. I two equals minus twenty-two degrees Celsius.

First law over compressor: two to three. Q dot equals m dot R134a times (h two minus h three) plus W dot k.

h two equals h g (minus twenty-two degrees Celsius) equals two hundred thirty-seven point zero eight kilojoules per kilogram.

h three equals question mark. S two equals S three equals question mark. S two equals S g (minus twenty-two degrees Celsius) equals zero point nine three five one kilojoules per kilogram Kelvin.

s three equals zero point eight nine three five one kilojoules per kilogram Kelvin.

h three (p bar, zero point nine three five one kilojoules per kilogram Kelvin) equals equals two hundred sixty-nine point one five kilojoules per kilogram plus (zero point nine three five one minus zero point nine zero zero six one) kilojoules per kilogram Kelvin divided by zero point nine three two four kilojoules per kilogram Kelvin minus zero point nine zero zero six kilojoules per kilogram Kelvin times (zero point nine three two four kilojoules per kilogram Kelvin minus zero point nine zero six six kilojoules per kilogram Kelvin).

equals two hundred sixty-four point one eight kilojoules per kilogram.

Q dot equals m dot R134a times (h two minus h three) plus W dot k.

m dot R134a equals minus W dot k divided by (h two minus h three) equals minus zero point zero two eight kilowatts divided by two hundred thirty-four point zero eight kilojoules per kilogram minus two hundred sixty-nine point one eight kilojoules per kilogram equals three point three four nine kilograms per hour.