a) Q out equals question mark.

d e over d t equals m times h one minus h two plus Q out.

b) Q out equals m times h two minus h one.

Q out equals m times c times bracket t two minus t one bracket.

equals bracket 238.15 minus 228.15 bracket.

c) Ansatz

The equation is shown in a large bracket:

d U sub x over d t equals the sum of E sub k, str, i of t plus the sum of E sub i, x, a, j of t from zero to n minus one minus rho n plus one d U of t over d t minus E sub x, vert of t.

E sub k, str equals h minus h sub zero minus i sub zero times s sub s, zero, t, k, e.

e sub r, str equals h sub one minus h sub zero minus t sub zero times s sub one minus s sub zero, t, k, e.

This equals c sub p times t sub one minus t sub zero minus i sub zero times c sub p times ln of t sub one over t sub zero minus R times ln of p sub one over p sub zero plus one over i times ln of v double prime over v.

p equals p_amb plus rho g h squared  
equals p_amb plus rho g over pi r squared  
equals 10 to the power of 5 plus 52 times 3.8 over pi times (5 plus 10 to the power of 3) squared  
equals 1.4 bar  

D equals 2r  
r equals 5 cm  

n equals p V over R T  
R equals R over eta equals 8.314 over 50 times 10 to the power of 3 equals 166.28 Joules per kilogram Kelvin  

n equals 1.4 times 3.12 times 10 to the power of 5 over 166.28 times (500 plus 273.15)  
equals 0.34  

V equals 3.12 times 10 to the power of negative 3 cubic meters  
p equals 1.4 times 10 to the power of 5 Pascal  

b)  

x_eis greater than 0  

Die Grenze die das Gas verpasst ist die gleiche wie das Eis. p_32 equals 1.4 times 10 to the power of 5 Pascal equals 1.4 bar. Die Temperatur ist also 0.000 degrees Celsius nach der Tabelle.  

c)  

dE over dt equals d over dt of integral from 0 to 1 h_2 minus h_1 plus Q  

Delta u equals q_n  

(v_2 minus u_n) equals q_n  

c_v (T_2 minus T_1) equals q_n  

q_n equals 0.633 times (0.005 minus 500)  
equals 346.5 kilojoules per kilogram  

T_L equals 0.005 degrees Celsius  

Q equals negative q_n  
equals 36 times 10 to the power of 3 minus 316.5  
equals negative 1.440 joules