h sub e equals h sub f open parenthesis T equals seventy degrees Celsius close parenthesis equals two hundred ninety-two point ninety-eight kilojoules per kilogram

h sub a equals h sub f open parenthesis T equals one hundred degrees Celsius close parenthesis equals four hundred seventy-nine point zero nine kilojoules per kilogram

zero equals m dot open parenthesis h sub e minus h sub a close parenthesis plus sum of Q dot

equals m dot open parenthesis h sub e minus h sub a close parenthesis plus Q sub R minus Q sub aus

Q sub aus equals zero point three kilograms per second open parenthesis two hundred ninety-two point ninety-eight kilojoules per kilogram minus four hundred seventy-nine point zero nine kilojoules per kilogram close parenthesis plus one hundred kilowatts

equals sixty-two point one eight two kilowatts

Zustand 3 p equals 8 bar s equals 0.9298 kilojoules per kilogram.

Arrow equals überhitz.

A equals 72 p equals 8 bar.

h subscript 3 equals 264.15 minus 273.66 divided by (0.9298 minus 0.9066) plus 267.75 divided by (0.9066 minus 0.9298).

Equals 277.37 kilojoules per kilogram.

h subscript 2 equals h subscript g (T equals minus 196 degrees Celsius) equals 237.74 kilojoules per kilogram.

28 W divided by (h subscript 3 minus h subscript 2) equals 0.834 grams per second equals 3 kilograms per hour equals in R734a.

c) p equals 8 bar h equals 277.37 kilojoules per kilogram.

Arrow z Arrow z equals A p equals 8 bar x equals 0 z h subscript f (8 bar) equals 93.42.

Isenthalp da Drossel.

Aus Tab A-10 bei p equals p subscript T equals 7.5248 bar.

x subscript T equals (h subscript T minus h subscript f) divided by (h subscript g minus h subscript f) equals 0.83.

Boxed value: 10.308.