a) Half-open system. One HHD

Q equals m times h two minus h one

m times v two minus v one equals zero, thus v one equals v two

b) Static flow process for half HHD

Q equals zero equals m times h two minus h one, thus zero equals index

Q in equals m times c times T two minus T one

c) six times delta H equals c times delta T times T two minus T one

a) Q output equals Q input (heat exchanger)
Q input equals 733.600 kilojoules per hour
Q output equals 337.818 kilojoules

b) Entropy balance with flow process
O equals integral from s2 to s1 plus integral from O to isobar
Q output equals integral from s2 to s1 plus integral from O to isobar
Q output equals integral from s2 to s1
T equals integral from s2 to s1 of dT
Q output equals m times c times ln(T2 divided by T1)
equals c times ln(T2 divided by T1)

c) Q output equals 654 kilojoules
T reference equals 295 Kelvin
T reference equals 0.22 Kelvin

a) Stationary flow process:  
O = m dot (h2 - h1 + v2 squared over 2 - v1 squared over 2) + Q dot - W dot  
2 to 3: O = m dot (h2 - h3)  
m dot = W dot over h2 - h3  

b) x2 = 1 saturated steam  
adiabatic reversible and isentropic  

c) Entropy balance: 2 to 3 adiabatic  
0 = m dot (s2 - s3) + Q dot over T + delta S over delta t  
delta S over delta t = 0  

s2 = s3 reversible adiabatic = 0  
h2 = h3

a) h2 equals hfg at 160 degrees Celsius from table A-10. b1 equals h2 equals 2337.94 kilojoules per kilogram.

b) Phase change component: single line triple. T1 equals 10 degrees Celsius. T total equals T4 minus 5. T total equals 160 degrees Celsius. g2 equals yfg equals 0.329 kilojoules per kilogram.

c) h3 interpolation. j equals 400 degrees Celsius. j equals 373.15 Kelvin. b equals hfg at 373.9 degrees Celsius equals 2749.15 kilojoules per kilogram. b equals hfg at 373.9 degrees Celsius equals 2749.15 kilojoules per kilogram. j equals 373.15 Kelvin. j equals 373.9 degrees Celsius. equals in table A-12. s2 equals s3 equals sfg blank. b equals hfg at 373.9 equals 0.9066 kilojoules per kilogram. j equals 400 degrees Celsius. equals 0.8374 kilojoules per kilogram. h3 equals hfg at 373.9 degrees Celsius plus hfg at 373.9 degrees Celsius equals 273.6 kilojoules per kilogram.