F equals F one plus F two plus F three equals F u. F two plus F three equals F G equals P G times A divided by A F.

P G equals one point four zero zero five times ten to the power of five pascal. P G equals fourteen bar.

A equals pi times r squared equals pi times zero point zero five meters squared equals seven point eight five times ten to the power of negative three square meters.

The equilibrium of a mixture is incompressible. The equilibrium is equal when the forces remain constant (remain constant).

Fn equals F1 plus F2 plus F3 arrow equals F1 plus F2 plus F3.

Psi equals F1 plus F2 plus F3 equals Par equals 1 divided by U per hour.

The volume and the temperature are included.

Tab. 1

6. pv equals m times R times T equals T equals Tab. 1.

6. Te equals 0 degrees Celsius.

Omega PM equals 1 divided by U per hour arrow equals answer Tab. 1.

6. from A 1.1: ln (U2 minus U1) equals Q12 minus U1 plus Nosar divided by 0.

U2 minus U1 equals exp times c times (T2 minus T1) arrow equals U2 minus U1 equals Q12 divided by ln.

U2 minus U1 equals Q12 divided by ln.

T2 minus T1 divided by ln c times (T2 minus T1).

T2 equals TA plus Q12 divided by m times c.

U h equals x one times U heating plus x two times U rest.  
U h equals 200.9328 kilograms.  
U two equals U h plus Q twelve.  
U two equals 185.0328 kilograms.  
T twenty-five equals 0.003 degrees Celsius, arrow K rest (0.0032 degrees Celsius) equals minus 333.4428 kilograms.  
b heating (0.00328 degrees Celsius) equals minus 0.033 kilograms.  
U two equals (one plus x two) times U heating plus x two times U rest.  
U two equals U heating plus x two times U rest plus U heating.  
x two equals U two minus U heating over U rest minus U heating.  
x two equals 0.5555.