Energy balance of the reaction

dE/dt = m in (h in - h out) + Q aus - sum W out + Q R

- Q aus = m in (h aus - h in)

- h in = h (T = 100 degrees Celsius, x vap) = 2626.8 kilojoules per kilogram

- h aus = h (T = 100 degrees Celsius, evap) = 2676.1 kilojoules per kilogram

- Q aus = 0.3 kilograms per second (2257.0 - 2333.8) + 100 kilojoules = 76.96 kilowatts

dE over dt equals delta m one two (h in) plus Q aus one two.

u two minus u one equals delta m one two (h in) minus Q aus one two.

Negative (m one y one plus delta m one two) (u two) minus m one y one (u one) equals delta m one two h in minus Q aus one two.

Negative delta m one two equals m one y one u one minus m one y one u two minus Q over u two minus h in.

h in equals u one (twenty degrees Celsius, x equals one) equals two five three eight point one kilojoules per kilogram.

u one equals u one (one hundred degrees Celsius, x equals one) equals two six seven six point one kilojoules per kilogram.

u two equals u two (seventy degrees Celsius, x equals one) equals two six two six point eight kilojoules per kilogram.

Negative delta m one two equals five seven five five kilograms times two six seven six point one minus five seven five five times two six two six point eight over two six two six point eight minus two five three eight point one minus one hundred kilojoules.

Energy balance of a flying engine (system boundary of the entire engine).

dE over dt equals m over g times (h0 minus h6 plus w output squared over 2 minus w0 squared over 2) plus the sum from i of Qi minus the sum from o of Wo.

Negative w0 squared equals 2 times h0 minus 2 times h6 plus w output squared.

Negative h0 minus h6 equals the integral from T0 to T6 of Cp dT.

To determine T6: T6 equals Ts times (P0 over P6) to the power of (1.4 minus 1 over 1.4) which equals 431.5 K.

T6 equals 431.5 K times (0.191 over 0.15) to the power of (1.4 minus 1 over 1.4) equals 328.08747 K.

Negative h0 minus h6 equals Cp times (743.15 K minus 328.08747 K) equals negative 85.134 kJ over kg.

Negative w0 equals the square root of 2 times (negative 85.134) plus 200 m squared over s squared.

A diagram is shown with axes labeled as P and T. A quadrilateral shape is drawn with numbered points 1, 2, 3, and 4, connected by arrows.