Energy balance of an open system:

Delta E equals m2 times u2 minus m1 times u1 equals Delta m12 times h12 plus QRA2 minus Qaus.

m2 equals mges,1 plus Delta m12. m1 equals mges,1.

TAB A2: u2 equals uf at seventy degrees Celsius equals two hundred ninety-two point ninety-five kilojoules per kilogram.

uf at one hundred degrees Celsius equals four hundred eighteen point ninety-four kilojoules per kilogram. ug at one hundred degrees Celsius equals two thousand five hundred six point five kilojoules per kilogram.

u1 equals uf plus xd times (ug minus uf) equals four hundred twenty-nine point three eight kilojoules per kilogram.

(m1 plus Delta m12) times u2 minus m1 times u1 equals Delta m12 times h12.

Delta m12 times (u2 minus h12) equals m1 times u1 minus m1 times u2.

Delta m12 equals (m1 times u1 minus m1 times u2) divided by (u2 minus h12).

Delta m12 equals three thousand seven hundred fifty-six point four three kilograms.

Delta e exist equals (h e minus h o minus T o times (s e minus s o) star Delta n e) equals c p times (T e minus T o) minus T o times (c p times ln (T e divided by T o)) plus (w e squared minus w o squared divided by two) equals 110.065 w divided by kg.

Energy balance of a closed system (gas):  
Delta E equals Q one two minus W one two  

m gas multiplied by c v multiplied by (T two g minus T one g) equals Q one two minus the integral from V one to V two of p d V  

Q one two equals m gas multiplied by c v multiplied by (T two g minus T one g) plus p two g multiplied by (V two minus V one)  

equals minus one point zero eight three two kilojoules plus one one four four point nine joules  

equals thirty-one point two one joules (should be less than zero)