e sub x, s plus h G equals e sub x, s plus h naught minus T sub zero times (s sub six minus s sub naught) plus omega squared over two minus omega squared over two times (h sub s minus h naught minus T sub zero times (s sub five minus s sub naught) plus omega sub s squared over two).  
Equals omega squared over two times (h sub six minus h sub five) minus T sub zero times (s sub six minus s sub five) plus omega squared minus omega sub s squared over two.  
Equals integral of s p d T minus T sub zero times integral of c sub p d t minus R times ln (p sub 24 over p sub s1) plus omega squared minus omega sub s squared over two.  
R equals c sub p minus c sub v equals c sub p over c sub p minus c sub p over k equals 0.28742 kilojoules per kilogram Kelvin.  
T sub zero equals 293.15 Kelvin.  

Delta e sub x, s plus h equals c sub p times (T sub six minus T sub five) minus T sub zero times c sub p times ln (T sub six over T sub five) minus T sub zero times ln (p sub 26 over p sub s1) plus omega squared minus omega sub s squared over two.  
Equals negative 109.95 minus 67.26 minus 67.255 plus 1 plus 74.437.  
Equals negative 167.97 kilojoules per kilogram.

Delta E equals delta U minus Q two minus W equals Q one two minus S p d v equals Q one two over R times (T two minus T one) over R minus n.

R G equals eight point three one four over fifty times ten to the power of negative three times one hundred sixty-six point two eight equals c p minus c v.

Q one two equals delta U plus S p d v equals m g times integral from T one to T two of c v d T plus S p d v equals m g c v (T two minus T one) plus P g three times (V two minus V one).

V two equals m g R G T g two over P three two equals zero point zero zero four one zero three meters cubed.

Q one two equals negative one point zero eight two seven kilojoules minus zero point two eight nine five three kilojoules equals negative one point three six seven three kilojoules.