Exergy:  
delta e subscript xstr equals open bracket h minus h subscript o minus T subscript o times open parenthesis s minus s subscript o close parenthesis plus ke plus pe close bracket.  
delta e subscript xstr equals open bracket h subscript 6 minus h subscript o minus T subscript o times open parenthesis s subscript 6 minus s subscript o close parenthesis plus ke plus pe superscript o close bracket equals 12.22 kilojoules per kilogram.  
h subscript 6 open parenthesis p subscript 6 equals 0.191, t subscript 6 equals 328.07 close parenthesis equals.  
s subscript 6 open parenthesis p subscript 6 equals 0.191, t subscript 6 equals 328.07 close parenthesis equals.  
h subscript 6 minus h subscript o equals C subscript p times s times open parenthesis T subscript 6 minus T subscript o close parenthesis.  
s subscript 6 minus s subscript o equals c subscript p times open parenthesis ln open parenthesis T subscript 6 divided by T subscript G close parenthesis minus R times ln open parenthesis p subscript 6 divided by p subscript o close parenthesis close parenthesis.  
wie bei aufgabe 1 angeleitet.  
p subscript 6 divided by p subscript o equals 1.  
ln open parenthesis 1 close parenthesis equals 0.  
h subscript 6 minus h subscript o equals c subscript p times g times open parenthesis T subscript 6 minus T subscript o close parenthesis equals 85.43 line over h divided by kg.  
s subscript 6 minus s subscript o equals 0.30 line over kg.  
implies T subscript o equals 75.22 line over h divided by kg.  
ke equals w subscript c squared divided by two minus w subscript Luft squared divided by two equals 110 kilojoules per kilogram.