Delta e x zero equals m times (h zero minus h zero minus T zero (s zero minus s zero) plus k e zero minus k e zero).

h zero
s c minus s zero equals s c (T zero) minus s zero (T zero) minus R ln (p zero over p zero).

s zero (T zero) minus s zero (T zero) equals 1.293783 minus 1.782824 times (32 times 67 times 325) times 1.782824 equals 12674 times 3 times 32 times 325.

s zero (T zero) minus s zero (213.15 Kelvin) equals 1.515171 minus 1.678264 times (243.15 minus 240) plus 1.678264 minus 1.47811 times 26 over 750 times 240.

h zero equals h (213.15 Kelvin) equals 256.05 minus 240.02 over 240 minus 240 plus (243.15 minus 240) plus 246.02 equals 293.21.

s zero equals m times (328.40 minus 243.21 minus 213.15 times (1.7794 minus 1.4811) times one-half times (56826 squared minus 70 times x squared).

Q subscript in two. Energy balance:

U subscript two minus U subscript one equals Q subscript in minus work. 

U subscript two minus U subscript one equals mass subscript two times specific heat times (temperature subscript two minus temperature subscript one) equals three point nine times six point six three joules per kilogram Kelvin times (zero minus five hundred degrees Celsius) equals negative one thousand seventy-six joules equals negative one point zero seven six kilojoules.

Work equals integral of pressure with respect to volume equals pressure times volume equals mass times pressure times (volume subscript two minus volume subscript one) equals eight point nine times one point four bar times (negative zero point zero zero two zero one cubic meters) equals negative zero point zero zero two zero one cubic meters.

Work equals negative zero point nine six one zero eight joules. 

(next page)