a) The temperature does not have to increase in a stationary flow process.

Q equals m times (h in minus h out) plus Q x plus Q aus.

Q aus equals m in (h aus minus h in) minus Q x.

Boiling liquid as pure water assumed.

h aus equals h fg (100 degrees Celsius) equals 2257.0 kilojoules per kilogram.

m in equals 9.3 kilograms per second.

h in equals h fg (70 degrees Celsius) equals 2333.8 kilojoules per kilogram.

Q c equals 100 kilowatts.

Q aus equals minus 123.04 kilowatts.

b) T equals integral from s e to s i T ds over s i minus s e.

s a minus s e equals e to the power of c if times ln (T 2 over T 1).

Integral from s i to s e ds equals s a minus s e.

T equals T 1 plus T 2 over 2 equals 233.95 degrees Celsius because if with constant c if.

c) Closed system over the wall.

Q aus equals minus 123.04 kilowatts.

S ges equals Q aus over T if minus Q aus over T equals 0.085 kilojoules per Kelvin.

T k equals 100 degrees Celsius.

T if equals 20 degrees Celsius.

Delta S equals m times s sub 2 minus m times s sub 1 equals Delta m times s sub 2.

m sub 2 equals m sub 1 plus Delta m sub 2 equals ten thousand two hundred twenty-three point three one kilograms.

m sub 1 equals five thousand seven hundred fifty-five kilograms.

s sub 2 equals I know entropy of boiling water, so s sub 2 equals s sub f plus s sub g divided by two.

s sub f equals four point three five five seven kilojoules per kilogram Kelvin.

s sub 2 equals x times s sub g plus one minus x times s sub f equals one point three three seven seven four.

s sub g equals seven point three five four nine.

Arrow to Aus A-2 Delta S equals thirty-six point eight two eight crossed out megajoules per kilogram Kelvin.

s sub f equals one point three zero six three.

Momentum is constant

Mein equals rho 5 A 5 w 5 equals rho e A e w e leads to A 5 equals A e leads to assumption (no idea)

T 5 equals 43.1, 9 Kelvin
V 5 equals 2.42 cubic meters per kilogram
T 6 equals 322.07 Kelvin
V e equals 4.937 cubic meters per kilogram

s g equals 56

w e equals p 5 over p e w 5
w e equals V e over V 5 w 5
w e equals 437.49 meters per second