Stationary flow process:

O equals m dot in times (h in minus h out) plus Q dot R minus Q dot aus.

Q dot aus equals m dot in times (h in minus h aus) plus Q dot R.

h in minus h (70 degrees Celsius, x equals 0) equals h f (70 degrees Celsius) equals 292.98 kilojoules per kilogram (A-2).

h aus equals h (100 degrees Celsius, x equals 0) equals h f (100 degrees Celsius) equals 419.04 kilojoules per kilogram (A-2).

Q dot aus equals 0.3 kilograms per second times (292.98 kilojoules per kilogram minus 419.04 kilojoules per kilogram) plus 100 kilowatts.

Equals 62.18 kilowatts.

m sub 1 plus delta m sub 12 times u sub 2 minus m sub 1 u sub 1 equals delta m sub 12. h sub ein,12 minus Q sub aus,12.

delta m sub 12 times (u sub 2 minus h sub ein,12) equals m sub 1 u sub 1 minus m sub 1 u sub 2 minus Q sub aus,12.

delta m sub 12 equals (m sub 1 u sub 1 minus m sub 1 u sub 2 minus Q sub aus,12) divided by (u sub 2 minus h sub ein,12), m sub 1 equals M sub gas,1 equals 3755 kilograms.

h sub ein,12 equals h(20 degrees Celsius, x equals 0) equals h sub f(20 degrees Celsius) equals 83.36 kilojoules per kilogram (A-2).

u sub 1 equals u(100 degrees Celsius, x equals 0) equals u sub f(100 degrees Celsius) equals 418.94 kilojoules per kilogram (A-2).

u sub 2 equals u(70 degrees Celsius, x equals 0) equals u sub f(70 degrees Celsius) equals 292.95 kilojoules per kilogram (A-2).

delta A sub m 12 equals u sub 1 equals u(100 degrees Celsius, x equals 0.005) minus u sub f(100 degrees Celsius) plus x times (u sub g(100 degrees Celsius) minus u sub f(100 degrees Celsius)) equals 429.38 kilojoules per kilogram (A-2).

delta m sub 12 equals 3588.4 kilograms.

(e) delta S equals m sub 2 S sub 2 minus m sub 1 S sub 1 equals (m sub 2 1 plus delta m sub 12) S sub 2 minus m sub 1 S sub 1.

S sub 1 equals s(100 degrees Celsius, x equals 0.005) equals S sub f(100 degrees Celsius) plus x times (S sub g(100 degrees Celsius) minus S sub f(100 degrees Celsius)) equals 1.337 kilojoules per kilogram per Kelvin (A-2).

S sub 2 equals s(70 degrees Celsius, x equals 0) equals S sub f(70 degrees Celsius) equals 0.3549 kilojoules per kilogram per Kelvin (A-2).

delta S equals 1227.7 kilojoules per Kelvin.