c)  

Reactor  

Q dot aus over T reactor minus Q dot aus over T KW plus S dot ir times t  
equals S dot ir times t equals 65 kilowatts over 295 Kelvin minus 15 kilowatts over 373.45 Kelvin  
equals 0.046 kilowatts per Kelvin

A table is drawn with columns labeled Z, T, V, P, Q, W, and Notiz. 

- Row Z0: T is labeled as 'Referenz' and '-30 degrees Celsius'. V is labeled '0.191 bar'.
- Row Z1: No entries are present.
- Row Z2: No entries are present.
- Row Z3: No entries are present.
- Row Z4: No entries are present.
- Row Z5: T is labeled '491 K'. V is labeled '0.5 bar'. Q is labeled '220 cubic meters per second'.
- Row Z6: No entries are present.
  
Under Notiz:
- 1 to 2: isentrope
- 2 to 3: isotherm
- 3 to 4: adiabatic
- 5 to 6: isentrope

Below the table, equations and notes are written:
- W dot plus equals 200 cubic meters per second.
- p0 equals 0.191 bar.
- T0 equals minus 30 degrees Celsius.
- m dot M over m dot K equals 5.293.

A sketch of an arrow is drawn next to the text:
- Luft: 1 G.
- Cp equals 1.006 kilojoules per kilogram Kelvin.
- n equals k equals 1.4.

A graph is drawn with labeled points and lines. The graph has an upward slope from point 0 to point 2, labeled "1". Then it continues upward from point 2 to point 3, labeled "2". From point 3, it slopes downward to point A, labeled "3". From point A, it slopes upward to point 5, labeled "4". Finally, it slopes downward from point 5 to point C. The labels on the graph are P1, P2, P3, and P4. There is a note on the side that reads "0.191 bar / p0 / p0".

c) Delta e x s t r equals h v minus h zero minus T zero s six minus s zero plus one half omega zero squared minus one half omega two squared.

equals T b minus T zero c p i g minus T zero c p i g ln T b over T zero minus R ln p b over p zero minus one half k omega zero squared plus one half k omega two squared.

R equals c p i g minus c v i g

equals c p i g minus c p i g over n equals c p zero left parenthesis one minus one over n right parenthesis equals one point zero zero six k j over k g k left parenthesis one minus one over one point four right parenthesis equals zero point two eight seven k j over k g.

a) Delta e x s t r equals left parenthesis three four zero K minus two four three point one five K right parenthesis one point zero zero six k j over k g k minus two four three point one five K left parenthesis one point zero zero six k j over k g k ln left parenthesis three four zero K over two four three point one five K right parenthesis right parenthesis minus zero point two five seven k j over k g k ln left parenthesis one right parenthesis plus one half left parenthesis two hundred m squared per s squared right parenthesis squared plus one half left parenthesis five hundred m squared per s squared right parenthesis squared.

equals

d) e x e r g y equals T zero s zero minus s zero.

zero equals q B over T B plus s zero.

s i r r equals plus q B over T B equals one one zero five k j over two nine eight K minus zero point nine two seven k j over k g k.

e x e r g y equals three zero three point one five K times zero point nine two seven k j over k g k minus two point five one M W.