W dot G equals five hundred ten cubic meters per second, T zero equals three hundred forty Kelvin, R equals crossed out content, C p equals C v times n, n equals C p over C v.

C v equals C p over n.

C v equals one point zero zero six times crossed out content over one point four.

C v equals zero point seven one eight five seven.

Zero e dot s f equals crossed out content times h c minus h zero minus T zero times S c minus S zero.

S zero dot f minus S zero dot i equals integral from T zero to T c of C p of T over T d T minus R ln p c over p zero.

Equals minus C p of T times T c minus T zero minus R ln p G over p zero equals crossed out content over three hundred ten Kelvin minus two hundred forty-three point one five Kelvin.

Minus one point zero zero six times crossed out content minus zero point seven one eight five times ln zero point eight nine point one zero to the power of zero point one nine four point one zero to the power of one.

One point zero zero six times crossed out content over crossed out content times three hundred ten Kelvin minus two hundred forty-three point one five Kelvin minus S plus crossed out content minus crossed out content.

S zero dot f minus S zero dot i equals C p ln T G over T zero equals one point zero zero six times ten to the power of negative three over crossed out content times ln three hundred ten Kelvin over two hundred forty-three point one five Kelvin equals.

Equals three hundred thirty-seven point two seven eight eight crossed out content over crossed out content.

Equals D zero e dot s f equals eighty-five point four three five crossed out content over crossed out content minus two hundred forty-three point one five Kelvin minus three hundred thirty-seven point two seven eight eight crossed out content over crossed out content.

Zero e dot s f equals three hundred forty-two point one eight eight five eight crossed out content over crossed out content.