S dot er 2 equals question mark.

d S over d t equals zero stat equals m dot k F times (h e minus h a) plus Q dot aus over T k F plus S dot er 2.

S dot er 2 equals m dot times (h a minus h e) minus Q dot aus over T k F.

Diagram: A rectangle with labels 298.15 K and 288.15 K inside, labeled as 'prison box'. Yellow highlights around the rectangle.

Q dot aus equals 65 kW.

T k F equals 295 K.

h a (298.15 K) equals h f (Gamma 2) plus v i times (p minus p sat (T)).

h e (288.15 K) equals h f (T A) plus v i times (p minus p sat (T)).

Delta h equals h f (Gamma 2) minus h f (T A) equals C i f times (T 2 minus T A).

Delta E exergy system control volume equals m dot times [h6 minus h0 minus T0 times (s6 minus s0) plus w6 squared over 2] equals m dot ges.

Delta E exergy system equals 12.158 kilojoules per kilogram plus w6 squared over 2 equals 116.487 kilojoules per kilogram.

h6 minus h0 equals c times (T6 minus T0) plus v times (p6 minus p0) equals 85.434 kilojoules per kilogram equals 0.

T6 equals 328.075 Kelvin.

T0 equals 30 plus 273.15 equals 243.15 Kelvin.

s6 minus s0 equals c times (ln(T6 over T0)) equals 0.30143 kilojoules per kilogram Kelvin.

c times c equals 507.24 meters per second.

w6 squared over 2 equals 128646.

At state 2 equilibrium, delta U equals zero.

Delta U equals delta U gas plus delta U EW.

c sub v (T sub 2g minus T sub g) c sub if (T sub 2W minus T sub W).

T sub 2g equals T sub 2W equals 0.003 degrees Celsius.

Delta E equals Q minus W sub v equals zero.

Q equals W sub v, therefore q equals omega v equals R (T sub 2 minus T sub 1) over 1 minus n.

R equals c sub v (k minus lambda).

R over c sub v plus 1 equals k.

Crossed out content.

Closed system.

Delta E equals m (u sub 2 minus u sub 1) equals Q.

c sub v (T sub 2 minus T sub a).

Throttle isenthalpic, isothermal

x four equals zero
p four equals eight bar
h two equals ninety-three point forty-two kilojoules per kilogram
TAB A four one one

T four equals thirty-one point thirty-three

h one equals ninety-two point forty-two
p u equals six bar

Interpolating at TAB A four twelve

h equals phi of p one minus phi of p two divided by p one minus p two times (p minus p two) plus phi of p two

P equals h minus phi of p two divided by phi of p one minus phi of p two times (p one minus p two) plus p two