d one equals G sub t equals one over Q dot k times one minus Q dot k over Q dot t

T one four three equals three to four

Q equals m two times h two minus h one minus Q dot a b

Q dot a b equals m two times h two minus h one

b sub s u equals h two final plus f of b critical equals zero point three four two times l sub s over l sub k

T four three equals four eleven

h one equals h one final (s heater)

x two equals s two minus s one final over s three initial minus s one final (at eight bar)

s three initial greater than s two greater than s one final

h three equals h three final plus x two times (h three two minus h three final) (at eight bar)

Delta U equals Q one two implies m two ew times (u one minus u one f) equals Q one two.

m two ew times m two ew equals Q one two divided by d one f.

u two equals Q one two divided by m two ew minus u one equals minus one hundred twenty-two point five eight kilojoules per kilogram.

u two equals u one f e.

u two equals zero degrees Celsius.

u two (zero degrees Celsius) equals u one f e plus x two times (u one g e minus u one f e).

Equals three hundred thirty-three point four five eight plus zero point six times (zero point zero four five times three hundred thirty-three point four five eight).

Equals minus one hundred thirty-three point four one zero two kilojoules per kilogram.

T ew two equals Q zero point zero zero five divided by zero point zero zero three times alpha.

x two equals u two minus u two f r divided by u two f t minus u two f r equals zero point six three two.

Zero equals delta exergy start minus exergy converted.

Exergy converted equals 100 kilojoules per kilogram.