h two phase mixture equals u times k sub s over l

T two equals negative twenty two degrees Celsius

x two equals question mark

s one equals s two equals s critical equals s one final

p critical equals eight bar

s critical of eight bar equals zero point three four five zero

T four three equals four eleven

x one equals s one minus s one final over s one two final minus s one final

zero less than or equal to delta h two phase mixture minus h two final

TE equals 0.003 times c equals 273.15 times c

dE equals minus Q12

mG2 minus mG1 equals minus Q12

mG (u2 minus u1) equals minus Q12

Q12 equals mG (u1 minus u2) equals 1.083 joules

u1 minus u2 equals c (T1 minus T2) equals 316.438 joules per kilogram times Kelvin divided by kilogram times seconds

v zero equals 510 meters per second.

Delta exergy start minus exergy start zero equals exergy destroyed.

Exergy start equals m dot times h zero minus h zero zero plus s zero minus s zero zero plus w zero squared divided by two.

Exergy start zero equals m dot times h zero minus T zero times s zero minus s zero zero plus w zero zero squared divided by two.

Delta exergy start equals m dot times h zero minus h zero zero minus T zero times s zero minus s zero zero plus v zero squared divided by two minus w zero zero squared divided by two.

h zero minus h zero zero equals c p times T zero minus T zero zero equals 85.435 kilojoules per kilogram.

s zero minus s zero zero equals c p times ln T zero divided by T zero zero minus R times ln p zero divided by p zero zero equals c p times ln T zero divided by T zero zero equals 8.301 kilojoules per kilogram Kelvin.

v zero squared divided by two minus w zero zero squared divided by two equals 631850.

Falls is relevant direct with einstein.