a) O equals m dot ein times (h ein minus h aus) plus Q dot R minus Q dot aus minus W dot zero. m dot ein equals m dot aus equals m dot.

Stationary flow process:

Q dot aus equals m dot ein times (h ein minus h aus) plus Q dot R.

Equals 0.3 kg per second times (292.38 kJ per kg minus 930.12 kJ per kg) plus 100 kW equals 58.86 kW.

h ein equals h f at [70 degrees C] equals 292.38 kJ per kg.

X D equals h aus minus h f over h g minus h f at T equals 100 degrees C.

h aus equals h f plus X D times (h g minus h f) equals 919.06 kJ per kg plus 0.005 times (2631.3 minus 919.06) kJ per kg equals 930.12 kJ per kg.

b) T bar KF equals T KF, ein plus T KF, aus over 2 equals 288.15 Kelvin plus 298.15 Kelvin over 2 equals 293.15 Kelvin.

c) S dot erz

Entropy balance:

O equals m dot times (s ein minus s aus) plus Q dot R over T rein dot 1 minus Q dot aus over T KF plus S dot erz.

S dot erz equals Q dot aus over T KF plus m dot times (s aus minus s aus eia) minus Q dot R over T rein dot 1.

TAB-AZ

s aus equals s f plus X D times (s g minus s f) equals 1.3069 kJ per kg Kelvin plus 0.005 times (7.3549 minus 1.3069) kJ per kg Kelvin.

At T equals 160 degrees C equals 1.3374 kJ per kg Kelvin.

S_en equals S_f, evaluated at T equals 70 degrees Celsius, equals 0.9554 kilojoules per kilogram Kelvin.

S_dot_en equals 58.86 kilowatts divided by 293.15 Kelvin plus 0.3 kilograms per second multiplied by (1.3379 kilojoules per kilogram minus 0.9554 kilojoules per kilogram Kelvin) equals 100 kilowatts divided by 371.15 Kelvin.

Equals 0.096 kilowatts per Kelvin.