Energy balance:
Zero equals mass flow rate times (enthalpy in minus enthalpy out) plus heat output plus heat recovery.

Zero equals mass flow rate times (enthalpy at 70 degrees Celsius minus enthalpy at 100 degrees Celsius) minus heat output plus heat recovery.

Arrow indicates mass flow rate equals 0.3 kilograms per second.

Enthalpy at 70 degrees Celsius equals 232.98 kilojoules per kilogram.

Enthalpy at 100 degrees Celsius equals 419.011 kilojoules per kilogram.

Heat output equals mass flow rate times (enthalpy at 70 degrees Celsius minus enthalpy at 100 degrees Celsius) plus 100 kilowatts.

Heat output equals 62.182 kilowatts.

W equals R times (Tg minus Ts) divided by 1 minus n.

Wc equals 259.56 kilojoules.

Wc equals the square root of 2 times (h4 minus h3 minus Wc) plus Ws squared divided by 2.

Wc equals the square root of 2 times (Cp times (Tg minus Ts) minus R times (Tg minus Ts) divided by 1 minus n) plus Ws squared divided by 2.

Wc equals 551.5 kilojoules per kilogram.

Cv equals Cp divided by k.

R equals Cp minus Cv divided by k equals 0.2879 kilojoules per kilogram per kelvin.

Ws equals 220 joules per kilogram.

(h5 minus hc) equals Cp times (Tg minus Ts), ideal gas.

c) Wc equals 510 joules per kilogram divided by Tc equals 310 kelvin.

O equals m dot times (hen minus haus minus To times (Sein minus Saus) plus Ws squared minus Uc squared divided by 2) plus Q dot in minus Ex ideal.

Delta esist equals Wc minus hc minus Tc times (Sc minus Sl) plus Ws squared minus Uc squared divided by 2.

Delta esist equals Cp times (Tc minus Ta minus To ln (Tc divided by To) plus Ws squared minus Uc squared divided by 2.

hc minus ho equals Cp times (Tc minus To).

fc minus sc equals Cp ln (Tc divided by To).

d) Ex ideal minus To times Sez.

Sez equals m dot times (Saus minus Sein).

Exine equals To times (Saus minus Sein) equals.