a) [Diagram of a reactor with arrows labeled]
- m dot in
- Q dot R equals 100 kilowatts
- Q dot aus
- m dot aus

0 equals m dot (h ein minus h aus) plus Q dot R minus Q dot aus

h ein equals 292.39 kilojoules per kilogram (Tab A-2, 70 degrees Celsius) (4.1)

h aus equals h f (100 degrees Celsius) equals 419.04 kilojoules per kilogram (Tab A-2)

Q dot aus equals m dot (h ein minus h aus) plus Q dot R equals 62.182 kilowatts

b) [Diagram with arrows]
T equals T a,a minus T e,e over S a minus S e

S a minus S e equals c w,in ln (T w over T c)

0 equals m dot in (h e minus h a) plus Q dot aus

d) equals m dot in c w,in delta T plus Q dot aus
R dot equals minus 10 kilojoules

T equals integral J dot T dS over S a minus S e

fehlt diese Angabe in der Aufgabenstellung?

c) S dot ex equals minus (m dot aus c w,in ln (T w over T ein) plus Q dot aus over 293 Kelvin)

von KF

d) m zero one equals fifty seven point five five kilograms at one hundred degrees Celsius, x equals zero point zero zero five. 

Arrow pointing right m zero two at seventy degrees Celsius, m zero two equals m zero one plus delta m zero two.

Arrow pointing right m zero two U two minus m zero one U one equals delta m zero two plus Q waste two.

U one equals four hundred seventy eight point one plus zero point zero zero five times two thousand five hundred six point five minus two hundred fifty two point zero zero zero zero zero nine. 

(TAB A-2, U field) at one hundred degrees Celsius.

U two equals two hundred fifty two point eight five plus zero point zero zero five times two thousand four hundred forty six point six minus two hundred fifty two point five two nine. 

Arrow pointing left at seventy degrees Celsius.

Arrow pointing right delta m zero two equals m zero two times (U two minus U one) minus Q waste two divided by one minus U two equals two thousand five hundred one point four zero five kilograms.

e) S one equals m zero one times (one point three zero six plus zero point zero zero five times seven point three five four five minus one point three zero six four).

S two equals m zero two times (zero point five five four plus zero point zero zero five times seven point five five two minus zero point five three five four).

(Werte für S f d g aus TAB A-2 für S one at one hundred degrees Celsius, für S two at seventy degrees Celsius).

m zero two equals eight thousand two hundred fifty six point two zero five kilograms per square meter.

Delta S twelve equals S two minus S one equals two hundred sixty nine point five three kilojoules per Kelvin.