x subscript EWS comma 1 equals m subscript EWS comma 1 divided by m subscript EW equals 0.1 kilograms. 0.6 if and only if m subscript EWS comma 1 equals 0.06 kilograms implies m subscript FW equals m subscript EW minus m subscript EWS comma F equals 0.04 kilograms.

U subscript EW comma 1 equals m subscript EWS comma 1 U subscript rest plus m subscript FL comma 1 U subscript FL equals 0.06 kilograms times negative 333.458 kilojoules per kilogram plus 0.04 kilograms times negative 0.045 kilojoules per kilogram approximately negative 20 kilojoules.

U subscript EW comma 2 equals U subscript EW comma 1 plus Q subscript 12 equals negative 20 kilojoules plus 1440.7 joules equals negative 18.56 kilojoules.

m subscript EW comma 2 U subscript rest plus m subscript FL comma 2 U subscript FL equals m subscript EW comma 2 times negative 333.458 kilojoules per kilogram plus 0.1 kilograms minus m subscript EW comma 2 times negative 0.045 kilojoules per kilogram.

m subscript EW comma 2 equals negative 333.458 kilojoules per kilogram plus 0.045 kilojoules per kilogram minus 0.1 kilograms times negative 0.045 kilojoules per kilogram.

m subscript EW comma 2 equals 0.1 kilograms times 0.045 kilojoules per kilogram minus 18.56 kilojoules divided by negative 333.458 kilojoules per kilogram plus 0.045 kilojoules per kilogram approximately 0.0557 kilograms.

x subscript EWS comma 2 equals m subscript EWS comma 2 divided by m subscript EW equals 0.0557 kilograms divided by 0.1 kilograms equals 0.557.