dE over dt equals the sum from i of m sub i of t times l sub i of t times p sub ext of t plus the sum from i of Q sub j of t equals the sum from i of d sub n of t.

u2 minus u1 equals according to my opinion the first law: Q sub int plus QR.

For v2g2:

Vg2 equals m divided by p equals three point four nine times ten to the power of three kilograms divided by zero point one six six two eight cubic meters per kilogram times two hundred seventy three point one five Kelvin divided by one point four times ten to the power of two cubic meters per kilogram.

Equals one point one zero nine times ten to the power of minus three cubic meters.

Vg2 equals one point one zero nine times ten to the power of minus three cubic meters divided by three point four nine times ten to the power of three kilograms equals zero point three two four three six four cubic meters per kilogram.

W12 equals the integral from one to two of p dv equals R times p times (v2 minus v1) equals one point four times v2 minus v1 cubic meters times (equals seven point one four times ten to the power of two cubic meters per kilogram times (zero point three two four three six four cubic meters per kilogram minus zero point nine four eight three three seven cubic meters per kilogram) equals minus eight three point one six four cubic meters per kilogram.

W12 minus W12 mg equals minus eight three point one six four cubic meters per kilogram equals three point four nine times ten to the power of three kilograms equals minus zero point two eight four three four cubic meters per kilogram.

U2 minus U1 equals cv times (t2 minus t1) times mg equals zero point six eight three cubic meters per kilogram times (two hundred seventy three point one five Kelvin minus seventy seven point three five Kelvin) times three point four nine times ten to the power of three kilograms.

Equals minus seven one zero eight two seven cubic meters per kilogram.

Q12 equals U2 minus U1 plus W12 equals minus one three six six point four cubic meters per kilogram.

Absolute value of Q12 equals seven three six six point four cubic meters per kilogram.