Delta exergy stream equals mass flow rate multiplied by (enthalpy at state e minus enthalpy at state s minus temperature zero multiplied by (entropy at state s minus entropy at state s zero) plus kinetic energy at state e minus kinetic energy at state s).  

Delta exergy stream equals mass flow rate multiplied by (enthalpy at state e minus enthalpy at state s minus temperature zero multiplied by (entropy at state s minus entropy at state s zero) plus (velocity squared at state e minus velocity squared at state s) divided by two).  

Enthalpy at state e minus enthalpy at state s equals the integral of specific heat capacity multiplied by dT.  

Entropy at state s minus entropy at state s zero equals the integral of specific heat capacity divided by temperature multiplied by dT minus gas constant multiplied by the natural logarithm of pressure at state zero divided by pressure at state zero.  

Entropy at state s minus entropy at state s zero equals 1.006 multiplied by the natural logarithm of 328.07 divided by 243.15 minus 1.725 kilojoules per kilogram Kelvin multiplied by the natural logarithm of pressure ratio.  

Entropy at state s minus entropy at state s zero equals 0.301 kilojoules per kilogram Kelvin.  

Delta exergy stream equals mass flow rate multiplied by (85.43 kilojoules per kilogram minus 243.15 Kelvin multiplied by 0.301 kilojoules per kilogram Kelvin minus 24659.122 kilojoules per kilogram).  

Delta exergy stream equals mass flow rate multiplied by (24659.122 kilojoules per kilogram).