R subscript g equals 8.314 divided by M equals 50.  

p times V equals m times R times T.  

Pressure in EW:  

A equals 10 times 0.05 squared times pi equals 0.007853.  

p subscript EW equals m subscript K times g divided by A plus p subscript amb equals 1.33937 bar.  

Diagram: A cylinder is shown with the upper chamber labeled m subscript EW equals 0.1 kilograms and the lower chamber labeled m subscript g. Forces are indicated pressing down on the cylinder.

Energy balance for water:  
Change in internal energy (\( \Delta U \)) equals heat transfer (\( Q_{12} \)) minus work (\( W_{12} \)).  
\( \Delta U = Q_{12} - W_{12} \)  
\( Q_{12} = W_{12} + \Delta U \)  
\( = -1.367 \, \text{kJ} \)  

Work done on water:  
\( \Delta U_{\text{water}} = m_{\text{water}} \cdot (u_2 - u_1) \)  
\( = 0.1 \cdot (1488 - 106) \)  
\( = 148.8 - 10.6 \)  
\( = 432.4 \, \text{J} \)  

Work done on the environment:  
\( W_{\text{water}} = p_{\text{amb}} \cdot \Delta V \)  
\( = -2.031 \cdot 1 \, \text{bar} = -203.07 \, \text{J} \)  

Work done on water minus work on the environment:  
\( = 489.16 \, \text{J} = W_{\text{water}} \)

u2 equals u1 (at 0 degrees Celsius) equals -200.0328 kilojoules per kilogram.  

u2 equals x multiplied by u(vapor) plus (1 minus x) multiplied by u(liquid).  

u2 equals x multiplied by (u(vapor) minus u(liquid)) plus u(liquid).  

u2 equals x multiplied by u(vapor) minus u(liquid) plus u(liquid).  

x equals (u2 minus u(liquid)) divided by (u(vapor) minus u(liquid)).  

x equals (u2 minus u(liquid)) divided by (u(vapor) minus u(liquid)).  

u2 equals u1 plus 423.22 equals 223.127 kilojoules per kilogram.  

x equals 0.0669.  

Somewhere an error in x adds up and is negative?  

p equals 1 bar.  

T equals 0 degrees Celsius.