Delta exergy of the stream equals exergy of the stream at state 6 minus exergy of the stream at state 0.  
Delta exergy of the stream equals h sub c minus h sub 0 minus T sub 0 multiplied by (s sub c minus s sub 0) plus kinetic energy at state c minus kinetic energy at state 0.  

h sub c minus h sub 0 equals the integral from T sub 0 to T sub c of c sub p of air multiplied by dT equals c sub p of air multiplied by (T sub c minus T sub 0).  
c sub p of air equals 1.006 kilojoules per kilogram Kelvin.  
(325.0 Kelvin minus 243.15 Kelvin) equals 85.43 kilojoules per kilogram.  

From Table A-22:  
s superscript 0 of T sub c equals (1.97833 minus 1.978249) kilojoules per kilogram Kelvin (325.0 Kelvin plus 325 Kelvin) divided by 2 equals 1.978249 kilojoules per kilogram Kelvin.  
s superscript 0 of T sub 0 equals 1.7919 kilojoules per kilogram Kelvin.  
s superscript 0 of T sub 0 equals (1.49111 minus 1.491824) kilojoules per kilogram Kelvin (243.15 Kelvin minus 240 Kelvin) divided by (250 Kelvin minus 240 Kelvin) equals 1.49111 kilojoules per kilogram Kelvin.  

Delta exergy of the stream equals h sub c minus h sub 0 minus T sub 0 multiplied by (s sub c minus s sub 0) plus kinetic energy at state c minus kinetic energy at state 0.  
Kinetic energy at state c equals 0.5 multiplied by w sub c squared.  
Kinetic energy at state 0 equals 0.5 multiplied by w sub 0 squared equals 20,000 meters squared per second squared.  

Delta exergy of the stream equals 85.43 kilojoules per kilogram minus 243.15 Kelvin multiplied by (1.7919 kilojoules per kilogram Kelvin minus 1.49111 kilojoules per kilogram Kelvin) plus (1288651.28 minus 20000) meters squared per second squared.  

Delta exergy of the stream equals 1280.94 kilojoules per kilogram.