Delta exergy stream equals exergy stream six minus exergy stream zero.  

Delta exergy stream equals (enthalpy six minus enthalpy zero) minus T zero multiplied by (entropy six minus entropy zero) plus Delta kinetic energy.  

Delta kinetic energy equals velocity six squared divided by two minus velocity zero squared divided by two.  
Delta kinetic energy equals (three hundred twenty meters per second squared divided by two) minus (two hundred meters per second squared divided by two).  
Delta kinetic energy equals (five hundred ten meters per second squared divided by two) minus (two hundred meters per second squared divided by two).  

Enthalpy six minus enthalpy zero equals c_p multiplied by (T six minus T zero).  
Enthalpy six minus enthalpy zero equals one thousand fifty-six multiplied by (four hundred thirty-one point nine minus two hundred seventy-three point one five).  
Enthalpy six minus enthalpy zero equals eleven thousand fifty joules per kilogram.  

T zero multiplied by (entropy six minus entropy zero) equals two hundred forty-three point one five multiplied by c_p multiplied by ln (T six divided by T zero) minus R multiplied by ln (p six divided by p zero).  
T zero multiplied by (entropy six minus entropy zero) equals eighty-two point zero one kilojoules per kilogram.  

Delta exergy stream equals ninety-seven minus eighty-two point zero one plus one hundred ten point one kilojoules per kilogram.  
Delta exergy stream equals one hundred twenty-five point zero nine kilojoules per kilogram.