A graph is drawn representing a phase diagram. The x-axis is labeled as 'T [K]' (temperature), and the y-axis is labeled as 'p [bar]' (pressure). The graph includes the following annotations:  
- A curve labeled 'Triple point' with a dot marking the triple point.  
- The regions are labeled as 'fest' (solid), 'flüssig' (liquid), and 'dampf' (vapor).  
- An arrow pointing upwards is labeled 'sicher' (safe).  
- Another arrow pointing to the right is labeled '2a'.

A graph is drawn on a grid with the y-axis labeled as "T [K]" (temperature in Kelvin) and the x-axis labeled as "s [kJ/kg·K]" (specific entropy). The graph represents a thermodynamic process with six states labeled as 0, 1, 2, 3, 4, 5, and 6.  

- **State 0**: Marked at the bottom left with \( T_0 = 243.15 \, \text{K} \).  
- **State 1**: Connected to state 0 via an upward vertical line labeled "adiabat" and "isentrop".  
- **State 2**: Connected to state 1 via a horizontal line labeled "isobar".  
- **State 3**: Connected to state 2 via a diagonal line labeled "adiabat irreversible".  
- **State 4**: Connected to state 3 via a horizontal line labeled "isobar".  
- **State 5**: Connected to state 4 via a diagonal line labeled "adiabat reversible → isentrop".  
- **State 6**: Connected to state 5 via a horizontal line labeled "isobar 0.191 bar".  

Below the graph, a table is drawn with columns labeled "P", "T", and "Notes".  

- **Row 0**: \( P = 0.191 \, \text{bar} \), \( T = 243.15 \, \text{K} \), Notes: "ambient".  
- **Row 1**: \( P = \text{isentrop} \), \( T = T_s \), Notes: "adiabat, reversible → isentrop".  
- **Row 2**: \( P = \text{isobar} \), \( T = T_s \), Notes: "isobar".  
- **Row 3**: \( P = \text{adiabat irreversible} \), \( T = \text{adiabat irreversible} \), Notes: "adiabat irreversible".  
- **Row 4**: \( P = \text{isobar} \), \( T = \text{isobar} \), Notes: "isobar".  
- **Row 5**: \( P = 0.5 \, \text{bar} \), \( T = 431.9 \, \text{K} \), Notes: "adiabat reversible → isentrop".  
- **Row 6**: \( P = 0.191 \, \text{bar} \), \( T = \text{ambient} \), Notes: "adiabat reversible → isentrop".  

Additional notes are written next to the table:  
- "adiabat reversible → isentrop"  
- "adiabat irreversible"  
- "isentrop"  
- "isobar"  

No further content is visible.