The page contains two T-s diagrams and one smaller schematic diagram related to the jet engine process.  

### First T-s Diagram:  
- The diagram is labeled with points 0, 1, 2, 3, 5, and 6.  
- The process transitions are marked as follows:  
  - From 0 to 1: "adiabatisch, irrev." (adiabatic, irreversible).  
  - From 1 to 2: "isentrop." (isentropic).  
  - From 2 to 3: "adiabatisch, irrev." (adiabatic, irreversible).  
  - From 3 to 5: "isobar" (isobaric).  
  - From 5 to 6: "isentrop." (isentropic).  
- The pressure relationships are noted:  
  - \( p_2 = p_3 \).  
  - \( p_0 = p_6 \).  

### Second T-s Diagram:  
- Similar to the first diagram, this one includes points 0, 1, 2, 3, 4/5, and 6.  
- The process transitions are labeled:  
  - From 0 to 1: "adiabatisch, irrev." (adiabatic, irreversible).  
  - From 1 to 2: "isentrop." (isentropic).  
  - From 2 to 3: "adiabatisch, irrev." (adiabatic, irreversible).  
  - From 3 to 4/5: "isobar Mantelstrom" (isobaric mantle flow).  
  - From 4/5 to 6: "isentrop." (isentropic).  
- Additional notes:  
  - \( p_2 = p_3 \).  
  - \( p_4 = p_5 \) (relativ als p_0, p_6) (relative to \( p_0 \), \( p_6 \)).  
  - \( p_0 = p_6 \).  

### Smaller Schematic Diagram:  
- A simplified representation of the process with points 0, 1, 2, 3, 4/5, and 6.  
- The transitions between points are visually connected but not labeled with specific processes.  

Axes:  
- Both T-s diagrams have the x-axis labeled as \( s \) (specific entropy) with units \( [\frac{w}{kg}] \).  
- The y-axis is labeled as \( T \) (temperature).  

No additional text or equations are present.