The page contains mathematical equations and diagrams related to thermodynamic processes.  

Equations:  
- z squared over z zero minus z squared over z zero plus (phi over phi one) multiplied by w minus (phi one minus phi one) multiplied by w zero minus (phi one minus phi one) multiplied by w zero equals ...  
- (phi one minus phi one) multiplied by w zero minus z squared over z zero equals z squared over z zero.  
- z squared over z zero minus z squared over z zero plus (phi minus phi one) multiplied by w minus (phi one minus phi one) multiplied by w zero minus phi one multiplied by w zero equals zero.  

Diagrams:  
Two diagrams are drawn at the bottom of the page.  
1. The first diagram shows a graph with labeled axes. The x-axis is labeled "s," and the y-axis is labeled "1." A curve is drawn, starting from the origin and curving upwards. A dashed line intersects the curve.  
2. The second diagram also shows a graph with labeled axes. The x-axis is labeled "s," and the y-axis is labeled "1." A curve is drawn, starting from the origin and curving upwards, but this time it intersects with multiple lines, including a bold curve and a dashed line.  

Additional notes:  
Some parts of the equations and diagrams are crossed out or overwritten, making them difficult to interpret fully.

A diagram is drawn with axes labeled "T" (temperature) and "S" (entropy). The diagram includes several curves and lines:
- A curved line labeled "1 → 2" representing an isentropic compression process.
- A vertical line labeled "2 → 3" indicating isobaric heat addition.
- A curved line labeled "3 → 4" representing an adiabatic expansion process.
- A dashed line labeled "5 → 6" indicating a mixing process.
- The diagram also includes arrows and annotations showing the flow of the thermodynamic processes.

Equations and annotations:
1. \( s_1 = s_2 \) (isentropic process).
2. \( s_5 = s_6 \) (isentropic mixing).
3. \( \frac{w_6^2}{2} - \frac{w_5^2}{2} = 0 \) (velocity change equation).
4. \( h_6 = h_5 + \frac{w_5^2}{2} - \frac{w_6^2}{2} \) (enthalpy equation).
5. \( \dot{m}_M \cdot w_6 = \dot{m}_K \cdot w_5 \) (mass flow rate equation).
6. \( ex_{str,6} - ex_{str,0} = \frac{w_6^2}{2} - \frac{w_0^2}{2} + h_6 - h_0 \) (specific exergy change equation).

Additional notes:
- \( ex_{verl} = ex_{str,0} + ex_{str,6} - ex_{str,5} \) (specific exergy loss equation).
- \( w_6 = w_5 \) (velocity equality).
- \( h_6 = h_5 \) (enthalpy equality).

No further content or clear task labels are visible.