The page contains two diagrams related to Task 2.  

**Diagram 1 (Top):**  
A temperature-entropy (T-s) diagram is drawn with labeled isobars and process steps.  
- The vertical axis is labeled as "T (째C)" for temperature.  
- The horizontal axis is labeled as "s (kJ/kgK)" for entropy.  
- The diagram includes the following labeled points and processes:  
  - Point 0: \( p = 0.197 \, \text{bar}, T = -30^\circ \text{C} \).  
  - Point 1: Vorverdichter (pre-compressor).  
  - Point 2: Verdichter (compressor).  
  - Point 3: Brennkammer (combustion chamber).  
  - Point 4: Turbine.  
  - Point 5: Mischkammer (mixing chamber).  
  - Point 6: Schubd체se (nozzle).  
- The processes are labeled:  
  - Compression between points 0 and 2.  
  - Isentropic process between points 2 and 3.  
  - Isobaric heat addition in the combustion chamber (point 3).  
  - Adiabatic process in the turbine (point 4).  
  - Mixing chamber (point 5).  
  - Exhaust through the nozzle (point 6).  

**Diagram 2 (Bottom):**  
Another T-s diagram is drawn with similar labels.  
- The vertical axis is labeled as "T (째C)" for temperature.  
- The horizontal axis is labeled as "s (kJ/kgK)" for entropy.  
- The same points (0, 1, 2, 3, 4, 5, 6) are labeled, along with the processes:  
  - Vorverdichter (pre-compressor).  
  - Verdichter (compressor).  
  - Brennkammer (combustion chamber).  
  - Turbine.  
  - Mischkammer (mixing chamber).  
  - Schubd체se (nozzle).  

Additional notes are written near the diagrams:  
- "Brennkammer Turbine isobare adiabate" (combustion chamber and turbine processes are isobaric and adiabatic).  
- "kompression" (compression).  
- "isentrop" (isentropic).  

No equations or further explanations are provided.