Two diagrams are drawn, both labeled with axes and annotations:  

1. **First Diagram:**  
   - The x-axis is labeled as 's [2/u]'.  
   - The y-axis is labeled as 'T (K)'.  
   - Points are marked as '0', '1', and '2'.  
   - A curve connects these points, with annotations:  
     - 'p0 = 0.191 bar' near point '0'.  

2. **Second Diagram:**  
   - The x-axis is labeled as 's [2/u]'.  
   - The y-axis is labeled as 'T (K)'.  
   - Points are marked as '0', '2', '3', '4', and '6'.  
   - A series of lines connect these points, forming a cycle.  
   - Annotations include:  
     - '0.5 bar' near point '3'.  
     - 'clear axial gas flows' near point '4'.  
     - 'p0' with an arrow pointing downward near point '6'.  

No additional text or equations are present.

Two diagrams are drawn:  

1. **Top Diagram**:  
   - The vertical axis is labeled as "T (K)" (temperature in Kelvin).  
   - The horizontal axis is unlabeled.  
   - The diagram consists of curves and straight lines forming a closed cycle.  
   - Points are labeled as 0, 1, 2, 3, 4, and 6.  
   - Curves connect these points, representing transitions between states.  

2. **Bottom Diagram**:  
   - The vertical axis is unlabeled.  
   - The horizontal axis is unlabeled.  
   - The diagram consists of curves and straight lines forming a closed cycle.  
   - Points are labeled as 0, 1, 2, 4, 5, and 6.  
   - Curves connect these points, representing transitions between states.  

The label "SL" appears near the bottom diagram.