Energy balance for the heat exchanger in the cooling cycle  

[Diagram]  
A rectangular diagram is drawn, representing the heat exchanger. Inside the diagram, the refrigerant R134a is labeled, and a downward arrow labeled \( \dot{Q}_K \) represents heat transfer.  

SFP:  
Zero equals \( \dot{m}_R \) times \( h_1 \) minus \( h_2 \) plus \( \dot{Q}_K \).  

Entropy balance for the wall:  
[Diagram]  
Another rectangular diagram is drawn, similar to the first one, with arrows indicating heat transfer \( \dot{Q}_K \).  

\( Q_e = m \) times \( s_2 \) minus \( s_A \), which equals \( \frac{\dot{Q}_K}{T_i} - \frac{\dot{Q}_K}{T_{ii}} \).  

\( \dot{Q}_K = m \) times \( s_2 \) minus \( s_A \), times \( -T_{ii} + T_{ai} \).  

\( \dot{m}_R = -\frac{\dot{Q}_K}{h_1 - h_2} \).

Two diagrams are drawn, both labeled with "a) p [bar]".  

1. **First Diagram**:  
   - The y-axis is labeled as "p [bar]" (pressure).  
   - The x-axis is labeled as "T [K]" (temperature).  
   - A curve is drawn resembling a phase diagram.  
   - The left region is labeled "unterk체hlte Fl체ssigkeit" (subcooled liquid).  
   - The middle region under the curve is labeled "Nassdampf" (wet steam).  
   - The right region is labeled "체berhitzter Dampf" (superheated steam).  
   - Two points are marked on the curve:  
     - Point "2" is on the left side of the curve.  
     - Point "1" is on the right side of the curve.  

2. **Second Diagram**:  
   - The y-axis is labeled as "p [bar]" (pressure).  
   - The x-axis is labeled as "T [째C]" (temperature).  
   - A curve is drawn resembling a phase diagram.  
   - Two points are marked on the curve:  
     - Point "2" is on the left side of the curve.  
     - Point "1" is on the right side of the curve.  
   - The labels "T_i - 6 K" and "T_i" are written along the x-axis.