The page contains multiple T-s diagrams with labeled isobars and processes:  
- The first diagram shows a curve labeled with states 1, 5, and 6. The isobar at 0.5 bar is marked, and the isobar at \( p_0 \) is also labeled.  
- The second diagram includes states 1, 5, and 6, with an isobar labeled \( p_0 = 0.191 \, \text{bar} \). The process is described as "isotropen Wirkungsgrad" (isentropic efficiency).  
- The axes are labeled \( T \) (temperature in Kelvin) and \( S \) (entropy in \( \text{kJ/kg·K} \)).

The diagram is a temperature-entropy (T-s) graph with the following labeled points and processes:  

- The y-axis is labeled as "T [°C]" (temperature).  
- The x-axis is labeled as "S [kJ/kg·K]" (entropy).  

Processes and points:  
1. Point "0" is at the bottom left, labeled with "p0" and "isobar".  
2. Point "1" is labeled with "p5" and "isobar". The process leading to point "1" is labeled "Kompression" (compression).  
3. Point "2" is labeled with "p1/p3" and "isentrop adiabatic" (isentropic adiabatic).  
4. Point "3" is labeled with "isobar".  
5. Between points "4/5" and "6", the process is labeled "adiabat, reversibel" (adiabatic, reversible).  
6. The process between points "3" and "4/5" is labeled "isobar, Mischung" (isobaric mixing).  
7. The process between points "0" and "1" is labeled "isobar".  

Additional annotations:  
- The curve connecting points "3" and "4/5" is labeled "irreversibel adiabatic" (irreversible adiabatic).  
- The curve connecting points "4/5" and "6" is labeled "adiabat, reversibel" (adiabatic, reversible).