TASK 2c  
The following calculations determine the mass-specific increase in flow exergy \( \Delta ex_{\text{flow}} \):

Given values:  
\( T_6 = 328.1 \, \text{K} \), \( T_0 = 243.15 \, \text{K} \)  
\( w_6 = 507.2 \, \frac{\text{m}}{\text{s}} \), \( w_0 = 200 \, \frac{\text{m}}{\text{s}} \)  
\( c_p = 1.006 \, \frac{\text{kJ}}{\text{kg·K}} \)

The formula for \( \Delta ex_{\text{flow}} \) is:  
\[
\Delta ex_{\text{flow}} = h_6 - h_0 - T_0 (s_6 - s_0) + \frac{w_6^2}{2} - \frac{w_0^2}{2}
\]

Breaking it down:  
\[
\Delta ex_{\text{flow}} = h_6 - h_0 - T_0 \left( s_6 - s_0 \right) + \frac{w_6^2}{2} - \frac{w_0^2}{2}
\]  
\[
= c_p (T_6 - T_0) - T_0 \left( c_p \ln \frac{T_6}{T_0} \right) + \frac{w_6^2 - w_0^2}{2}
\]  
\[
= c_p (T_6 - T_0) - T_0 \left( c_p \ln \frac{T_6}{T_0} \right) + \frac{w_6^2 - w_0^2}{2}
\]

Substituting values:  
\[
= 12.165 \, \frac{\text{kJ}}{\text{kg}} + 102625.8 \, \frac{\text{m}^2}{\text{s}^2} \cdot \frac{1}{2}
\]  
\[
= 12.165 \, \frac{\text{kJ}}{\text{kg}} + 108.63 \, \frac{\text{kJ}}{\text{kg}}
\]  
\[
= 120.8 \, \frac{\text{kJ}}{\text{kg}}
\]

---

TASK 2a  
The diagram below is a qualitative representation of the jet engine process in a \( T \)-\( s \) diagram.  

Description of the diagram:  
- The vertical axis represents temperature \( T \) in Kelvin, ranging from \( 243.15 \, \text{K} \) to \( 431.9 \, \text{K} \).  
- The horizontal axis represents entropy \( s \) in \( \frac{\text{kJ}}{\text{kg·K}} \).  
- The process is labeled with states 1 through 6, showing the progression of the jet engine cycle.  
- Curves labeled "Isobars" represent constant pressure lines, including \( 1.5 \, \text{bar} \) and \( 0.5 \, \text{bar} \).  
- Arrows indicate the direction of the process, with transitions between states labeled as "isentropic" or "isobaric."  
- The diagram includes annotations for key transitions, such as compression, combustion, and expansion.  

Key features:  
- State 1 to 2: Compression (isentropic).  
- State 2 to 3: Combustion (isobaric).  
- State 3 to 4: Expansion (isentropic).  
- State 5 to 6: Mixing and nozzle exit.  

The diagram visually illustrates the thermodynamic behavior of the jet engine cycle.