TASK 2a  
The page contains information related to Task 2, which involves a jet engine operating under specific conditions. Constants and parameters are noted:  
- \( \kappa = 1.4 \)  
- \( c_p = 1.006 \, \text{kJ/kg·K} \)  

A table is partially filled with values for pressure (\( p \)), temperature (\( \bar{T} \)), and velocity (\( w \)):  
\[
\begin{array}{|c|c|c|c|}
\hline
\text{State} & p & \bar{T} & w \\
\hline
0 & 0.191 \, \text{bar} & 293.15 \, \text{K} & - \\
\hline
5 & 0.5 \, \text{bar} & 431.9 \, \text{K} & 220 \, \text{m/s} \\
\hline
\end{array}
\]

Two diagrams are drawn below the table:  

1. **Diagram 1 (T-s diagram)**:  
   - The axes are labeled as \( T \, (\text{K}) \) for temperature and \( s \, (\text{kJ/kg·K}) \) for entropy.  
   - The diagram shows several curved lines representing isobars.  
   - States 0, 1, 2, 3, 4, 5, and 6 are marked along the curves, with arrows indicating the process flow.  
   - The path includes compression, combustion, and expansion processes.  
   - The isobaric lines are clearly labeled, and transitions between states are shown with arrows.  

2. **Diagram 2 (T-s diagram)**:  
   - Similar axes are used (\( T \, (\text{K}) \) and \( s \, (\text{kJ/kg·K}) \)).  
   - The diagram focuses on states 0, 1, 5, and 6, with arrows indicating the transitions.  
   - Isobaric lines are labeled, and the processes are shown with directional arrows.  

Both diagrams visually represent the thermodynamic processes occurring within the jet engine, including compression, combustion, and expansion.  

No additional textual explanation is provided beyond the constants, table, and diagrams.