TASK 2a  
The diagram is a qualitative representation of the jet engine process in a \( T \)-\( s \) diagram. The temperature \( T \) is plotted on the vertical axis, and the specific entropy \( s \) is plotted on the horizontal axis. The diagram includes labeled isobars and process states:  
- State 0 represents the ambient conditions.  
- State 1 shows the inlet conditions.  
- State 2 represents the compression process.  
- State 3 corresponds to the combustion process.  
- State 4 represents the turbine process.  
- State 5 shows the mixing chamber conditions.  
- State 6 represents the nozzle exit conditions.  

The isobars are labeled as:  
- \( p_5 = 0.5 \, \text{bar} \)  
- \( p_0 = 0.797 \, \text{km} \)  

TASK 2b  
The ambient temperature is given as \( T_0 = -30^\circ\text{C} = 243.15 \, \text{K} \).  

The following equations and calculations are provided:  
1. The ideal gas law is used to determine the specific volume at ambient conditions:  
   \[
   p_0 V_0 = R T_0 \quad \Rightarrow \quad V_0 = \frac{R T_0}{p_0}
   \]  

2. The specific gas constant \( R \) is calculated using the relation:  
   \[
   R = c_p - c_v = c_p \cdot \frac{c_v}{c_p} - c_p \quad \Rightarrow \quad R = 0.287429 \, \text{kJ/kg·K}
   \]  

3. The specific volume \( V_0 \) is calculated as:  
   \[
   V_0 = 3.65908 \, \text{m}^3/\text{kg}
   \]  

4. The temperature ratio \( \frac{T_6}{T_0} \) is derived using the polytropic relation:  
   \[
   \frac{T_6}{T_0} = \left( \frac{V_0}{V_6} \right)^{k-1} \quad \Rightarrow \quad T_6 = T_0 \cdot \left( \frac{R T_6}{p_6 V_0} \right)^{k-1}
   \]  

5. The final expression for \( T_6 \) is given as:  
   \[
   T_6 = \frac{R}{p_6 V_0} \cdot T_0^{k-1}
   \]  

Several intermediate steps and crossed-out calculations are visible but not transcribed as per instructions.