TASK 2a  
The page begins with a labeled \( T \)-\( s \) diagram for the jet engine process. The diagram includes the following features:  
- Axes: \( T \) (temperature) on the vertical axis and \( s \) (specific entropy) on the horizontal axis, with units \( \text{kJ/kg·K} \).  
- Points labeled \( 1 \), \( 2 \), \( 3 \), \( 5 \), and \( 6 \) corresponding to different states in the jet engine process.  
- The process includes isobaric and adiabatic transformations:  
  - Between \( 1 \) and \( 2 \): Isobaric heating.  
  - Between \( 2 \) and \( 3 \): Adiabatic compression.  
  - Between \( 3 \) and \( 5 \): Isobaric combustion.  
  - Between \( 5 \) and \( 6 \): Adiabatic expansion.  
- The bypass stream is labeled \( \dot{m}_M \), and the ambient pressure is noted as \( p_0 = p_6 \).  

TASK 2b  
The task involves determining \( w_6 \) (outlet velocity) and \( T_6 \) (outlet temperature).  

The following calculations are shown:  
1. The adiabatic relation for temperature:  
   \[
   T_6 = T_5 \left( \frac{p_0}{p_5} \right)^{\frac{\kappa - 1}{\kappa}}
   \]  
   Substituting values:  
   \[
   T_6 = 431.9 \, \text{K} \cdot \left( \frac{0.191}{0.5} \right)^{\frac{0.4}{1.4}} = 328.075 \, \text{K}
   \]  
   The result is boxed: \( T_6 = 328.075 \, \text{K} \).  

2. To determine \( w_6 \), the energy balance equation is used:  
   \[
   0 = h_{\text{in}} - h_{\text{aus}} + \frac{w_{\text{in}}^2 - w_{\text{aus}}^2}{2} + \dot{Q}_B \cdot \frac{1}{\dot{m}_K}
   \]  
   The term \( \dot{Q}_B \cdot \frac{1}{\dot{m}_K} \) is crossed out.  

3. Enthalpy difference is calculated using:  
   \[
   h_{\text{in}} - h_{\text{aus}} = c_p \cdot (T_{\text{ein}} - T_{\text{aus}})
   \]  
   Substituting values:  
   \[
   2 \cdot \left( c_p \cdot (T_{\text{aus}} - T_{\text{ein}}) - \frac{Q_B}{5.293} \right) = 200^2 - w_6^2
   \]  
   Rearranging and solving:  
   \[
   280.68 \, \text{kJ} = 200^2 - w_6^2
   \]  

No final value for \( w_6 \) is explicitly calculated on the page.  

TASK 2a and 2b are completed.