TASK 4a  
A graph is drawn representing the freeze-drying process in a pressure-temperature (\(p\)-\(T\)) diagram. The diagram includes labeled phase regions for liquid, gas, and solid. The curve transitions between these phases, with points labeled as 1, 2, and 3. The temperature axis includes a mark at \(T_i = -10^\circ\text{C}\).

---

TASK 4b  
The energy balance equation for the system is written as:  
\[
Q = \dot{m} \left( h_e - h_g \right) + \dot{W}_K
\]  
where \( \dot{W}_K \) is the work done by the compressor, and \( h_e \) and \( h_g \) are enthalpies at different states. The equation is annotated with "adiabat" to indicate an adiabatic process.

The mass flow rate \( \dot{m} \) is calculated using:  
\[
\dot{m} = \frac{\dot{W}_K}{h_2 - h_g}
\]  

From the tables:  
- \( h_e \): The enthalpy at state 1 with \( x_1 = 1 \), \( T_i = -10^\circ\text{C} \).  
- \( h_2 \): The enthalpy at state 2, calculated as:  
\[
h_2 = 242.54 \, \text{kJ/kg} + 250.02 \, \text{kJ/kg} \cdot x_2
\]  
where \( x_2 \) is the vapor quality. This results in:  
\[
h_2 = 247.345 \, \text{kJ/kg}
\]  

At state 3, the pressure is 8 bar with the same enthalpy as state 2. Using the tables:  
\[
s_2 = s_3 = 0.5233 + 0.5267 = 0.5233 \, \text{kJ/kg·K}
\]  

From Table A-12:  
- \( s_3 = 0.5233 \, \text{kJ/kg·K} \)  
- \( T_{sat} = 37.33^\circ\text{C} \), \( T_4 = 0.3733 \, \text{kJ/kg·K} \).  

At state 3:  
\[
h_3 = 223.66 \, \text{kJ/kg} + 0.5233 \cdot \left( \frac{\text{kJ}}{\text{kg·K}} \right) - 0.3373 \cdot \left( \frac{\text{kJ}}{\text{kg·K}} \right)
\]  
This results in:  
\[
h_3 = 265.524 \, \text{kJ/kg}
\]  

The mass flow rate \( \dot{m} \) is calculated as:  
\[
\dot{m} = \frac{9.378 \, \text{kW}}{265.524 - 206.66 \, \text{kJ/kg}}
\]  

The final result is annotated with corrections and adjustments for enthalpy values.

---

TASK 4c  
No explicit content for this subtask is visible on the page.  

---

TASK 4d  
No explicit content for this subtask is visible on the page.  

---

TASK 4e  
No explicit content for this subtask is visible on the page.  