TASK 2a  
A graph is drawn representing a T-s diagram (temperature-entropy diagram). The diagram includes labeled isobars \( p_2 \), \( p_3 \), \( p_4 \), \( p_5 \), and \( p_6 \). The states are numbered from 1 to 6, with arrows indicating the process flow. The graph shows the qualitative behavior of the thermodynamic process, including compression, heat addition, expansion, and mixing. The axis labels are:  
- \( T \) (temperature) on the vertical axis.  
- \( s \) (entropy) on the horizontal axis.  

The isobars are curved lines, and the transitions between states are marked with arrows. The process appears to include adiabatic compression, isobaric heat addition, and adiabatic expansion.  

TASK 2b  
The outlet velocity \( w_5 \) is given as:  
\[
w_5 = 220 \, \text{m/s}
\]  
The outlet pressure \( p_5 \) is:  
\[
p_5 = 0.5 \, \text{bar}
\]  
The outlet temperature \( T_5 \) is:  
\[
T_5 = 431.9 \, \text{K}
\]  

Using the adiabatic relation for temperature:  
\[
T_G = T_5 \cdot \left( \frac{p_6}{p_5} \right)^{\frac{\kappa - 1}{\kappa}}
\]  
where \( \kappa = 1.4 \). Substituting the values:  
\[
T_G = 431.9 \cdot \left( \frac{0.191}{0.5} \right)^{\frac{1.4 - 1}{1.4}}
\]  
The calculated temperature is:  
\[
T_G = 328.075 \, \text{K}
\]  

TASK 2c  
The energy balance equation is written as:  
\[
\dot{m} \cdot \left( h_a - h_e + \frac{w_e^2 - w_a^2}{2} \right) + q^2 + w
\]  
where \( h_a \) and \( h_e \) are enthalpies, \( w_a \) and \( w_e \) are velocities, \( q^2 \) represents heat transfer, and \( w \) represents work.  

The entropy production equation is expressed as:  
\[
\dot{m} \cdot w^2 = \frac{1}{2} \cdot v \cdot dp + dq + q^2
\]  

Some terms are crossed out, indicating corrections or adjustments to the equations.  

No further explanation or final results are provided for this part.