TASK 3a  
The system consists of a perfect gas in the lower chamber with \( c_V = 0.633 \, \text{kJ/kg·K} \) and \( M_g = 50 \, \text{kg/kmol} \). The upper chamber contains a phase equilibrium of ice and water (EW). The volume \( V \) remains constant. The piston has a mass \( m_K = 32 \, \text{kg} \), atmospheric pressure \( p_{\text{amb}} = 1 \, \text{bar} \), and a cylinder diameter \( D = 10 \, \text{cm} \).  

The initial state is labeled as state 1.  

To determine the gas pressure \( p_{g,1} \) in state 1:  
The equilibrium condition is given as:  
\[
p_{g,1} = p_{\text{amb}} + \frac{m_K \cdot g}{A}
\]  
where \( A = \pi \cdot \left(\frac{D}{2}\right)^2 \).  

Substituting values:  
\[
A = \pi \cdot \left(\frac{0.1}{2}\right)^2 = 7.854 \cdot 10^{-3} \, \text{m}^2
\]  
\[
p_{g,1} = 1 \, \text{bar} + \frac{32 \, \text{kg} \cdot 9.81 \, \text{m/s}^2}{7.854 \cdot 10^{-3} \, \text{m}^2}
\]  
\[
p_{g,1} = 1 \, \text{bar} + 4 \, \text{bar}
\]  
\[
p_{g,1} = 1 + 4 = 5 \, \text{bar}
\]  

To calculate the gas mass \( m_g \):  
Using the ideal gas law:  
\[
p \cdot V = m_g \cdot R \cdot T
\]  
Rearranging:  
\[
m_g = \frac{p \cdot V}{R \cdot T}
\]  
Substituting values:  
\[
R = \frac{8.314}{M_g} = \frac{8.314}{50} = 0.16628 \, \text{kJ/kg·K}
\]  
\[
m_g = \frac{5 \cdot 3.14}{0.16628 \cdot 773.15}
\]  
\[
m_g = \frac{15.7}{128.57} = 0.122 \, \text{kg}
\]  

TASK 3b  
The ice mass fraction \( x_{\text{ice},2} > 0 \) in state 2.  

The temperature \( T_{g,2} \) and pressure \( p_{g,2} \) are determined as follows:  
The gas pressure remains constant because the EW chamber is incompressible, and thus only the piston and atmospheric pressure determine \( p_{g,2} \).  
The temperature \( T_{g,2} \) adjusts to thermal equilibrium with the EW chamber.  

TASK 3c  
To calculate the transferred heat \( Q_{12} \):  
Using the energy balance:  
\[
\Delta E_{\text{tot}} = \sum Q - \sum W
\]  
\[
\Delta U = Q_{12} - W_{\text{ext}}
\]  
where \( W_{\text{ext}} = p_{\text{ext}} \cdot (V_2 - V_1) \).  

The heat transfer is given as:  
\[
Q_{12} = \Delta U + W_{\text{ext}}
\]  
Substituting values:  
\[
V_2 = \frac{m_{EW} \cdot T}{p_2} = 1.1 \, \text{L}
\]  
\[
p_{g,2} = 1.4 \, \text{bar}
\]  

TASK 3d  
No explicit calculation is provided for the final ice fraction \( x_{\text{ice},2} \), but it is determined using the solid-liquid equilibrium table.  

**Figure Description:**  
The diagram shows a cylinder divided into two chambers. The lower chamber contains the gas, while the upper chamber contains the ice-water mixture. A piston rests on top of the ice-water mixture, exerting pressure downward. The atmospheric pressure and the piston weight contribute to the total pressure on the gas.