TASK 2a  
The page contains two diagrams illustrating the thermodynamic process in a jet engine on a temperature-entropy (\(T\)-\(S\)) diagram.  

### Diagram Description:  
1. **Top Diagram**:  
   - The axes are labeled as \(T\) (temperature) on the vertical axis and \(S\) (entropy) on the horizontal axis.  
   - Several curves are drawn, representing isobars and adiabatic processes.  
   - Points labeled \(0\), \(1\), \(2\), \(3\), \(5\), and \(6\) correspond to different states in the jet engine process.  
   - The process transitions are annotated:  
     - From \(0\) to \(1\): Adiabatic, reversible, isentropic.  
     - From \(1\) to \(2\): Adiabatic.  
     - From \(2\) to \(3\): Isobaric.  
     - From \(3\) to \(5\): Isobaric.  
     - From \(5\) to \(6\): Adiabatic, reversible, isentropic.  
   - Pressure values are indicated for specific states:  
     - \(p_0 = 0.191 \, \text{bar}\)  
     - \(p_5 = 0.5 \, \text{bar}\)  

2. **Bottom Diagram**:  
   - Similar to the top diagram, the axes are labeled as \(T\) (temperature) and \(S\) (entropy).  
   - The same states (\(0\), \(1\), \(2\), \(3\), \(5\), \(6\)) are marked, with transitions between them annotated similarly.  
   - Additional details include:  
     - \(T_5 = 431.9 \, \text{K}\) marked near state \(5\).  
     - \(T_0 = 293.15 \, \text{K}\) noted near the origin.  
   - The process annotations match the top diagram, with the same pressure values and transitions described.  

Both diagrams qualitatively represent the thermodynamic processes in the jet engine, including adiabatic and isobaric transitions, as well as entropy changes between states.  

No additional textual content is visible on the page.