TASK 2a  
The diagram shows a qualitative representation of the jet engine process in a \( T \)-\( s \) diagram. The axes are labeled as follows:  
- \( T \) [K] on the vertical axis (temperature).  
- \( s \) [kJ/kg·K] on the horizontal axis (specific entropy).  

The diagram includes the following features:  
- Isobar \( p_0 \) (ambient pressure) and isobar \( p_5 \) (pressure after mixing chamber).  
- The process path is marked with numbered states: \( 1 \), \( 2 \), \( 3 \), \( 4 \), \( 5 \), and \( 6 \).  
- The transitions between states are shown with arrows, indicating compression, combustion, and expansion processes.  
- The entropy increases during the combustion process, while the compression and expansion processes are nearly vertical, representing adiabatic changes.  

TASK 2b  
The temperature \( T_6 \) is calculated using the polytropic temperature relation:  
\[
T_6 = T_5 \left( \frac{p_2}{p_5} \right)^{\frac{\kappa - 1}{\kappa}}
\]  
Where:  
- \( \kappa = 1.4 \) (isentropic exponent).  
- \( p_0 = 0.191 \, \text{bar} \), \( p_5 = 0.5 \, \text{bar} \).  
- \( T_5 = 431.9 \, \text{K} \).  

Substituting values:  
\[
T_6 = 431.9 \, \text{K} \cdot \left( \frac{0.191}{0.5} \right)^{\frac{0.4}{1.4}} = 328.075 \, \text{K}
\]  

TASK 2c  
The mass-specific increase in flow exergy \( \Delta ex_{\text{flow}} \) is calculated using the following relation:  
\[
\Delta ex_{\text{flow}} = \dot{m} \left[ h_6 - h_0 - T_0 (s_6 - s_0) + \frac{w_6^2}{2} - \frac{w_0^2}{2} \right]
\]  
Where:  
- \( h_6 - h_0 \) is the enthalpy difference.  
- \( T_0 \) is the ambient temperature.  
- \( s_6 - s_0 \) is the entropy difference.  
- \( w_6 \) and \( w_0 \) are the velocities at states 6 and 0, respectively.  

The entropy difference \( s_6 - s_0 \) is calculated as:  
\[
s_6 - s_0 = c_p \ln \frac{T_6}{T_0} - R \ln \frac{p_6}{p_0}
\]  
Substituting values:  
\[
s_6 - s_0 = 1.006 \ln \frac{328.075}{243.15} - 0.287 \ln \frac{0.5}{0.191}
\]  
\[
s_6 - s_0 = 1.006 \cdot 0.301 - 0.287 \cdot 0.916 = 0.303 \, \text{kJ/kg·K}
\]  

The entropy change \( \Delta S \) is calculated as:  
\[
\Delta S = T_0 \cdot s_6 - s_0 = 243.15 \cdot 0.301 = 73.22 \, \text{kJ/kg}
\]  

TASK 2d  
The coefficient \( R \) is calculated using the relation:  
\[
R = c_p - c_v
\]  
Where:  
- \( c_p = 1.006 \, \text{kJ/kg·K} \).  
- \( c_v = 0.718 \, \text{kJ/kg·K} \).  

Substituting values:  
\[
R = 1.006 - 0.718 = 0.287 \, \text{kJ/kg·K}
\]