TASK 2a  
The diagram represents a qualitative \( T \)-\( s \) diagram for the jet engine process. It includes labeled isobars and key states:  
- State 0 represents the ambient condition.  
- State 1 is the inlet to the compressor.  
- State 2 is the outlet of the compressor.  
- State 3 is the combustion chamber outlet.  
- State 4 is the turbine outlet.  
- State 5 is the mixing chamber outlet.  
- State 6 is the nozzle exit.  

The process transitions are marked as follows:  
- The compression from state 0 to state 2 is labeled as "isentropic."  
- The combustion process from state 2 to state 3 is labeled as "isobaric \( p = 0.191 \, \text{bar} \)."  
- The expansion from state 3 to state 5 is labeled as "adiabatic reversible."  

The axes are labeled:  
- The vertical axis is \( T \) (temperature).  
- The horizontal axis is \( s \) (specific entropy), with units \( \frac{\text{kJ}}{\text{kg·K}} \).  

---

TASK 2b  
The energy balance for the entire jet engine is written as:  
\[
\dot{S}_{\text{FP}} = 0  
\]  
\[
\frac{dE}{dt} = \sum (\dot{m} h + \dot{m} \frac{w^2}{2}) + \dot{Q} - \sum (\dot{m} h + \dot{m} \frac{w^2}{2}) - \dot{W} = 0  
\]  

Simplifying for steady-state operation:  
\[
\dot{m} \left( h_0 + \frac{w_0^2}{2} \right) = \dot{m} \left( h_6 + \frac{w_6^2}{2} \right) + \dot{Q}  
\]  

Rearranging:  
\[
h_0 - h_6 + \frac{w_0^2}{2} - \frac{w_6^2}{2} + \dot{q} = 0  
\]  

The outlet velocity \( w_6 \) is calculated as:  
\[
w_6 = \sqrt{2 c_p (T_0 - T_6) + \frac{w_0^2}{2} + \dot{q}}  
\]  
Substituting values:  
\[
w_6 = 1503 \, \text{m/s}  
\]  

Additional notes:  
- The process from state 5 to state 6 is labeled as "adiabatic reversible," meaning it is isentropic (\( \eta = \kappa \)).  
- The temperature ratio is calculated as:  
\[
\frac{T_c}{T_s} = \left( \frac{p_6}{p_5} \right)^{\frac{\kappa - 1}{\kappa}}  
\]  

Given values:  
\[
T_0 = 328.14 \, \text{K}, \quad T_6 = 50.55^\circ \text{C}  
\]  

---

TASK 2c  
The mass-specific increase in flow exergy is calculated as:  
\[
\Delta ex_{\text{flow}} = \dot{m} \left( h_6 - h_0 - T_0 (s_6 - s_0) + \frac{w_6^2}{2} - \frac{w_0^2}{2} \right)  
\]  

Substituting values:  
\[
\Delta ex_{\text{flow}} = \dot{m} \left( h_6 - h_0 - T_0 (s_6 - s_0) + \frac{w_6^2}{2} - \frac{w_0^2}{2} \right)  
\]  

Entropy difference is expressed as:  
\[
s_6 - s_0 = c_p \ln \left( \frac{T_6}{T_0} \right) - R \ln \left( \frac{p_6}{p_0} \right)  
\]  

Substituting into the exergy destruction formula:  
\[
\Delta ex_{\text{dest}} = c_p (T_0 - T_6) - T_0 c_p \ln \left( \frac{T_0}{T_6} \right) + \frac{w_6^2}{2} - R \ln \left( \frac{p_6}{p_0} \right)  
\]  

Final result:  
\[
\Delta ex_{\text{dest}} = 122.2 \, \frac{\text{kJ}}{\text{kg}}  
\]  

Note: The calculation assumes \( T_0 = 328.14 \, \text{K} \) and \( T_6 = 50.55^\circ \text{C} \).