TASK 2a  
The table at the top of the page lists values for pressure \( p \) (in bar), temperature \( T \) (in \( ^\circ \text{C} \)), and specific entropy \( s \) (in \( \text{kJ/kg·K} \)) for an ideal gas (air). The table includes the following entries:  
\[
\begin{array}{|c|c|c|}
\hline
p (\text{bar}) & T (^\circ \text{C}) & s (\text{kJ/kg·K}) \\
\hline
0 & -30 & \\
1 & & \\
2 & & \\
3 & & \\
4 & & \\
5 & & \\
6 & & 328.07 \\
\hline
\end{array}
\]

Below the table, the following notes are written:  
- \( \Delta Q = 0 \), isentropic process (\( \eta < 1 \)) for compression.  
- Isentropic process = additional reversible process.  
- Adiabatic process.  
- Isobaric process (\( p_4 = p_5 \)).  
- Isentropic process = reversible adiabatic process.  

---

TASK 2b  
The process is described as isentropic because it is reversible and \( \Delta Q = 0 \). The temperature \( T_6 \) is calculated using the following formula:  
\[
T_6 = T_s \left( \frac{p_6}{p_s} \right)^{\frac{n-1}{n}}
\]
where \( n = k = \frac{c_p}{c_v} = 1.4 \).  

The calculation yields:  
\[
T_6 = 328.07 \, \text{K}
\]

Additional notes:  
- Energy balance is applied to a stationary system with one mass flow.  
- \( p_e = 0 \).  
- The energy balance equation is:  
\[
0 = \dot{m}_{\text{gas}} \left( h_5 - h_e + \frac{w_5^2 - w_e^2}{2} \right) + \dot{Q}_{\text{ext}} - \dot{W}_{\text{ext}}
\]
where \( \dot{Q}_{\text{ext}} \) and \( \dot{W}_{\text{ext}} \) are external heat and work terms.  

It is noted that \( w_e = w_{\text{ext}} = w_{\text{gas}} \).

---

TASK 2a (continued)  
A qualitative \( T \)-\( s \) diagram is drawn to represent the process. The diagram includes labeled isobars and isentropes, with points 0, 1, 2, 3, 4, 5, and 6 marked along the curves. The isentropic lines are vertical, while the isobaric lines curve upward.  

Key features of the diagram:  
- The isentropic lines are labeled as "isentrop."  
- The isobaric lines are labeled as "isobar."  
- Points \( p_{2,3} \), \( p_1 \), and \( p_{0,6} \) are marked along the curves.  
- The axes are labeled as \( T [K] \) (temperature) and \( s [\text{kJ/kg·K}] \) (specific entropy).  

This diagram visually represents the thermodynamic processes occurring in the jet engine.