TASK 2a  
The task involves drawing the jet engine process qualitatively in a \( T \)-\( s \) diagram with labeled isobars and units on the axes.  

### Diagram Description:  
The \( T \)-\( s \) diagram is drawn with the temperature \( T \) (in Kelvin) on the vertical axis and entropy \( s \) (in \( \text{kJ/kg·K} \)) on the horizontal axis. The process is divided into six states, labeled 0 through 6, with transitions between states described as follows:  
1. From state 0 to state 1: Adiabatic compression (isentropic).  
2. From state 1 to state 2: Isobaric heat addition.  
3. From state 2 to state 3: Adiabatic compression (isentropic).  
4. From state 3 to state 4: Isobaric heat addition (irreversible).  
5. From state 4 to state 5: Isobaric mixing.  
6. From state 5 to state 6: Adiabatic expansion (isentropic).  

The diagram includes labeled isobars for pressures \( p_0 = 0.191 \, \text{bar} \), \( p_5 = 0.5 \, \text{bar} \), and \( p_6 = p_0 \).  

### Table of States:  
A table is provided summarizing the pressure \( p \), temperature \( T \), and key notes for each state:  
- **State 0**: \( p_0 = 0.191 \, \text{bar} \), \( T_0 = 243.15 \, \text{K} \).  
- **State 1**: Adiabatic compression, \( \eta < 1 \).  
- **State 2**: Isobaric heat addition, \( T_s = 1289 \, \text{K} \).  
- **State 3**: Adiabatic compression (isentropic).  
- **State 4**: Isobaric heat addition (irreversible).  
- **State 5**: \( p_5 = 0.5 \, \text{bar} \), \( T_5 = 431.9 \, \text{K} \).  
- **State 6**: \( p_6 = p_0 \), adiabatic expansion (isentropic).  

Key notes are written alongside the table, emphasizing the assumptions:  
- Adiabatic processes are reversible and isentropic.  
- Isobaric processes involve heat addition.  
- Irreversible processes occur during combustion.  

No additional calculations or explanations are visible on the page.