TASK 2a  
The page contains a temperature-entropy (\( T \)-\( S \)) diagram and a table summarizing the states of the jet engine process.  

### Diagram Description:  
The \( T \)-\( S \) diagram illustrates the thermodynamic process of the jet engine. The axes are labeled as follows:  
- The vertical axis represents temperature (\( T \)) in Kelvin (\( \text{K} \)).  
- The horizontal axis represents entropy (\( S \)) in \( \text{kJ/kg·K} \).  

Key features of the diagram:  
- Points labeled \( 0, 1, 2, 3, 4, 5, \) and \( 6 \) correspond to different states in the jet engine process.  
- The process includes isobaric lines and adiabatic transitions.  
- The compression process from \( 0 \) to \( 3 \) is shown as an upward curve.  
- The combustion process occurs between \( 3 \) and \( 4 \), represented as a vertical line.  
- The turbine expansion from \( 4 \) to \( 5 \) is depicted as a downward curve.  
- The mixing and nozzle processes are shown from \( 5 \) to \( 6 \).  
- The pressure at state \( 0 \) is noted as \( 0.191 \, \text{bar} \).  

### Table Description:  
The table summarizes the pressure (\( P \)), temperature (\( T \)), velocity (\( w \)), and other relevant parameters for each state:  

| \( P \)         | \( T \)                  | \( w \)         | Notes                                                                 |
|------------------|--------------------------|-----------------|----------------------------------------------------------------------|
| \( 0.191 \, \text{bar} \) | \( T = 243.15 \, \text{K} \) (\( -30^\circ\text{C} \)) | \( 200 \, \text{m/s} \) | \( Q_{\text{0A}} = 0 \)                                               |
|                  |                          |                 | \( \dot{m}_R = \frac{\dot{m}_M}{\dot{m}_K} = 5.293 \)                 |
|                  |                          |                 | \( q_B = 1195 \, \text{kJ/kg} \)                                      |
| \( p_2 \)       |                          |                 |                                                                      |
| \( p_3 \)       |                          |                 |                                                                      |
| \( 0.5 \, \text{bar} \) | \( T = 431.9 \, \text{K} \)          | \( 220 \, \text{m/s} \) |                                                                      |
| \( 0.191 \, \text{bar} \) |                          |                 | \( \Delta S = 0 \)                                                   |  

The table provides key thermodynamic properties for each state in the jet engine process, including the pressure, temperature, and velocity. Additional notes include the heat transfer (\( Q_{\text{0A}} \)), mass flow rate ratio (\( \dot{m}_R \)), and specific heat input (\( q_B \)).  

No further explanatory text or calculations are visible.