TASK 4a  
The page contains two diagrams related to the freeze-drying process described in Task 4.  

1. **First Diagram**:  
   - The graph is labeled as a pressure-temperature (\(p\)-\(T\)) diagram.  
   - The axes are marked with \(p\) (pressure) on the vertical axis and \(T\) (temperature in Kelvin) on the horizontal axis.  
   - Four states are labeled: \(1\), \(2\), \(3\), and \(4\).  
   - The process between states \(1\) and \(2\) is marked as "sotrop" (likely indicating an isentropic process).  
   - The curve transitions between states, with arrows indicating the direction of the process.  

2. **Second Diagram**:  
   - The graph is labeled as a pressure-enthalpy (\(p\)-\(h\)) diagram.  
   - The axes are marked with \(p\) (pressure) on the vertical axis and \(h\) (enthalpy) on the horizontal axis.  
   - Four states are labeled: \(1\), \(2\), \(3\), and \(4\).  
   - The process transitions between states, with curved arrows indicating the direction of the process.  

TASK 4b  
Below the diagrams, a table is provided with columns labeled:  
- \(p\) (pressure),  
- \(T\) (temperature),  
- \(h\) (enthalpy),  
- \(\dot{Q}/\dot{W}\) (heat or work flow),  
- \(x\) (vapor quality),  
- Notes.  

The rows correspond to states \(1\), \(2\), \(3\), and \(4\):  
- **State 1**:  
  - \(\dot{Q}_K\) is listed under \(\dot{Q}/\dot{W}\).  

- **State 2**:  
  - \(W_K = 28 \, \text{W}\) is listed under \(\dot{Q}/\dot{W}\).  
  - Vapor quality \(x = 1\).  
  - Notes mention "adiabatic reversible."  

- **State 3**:  
  - Pressure \(p = 8 \, \text{bar}\).  

- **State 4**:  
  - Pressure \(p = 8 \, \text{bar}\).  
  - Vapor quality \(x = 0\).  

No additional numerical values or explanations are provided.