TASK 4a  
A diagram is drawn showing a temperature (\( T \)) versus entropy (\( S \)) graph. The graph includes phase regions labeled as "solid," "vapor," and "vapor-gas mixture." The curve represents the phase boundaries, with points \( z_1 \), \( z_2 \), \( z_3 \), and \( z_4 \) marked. The region between \( z_2 \) and \( z_3 \) is labeled "mass dampf gebiet" (mass vapor region). The axes are labeled as follows:  
- \( T \) (temperature) on the vertical axis in Kelvin (\( K \)).  
- \( S \) (entropy) on the horizontal axis in \( \frac{\text{kJ}}{\text{kg·K}} \).  

TASK 4b  
The energy balance equation is written as:  
\[
0 = \dot{m}_{\text{R134a}} \left[ h_2 - h_4 \right] + \dot{Q} - \dot{W}
\]  
The mass flow rate of the refrigerant is expressed as:  
\[
\dot{m}_{\text{R134a}} = \frac{-\dot{W}_K}{h_2 - h_3}
\]  
The enthalpy \( h_2 \) is determined using Table A-10 and linear interpolation (LERP):  
\[
h_2 = 243.72 \, \frac{\text{kJ}}{\text{kg}}
\]  
The interpolation formula is given as:  
\[
h_2 = y_2 - y_1 \cdot \frac{x - x_1}{x_2 - x_1} + y_1
\]  
Values for interpolation are provided:  
\[
x_2 = -8, \, y_2 = 242.54  
\]  
\[
x_1 = -1, \, y_1 = 249.50  
\]  

Additional notes reference Table A-10 for further calculations and interpolation steps. The text indicates continuation on the next page.  

TASK 4  
A table is provided with thermodynamic properties at different states (\( z_1 \) to \( z_4 \)):  
- \( T \): Temperature in \( ^\circ \text{C} \).  
- \( p \): Pressure in bar.  
- \( V \): Specific volume.  
- \( U \): Internal energy.  
- \( S \): Entropy.  

Values are filled in for some states:  
- \( z_1 \): \( T = 0^\circ \text{C} \), \( p = 1 \).  
- \( z_2 \): \( T = -6^\circ \text{C} \), \( p = 1 \), \( U = 243.72 \), \( S = 0.9226 \).  
- \( z_3 \): \( T = -6^\circ \text{C} \), \( p = 8 \), \( S = S_2 = 0.9226 \).  
- \( z_4 \): \( T = -6^\circ \text{C} \), \( p = 8 \).  

Additional notes state:  
\[
T_i = 0^\circ \text{C} \rightarrow T(z_2) = -6^\circ \text{C}
\]