TASK 2a  
The diagram represents a qualitative \( T \)-\( s \) diagram for the jet engine process. The axes are labeled as follows:  
- The vertical axis represents temperature (\( T \)) in degrees Celsius (\( ^\circ C \)).  
- The horizontal axis represents entropy (\( s \)) in \( \text{kJ}/\text{kg·K} \).  

Key features of the diagram:  
- The process begins at state \( 0 \), marked as "isentrop."  
- State \( 1 \) is connected to state \( 2 \) via an isentropic compression process.  
- State \( 2 \) transitions to state \( 3 \) along an isobaric line.  
- State \( 3 \) transitions to state \( 4 \), also along an isobaric line.  
- State \( 4 \) transitions to state \( 5 \) through an isentropic expansion process.  
- State \( 5 \) transitions to state \( 6 \) along an isobaric line, with \( p_0 \) labeled.  

TASK 2b  
The problem involves determining the outlet velocity (\( w_6 \)) and temperature (\( T_6 \)) for the jet engine system.  

The energy balance for the system is expressed as:  
\[
0 = \dot{m} \left( h_e - h_q + \frac{w_e^2 - w_q^2}{2} \right) + \dot{Q} - \dot{W}
\]  
Simplified:  
\[
0 = h_e - h_q + \frac{w_e^2 - w_q^2}{2}
\]  
Rewritten:  
\[
0 = h_0 - h_6 + \frac{w_0^2}{2} - \frac{w_6^2}{2}
\]  
Solving for \( w_6^2 \):  
\[
w_6^2 = 2 \left( h_0 - h_6 \right) + w_0^2
\]  
Using \( h_0 - h_6 = 2 \cdot c_p \cdot (T_1 - T_6) \):  
\[
w_6^2 = 2 \cdot c_p \cdot (T_1 - T_6) + w_0^2
\]  

The state \( S_6 \) is isentropic, with the following conditions:  
\[
p_5 = 0.5 \, \text{bar}, \quad p_6 = 0.191 \, \text{bar}, \quad T_5 = 431.9 \, \text{K}
\]  

The temperature ratio for isentropic conditions is given by:  
\[
\frac{T_6}{T_5} = \left( \frac{p_c}{p_5} \right)^{\frac{n-1}{n}}
\]  
Where \( n = 1.4 \).  

Substituting values:  
\[
T_6 = T_5 \cdot \left( \frac{p_c}{p_5} \right)^{\frac{n-1}{n}}
\]  
\[
T_6 = 431.9 \, \text{K} \cdot \left( \frac{0.191}{0.5} \right)^{\frac{1.4 - 1}{1.4}}
\]  
\[
T_6 = 431.9 \, \text{K} \cdot 0.414 = 328.07 \, \text{K}
\]  

The outlet velocity (\( w_6 \)) is calculated as:  
\[
w_6 = \sqrt{2 \cdot 1.006 \cdot \left( (-30 + 273.15) \, \text{K} - 328.07 \, \text{K} \right) + 200^2}
\]  
\[
w_6 = 193.5 \, \text{m/s}
\]  

Final results:  
\[
T_6 = 328.07 \, \text{K}, \quad w_6 = 193.5 \, \text{m/s}
\]