TASK 4a  
A graph is drawn representing the freeze-drying process in a pressure-temperature (\(p\)-\(T\)) diagram. The diagram includes labeled phase regions and process steps.  
- The curve labeled "Mass dampfgebiet" (wet steam region) separates the saturated liquid and vapor phases.  
- Four states are marked:  
  - State 1 is at the lower left, near the saturated liquid line.  
  - State 2 is slightly above State 1, along the same pressure line.  
  - State 3 is higher on the diagram, indicating increased pressure.  
  - State 4 is horizontally aligned with State 3, showing isobaric condensation.  
- Heat transfer (\(Q = q\)) is indicated along the process paths.  

TASK 4b  
A table is presented summarizing the thermodynamic properties at four states during the freeze-drying process. The columns are labeled \(P\), \(T\), \(V\), \(\dot{W}\), \(\dot{Q}\), \(\dot{S}\), and \(x\).  

| \(P\) | \(T\) | \(V\) | \(\dot{W}\) | \(\dot{Q}\) | \(\dot{S}\) | \(x\) |  
|------|------|------|------------|------------|------------|------|  
| \(P_1 = P_2\) | \(1.5748 \, \text{bar}\) | - | \(28 \, \omega\) | \(0\) | \(0\) | \(1\) |  
| \(P_2\) | \(-16^\circ \text{C}\) | - | - | \(0\) | \(0\) | \(0\) |  
| \(P_3 = 8 \, \text{bar}\) | - | - | - | \(0\) | \(0\) | \(0\) |  
| \(P_4 = 8 \, \text{bar}\) | - | - | - | \(0\) | \(0\) | \(0\) |  

Additional notes:  
- \(P_1 = P_2\)  
- \(T_2 = T_1 - 6 \, \text{K}\)  
- \(T_i\) is referenced from Figure 5 (\(p = 1 \, \text{bar}\)), with \(T_i = -10^\circ \text{C}\).  
- Sublimation temperature is \(T_2 = -16^\circ \text{C}\).  
- Heat transfer values \(Q_{4} = 0\) and \(Q_{23} = 0\).  
- Entropy generation \(\dot{S}_{23}\) is zero due to adiabatic and reversible conditions.  
- \(P_2\) is calculated using Table A-10:  
  \[
  P_2 = P_{\text{tab}} - 10 \, \text{K} \quad (T = -16^\circ \text{C}) = 1.5748 \, \text{bar} = P_1
  \]