TASK 2a  
A table is presented with columns labeled \( T \) (temperature) and \( p \) (pressure). It includes the following data:  

- Row 0: \( T = 243.15 \, \text{K} \), \( p = 0.191 \, \text{bar} \)  
- Row 1: Isentropic compression, \( \frac{v_1}{v_5} \), and a bypass stream labeled "mix."  
- Row 2: \( q_B = 1195 \, \text{kJ/kg} \), \( \bar{T}_B = 1289 \, \text{K} \).  
- Row 3: \( p = 0.5 \, \text{bar} \), isobaric process.  
- Row 4: \( T = 431.9 \, \text{K} \), \( p = 0.5 \, \text{bar} \), \( w_5 = 220 \, \text{m/s} \).  
- Row 5: \( T = 328.075 \, \text{K} \), \( p = 0.191 \, \text{bar} \), isentropic process.  

The airspeed at the inlet is noted as \( w_{\text{air}} = 200 \, \text{m/s} \).  

---

TASK 2b  
A graph is drawn representing a \( T \)-\( s \) diagram (temperature vs. entropy). The process is labeled with states 0, 1, 2, 3, 4, and 5.  

- State 0: Starting point at low temperature and entropy.  
- State 1: Compression process, entropy remains constant.  
- State 2: Combustion process, temperature increases significantly.  
- State 3: Expansion process, temperature decreases.  
- State 4: Mixing process, entropy increases slightly.  
- State 5: Final state at lower temperature and entropy.  

The axes are labeled:  
- \( T \) (K) for temperature.  
- \( s \, (\text{kJ}/\text{kg·K}) \) for entropy.  

---

TASK 2c  
The following calculations are shown:  

1. Determination of \( T_c \) and \( T_s \):  
\[
T_c = \frac{p_2}{p_0} \cdot T_s = 328.075 \, \text{K}
\]

2. Velocity calculations:  
\[
w_c = v_6 = 437.427 \, \text{m/s}
\]
\[
v_s = \frac{R T_s}{p_s} = 0.00248 \, \text{m/s}
\]

3. Thermodynamic constants:  
\[
R = c_p - c_v = 0.2874
\]
\[
\kappa = \frac{c_p}{c_v} = 0.719
\]

4. Specific volume:  
\[
v_g = \frac{R T_c}{p_6} = 0.0049 \, \text{kg/m}^3
\]  

Several crossed-out calculations are ignored.  

---

Description of Figures  
The graph visually represents the thermodynamic processes in the jet engine, including compression, combustion, expansion, and mixing. States are clearly labeled, and the entropy changes are depicted qualitatively.  

