TASK 4a  
The handwritten page includes a table and multiple diagrams related to Task 4, which concerns the freeze-drying process with the R134a cycle.

### Table Description:
The table lists four states of the R134a cycle with corresponding values for \( p \) (pressure in bar), \( x \) (vapor quality), and notes about the processes at each state:
1. \( p = 1 \, \text{bar}, x = \text{C} \): Heat \( \dot{Q}_K \) is removed at \( T_i \).  
2. \( p = 1 \, \text{bar}, x = 1 \): Isentropic compression occurs.  
3. \( p = 8 \, \text{bar}, x = \text{V} \): \( \dot{W}_K = 28 \, \text{kW} \).  
4. \( p = 8 \, \text{bar}, x = 0 \): Heat \( \dot{Q}_K \) is added.

### Diagram Descriptions:
1. **First Diagram (p-T Diagram)**:
   - The diagram shows the pressure-temperature relationship for the freeze-drying process.  
   - States 1, 2, 3, and 4 are labeled along the curve, with transitions between phases (fluid, vapor, and liquid).  
   - The triple point is marked, and the process includes decompression and phase changes.

2. **Second Diagram (p-T Diagram)**:
   - A more detailed view of the freeze-drying process, showing phase regions (fluid, vapor, and liquid).  
   - States 1, 2, 3, and 4 are labeled, with arrows indicating transitions between states.  
   - The triple point is labeled, and decompression is noted.

TASK 4b  
The process transitions between states are described:
- From state 2 to state 3: Isentropic compression occurs (\( s = \text{constant} \)).  
- From state 2 to state 3: The refrigerant is gaseous, transitioning to a mixture of liquid and vapor.  
- From state 4 to state 1: Isenthalpic throttling occurs.

### First Law of Thermodynamics:
The energy balance for the cycle is given as:  
\[
Q = \dot{m}(h_2 - h_3) - \dot{W}_K
\]  
Where \( h_2 \) and \( h_3 \) are specific enthalpies at states 2 and 3, respectively, and \( \dot{W}_K \) is the work input to the compressor.