TASK 2a  
The first diagram is a qualitative representation of the jet engine process on a temperature-entropy (\( T \)-\( S \)) diagram. It includes labeled isobars and key states:  
- State 1: Initial compression.  
- State 2: Adiabatic compression.  
- State 3: Isobaric heat addition.  
- State 4: Expansion in the turbine.  
- State 5: Mixing chamber.  
- State 6: Nozzle exit.  

The axes are labeled as follows:  
- \( T \) (temperature in Kelvin) on the vertical axis.  
- \( S \) (entropy in \( \frac{\text{kJ}}{\text{kg·K}} \)) on the horizontal axis.  

TASK 2a (additional diagram)  
The second diagram is another representation of the jet engine process, showing the temperature (\( T \)) versus entropy (\( S \)) curve. It includes arrows indicating mass flow rates (\( \dot{m}_K \) and \( \dot{m}_M \)) at various states. States 1 through 5 are labeled along the curve, with the axes similarly labeled as \( T \) (Kelvin) and \( S \) (\( \frac{\text{kJ}}{\text{kg·K}} \)).  

TASK 2b  
The following equations and calculations are provided:  
1. The mass flow rate equation:  
\[
\dot{m}_{\text{gas}} = \rho \cdot A \cdot w
\]  
where \( \rho = \frac{1}{v} \) (density is the inverse of specific volume).  

2. Energy balance equation:  
\[
0 = \dot{m}_{\text{gas}} \left( \frac{w_6^2 - w_0^2}{2} \right) - W_t
\]  
where \( W_t = \psi \int_{p_1}^{p_2} v \, dp \).  

3. Known values:  
\[
w_6 = 220 \, \frac{\text{m}}{\text{s}}
\]  
\[
w_a = w_6 = 500 \, \frac{\text{m}}{\text{s}}
\]  
\[
T_6 = 340 \, \text{K}
\]  

No further explanation or calculations are provided beyond these equations and values.