TASK 2a

The page contains a diagram and mathematical derivations related to thermodynamic processes. Below is the transcription:

---

**Diagram Description:**
The diagram is a qualitative representation of a thermodynamic process on a \( T \)-\( s \) (temperature-entropy) diagram. It includes:
- Several curves and arrows indicating the progression of the process.
- Labeled points corresponding to different states (e.g., \( 1 \), \( 2 \), \( 5 \)).
- Isobars and entropy changes are marked, with arrows showing transitions between states.
- A vertical green line indicates a specific entropy difference.

---

**Mathematical Derivations:**

1. **Entropy Relation:**
   \[
   s_5 = s_6
   \]

2. **Energy Balance for Reversible Adiabatic Process:**
   \[
   h_5 - h_6 = \frac{w_6^2}{2} - \frac{w_5^2}{2}
   \]

3. **Velocity Relation:**
   \[
   w_6 = \sqrt{w_5^2 + 2(h_5 - h_6)}
   \]

4. **Flow Exergy Change:**
   \[
   \Delta ex_{\text{flow}} = \left( \frac{w_6^2}{2} - \frac{w_0^2}{2} \right) + (h_6 - h_0) - T_0(s_6 - s_0)
   \]

5. **Exergy Destruction:**
   \[
   ex_{\text{dest}} = ex_{\text{in}} - ex_{\text{out}}
   \]

6. **Specific Work and Exergy Relation:**
   \[
   W_{\text{specific}} = (+) W_m - ex_{\text{out}} + ex_{\text{in}}
   \]

7. **Additional Relations:**
   \[
   h_6 = h_5 - \frac{w_6^2}{2}
   \]
   \[
   s_6 = s_5
   \]

8. **Mass Flow Rate Calculation:**
   \[
   \dot{m} = \frac{w}{T} \cdot \Delta s
   \]

---

**Notes:**
- The derivations include entropy, enthalpy, and velocity relationships, as well as exergy calculations.
- The equations are consistent with the jet engine exergy problem described in Task 2.
- Some parts of the derivations are partially obscured or unclear but appear to follow standard thermodynamic principles.

