TASK 2a  
The page begins with diagrams illustrating thermodynamic processes in a jet engine system.  

**Description of diagrams:**  
1. The first diagram is a temperature-entropy (\( T \)-\( s \)) plot showing labeled states \( 1 \), \( 2 \), \( 3 \), and \( 4 \). The process paths include isobaric and adiabatic transitions. The arrow directions indicate the flow of the process, with \( s_{\text{mix}} \) and \( s_{\text{bypass}} \) labeled along the entropy axis.  
2. The second diagram is another \( T \)-\( s \) plot with states \( 1 \), \( 2 \), \( 3 \), \( 4 \), and \( 5 \) labeled. The process includes an adiabatic compression and expansion, as well as isobaric heat addition. The isobars are marked, and the flow direction is indicated with arrows.  
3. The third diagram is a detailed \( T \)-\( s \) plot with states \( 0 \), \( 1 \), \( 2 \), \( 3 \), \( 4 \), and \( 5 \) labeled. The isobars \( p_0 \), \( p_1 \), \( p_2 \), \( p_3 \), and \( p_4 \) are shown, and the entropy axis is labeled \( s_{\text{mix}} \).  

Below the diagrams, the energy balance for the nozzle is derived:  
\[
\text{Energy balance for the nozzle: } \quad 0 = \dot{m}_{\text{gas}} \left( h_5 - h_6 + \frac{w_5^2 - w_6^2}{2} \right) = 0
\]
\[
h_6 - h_5 = \frac{w_5^2 - w_6^2}{2}
\]

The text explains that the nozzle is modeled as a throttling process with no work done (\( \text{Dose} = \text{Drossel Keine Arbeit} \)).  

**Isentropic adiabatic reversible process:**  
The temperature ratio is calculated using the isentropic relation:  
\[
\frac{T_6}{T_5} = \left( \frac{p_0}{p_5} \right)^{\frac{\kappa - 1}{\kappa}} \quad \text{where } \kappa = 1.4
\]
\[
T_6 = T_5 \cdot \left( \frac{p_0}{p_5} \right)^{\frac{\kappa - 1}{\kappa}} = 431.9 \, \text{K} \cdot \left( \frac{0.191}{0.5} \right)^{0.4/1.4} = 328.1 \, \text{K}
\]

**Ideal gas enthalpy change:**  
The enthalpy difference is calculated using the specific heat capacity:  
\[
h_6 - h_5 = c_p \cdot \left( T_6 - T_5 \right)
\]
\[
h_6 - h_5 = 1.006 \, \text{kJ/kg·K} \cdot \left( 328.1 \, \text{K} - 431.9 \, \text{K} \right) = -104.145 \, \text{kJ/kg}
\]

The final enthalpy difference is noted as \( -104.145 \, \text{kJ/kg} \).  

No further content is visible on the page.