TASK 4a  
Two diagrams are drawn.  

1. The first diagram is a pressure-volume (\(P\)-\(v\)) graph showing a cycle with labeled states. The cycle includes compression, expansion, and heat transfer processes. The states are marked as 1, 2, and 3, with arrows indicating the direction of the cycle.  
2. The second diagram is an enthalpy-pressure (\(h\)-\(P\)) graph showing the refrigerant cycle. States 1, 2, and 3 are labeled, and the processes include isobaric heat transfer and adiabatic compression.  

TASK 4b  
The energy balance for the compressor and the system is described.  

The work per unit mass flow rate is expressed as:  
\[
\frac{\dot{W}_k}{\dot{m}} = w_k = \int v \, dp
\]  
This leads to:  
\[
w_k = \frac{\dot{W}_k}{\dot{m}}
\]  

Temperature relationships are partially written but crossed out. The energy balance equation is given as:  
\[
\Delta U = q - W
\]  

TASK 4c  
The vapor quality \(x_1\) directly after the expansion (drossel) is calculated.  

The temperature after expansion is given as:  
\[
T_1 = T_i - 6 \, \text{K}
\]  

The process from state 4 to state 1 is described as adiabatic.  

The vapor quality \(x_1\) is calculated using the formula:  
\[
x = \frac{s_A - s_{if}}{s_g - s_{if}}
\]  

A small diagram is drawn showing a pressure-temperature (\(P\)-\(T\)) graph with a phase region. The state after expansion is marked within the phase region.  

Additional notes are written at the bottom:  
\[
\frac{q}{\dot{m}} = 0 \quad \frac{T_m - T_c}{T_m} = 5 \, \text{cm}
\]  
\[
\frac{q}{\dot{m}} = \frac{k}{T_m}
\]  

Descriptions of the diagrams and equations are partially crossed out but remain legible.