TASK 2a  
The task involves drawing the process qualitatively in a \( T \)-\( s \) diagram with labeled isobars and units on the axes.  

The diagram shows a temperature (\( T \)) versus entropy (\( s \)) plot. The process begins at \( T_0 \) and progresses through various states labeled 1, 2, 3, 4, 5, and 6. The following features are visible:  
- State 1 to 2 is marked as "isentropic compression."  
- State 2 to 3 is labeled "isobaric heat addition."  
- State 3 to 4 is marked as "isentropic expansion."  
- State 4 to 5 is labeled "mixing."  
- State 5 to 6 is marked as "isentropic expansion."  
- The isobars \( p_2 = p_3 \) and \( p_0 \) are clearly labeled.  

The axes are labeled as follows:  
- The vertical axis is \( T \) (temperature in Kelvin).  
- The horizontal axis is \( s \) (entropy in \( \text{kJ}/\text{kg·K} \)).  

TASK 2b  
A table is provided with temperature (\( T \)) and pressure (\( p \)) values for different states:  
\[
\begin{array}{|c|c|c|}
\hline
\text{State} & T \, [\text{K}] & p \, [\text{bar}] \\
\hline
1 & 223.15 & 0.191 \\
2 & \text{(crossed out)} & \text{(crossed out)} \\
3 & 120 & \text{(not provided)} \\
4 & \text{(not provided)} & \text{(not provided)} \\
5 & 431.9 & 0.5 \\
6 & 314.48 & 0.191 \\
\hline
\end{array}
\]

Additional constants are noted:  
\[
c_p = 1.006 \, \text{kJ}/\text{kg·K}, \quad \kappa = 1.4
\]  

No further explanation or calculations are visible.  

TASK 2a Diagram Description  
The \( T \)-\( s \) diagram visually represents the thermodynamic processes in the jet engine cycle. Each state is connected by curves or lines corresponding to the described processes (e.g., isentropic compression, isobaric heat addition). The isobars are shown as horizontal lines, and the entropy increases or remains constant depending on the process.