TASK 2a  
The page contains mathematical derivations and a graph related to thermodynamic processes. Below is the transcription:

### Mathematical Derivations:
1. The heat flow equation is written as:
   \[
   \frac{S_u}{S_{u0}} = \frac{2}{\left(\frac{S_u}{S_{u0}}\right) + (4.8 \cdot 10^{-3} - 4.8 \cdot 10^{-3}) \cdot \frac{900 \cdot r - 2}{r \cdot \text{(200)}}}
   \]

2. Another equation is derived:
   \[
   S_m + (S_4 - S_u) \cdot D_2 = S_m
   \]

3. Rearranged terms:
   \[
   S_m + (S_4 - S_u) \cdot Z = S_m
   \]

4. Further simplifications:
   \[
   \frac{S_m \cdot u}{Z} = \frac{S_m \cdot u}{Z} + (S_4 - S_u) \cdot u
   \]

5. Final form:
   \[
   \left(\frac{Z}{S_m - S_m}\right) \cdot u + (S_4 - S_u) \cdot u = 0
   \]

6. A constant value is noted:
   \[
   X \cdot 0.8280 = X \cdot 0.8280
   \]

7. Another equation:
   \[
   \frac{0.9050}{0.9050} = \frac{X}{X}
   \]

8. A ratio is calculated:
   \[
   \frac{S_1 \cdot u}{v - u} = 9
   \]

### Graph Description:
The graph at the bottom of the page appears to be a qualitative representation of a thermodynamic process in a \( T \)-\( S \) diagram (temperature vs. entropy). The following details are visible:
- The graph includes multiple curved lines labeled with entropy values (\( S_d \)).
- Points are marked along the curves, labeled as \( S_d \), \( S_4 \), \( S_5 \), \( S_6 \), and \( S_7 \).
- A dip in the curve is labeled "depression."
- The axes are labeled:
  - Horizontal axis: \( S \) (entropy).
  - Vertical axis: \( T \) (temperature).

The graph visually represents the entropy changes and temperature variations during a thermodynamic process, possibly related to a jet engine or refrigeration cycle.

TASK 2a ends here.