TASK 2a  
The page contains diagrams and annotations related to the jet engine process described in Task 2.  

### Diagram Description:  
1. **T-s Diagram**:  
   - The diagram is a temperature-entropy (\( T \)-\( s \)) plot illustrating the thermodynamic processes in the jet engine.  
   - The axes are labeled as follows:  
     - \( T \) (\( ^\circ \text{C} \)) on the vertical axis (temperature).  
     - \( s \) (\( \text{kJ/kg·K} \)) on the horizontal axis (specific entropy).  
   - Key points and processes are labeled:  
     - Point \( 0 \): Ambient conditions (\( p_0 = 0.197 \, \text{bar} \), \( T_0 = -30^\circ \text{C} \)).  
     - Compression from \( 0 \) to \( 1 \): Isentropic compression.  
     - Point \( 2 \): High-pressure state after compression.  
     - Combustion chamber from \( 2 \) to \( 3 \): Isobaric heat addition.  
     - Turbine from \( 3 \) to \( 4 \): Adiabatic expansion.  
     - Mixing chamber from \( 4 \) to \( 5 \): Mixing of bypass and core streams.  
     - Point \( 6 \): Nozzle exit conditions (\( p_6 = p_0 \)).  

2. **Process Labels**:  
   - "Vorverdichter" (pre-compressor) is marked near point \( 0 \).  
   - "Verdichter" (compressor) is labeled between \( 0 \) and \( 2 \).  
   - "Brennkammer" (combustion chamber) is labeled between \( 2 \) and \( 3 \).  
   - "Turbine" is labeled between \( 3 \) and \( 4 \).  
   - "Mischkammer" (mixing chamber) is labeled near point \( 5 \).  
   - "Schubdüse" (nozzle) is labeled near point \( 6 \).  

3. **Annotations**:  
   - The processes are described as:  
     - "Isentrop" (isentropic) for compression and expansion.  
     - "Isobar" (isobaric) for combustion.  
     - "Adiabatisch" (adiabatic) for turbine operation.  

### Additional Notes:  
- The diagram visually represents the thermodynamic cycle of the jet engine, with clear transitions between states and processes.  
- The annotations provide clarity on the nature of each process (isentropic, isobaric, adiabatic).  

No additional textual explanations or calculations are visible on the page.