TASK 2a  
A temperature-entropy (\(T\)-\(s\)) diagram is drawn. The diagram shows a qualitative representation of the jet engine process. The following points are labeled:  
- Point 1: Initial state.  
- Point 2: Compression process.  
- Point 3: Combustion process.  
- Point 4: Expansion process in the turbine.  
- Point 5: Mixing chamber state.  
- Point 6: Nozzle exit state.  

The diagram includes curved lines representing isobars, with labels such as \(0.5 \, \text{bar}\) and \(0.191 \, \text{bar}\). The arrows indicate the direction of the thermodynamic processes. The axes are labeled as \(T \, [\text{K}]\) for temperature and \(s \, [\text{kJ/kg·K}]\) for entropy.

---

TASK 2c  
The equation for the mass-specific increase in flow exergy is written as:  
\[
\Delta ex_{\text{flow}} = \dot{m} \cdot (h_6 - h_0 - T_0 \cdot (s_6 - s_0)) + \Delta KE
\]  
where \(h_6\) and \(h_0\) are specific enthalpies, \(T_0\) is the ambient temperature, \(s_6\) and \(s_0\) are specific entropies, and \(\Delta KE\) represents the change in kinetic energy.

---

TASK 2d  
The equation for mass-specific exergy destruction is written as:  
\[
0 = \dot{m} \cdot (h_6 - h_0 - T_0 \cdot (s_6 - s_0)) + \Delta KE + \dot{Q}_B \cdot \left(1 - \frac{T_0}{\bar{T}_B}\right) - \dot{W}_{\text{comp}}
\]  
where \(\dot{Q}_B\) is the heat input during combustion, \(\bar{T}_B\) is the average temperature during combustion, and \(\dot{W}_{\text{comp}}\) is the work done by the compressor.

The final value for exergy destruction is calculated as:  
\[
\text{Exergy destruction} = 100 \, \text{kJ}
\]  

Additional notes mention "Grüne Linie" (green line) and "Laufzeit Verdicht" (compression duration), possibly referring to annotations or process details.