TASK 2a  
A qualitative \( T \)-\( s \) diagram is drawn to represent the jet engine process. The diagram includes labeled isobars and key states (1 through 6).  
- State 1: Start of the process, marked as "isentrope."  
- State 2: Transition to an isobar.  
- State 3: Compression phase, labeled as "isobar."  
- State 4: Combustion phase, labeled as "isobar."  
- State 5: Mixing chamber, labeled as "isobar."  
- State 6: Nozzle exit, labeled as "isentrope."  

The axes are labeled:  
- \( T \) (temperature) on the vertical axis.  
- \( s \) (specific entropy, \( \text{kJ/kg·K} \)) on the horizontal axis.  

TASK 2b  
The equation for the outlet velocity \( w_6 \) is derived using the energy balance:  
\[
w_6 = \sqrt{w_5^2 + 2(h_5 - h_6)}
\]  
where \( h_5 \) and \( h_6 \) are the specific enthalpies at states 5 and 6, respectively.  

The molar mass \( M_L \) is given as:  
\[
M_L = 28.07 \, \text{g/mol}
\]  

The specific entropy at state 6 is equal to the specific entropy at state 5:  
\[
s_6 = s_5
\]  

Using the ideal gas relation and isentropic assumptions:  
\[
s_6 - s_5 = c_p \ln \left( \frac{T_6}{T_5} \right) - \frac{R}{M_L} \ln \left( \frac{p_6}{p_5} \right)
\]  

From the pressure ratio:  
\[
\frac{T_6}{T_5} = \left( \frac{p_6}{p_5} \right)^{\frac{\kappa - 1}{\kappa}}
\]  
where \( \kappa \) is the specific heat ratio.  

The temperature at state 6 is calculated as:  
\[
T_6 = 328.07 \, \text{K}
\]  

The outlet velocity \( w_6 \) is determined as:  
\[
w_6 = 507.24 \, \text{m/s}
\]  

TASK 2c  
The mass-specific increase in flow exergy \( \Delta ex_{\text{flow}} \) is calculated using the following equation:  
\[
\Delta ex_{\text{flow}} = m_{\text{gas}} \left[ h_6 - h_0 - T_0 (s_6 - s_0) + \frac{w_6^2}{2} - \frac{w_0^2}{2} \right]
\]  

Additional assumptions:  
- The process is adiabatic, reversible, and isentropic.  
- \( w_5 = 0 \), \( Q = 0 \).  

No further numerical values are provided for \( \Delta ex_{\text{flow}} \).  

TASK 2  
A table is provided with the following values:  
- \( p_0 = 0.191 \, \text{bar} \)  
- \( p_5 = 0.5 \, \text{bar} \)  
- \( T_0 = -30^\circ\text{C} \)  
- \( T_5 = 431.9 \, \text{K} \)  
- \( T_6 = 328.07 \, \text{K} \)  
- \( s_5 = s_6 \)  

No additional calculations or explanations are visible for this table.  

TASK 2c  
The entropy production \( s_6 - s_5 \) is noted as zero under isentropic conditions.  

No further content is visible.