TASK 2a  
The diagram provided is a qualitative temperature-entropy (\(T\)-\(s\)) diagram for the jet engine process. It shows the thermodynamic states labeled as 0, 1, 2, 3, 4, and 5, with arrows indicating the direction of the process flow.  

- **State 0 to State 1:** The process is labeled as "isentrop," indicating an isentropic compression.  
- **State 1 to State 2:** The process is labeled as "isobar p2=p3," indicating an isobaric heat addition.  
- **State 2 to State 3:** The process is labeled as "isobar p3=p2," indicating another isobaric process.  
- **State 3 to State 4:** The process involves expansion, likely in a turbine.  
- **State 4 to State 5:** The process is labeled as "isobar p0=p5," indicating an isobaric mixing or cooling process.  

The smaller diagram to the right is a simplified \(T\)-\(s\) representation, showing the key states and transitions in a compact form.  

Below the diagram is a table labeled "Zustandstabelle" (State Table), which lists the properties of the thermodynamic states. The columns include:  
- **Zustand (State):** The states are numbered as 1, 2, 3, 4, 5, 6, and 0.  
- **\(p\) [bar]:** Pressure values are partially filled. For example, \(p_5 = 0.5 \, \text{bar}\), \(p_0 = 0.191 \, \text{bar}\).  
- **\(T\) [K]:** Temperature values are partially filled. For example, \(T_5 = 431.9 \, \text{K}\), \(T_0 = 243.15 \, \text{K}\).  
- **\(\dot{m}\) [kg/s]:** Mass flow rates are not provided.  
- **\(s\):** Specific entropy values are partially filled, with \(s_1 = s_0\).  
- **\(h\):** Specific enthalpy values are not provided.  
- **\(w\) [m/s]:** Velocity values are partially filled. For example, \(w_5 = 220 \, \text{m/s}\), \(w_0 = 200 \, \text{m/s}\).  

This table summarizes the thermodynamic properties at each state in the jet engine process.