TASK 2a  
The table lists various states of the jet engine process with corresponding values for pressure (\( p \)), temperature (\( T \)), and entropy (\( s \)).  

- State 0:  
  \( p = 0.191 \, \text{bar} \), \( T = -30^\circ\text{C} \), \( s \) is not provided.  

- State 1:  
  \( p \) and \( T \) are the same as state 0, \( s \) is not provided.  

- State 2:  
  \( p \) and \( T \) are the same as state 1, \( s \) is not provided.  

- State 3:  
  \( p \) and \( T \) are not provided, \( s \) is not provided.  

- State 4:  
  \( p \) and \( T \) are not provided, \( s \) is not provided.  

- State 5:  
  \( p = 0.5 \, \text{bar} \), \( T = 431.9 \, \text{K} \), \( s \) is not provided.  

- State 6:  
  \( p = 0.191 \, \text{bar} \), \( T = 2340 \, \text{K} \), \( s \) is not provided.  

Additional notes:  
- At state 0, the airspeed is \( w_{\text{air}} = 200 \, \text{m/s} \).  
- At state 5, the outlet velocity is \( w_5 = 220 \, \text{m/s} \).  

---

TASK 2b  
The graph is a \( T \)-\( s \) diagram illustrating the thermodynamic process of the jet engine.  

- The vertical axis represents temperature (\( T \)) in \( ^\circ\text{C} \), ranging from \( -30^\circ\text{C} \) to approximately \( 67^\circ\text{C} \).  
- The horizontal axis represents entropy (\( s \)) in unspecified units.  

Key features of the graph:  
1. State 0 is marked at the bottom left, corresponding to ambient conditions (\( T = -30^\circ\text{C} \), \( p = 0.191 \, \text{bar} \)).  
2. State 1 is labeled near state 0, indicating the mixing process.  
3. State 2 is slightly higher on the graph, showing an increase in temperature.  
4. State 3 is marked further up, representing the compression process (isentropic).  
5. State 5 is labeled near the top right, corresponding to the mixing chamber conditions (\( T = 431.9 \, \text{K} \), \( p = 0.5 \, \text{bar} \)).  
6. State 6 is marked at the far right, showing the nozzle exit conditions (\( T = 2340 \, \text{K} \), \( p = 0.191 \, \text{bar} \)).  

Arrows indicate the direction of the process flow, with labels such as "isentropic" for the compression process and "p = 0.191" for the nozzle exit.