TASK 4a  
A pressure-temperature (\(p\)-\(T\)) diagram is drawn, showing the freeze-drying process. The diagram includes the following features:  
- A curved line representing the phase boundary between liquid and vapor.  
- A straight diagonal line labeled "i" and "ii," indicating the two steps of the freeze-drying process.  
- The triple point is marked on the diagram.  
- The axes are labeled as \(p\) [bar] on the vertical axis and \(T\) [K] on the horizontal axis.  

TASK 4b  
A table is provided with values for temperature (\(T\)), pressure (\(p\)), entropy (\(s\)), and enthalpy (\(h\)) for different states (1, 2, 3, and 4). Some values are crossed out, but the following are visible:  
- \(T_1 = 0^\circ\text{C} + 10 \, \text{K} = 10^\circ\text{C}\)  
- \(T_{\text{reduced}} = T_2 = 10^\circ\text{C} - 6 \, \text{K} = 4^\circ\text{C}\)  
- \(s_2 = s_g(4^\circ\text{C}) = 0.9165 \, \text{kJ/kg·K}\) (from Table A-10)  
- \(T_3 = \frac{31.33 + 4}{2} = 37.1^\circ\text{C}\)  
- \(s_3 = (0.9374 - 0.9165) \, \text{kJ/kg·K}\)  

TASK 4c  
The first law of thermodynamics is applied to states 2 and 3:  
\[
0 = \dot{m}_{\text{R134a}} \cdot (h_2 - h_3) - \dot{W}_K  
\]
The enthalpy at state 2 is given as:  
\[
h_2 = h_g(10^\circ\text{C}) = 249.53 \, \text{kJ/kg}  
\]  
The enthalpy at state 3 (\(h_3\)) is not fully calculated on the page.  

No further calculations or results are visible for this subtask.  

TASK 4d  
No explicit calculations or results for the coefficient of performance (\(\epsilon_K\)) are visible on the page.  

TASK 4e  
No content related to the evolution of \(T_i\) in Step ii is visible on the page.  

Descriptions of diagrams and partial calculations are provided, but some values are incomplete or crossed out.