TASK 2a  
The diagram represents a qualitative \( T \)-\( s \) diagram for the jet engine process. The axes are labeled as follows:  
- \( T \) (temperature) on the vertical axis.  
- \( s \) (specific entropy, in \( \text{kJ}/\text{kg·K} \)) on the horizontal axis.  

The process is divided into the following stages:  
1. **Isentropic compression**: The curve from state 1 to state 2 is vertical, indicating constant entropy.  
2. **Isobaric heat addition**: The curve from state 2 to state 3 is horizontal, indicating constant pressure.  
3. **Adiabatic, irreversible turbine**: The curve from state 3 to state 4 slopes downward, indicating entropy increase.  
4. **Isobaric mixing chamber**: The curve from state 4 to state 5 is horizontal, indicating constant pressure.  
5. **Isentropic nozzle expansion**: The curve from state 5 to state 6 is vertical, indicating constant entropy.  

Dashed lines labeled "Dome" indicate phase boundaries.  

---

TASK 2b  
The first law of thermodynamics (1HS) is applied to the nozzle:  
\[
\dot{m} \left( h_5 - h_6 + \frac{w_5^2 - w_6^2}{2} \right) = 0
\]  
Neglecting potential energy and assuming adiabatic conditions, the equation simplifies to:  
\[
\dot{m} \frac{w_5^2}{2} + \dot{m} h_5 = \dot{m} \frac{w_6^2}{2} + \dot{m} h_6
\]  

Rearranging for \( w_6 \):  
\[
w_6 = \sqrt{w_5^2 + 2(h_5 - h_6)}
\]  

From Table A-22, \( h_5 \) and \( h_6 \) are interpolated:  
\[
h_5 = 431.43 \, \text{kJ/kg}, \quad h_6 = 421.26 \, \text{kJ/kg}
\]  
Interpolating further:  
\[
h_s = 431.43 - 421.26 + (431.9 - 430) + 421.26 = 421.44 \, \text{kJ/kg}
\]  

The temperature \( T_6 \) is calculated using the isentropic relation:  
\[
T_6 = T_c \left( \frac{p_6}{p_s} \right)^{\frac{n-1}{n}}
\]  
Where:  
\[
n = \frac{c_p}{c_v} = \frac{1.006 \, \text{kJ/kg·K}}{c_p - R}, \quad \text{given } n = 1.4
\]  

Further calculations are required to determine \( T_6 \).  

No diagrams are provided for this subtask.