TASK 2a  
The task begins with a T-s diagram representing the thermodynamic processes of a jet engine. The diagram is labeled with entropy \( s \) (in \( \text{kJ/kg} \)) on the x-axis and temperature \( T \) (in \( \text{K} \)) on the y-axis. The diagram includes five states connected by various processes:  
- \( 1 \to 2 \): Adiabatic, reversible compression.  
- \( 2 \to 3 \): Isobaric heat addition.  
- \( 3 \to 4 \): Adiabatic, irreversible expansion.  
- \( 4 \to 5 \): Isobaric mixing chamber.  
- \( 5 \to 6 \): Reversible adiabatic nozzle.  

The processes are labeled as follows:  
- \( 1 \to 2 \): Adiabatic reversible compression.  
- \( 2 \to 3 \): Isobaric heat transfer.  
- \( 3 \to 4 \): Adiabatic irreversible expansion.  
- \( 4 \to 5 \): Isobaric mixing chamber.  
- \( 5 \to 6 \): Reversible adiabatic nozzle.  

---

TASK 2b  
The outlet temperature \( T_6 \) and velocity \( w_6 \) are calculated using the following equations:  

1. The temperature \( T_6 \) is determined using the isentropic relation:  
\[
T_6 = T_5 \left( \frac{p_0}{p_5} \right)^{\frac{\kappa - 1}{\kappa}}
\]  
Substituting values:  
\[
T_6 = 431.9 \, \text{K} \left( \frac{0.191}{0.5} \right)^{\frac{1.4 - 1}{1.4}} = 328.07 \, \text{K}
\]

2. The velocity \( w_6 \) is calculated using the energy balance:  
\[
2c_V(T_6 - T_0) = w_0^2 - w_6^2
\]  
Rearranging for \( w_6^2 \):  
\[
w_6^2 = w_0^2 + 2c_V(T_0 - T_6)
\]  
Substituting values:  
\[
c_V = \frac{c_p}{\kappa} = \frac{1.006}{1.4} = 0.7186 \, \text{kJ/kg·K}
\]  
\[
w_6 = \sqrt{200^2 + 2 \cdot 0.7186 \cdot (243.15 - 328.07)} = 199.85 \, \text{m/s}
\]

---

TASK 2c  
The mass-specific increase in flow exergy \( \Delta ex_{\text{flow}} \) is calculated as:  
\[
\Delta ex_{\text{flow}} = ex_{\text{flow},6} - ex_{\text{flow},0}
\]  
Using the detailed equation:  
\[
ex_{\text{flow}} = h_6 - h_0 - T_0(S_6 - S_0) + \frac{w_6^2 - w_0^2}{2}
\]  
Substituting terms:  
\[
ex_{\text{flow}} = c_p(T_6 - T_0) - T_0 \left[ \ln\left(\frac{T_6}{T_0}\right) - R \ln\left(\frac{p_6}{p_0}\right) \right] + \frac{w_6^2 - w_0^2}{2}
\]  
Numerical calculation yields:  
\[
\Delta ex_{\text{flow}} = 110.4 \, \text{kJ/kg}
\]