TASK 2a  
The ambient temperature is given as \( T_0 = 263.15 \, \text{K} \), and the ambient pressure is \( p_0 = 0.191 \, \text{bar} \). The mass flow ratio is \( \dot{m}_M / \dot{m}_K = 5.293 \). The specific heat capacity of air is \( c_p = 1.006 \, \text{kJ/kg·K} \), and the adiabatic index is \( \kappa = 1.4 \).

Two diagrams are drawn:  
1. **T-s Diagram**:  
   - The diagram shows temperature \( T \) (in Kelvin) on the vertical axis and entropy \( s \) (in \( \text{kJ/kg·K} \)) on the horizontal axis.  
   - States 1 through 6 are labeled, with arrows indicating transitions between states.  
   - Isobars are drawn, representing constant pressure lines. The ambient pressure \( p_0 \) and another pressure \( 0.5 \, \text{bar} \) are marked.  
   - The process includes compression (state 1 to state 3), combustion (state 3 to state 4), turbine expansion (state 4 to state 5), and mixing (state 5 to state 6).  

2. **Zoomed T-s Diagram**:  
   - A more detailed view of the same process, emphasizing the transitions between states 3, 4, 5, and 6.  
   - The isobar at \( 0.5 \, \text{bar} \) is highlighted.  

TASK 2b  
The temperature at state \( T_B \) is calculated using the formula:  
\[
T_B = T_5 \left( \frac{p_0}{p_5} \right)^{\frac{\kappa - 1}{\kappa}}
\]  
Substituting values:  
\[
T_B = 431.9 \, \text{K} \left( \frac{0.191}{0.5} \right)^{\frac{1.4 - 1}{1.4}} = 328.07 \, \text{K}
\]

TASK 2c  
The outlet velocity \( w_6 \) is determined using the energy balance:  
\[
w_6 = \sqrt{\frac{w_5^2}{2} - (h_6 - h_5)}
\]  
Substituting values:  
\[
w_6 = \sqrt{\frac{507.25^2}{2} - c_p \Delta T}
\]  
where \( h_6 - h_5 = c_p \Delta T \).

TASK 2d  
The general energy balance equation is written as:  
\[
\frac{dE}{dt} = \dot{m}_{\text{gas}} (h_5 - h_6) + \frac{w_5^2}{2} - \frac{w_6^2}{2} + \dot{Q} - \dot{X}
\]  
This equation accounts for changes in enthalpy, kinetic energy, heat transfer, and exergy destruction.  

No additional content is visible on the page.