TASK 2a  
A graph is drawn representing a qualitative \( T \)-\( s \) diagram. The x-axis is labeled \( s \, [\text{kJ/kg·K}] \), and the y-axis is labeled \( T \, [\text{K}] \). The diagram includes several curves and points:  
- Points \( 0 \), \( 1 \), \( 2 \), \( 3 \), \( 4 \), \( 5 \), and \( 6 \) are marked.  
- The curves represent isobars, with labels \( p_0 \), \( p_5 = p_4 \), \( p_3 = p_7 \), and \( p_2 = p_3 \).  
- The process lines are drawn in magenta, connecting the points in sequence.  
- A note on the right states: "Blau Kurve nicht beachten!" ("Do not consider the blue curve!")  

TASK 2b  
The outlet velocity \( w_6 \) and temperature \( T_6 \) are calculated.  

The following equations and steps are provided:  
1. The pressure at state 6 is equal to ambient pressure:  
   \[
   p_6 = p_0 = 0.191 \, \text{bar}
   \]  

2. The steady-state energy balance is written:  
   \[
   \frac{dE}{dt} = 0 = \dot{m} \left[ h_6 - h_5 + \frac{w_6^2}{2} - \frac{w_5^2}{2} \right]
   \]  

3. The enthalpy difference \( h_5 - h_6 \) is calculated using:  
   \[
   h_5 - h_6 = c_p \cdot (T_5 - T_6)
   \]  
   \[
   T_6 = T_5 \left( \frac{p_6}{p_5} \right)^{\frac{\kappa - 1}{\kappa}}
   \]  

4. Substituting values:  
   \[
   T_6 = 431.9 \, \text{K} \cdot \left( \frac{0.191}{0.5} \right)^{\frac{0.4}{1.4}} = 328.07 \, \text{K}
   \]  

5. The enthalpy difference is determined:  
   \[
   h_5 - h_6 = 1.006 \, \text{kJ/kg·K} \cdot (431.9 - 328.07) = 104.46 \, \text{kJ/kg}
   \]  

6. Kinetic energy difference is calculated:  
   \[
   k_{e6} - k_{e5} = \frac{1}{2} \left( w_6^2 - w_5^2 \right)
   \]  

7. \( w_6 \) is determined, but the value is crossed out and unclear.  

TASK 2c  
The mass-specific increase in flow exergy \( \Delta ex_{\text{flow}} \) is calculated.  

The following equations are provided:  
1. Flow exergy difference:  
   \[
   \Delta ex_{\text{flow}} = ex_{\text{flow},6} - ex_{\text{flow},0}
   \]  

2. Substituting the expression for flow exergy:  
   \[
   \Delta ex_{\text{flow}} = h_6 - h_0 - T_0 (s_6 - s_0) + k_{e6} - k_{e0}
   \]  

3. Kinetic energy at state 6:  
   \[
   k_{e6} = \frac{1}{2} w_6^2
   \]  

No further numerical results are provided.  

No additional content is visible.