TASK 3d  
The entropy change \( x_{\text{ice},2} \) is calculated using the energy balance for the ice-water mixture (EW).  

The energy balance equation for the EW system is written as:  
\[
\frac{dE}{dt} = \sum \dot{m}_i \left( h_i + \frac{v_i^2}{2} + g z_i \right) + \sum Q_i - \sum W_i
\]  

Assumptions:  
- The system is isolated.  
- Heat transfer \( Q \) occurs between the gas and EW.  
- The process is isothermal for the EW.  

The energy balance simplifies to:  
\[
m_{\text{EW}} \cdot (u_2 - u_1) = Q_{12}
\]  

The internal energy \( u_2 \) is expressed as:  
\[
u_2 = \frac{Q_{12}}{m_{\text{EW}}} + u_1
\]  

The internal energy \( u_1 \) is calculated as:  
\[
u_1 = u_{\text{f,ref}} + x_{\text{EW}} \cdot (u_{\text{ice}} - u_{\text{ref}})
\]  

Here, \( p_{\text{EW}} = p_0 + p_{\text{cyl}} \), where \( p_{\text{cyl}} \) is the pressure exerted by the piston.  

Substituting values:  
\[
u_1 = -333.476 \, \text{kJ/kg} + 0.6 \cdot (-333.458 - (-333.476)) = -333.4102 \, \text{kJ/kg}
\]  

The internal energy \( u_2 \) is then calculated as:  
\[
u_2 = \frac{1500 \, \text{J}}{0.1 \, \text{kg}} + (-333.4102 \, \text{kJ/kg}) = -318.410 \, \text{kJ/kg}
\]  

The ice fraction \( x_{\text{ice},2} \) is determined using:  
\[
x_{\text{ice},2} = \frac{u_2 - u_{\text{f,ref}}}{u_{\text{ice}} - u_{\text{f,ref}}}
\]  

Substituting values:  
\[
x_{\text{ice},2} = \frac{-318.410 - (-333.476)}{-333.458 - (-333.476)} = 0.65
\]  

This indicates that part of the ice in the EW has melted.  

---

TASK 3e  
The energy balance for the gas system is expressed as:  
\[
\Delta E = Q - W
\]  

The work \( W \) is calculated using the integral:  
\[
W = \int p \, dV
\]  

For an ideal gas, \( p \) is expressed as:  
\[
p = \frac{nRT}{V}
\]  

Substituting into the integral:  
\[
W = \int \frac{nRT}{V} \, dV
\]  

Key observations:  
- \( T_{g,2} = 0^\circ\text{C} \).  
- \( p_{g,2} \) is never in equilibrium with \( p_{\text{amb}} \) due to the molecular arrangement of the gas.  
- \( T_{g,2} \) is less than \( T_{\text{amb}} \).  

The gas pressure \( p_{g,2} \) and temperature \( T_{g,2} \) are influenced by the heat transfer process and the final equilibrium state.