TASK 4a  
The page contains two diagrams related to the freeze-drying process in a \( p \)-\( T \) diagram.

---

**First Diagram Description:**  
The first diagram is a \( p \)-\( T \) plot with the pressure \( p \) on the vertical axis (labeled in bar) and temperature \( T \) on the horizontal axis (labeled in Kelvin). The diagram shows a phase curve separating different regions:  
- On the left side of the curve, the region is labeled "unterkühlte Flüssigkeit" (subcooled liquid).  
- On the right side of the curve, the region is labeled "überhitzter Dampf" (superheated vapor).  
- The area under the curve is labeled "Nassdampf" (wet vapor).  

Two points are marked on the diagram:  
- Point 1 is located on the right side of the curve, in the superheated vapor region.  
- Point 2 is located on the left side of the curve, in the subcooled liquid region.  

The curve represents the phase boundary between liquid and vapor phases.

---

**Second Diagram Description:**  
The second diagram is also a \( p \)-\( T \) plot with pressure \( p \) on the vertical axis (labeled in bar) and temperature \( T \) on the horizontal axis (labeled in Celsius). The diagram features a similar phase curve, with two points marked:  
- Point 1 is located near the peak of the curve.  
- Point 2 is slightly to the left of Point 1, also near the peak.  

The horizontal axis includes labels \( T_i \) and \( T_i - 6 \, \text{K} \), indicating temperature values relevant to the freeze-drying process.  

This diagram visually represents the freeze-drying process steps, including the isobaric evaporation and temperature differences.