TASK 2a  
The page contains a graph and a table related to thermodynamic processes, likely corresponding to Task 2 (Jet Engine Exergy). Below is the transcription and description:

---

**Graph Description:**  
The graph is a qualitative \( T \)-\( s \) diagram showing thermodynamic processes. It includes three distinct curves representing isobars (constant pressure lines). Key points are labeled as follows:  
- \( 0 \): Initial state  
- \( 1 \): Compression process  
- \( 2 \): Combustion process  
- \( 3 \): Expansion process  
- \( 4 \): Mixing process  
- \( 5 \): Final state after mixing  

Vertical lines connect points \( 0 \) to \( 1 \), \( 2 \) to \( 3 \), and \( 4 \) to \( 5 \), indicating transitions between states. The curves are annotated with approximate temperature values:  
- \( 1097 \, \text{K} \)  
- \( 1450 \, \text{K} \)  

The graph visually represents the thermodynamic cycle of the jet engine, with entropy (\( s \)) increasing along the horizontal axis and temperature (\( T \)) increasing along the vertical axis.

---

**Table Description:**  
The table contains numerical data for various states in the thermodynamic process. Columns are labeled as follows:  
- \( \dot{m} \): Mass flow rate  
- \( V \): Specific volume  
- \( T \): Temperature  
- \( p \): Pressure  

Rows correspond to states \( 0 \) through \( 5 \), with values provided for each parameter. Some entries include:  
- \( \dot{m} = 0.175 \, \text{kg/s} \)  
- \( V = 0.02225 \, \text{m}^3/\text{kg} \)  
- \( T = 1450 \, \text{K} \)  
- \( p = 0.5 \, \text{bar} \)  

The table summarizes the thermodynamic properties at each state in the jet engine cycle.

---

No additional textual explanation is visible on the page.  

